### 2024-06-20 Simulation1.Rmd
A first serious commit

---
title: "Simulation"
output: pdf_document
date: "2024-06-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
```

```{r}
trees <- read_excel("~/work/Sim_article2024/artificial_forest_round.xls")
```

```{r}
# First visualisation
plot(x = trees$x, y = trees$y, main = "Forest")
```

```{r}
# True values
cat("Il y a au total", length(trees$x), "arbres et un volume total de", sum(trees$v), "\n", "Soit un volume moyen de", mean(trees$v), "\n", "Le diamètre moyen à hauteur de poitrine est de", mean(trees$d130))
```

```{r}
plot(x = trees$x, y = trees$y, main = "Forest", panel.first=grid())

```

```{r}
# Create another variable to indicate in which cell is each tree
for (i in vec){

}
```

```{r}
list <- sample(1:10)
```

```{r}
n <- 600 # dimension of a cell = 1 unit x 1 unit
vec <- c() # vector containing coordinates of cells
for (j in 0:9){ # for each number (1 to 10)
  for (i in 0:((n/10)-1)){ # translation
    vec <- append(vec, 200+j+10*i)
  }
}
```

```{r}
trees$cell2 <- 1*as.numeric((trees$x %in% seq(200, 300, by = .01)) & (trees$y %in% seq(200, 300, by = .01))) # Problem with 107th tree e.g.
trees$cell <- 1*as.numeric((200 <= trees$x) & (trees$x < 300) & (200 <= trees$y) & (trees$y < 300))
# trees[trees$cell == 1 & trees$cell2 == 0,]
# Where is the pb?
# 297.21 %in% seq(233, 300, by = .01) # FALSE, idem for numbers below 233
# 297.21 %in% seq(234, 300, by = .01) # TRUE, idem for numbers above 234
```

```{r}
for(l in vec){

}
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

### 2024-06-20 Tests.R

@@ -1,0 +1,26 @@
+### Premier essai avec ChatGPT -----
+
+# Générer la séquence
+sequence <- seq(200, 300, by = .01)
+
+# Tester l'appartenance
+is_in_sequence <- 297.21 %in% sequence
+
+# Afficher le résultat
+print(is_in_sequence)
+
+### Second essai avec ChatGPT -----
+
+# Générer la séquence
+sequence <- seq(234, 300, by = .01)
+
+# Tester l'appartenance
+is_in_sequence <- 297.21 %in% sequence
+
+# Afficher le résultat
+print(is_in_sequence) # TRUE with 234, FALSE with 233
+
+# Afficher une partie de la séquence autour de 297.21 pour vérifier la présence
+nearby_values <- sequence[which(abs(sequence - 297.21) < .001)]
+print(nearby_values) # Dans tous les cas, affiche 297.21
+

### 2024-06-20 Simulation1.Rmd
Not yet done

@@
 ```{r}
-for(l in vec){
+trees$cell3 <- rep(0, 30942)
+for (ligne in 1:60){
+
+  for(l in 1:60){
+    trees$cell3 <- ifelse(
+    (vec[l] <= trees$x) & (trees$x < vec[l]+1) & (vec[1] <= trees$y) & (trees$y < vec[1]+1), 
+    list[1], trees$cell3)
+  }
 
 }
+
+```
+
+```{r}
+trees$cell3 <- rep(0, 30942)
+trees$cell3 <- ifelse(
+  (vec[1] <= trees$x) & (trees$x < vec[1]+1) & (vec[1] <= trees$y) & (trees$y < vec[1]+1), 
+  1, trees$cell3)
+```
+
+```{r}
+trees$cell3 <- ifelse(
+  (200 <= trees$x) & (trees$x < 300) & (200 <= trees$y) & (trees$y < 300), 
+  1, trees$cell3)
 ```
@@
 ```
+
+```{r}
+
+```
+
+```{r}
+
+```
+
+```{r}
+
+```
+
+```{r}
+
+```

### 2024-06-21 Simulation1.Rmd
Some progress, 4 resistants

@@
 ```{r}
-library(readxl)
+library(readxl) # to read the initial file
+library(data.table) # for shift
 ```
@@
 ```
+
+# First approach
 
@@
 
+# Creating cells
+
 ```{r}
@@
 ```{r}
+# Randomizing the positions of the numbers used to identify cells
 list <- sample(1:10)
+```
+
+```{r}
+# Shift considered to add randomization
+trend <- as.numeric(sample(1:10, 1))
 ```
@@
 ```{r}
-trees$cell2 <- 1*as.numeric((trees$x %in% seq(200, 300, by = .01)) & (trees$y %in% seq(200, 300, by = .01))) # Problem with 107th tree e.g.
-trees$cell <- 1*as.numeric((200 <= trees$x) & (trees$x < 300) & (200 <= trees$y) & (trees$y < 300))
+rm(i, j) # Useless outside loops
+```
+
+```{r}
+# Tests (preliminaries)
+
+# trees$cell2 <- 1*as.numeric((trees$x %in% seq(200, 300, by = .01)) & (trees$y %in% seq(200, 300, by = .01))) # Problem with 107th tree e.g.
+# trees$cell <- 1*as.numeric((200 <= trees$x) & (trees$x < 300) & (200 <= trees$y) & (trees$y < 300))
+
 # trees[trees$cell == 1 & trees$cell2 == 0,]
@@
 ```{r}
+# Un peu long
+
+# PROBLEME: ne garde que le 8 (i.e. le dernier nb)
+
+trees$cell <- rep(0, 30942) # Initialisation de la variable
+
+for (nb in 1:10){ # All the categories (to identify the cells)
+for (ligne in 0:599){ # All the lines (en parcourant par rapport aux ordonnées)
+  for(c in 1:60){ # En parcourant sur une même ligne
+    # if (trees$cell == 0)
+    trees$cell <- ifelse(
+    # (trees$cell == 0) & 
+      (vec[(nb-1)*60 + 1] <= trees$x) & (trees$x < vec[(nb-1)*60 + 1]+1) & (200+ligne <= trees$y) & (trees$y < 200+ligne+1), 
+    list[nb], trees$cell)
+  }
+
+}
+}
+```
+
+(ligne-1)*trend + 
+(ligne-1)*trend +
+
+```{r}
+# Un peu long
+
+# PROBLEME: ne garde que le 8 (i.e. le dernier nb)
+
+trees$cell <- rep(0, 30942) # Initialisation de la variable
+
+for (ligne in 0:599){ # All the lines (en parcourant par rapport aux ordonnées)
+  # for(c in 1:60){ # En parcourant sur une même ligne
+    for (nb in 1:10){ # All the categories (to identify the cells)
+    # if (trees$cell == 0)
+    trees$cell <- ifelse(
+    # (trees$cell == 0) & 
+      (vec[(nb-1)*60 + 1] <= trees$x) & (trees$x < vec[(nb-1)*60 + 1]+1) & (200+ligne <= trees$y) & (trees$y < 200+ligne+1), 
+    list[nb], trees$cell)
+  }
+
+# }
+}
+```
+
+```{r}
+unique(trees$cell)
+```
+
+```{r}
+trees$cell3 <- rep(0, 30942)
+trees$cell3 <- ifelse(
+  (vec[1] <= trees$x) & (trees$x < vec[1]+1) & (vec[1] <= trees$y) & (trees$y < vec[1]+1), 
+  1, trees$cell3)
+```
+
+```{r}
+# Inaccurate cell
+trees$cell3 <- ifelse(
+  (200 <= trees$x) & (trees$x < 300) & (200 <= trees$y) & (trees$y < 300), 
+  1, trees$cell3)
+```
+
+```{r}
+# Invalid
 trees$cell3 <- rep(0, 30942)
@@
 }
+```
+
+```{r}
+# When only focusing on 1 10th of the population
+plot(x = trees[trees$cell3 == 9,]$x, y = trees[trees$cell3 == 9,]$y, main = "Forest", panel.first=grid())
+# Pretty nice
+```
+
+```{r}
+# Test
+
+trees$cell3 <- rep(0, 30942)
+nb = 1
+ligne = 0
+
+for(c in 1:60){ # En parcourant sur une même ligne
+    # if (trees$cell == 0)
+    trees$cell <- ifelse(
+    (vec[(c-1)*trend + (nb-1) + 1] <= trees$x) & (trees$x < vec[(c-1)*trend + nb]+1) & (200+ligne <= trees$y) & (trees$y < 200+ligne+1) & trees$cell, 
+    list[nb], trees$cell)
+  }
+```
+
+```{r}
+# When only focusing on 1 10th of the population
+plot(x = trees[trees$cell == 1,]$x, y = trees[trees$cell == 1,]$y, main = "Forest", panel.first=grid())
+```
+
+```{r}
+# When only focusing on 
+plot(x = trees[trees$cell == 9,]$x, y = trees[trees$cell == 9,]$y, main = "Forest", panel.first=grid())
+```
+
+```{r}
+# When only focusing on 
+plot(x = trees[trees$cell == 0,]$x, y = trees[trees$cell == 0,]$y, main = "Forest", panel.first=grid())
+```
+
+```{r}
 
@@
 
+# Sampling one point and "creating a circle around"
+
 ```{r}
-trees$cell3 <- rep(0, 30942)
-trees$cell3 <- ifelse(
-  (vec[1] <= trees$x) & (trees$x < vec[1]+1) & (vec[1] <= trees$y) & (trees$y < vec[1]+1), 
-  1, trees$cell3)
+a <- runif(1, 200, 800)
+b <- runif(1, 200, 800)
 ```
@@
 ```{r}
-trees$cell3 <- ifelse(
-  (200 <= trees$x) & (trees$x < 300) & (200 <= trees$y) & (trees$y < 300), 
-  1, trees$cell3)
+# Function to check if a point is inside the circle
+is_point_in_circle <- function(x, y, h, k, R) {
+  # Calculate the squared distance between the point and the circle's center
+  squared_distance <- (x - h)^2 + (y - k)^2
+  # Check if the squared distance is less than or equal to the squared radius
+  return(squared_distance <= R^2)
+}
+
+trees$Is_in_circle <- is_point_in_circle(a, b, trees$x, trees$y, 5)
+```
+
+```{r}
+# The sample thus obtained
+trees[trees$Is_in_circle == TRUE,]
+```
+
+```{r}
+# When considering only one circle
+total_trees <- nrow(trees[trees$Is_in_circle == TRUE,])
+total_d130 <- sum(trees[trees$Is_in_circle == TRUE,]$d130)
+```
+
+```{r}
+
+```
+
+## 1st step
+One line, one number, no shift yet
+```{r}
+for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
+    trees$cell <- ifelse(
+    (vec[k] <= trees$x) & (trees$x < vec[k]+1) & (200 <= trees$y) & (trees$y < 200+1), 
+    list[1], trees$cell)
+}
+```
+
+## 2nd step
+All the lines, still one number
+
+```{r}
+list_stable <- list
+```
+
+```{r}
+for (l in 1:599) {
+  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
+    trees$cell <- ifelse(
+    (vec[k] <= trees$x) & (trees$x < vec[k]+1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
+    # list[1 + trend*(l-1)], 
+    list_stable[1],
+    trees$cell)
+  }
+  list <- shift(list, n = trend, type = "cyclic") # shift for each line
+}
+```
+
+```{r}
+# When only focusing on 1 10th of the population
+plot(x = trees[trees$cell == 4,]$x, y = trees[trees$cell == 4,]$y, main = "Echantillonnage", panel.first=grid())
+```
+
+## 3rd step
+The same thing as before but with all possible identifiers (from 1 to 10).
+```{r}
+for (nb in 1:10) {
+  list <- list_stable
+  for (l in 1:599) {
+  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
+    trees$cell <- ifelse(
+    (vec[k + (nb-1)*60] <= trees$x) & (trees$x < vec[k + (nb-1)*60] + 1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
+    list_stable[nb],
+    trees$cell)
+  }
+  list <- shift(list, n = trend, type = "cyclic") # shift for each line
+}
+}
+```
+
+```{r}
+# When only focusing on 1 10th of the population
+plot(x = trees[trees$cell == 4,]$x, y = trees[trees$cell == 4,]$y, main = "Echantillonnage", panel.first=grid())
+```
+
+```{r}
+# When only focusing on 1 10th of the population
+plot(x = trees[trees$cell == 9,]$x, y = trees[trees$cell == 9,]$y, main = "Echantillonnage", panel.first=grid())
+```
+
+```{r}
+# When only focusing on the null values
+plot(x = trees[trees$cell == 0,]$x, y = trees[trees$cell == 0,]$y, main = "Echantillonnage", panel.first=grid())
+```
+
+```{r}
+trees[trees$cell == 0,]
+```
+
+```{r}
+trees[(trees$cell != 0) & (trees$y >= 799),] # vide
+# Problème d'arrondi pour les y
 ```
@@
 ```
-
-```{r}
-
-```
-
-```{r}
-
-```
-
-```{r}
-
-```
-
-```{r}
-
-```
-
-```{r}
-
-```
-
-```{r}
-
-```

### 2024-06-21 Test_square.R

@@ -1,0 +1,21 @@
+# Load necessary library
+library(ggplot2)
+
+# Define the size of the square space
+space_size <- 10
+
+# Define the size of the smaller squares
+square_size <- 1
+
+# Create a data frame to store the coordinates of the squares
+squares <- data.frame(
+  x = rep(seq(0, space_size - square_size, by = square_size), each = space_size / square_size),
+  y = rep(seq(0, space_size - square_size, by = square_size), times = space_size / square_size)
+)
+
+# Plot the tessellation
+ggplot() +
+  geom_tile(data = squares, aes(x = x, y = y), width = square_size, height = square_size, fill = "lightblue", color = "black") +
+  coord_fixed() +
+  theme_minimal() +
+  labs(title = "Square Tessellation", x = "X", y = "Y")

### 2024-06-21 Simulation1.Rmd
Friday evening

@@
 
-```{r}
-# Create another variable to indicate in which cell is each tree
-for (i in vec){
-
-}
-```
+We need to create another variable to indicate in which cell is each tree
 
@@
 ```
+
+## 1st step (1 for loop)
+One line, one number, no shift yet
+```{r}
+for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
+    trees$cell <- ifelse(
+    (vec[k] <= trees$x) & (trees$x < vec[k]+1) & (200 <= trees$y) & (trees$y < 200+1), 
+    list[1], trees$cell)
+}
+```
+
+## 2nd step (2 for loops)
+All the lines, still one number
+
+```{r}
+list_stable <- list
+```
+
+```{r}
+for (l in 1:599) {
+  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
+    trees$cell <- ifelse(
+    (vec[k] <= trees$x) & (trees$x < vec[k]+1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
+    # list[1 + trend*(l-1)], 
+    list_stable[1],
+    trees$cell)
+  }
+  list <- shift(list, n = trend, type = "cyclic") # shift for each line
+}
+```
+
+```{r}
+# When only focusing on 1 10th of the population
+plot(x = trees[trees$cell == 4,]$x, y = trees[trees$cell == 4,]$y, main = "Echantillonnage", panel.first=grid())
+```
+
+## 3rd step (3 for loops)
+The same thing as before but with all possible identifiers (from 1 to 10).
+```{r}
+for (nb in 1:10) {
+  list <- list_stable
+  for (l in 1:599) {
+  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
+    trees$cell <- ifelse(
+    (vec[k + (nb-1)*60] <= trees$x) & (trees$x < vec[k + (nb-1)*60] + 1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
+    list_stable[nb],
+    trees$cell)
+  }
+  list <- shift(list, n = trend, type = "cyclic") # shift for each line
+}
+}
+```
+
+```{r}
+# When only focusing on 1 10th of the population
+plot(x = trees[trees$cell == 4,]$x, y = trees[trees$cell == 4,]$y, main = "Echantillonnage", panel.first=grid())
+```
+
+```{r}
+# When only focusing on 1 10th of the population
+plot(x = trees[trees$cell == 9,]$x, y = trees[trees$cell == 9,]$y, main = "Echantillonnage", panel.first=grid())
+```
+
+```{r}
+# When only focusing on the null values
+plot(x = trees[trees$cell == 0,]$x, y = trees[trees$cell == 0,]$y, main = "Echantillonnage", panel.first=grid())
+```
+
+```{r}
+trees[trees$cell == 0,] # 4 trees that do not fill in any cell
+# Common characteristic: y is very high
+```
+
+```{r}
+trees[(trees$cell != 0) & (trees$y >= 799),] # vide
+# Problème d'arrondi pour les y
+```
+
+## Draft
 
@@
 }
+
+# (ligne-1)*trend + 
+# (ligne-1)*trend + 
 ```
-
-(ligne-1)*trend + 
-(ligne-1)*trend +
 
@@
 plot(x = trees[trees$cell3 == 9,]$x, y = trees[trees$cell3 == 9,]$y, main = "Forest", panel.first=grid())
-# Pretty nice
+# Pretty nice (at one point)
 ```
@@
 
-```{r}
-
-```
-
 # Sampling one point and "creating a circle around"
@@
 
-```{r}
+## One point at random in each cell with a given identifier
 
-```
-
-## 1st step
-One line, one number, no shift yet
-```{r}
-for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
-    trees$cell <- ifelse(
-    (vec[k] <= trees$x) & (trees$x < vec[k]+1) & (200 <= trees$y) & (trees$y < 200+1), 
-    list[1], trees$cell)
-}
-```
-
-## 2nd step
-All the lines, still one number
+Second stage of first phase
 
 ```{r}
-list_stable <- list
+random_points <- data.frame(x = numeric(), y = numeric())
 ```
@@
 ```{r}
+
+a <- runif(1, vec[1], vec[1] + 1)
+b <- runif(1, vec[1], vec[1] + 1)
+```
+
+```{r}
+nb <- sample(1:10, 1)
+```
+
+```{r}
+list <- list_stable
 for (l in 1:599) {
   for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
-    trees$cell <- ifelse(
-    (vec[k] <= trees$x) & (trees$x < vec[k]+1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
-    # list[1 + trend*(l-1)], 
-    list_stable[1],
-    trees$cell)
+    a <- runif(1, vec[k + (nb-1)*60], vec[k + (nb-1)*60] + 1)
+    b <- runif(1, 200 + (l-1), 200+l)
+    random_points <- rbind(random_points, list(a,b))
+    # trees$cell <- ifelse(
+    # (vec[] <= trees$x) & (trees$x < vec[k + (nb-1)*60] + 1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
+    # list_stable[nb],
+    # trees$cell)
   }
@@
 }
+
+# NB: 35 940 points are randomly selected if nb = 5
+# 71 880 points are randomly selected if nb = 8, idem with 10
+# whereas we should have exactly 36 000 cells of each type
+
+# PROBLEM
+# N'importe quoi, ne prend pas en compte le shift
 ```
@@
 ```{r}
-# When only focusing on 1 10th of the population
-plot(x = trees[trees$cell == 4,]$x, y = trees[trees$cell == 4,]$y, main = "Echantillonnage", panel.first=grid())
-```
-
-## 3rd step
-The same thing as before but with all possible identifiers (from 1 to 10).
-```{r}
-for (nb in 1:10) {
-  list <- list_stable
-  for (l in 1:599) {
-  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
-    trees$cell <- ifelse(
-    (vec[k + (nb-1)*60] <= trees$x) & (trees$x < vec[k + (nb-1)*60] + 1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
-    list_stable[nb],
-    trees$cell)
-  }
-  list <- shift(list, n = trend, type = "cyclic") # shift for each line
-}
-}
+colnames(random_points) <- list("x", "y")
 ```
@@
 ```{r}
-# When only focusing on 1 10th of the population
-plot(x = trees[trees$cell == 4,]$x, y = trees[trees$cell == 4,]$y, main = "Echantillonnage", panel.first=grid())
+plot(x = random_points$x, y = random_points$y, main = "Random points", panel.first=grid())
 ```
@@
 ```{r}
-# When only focusing on 1 10th of the population
-plot(x = trees[trees$cell == 9,]$x, y = trees[trees$cell == 9,]$y, main = "Echantillonnage", panel.first=grid())
+plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 220), ylim = c(200, 300))
+# Pas du tout random quand nb = 10
 ```
@@
 ```{r}
-# When only focusing on the null values
-plot(x = trees[trees$cell == 0,]$x, y = trees[trees$cell == 0,]$y, main = "Echantillonnage", panel.first=grid())
-```
+for (r in row) {
 
-```{r}
-trees[trees$cell == 0,]
-```
-
-```{r}
-trees[(trees$cell != 0) & (trees$y >= 799),] # vide
-# Problème d'arrondi pour les y
+}
 ```
@@
 ```
+
+```{r}
+
+```
+
+```{r}
+
+```
+
+```{r}
+
+```
+
+```{r}
+
+```
+
+```{r}
+
+```

### 2024-06-24 Draft.Rmd
Excluding some draft

--- 2024-06-20 Simulation1.Rmd
@@
 ---
-title: "Simulation"
-output: pdf_document
-date: "2024-06-20"
+title: "Draft"
+output: html_document
+date: "2024-06-24"
 ---
@@
 
-```{r}
-library(readxl)
-```
+## Draft
 
 ```{r}
-trees <- read_excel("~/work/Sim_article2024/artificial_forest_round.xls")
-```
+# Tests (preliminaries)
 
-```{r}
-# First visualisation
-plot(x = trees$x, y = trees$y, main = "Forest")
-```
+# trees$cell2 <- 1*as.numeric((trees$x %in% seq(200, 300, by = .01)) & (trees$y %in% seq(200, 300, by = .01))) # Problem with 107th tree e.g.
+# trees$cell <- 1*as.numeric((200 <= trees$x) & (trees$x < 300) & (200 <= trees$y) & (trees$y < 300))
 
-```{r}
-# True values
-cat("Il y a au total", length(trees$x), "arbres et un volume total de", sum(trees$v), "\n", "Soit un volume moyen de", mean(trees$v), "\n", "Le diamètre moyen à hauteur de poitrine est de", mean(trees$d130))
-```
-
-```{r}
-plot(x = trees$x, y = trees$y, main = "Forest", panel.first=grid())
-
-```
-
-```{r}
-# Create another variable to indicate in which cell is each tree
-for (i in vec){
-
-}
-```
-
-```{r}
-list <- sample(1:10)
-```
-
-```{r}
-n <- 600 # dimension of a cell = 1 unit x 1 unit
-vec <- c() # vector containing coordinates of cells
-for (j in 0:9){ # for each number (1 to 10)
-  for (i in 0:((n/10)-1)){ # translation
-    vec <- append(vec, 200+j+10*i)
-  }
-}
-```
-
-```{r}
-trees$cell2 <- 1*as.numeric((trees$x %in% seq(200, 300, by = .01)) & (trees$y %in% seq(200, 300, by = .01))) # Problem with 107th tree e.g.
-trees$cell <- 1*as.numeric((200 <= trees$x) & (trees$x < 300) & (200 <= trees$y) & (trees$y < 300))
 # trees[trees$cell == 1 & trees$cell2 == 0,]
@@
 ```{r}
+# Un peu long
+
+# PROBLEME: ne garde que le 8 (i.e. le dernier nb)
+
+trees$cell <- rep(0, 30942) # Initialisation de la variable
+
+for (nb in 1:10){ # All the categories (to identify the cells)
+for (ligne in 0:599){ # All the lines (en parcourant par rapport aux ordonnées)
+  for(c in 1:60){ # En parcourant sur une même ligne
+    # if (trees$cell == 0)
+    trees$cell <- ifelse(
+    # (trees$cell == 0) & 
+      (vec[(nb-1)*60 + 1] <= trees$x) & (trees$x < vec[(nb-1)*60 + 1]+1) & (200+ligne <= trees$y) & (trees$y < 200+ligne+1), 
+    list[nb], trees$cell)
+  }
+
+}
+}
+
+# (ligne-1)*trend + 
+# (ligne-1)*trend + 
+```
+
+```{r}
+# Un peu long
+
+# PROBLEME: ne garde que le 8 (i.e. le dernier nb)
+
+trees$cell <- rep(0, 30942) # Initialisation de la variable
+
+for (ligne in 0:599){ # All the lines (en parcourant par rapport aux ordonnées)
+  # for(c in 1:60){ # En parcourant sur une même ligne
+    for (nb in 1:10){ # All the categories (to identify the cells)
+    # if (trees$cell == 0)
+    trees$cell <- ifelse(
+    # (trees$cell == 0) & 
+      (vec[(nb-1)*60 + 1] <= trees$x) & (trees$x < vec[(nb-1)*60 + 1]+1) & (200+ligne <= trees$y) & (trees$y < 200+ligne+1), 
+    list[nb], trees$cell)
+  }
+
+# }
+}
+```
+
+```{r}
+unique(trees$cell)
+```
+
+```{r}
+trees$cell3 <- rep(0, 30942)
+trees$cell3 <- ifelse(
+  (vec[1] <= trees$x) & (trees$x < vec[1]+1) & (vec[1] <= trees$y) & (trees$y < vec[1]+1), 
+  1, trees$cell3)
+```
+
+```{r}
+# Inaccurate cell
+trees$cell3 <- ifelse(
+  (200 <= trees$x) & (trees$x < 300) & (200 <= trees$y) & (trees$y < 300), 
+  1, trees$cell3)
+```
+
+```{r}
+# Invalid
 trees$cell3 <- rep(0, 30942)
@@
 }
-
 ```
@@
 ```{r}
-trees$cell3 <- rep(0, 30942)
-trees$cell3 <- ifelse(
-  (vec[1] <= trees$x) & (trees$x < vec[1]+1) & (vec[1] <= trees$y) & (trees$y < vec[1]+1), 
-  1, trees$cell3)
+# When only focusing on 1 10th of the population
+plot(x = trees[trees$cell3 == 9,]$x, y = trees[trees$cell3 == 9,]$y, main = "Forest", panel.first=grid())
+# Pretty nice (at one point)
 ```
@@
 ```{r}
-trees$cell3 <- ifelse(
-  (200 <= trees$x) & (trees$x < 300) & (200 <= trees$y) & (trees$y < 300), 
-  1, trees$cell3)
+# Test
+
+trees$cell3 <- rep(0, 30942)
+nb = 1
+ligne = 0
+
+for(c in 1:60){ # En parcourant sur une même ligne
+    # if (trees$cell == 0)
+    trees$cell <- ifelse(
+    (vec[(c-1)*trend + (nb-1) + 1] <= trees$x) & (trees$x < vec[(c-1)*trend + nb]+1) & (200+ligne <= trees$y) & (trees$y < 200+ligne+1) & trees$cell, 
+    list[nb], trees$cell)
+  }
 ```
@@
 ```{r}
-
+# When only focusing on 1 10th of the population
+plot(x = trees[trees$cell == 1,]$x, y = trees[trees$cell == 1,]$y, main = "Forest", panel.first=grid())
 ```
@@
 ```{r}
-
+# When only focusing on 
+plot(x = trees[trees$cell == 9,]$x, y = trees[trees$cell == 9,]$y, main = "Forest", panel.first=grid())
 ```
@@
 ```{r}
-
+# When only focusing on 
+plot(x = trees[trees$cell == 0,]$x, y = trees[trees$cell == 0,]$y, main = "Forest", panel.first=grid())
 ```
-
-```{r}
-
-```
-
-```{r}
-
-```
-
-```{r}
-
-```
-
-```{r}
-
-```
-
-```{r}
-
-```

### 2024-06-24 Simulation1.Rmd
Excluding some draft

--- 2024-06-20 Simulation1.Rmd
@@
 plot(x = trees$x, y = trees$y, main = "Forest", panel.first=grid())
+```
 
+# Creating cells
+
+We need to create another variable to indicate in which cell is each tree
+
+```{r}
+# Randomizing the positions of the numbers used to identify cells
+list <- sample(1:10)
 ```
@@
 ```{r}
-# Create another variable to indicate in which cell is each tree
-for (i in vec){
-
-}
-```
-
-```{r}
-list <- sample(1:10)
+# Shift considered to add randomization
+trend <- as.numeric(sample(1:10, 1))
 ```
@@
 ```{r}
-trees$cell2 <- 1*as.numeric((trees$x %in% seq(200, 300, by = .01)) & (trees$y %in% seq(200, 300, by = .01))) # Problem with 107th tree e.g.
-trees$cell <- 1*as.numeric((200 <= trees$x) & (trees$x < 300) & (200 <= trees$y) & (trees$y < 300))
-# trees[trees$cell == 1 & trees$cell2 == 0,]
-# Where is the pb?
-# 297.21 %in% seq(233, 300, by = .01) # FALSE, idem for numbers below 233
-# 297.21 %in% seq(234, 300, by = .01) # TRUE, idem for numbers above 234
+rm(i, j, n) # Useless outside loops
 ```
@@
 ```{r}
-trees$cell3 <- rep(0, 30942)
-for (ligne in 1:60){
+trees$cell <- rep(0, 30942) # Initialisation de la variable
+```
 
-  for(l in 1:60){
-    trees$cell3 <- ifelse(
-    (vec[l] <= trees$x) & (trees$x < vec[l]+1) & (vec[1] <= trees$y) & (trees$y < vec[1]+1), 
-    list[1], trees$cell3)
+## 1st step (1 for loop)
+One line, one number, no shift yet
+```{r}
+for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
+    trees$cell <- ifelse(
+    (vec[k] <= trees$x) & (trees$x < vec[k]+1) & (200 <= trees$y) & (trees$y < 200+1), 
+    list[1], trees$cell)
+}
+```
+
+## 2nd step (2 for loops)
+All the lines, still one number
+
+```{r}
+list_stable <- list
+```
+
+```{r}
+vec_test <- c()
+```
+
+```{r}
+for (l in 1:599) {
+  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
+    vec_test <- append(vec_test, (k + (l-1)*60 -1)%%600 + 1)
+    # if ((k + (l-1)*60 -1)%%600 + 1 <= 0){
+    #   cat((k + (l-1)*60 -1)%%600 + 1, "k=", k, "; l=", l)
+    # }
+    trees$cell <- ifelse(
+    (vec[(k + (l-1)*60 -1)%%600 + 1] <= trees$x) & (trees$x < vec[(k + (l-1)*60 -1)%%600 + 1]+1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
+    # list[1 + trend*(l-1)], 
+    list_stable[1],
+    trees$cell)
+  }
+  # list <- shift(list, n = trend, type = "cyclic") # shift for each line
+}
+```
+
+```{r}
+# When only focusing on 1 10th of the population
+plot(x = trees[trees$cell == 5,]$x, y = trees[trees$cell == 5,]$y, main = "Echantillonnage", panel.first=grid())
+```
+
+```{r}
+# When only focusing on 1 10th of the population
+plot(x = trees[(trees$cell == 5) & (trees$x >= 300) & (trees$x < 310),]$x, y = trees[(trees$cell == 5) & (trees$x >= 300) & (trees$x < 310),]$y, main = "Echantillonnage", panel.first=grid())
+```
+
+## 3rd step (3 for loops)
+The same thing as before but with all possible identifiers (from 1 to 10).
+```{r}
+for (nb in 1:10) {
+  list <- list_stable
+  for (l in 1:599) {
+  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
+    trees$cell <- ifelse(
+    (vec[(k + (l-1)*60 -1)%%600 + 1 + (nb-1)*60] <= trees$x) & (trees$x < vec[(k + (l-1)*60 -1)%%600 + 1 + (nb-1)*60] + 1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
+    list_stable[nb],
+    trees$cell)
+  }
+  list <- shift(list, n = trend, type = "cyclic") # shift for each line
+}
+}
+```
+
+```{r}
+# When only focusing on 1 10th of the population
+plot(x = trees[trees$cell == 4,]$x, y = trees[trees$cell == 4,]$y, main = "Echantillonnage", panel.first=grid())
+```
+
+```{r}
+# When only focusing on 1 10th of the population
+plot(x = trees[trees$cell == 9,]$x, y = trees[trees$cell == 9,]$y, main = "Echantillonnage", panel.first=grid())
+```
+
+```{r}
+# When only focusing on a small part of the population
+plot(x = trees[(trees$cell == 2) & (trees$x < 350) & (trees$x >= 340),]$x, y = trees[(trees$cell == 2) & (trees$x < 350) & (trees$x >= 340),]$y, main = "Echantillonnage", panel.first=grid())
+# Les points sont compris entre 341.0 et 342.0
+```
+
+```{r}
+# When only focusing on a small part of the population
+plot(x = trees[(trees$cell == 2) & (trees$x < 350) & (trees$x >= 340) & (trees$y >= 320) & (trees$y < 380),]$x, y = trees[(trees$cell == 2) & (trees$x < 350) & (trees$x >= 340) & (trees$y >= 320) & (trees$y < 380),]$y, main = "Echantillonnage", panel.first=grid())
+# Les points sont compris entre 341.0 et 342.0
+```
+
+```{r}
+# When only focusing on the null values
+plot(x = trees[trees$cell == 0,]$x, y = trees[trees$cell == 0,]$y, main = "Echantillonnage", panel.first=grid())
+```
+
+```{r}
+trees[trees$cell == 0,] # 4 trees that do not fill in any cell
+# Common characteristic: y is very high
+```
+
+```{r}
+trees[(trees$cell != 0) & (trees$y >= 799),] # vide
+# Problème d'arrondi pour les y
+```
+
+# Sampling one point and "creating a circle around"
+
+```{r}
+a <- runif(1, 200, 800)
+b <- runif(1, 200, 800)
+```
+
+```{r}
+# Function to check if a point is inside the circle
+is_point_in_circle <- function(x, y, h, k, R) {
+  # Calculate the squared distance between the point and the center of the circle
+  squared_distance <- (x - h)^2 + (y - k)^2
+  # Check if the squared distance is less than or equal to the squared radius
+  return(squared_distance <= R^2)
 }
 
+trees$Is_in_circle <- is_point_in_circle(a, b, trees$x, trees$y, 5)
+```
+
+```{r}
+# The sample thus obtained
+trees[trees$Is_in_circle == TRUE,]
+```
+
+```{r}
+# When considering only one circle
+total_trees <- nrow(trees[trees$Is_in_circle == TRUE,])
+total_d130 <- sum(trees[trees$Is_in_circle == TRUE,]$d130)
+```
+
+## One point at random in each cell with a given identifier
+
+Second stage of first phase
+
+```{r}
+random_points <- data.frame(x = numeric(), y = numeric())
+```
+
+```{r}
+
+a <- runif(1, vec[1], vec[1] + 1)
+b <- runif(1, vec[1], vec[1] + 1)
+```
+
+```{r}
+nb <- sample(1:10, 1)
+```
+
+```{r}
+list <- list_stable
+for (l in 1:599) {
+  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
+    a <- runif(1, vec[k + (nb-1)*60], vec[k + (nb-1)*60] + 1)
+    b <- runif(1, 200 + (l-1), 200+l)
+    random_points <- rbind(random_points, list(a,b))
+    # trees$cell <- ifelse(
+    # (vec[] <= trees$x) & (trees$x < vec[k + (nb-1)*60] + 1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
+    # list_stable[nb],
+    # trees$cell)
   }
+  list <- shift(list, n = trend, type = "cyclic") # shift for each line
+}
+
+# NB: 35 940 points are randomly selected if nb = 5
+# 71 880 points are randomly selected if nb = 8, idem with 10
+# whereas we should have exactly 36 000 cells of each type
+
+# PROBLEM
+# N'importe quoi, ne prend pas en compte le shift
+```
+
+```{r}
+## A modifier 
+# (k + (l-1)*60 -1)%%600 + 1
+
+list <- list_stable
+for (l in 1:600) {
+  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
+    colnames(random_points) <- list("x", "y")
+    if (length(random_points[(random_points$x > vec[(k + (l-1)*60 -1 + (nb-1)*60)%%600 + 1])
+                             & (random_points$x < vec[(k + (l-1)*60 -1 + (nb-1)*60)%%600 + 1] + 1)
+                             & (random_points$y > 200 + (l-1))
+                             & (random_points$y < 200 + l) ]) == 0){ # Eviter les doublons dans chaque cellule
+    a <- runif(1, vec[(k + (l-1)*60 -1 + (nb-1)*60)%%600 + 1], vec[(k + (l-1)*60 -1 + (nb-1)*60)%%600 + 1] + 1)
+    b <- runif(1, 200 + (l-1), 200+l)
+    random_points <- rbind(random_points, list(a,b))
+    }
+    # trees$cell <- ifelse(
+    # (vec[] <= trees$x) & (trees$x < vec[k + (nb-1)*60] + 1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
+    # list_stable[nb],
+    # trees$cell)
+  }
+  # list <- shift(list, n = trend, type = "cyclic") # shift for each line
+}
+
+# NB: 35 940 points are randomly selected if nb = 5
+# 71 880 points are randomly selected if nb = 8, idem with 10
+# whereas we should have exactly 36 000 cells of each type
 
@@
 ```{r}
-trees$cell3 <- rep(0, 30942)
-trees$cell3 <- ifelse(
-  (vec[1] <= trees$x) & (trees$x < vec[1]+1) & (vec[1] <= trees$y) & (trees$y < vec[1]+1), 
-  1, trees$cell3)
+colnames(random_points) <- list("x", "y")
 ```
@@
 ```{r}
-trees$cell3 <- ifelse(
-  (200 <= trees$x) & (trees$x < 300) & (200 <= trees$y) & (trees$y < 300), 
-  1, trees$cell3)
+plot(x = random_points$x, y = random_points$y, main = "Random points", panel.first=grid())
+```
+
+```{r}
+plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
+# Semble régulier si nb = 2
+# Probleme : 2 fois trop de points tirés 
+```
+
+```{r}
+plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(202, 205), ylim = c(200, 205))
+# Il arrive qu'il y ait 2 points dans la même cellule...
+```
+
+```{r}
+plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
+# Semble régulier si nb = 2
+# Probleme : 10 fois trop de points
+```
+
+```{r}
+plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(202, 205), ylim = c(200, 205))
+# Un seul point par cellule
 ```
@@
 ```
-
-```{r}
-
-```

### 2024-06-24 Simulation1.Rmd
Montag Abend

@@
 ```{r}
+# Importing the database with the artificial forest
 trees <- read_excel("~/work/Sim_article2024/artificial_forest_round.xls")
@@
 ```{r}
-# First visualisation
+# First visualization
 plot(x = trees$x, y = trees$y, main = "Forest")
+# All trees have coordinates (abscissa and ordinate) between 200 and 800
 ```
@@
 # True values
-cat("Il y a au total", length(trees$x), "arbres et un volume total de", sum(trees$v), "\n", "Soit un volume moyen de", mean(trees$v), "\n", "Le diamètre moyen à hauteur de poitrine est de", mean(trees$d130))
-```
-
-```{r}
-plot(x = trees$x, y = trees$y, main = "Forest", panel.first=grid())
+cat("Il y a au total", length(trees$x), "arbres et un volume total de", sum(trees$v), "m^3 \n", "Soit un volume moyen de", mean(trees$v), "m^3 \n", "Le diamètre moyen à hauteur de poitrine est de", mean(trees$d130), "cm")
 ```
@@
 
-We need to create another variable to indicate in which cell is each tree
+We may create another variable to indicate in which cell is each tree.
 
@@
 ```{r}
-trees$cell <- rep(0, 30942) # Initialisation de la variable
+trees$cell <- rep(0, 30942) # Initialization of the variable
 ```
+
+3 steps to assign a type of cell (i.e. a number between 1 and 10) to every trees
 
@@
 All the lines, still one number
-
 ```{r}
@@
 ```{r}
-# When only focusing on 1 10th of the population
+# When only focusing on 1 10th of the population but with more precision
 plot(x = trees[(trees$cell == 5) & (trees$x >= 300) & (trees$x < 310),]$x, y = trees[(trees$cell == 5) & (trees$x >= 300) & (trees$x < 310),]$y, main = "Echantillonnage", panel.first=grid())
@@
 }
+```
 
+```{r}
 trees$Is_in_circle <- is_point_in_circle(a, b, trees$x, trees$y, 5)
@@
 ```{r}
-## A modifier 
-# (k + (l-1)*60 -1)%%600 + 1
+# It works a priori
+# l: toutes les lignes ; k: les cellules sur une ligne ; a: abscisse ; b: ordonnée
 
@@
 
-# NB: 35 940 points are randomly selected if nb = 5
-# 71 880 points are randomly selected if nb = 8, idem with 10
-# whereas we should have exactly 36 000 cells of each type
+# 36 000 points are randomly selected if nb = 5
+# Which is what we want!
 
+```
+
+```{r}
+rm(a,b,k,l) # Useless outside loops
 ```
@@
 ```{r}
-plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
+# plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
 # Semble régulier si nb = 2
@@
 ```{r}
-plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(202, 205), ylim = c(200, 205))
+# plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(202, 205), ylim = c(200, 205))
 # Il arrive qu'il y ait 2 points dans la même cellule...
@@
 # Semble régulier si nb = 2
-# Probleme : 10 fois trop de points
 ```
@@
 # Un seul point par cellule
+```
+
+# Circles around random points
+
+```{r}
+
+```
+
+```{r}
+# Adding columns to the dataframe
+# Number of trees inside each circle around each random point ; Total of diameter ; Total volume
+for (point in 1:36000) {
+  trees$Is_in_circle <- is_point_in_circle(a, b, trees$x, trees$y, 5)
+  # x, y, h, k, R
+  total_trees <- nrow(trees[trees$Is_in_circle == TRUE,])
+  total_d130 <- sum(trees[trees$Is_in_circle == TRUE,]$d130)
+}
+random_points
+```
+
+```{r}
+# Creating the local variable
+# Formule pages 10-11 de Chauvet et alii (2024)
+M_k <- function(x, y, h, k, R) {
+
+}
 ```
@@
 ```
-
-```{r}
-
-```
-
-```{r}
-
-```

### 2024-06-25 No_cell.Rmd
Martes tarde

---
title: "Uniform sampling over the all territory without any cell"
output: html_document
date: "2024-06-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("pracma") # double integral
library(readxl) # to read the initial file
library(data.table) # for shift
library(pracma)
library(magrittr)
```

# Preliminaries

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/artificial_forest_round.xls")
```

```{r}
# Sample size
n <- 100
```

```{r}
# Dataframe containing all coordinates of n randomly chosen points
random_points <- data.frame(x = rep(0, n), y = rep(0, n))
```

```{r}
# Uniform sampling over the whole territory
random_points$x <- runif(n, 0, 1000)
random_points$y <- runif(n, 0, 1000)
```

```{r}
# Marginal density: density of the uniform distribution over 1:1000
# Which leads us to the inclusion density function
pi <- sum(rep((1/1000)*(1/1000), n))
```

# With simple functions

## First function: (x,y) -> 1

```{r}
## First simple function: 1 given to each point
random_points$rho1 <- rep(1, n)
# Formula given in Cordy (1993), page 3
```

```{r}
## The most simple function
fun1 <- function(x,y){
  1
}
```

```{r}
# Value to estimate: the area of the territory
area <- 1000*1000
# integral2(fun1, 0, 1000, 0, 1000)$Q # the same
```

```{r}
# Estimated value
est_area <- sum((random_points$rho1)/pi) # Equal to 1 whatever the chosen points
```

## Second function: (x,y) -> (x/y) normalized

```{r}
# x/y given to each point
fun_ratio <- function(x,y){
  x/y
}
```

```{r}
# Normalization of the ratio
fun_norm <- function(x,y){
  (x/y)/(integral2(fun_ratio, 0, 1000, 0, 1000)$Q)
}
```

```{r}
random_points$rho2 <- fun_norm(random_points$x,random_points$y)
```

```{r}
# Value to estimate
ratio_norm <- integral2(fun_norm, 0, 1000, 0, 1000)$Q # = 1
```

```{r}
# Estimated value
est_ratio_norm <- sum((random_points$rho2)/pi)
# NOT SATISFACTORY: too low (btw 0 and 1)
```

```{r}
random_points$rho2 <- fun_ratio(random_points$x,random_points$y)
```

```{r}
# Value to estimate
ratio_norm <- integral2(fun_ratio, 0, 1000, 0, 1000)$Q # = 1
```

```{r}
# Estimated value
est_ratio <- sum((random_points$rho2)/pi)
# NOT SATISFACTORY
```

# Monte Carlo

```{r}
# Number of replications for the Monte-Carlo method
B <- 1000
```

```{r}
# Initialization with a first sample
series_MC <- data.frame(x.1 = runif(n, 0, 1000), y.1 = runif(n, 0, 1000))
col_names <- c("x1", "y1")
```

```{r}
# Making as many samples as necessary for MC
for (b in 2:B) {
  x <- paste("x", b, sep = "")
  y <- paste("y", b, sep = "")
  # Uniform sampling over the whole territory
  a1 <- runif(n, 0, 1000)
  a2 <- runif(n, 0, 1000)
  # series_MC$x <- runif(n, 0, 1000)
  # series_MC$y <- runif(n, 0, 1000)
  # append()
  series_MC <- series_MC %>% add_column(x = a1, y = a2)
  col_names <- append(col_names, c(x, y))
}
colnames(series_MC) <- col_names
```

```{r}
# Calculation of rho function for each pair (x,y)
rho_MC <- data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
col_names <- c()
```

```{r}
for (c in 1:B) {
  col_ <- paste("est", c, sep = "")
  # With normalized ratio
  a <- fun_norm(series_MC[(2*c)-1],series_MC[2*c])
  rho_MC <- rho_MC %>% add_column(col_ = a)
  col_names <- append(col_names, col_)
}
rho_MC$x.1 <- NULL
rho_MC$y.1 <- NULL
colnames(rho_MC) <- col_names
```

```{r}
# List of estimated totals thus obtained from each sample
est_MC <- c()
```

```{r}
for (c in 1:B) {
  est_tot <- sum((rho_MC[c])/pi)
  est_MC <- append(est_MC, est_tot)
}
```

```{r}
# Empirical mean based on MC
mean(est_MC) # should be close to 1
```

```{r}
# Empirical standard deviation based on MC
sd(est_MC)
```

```{r}
### Function to automate Monte Carlo method

true_vs_MC <- function(n, B, f){
  # n: sample size; B: number of iterations for MC; f: function to consider (with 2 variables, x and y)
  pi <- sum(rep((1/1000)*(1/1000), n))

  # 1st step: generating n samples
  series_MC <- data.frame(x.1 = runif(n, 0, 1000), y.1 = runif(n, 0, 1000))
  col_names <- c("x1", "y1")
  for (b in 2:B) {
    x <- paste("x", b, sep = "")
    y <- paste("y", b, sep = "")
    # Uniform sampling over the whole territory
    a1 <- runif(n, 0, 1000)
    a2 <- runif(n, 0, 1000)
    series_MC <- series_MC %>% add_column(x = a1, y = a2)
    col_names <- append(col_names, c(x, y))
  }
  colnames(series_MC) <- col_names

  # 2nd step: creating the values corresponding to the function
  rho_MC <- data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
  col_names <- c()
  for (c in 1:B) {
    col_ <- paste("est", c, sep = "")
    a <- f(series_MC[(2*c)-1],series_MC[2*c])
    rho_MC <- rho_MC %>% add_column(col_ = a)
    col_names <- append(col_names, col_)
  }
  rho_MC$x.1 <- NULL
  rho_MC$y.1 <- NULL
  colnames(rho_MC) <- col_names

  # 3rd step: List of estimated totals thus obtained from each sample
  est_MC <- c()
  for (c in 1:B) {
    est_tot <- sum((rho_MC[c])/pi)
    est_MC <- append(est_MC, est_tot)
  }

  true_value <- integral2(f, 0, 1000, 0, 1000)$Q 
  est_value <- mean(est_MC)
  return(c(true_value, est_value))
}
```

```{r}
true_vs_MC(n = 1000, B = 1000, f = fun_norm)
# 1.000000 2.265018 BOF (?)...
# 1.000000 2.127999
# 1.000000 4.984275
# 1.000000 6.072692
# 1.000000 1.982327
```

```{r}
true_vs_MC(n = 1000, B = 1000, f = fun1)
# 1e+06 1e+06 (Equality = great)
```

```{r}
true_vs_MC(n = 1000, B = 1000, f = fun_ratio)
# 3715802 6631207 BOF...
# 3715802 10413305
```

```{r}
true_vs_MC(n = 10000, B = 10000, f = fun_norm)
# 1.000000 
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

### 2024-06-25 Simulation1.Rmd
Martes tarde

@@
 ```{r}
+# Wrong algorithm
 list <- list_stable
@@
 plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
-# Semble régulier si nb = 2
+# Semble régulier si nb = 2, idem si nb = 8
 ```
@@
 ```{r}
-plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(202, 205), ylim = c(200, 205))
+plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(202, 205), ylim = c(205, 210))
 # Un seul point par cellule
@@
 }
-random_points
+# random_points
 ```

### 2024-06-25 Draft_fun.R

@@ -1,0 +1,15 @@
+# x-y given to each point
+fun_sous <- function(x,y){
+  x-y
+}
+
+test <- integral2(fun_sous, 0, 1000, 0, 1000)$Q #
+
+
+# x-y given to each point
+fun_ind <- function(x,y){
+  as.numeric(x > y)
+}
+
+test <- integral2(fun_ind, 0, 1000, 0, 1000)$Q 
+# 509148 if x >= y; 487316.7 if x > y

### 2024-06-25 No_cell.Rmd
Variance

@@
 
-  true_value <- integral2(f, 0, 1000, 0, 1000)$Q 
-  est_value <- mean(est_MC)
+  true_value <- integral2(f, 0, 1000, 0, 1000)$Q # Theoretical value
+  est_value <- mean(est_MC) # Estimated value
   return(c(true_value, est_value))
@@
 true_vs_MC(n = 10000, B = 10000, f = fun_norm)
-# 1.000000 
+# 1.000000 3.353247
+```
+
+# Variance
+
+Variance formula for the uniform case is based on the formula given by Cordy (1993), theorem 2 page 5 combined with the inclusion density given for example 1 page 4, which can be simplified in this particular case.
+
+## Back to simple cases
+
+### Case of the area
+
+```{r}
+n <- 100 # Sample size
+pi <- sum(rep((1/1000)*(1/1000), n))
+```
+
+```{r}
+# New variable: rho1^2
+random_points$carre <- (random_points$rho1)^2
+est_carre <- sum((random_points$carre)/pi)
+# est_carre = est_area # Logical since rho1 = carre = 1
+```
+
+```{r}
+var_area <- est_carre/pi - (1/n)*(est_area^2)
+# The empirical variance is null as expected
+```
+
+```{r}
+# fun1(x,y)^2 = fun1(x,y)
+varTH_area <- integral2(fun1, 0, 1000, 0, 1000)$Q/pi - (1/n)*(integral2(fun1, 0, 1000, 0, 1000)$Q^2)
+# The theoretical variance is null as expected
+# Since the total is equal to the area
+```
+
+```{r}
+# var_est <- function(f){
+#   random_points$carre <- (random_points$rho1)^2
+#   est_carre <- sum((random_points$carre)/pi)
+# }
+```
+
+### Case of the ratio
+
+```{r}
+# New variable: rho2^2
+random_points$carre2 <- (random_points$rho2)^2
+est_carre2 <- sum((random_points$carre2)/pi)
+# The new total is: 16571726
+
+var_ratio <- est_carre2/pi - (1/n)*(est_ratio^2)
+# Huge empirical variance: 124714284077
+```
+
+```{r}
+fun_ratio2 <- function(x,y){
+  fun_ratio(x,y)^2
+}
+varTH_ratio <- integral2(fun_ratio2, 0, 1000, 0, 1000)$Q/pi - (1/n)*(integral2(fun_ratio, 0, 1000, 0, 1000)$Q^2)
+# Doesn't work, I don't know why
 ```

### 2024-06-26 Bootstrap.Rmd
Mercredi midi

---
title: "Bootstrap"
output: pdf_document
date: "2024-06-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("pracma") # double integral
install.packages("boot") # for bootstrap
library(readxl) # to read the initial file
library(data.table) # for shift
library(pracma)
library(magrittr) # for pipes
library(tibble) # for add_column
library(boot)
```

# Preliminaries

We do not need the artificial forest for now. We just need a virtual 1000x1000 square.

```{r}
# Sample size
n <- 100
```

```{r}
# Marginal density: density of the uniform distribution over 1:1000
# Which leads us to the inclusion density function
pi <- sum(rep((1/1000)*(1/1000), n))
pi
```

# Creating one sample

```{r}
# Dataframe containing all coordinates of n randomly chosen points
random_points <- data.frame(x = rep(0, n), y = rep(0, n))
```

```{r}
# Uniform sampling over the whole territory
random_points$x <- runif(n, 0, 1000)
random_points$y <- runif(n, 0, 1000)
```

# Creating another sample based on the previous one

```{r}
for (point in 1:n) {
  random_points$x
}
```

```{r}
boot()
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

### 2024-06-26 Draft.Rmd
Martes tarde
Mercredi midi

@@
 ```
+
+# Draft for part after 25 June
+
+```{r}
+fun_diag <- function(x,y){
+  (x + y) <= 1000
+}
+```
+
+```{r}
+random_points$elt <- random_points$rho2/pi
+```
+
+```{r}
+est_ratio2 <- sum(random_points$elt)
+```
+
+```{r}
+integral2(fun_diag, 0, 1000, 0, 1000)
+```
+
+```{r}
+integrate(function(y) {
+  sapply(y, function(y){
+    integrate(function(x){
+      fun_ratio(x,y)}, 0, 1000)
+    })
+  }, 0, 1000)
+
+```
+
+# Draft for variance in No_cell.Rmd
+
+```{r}
+# var_est <- function(f){
+#   random_points$carre <- (random_points$rho1)^2
+#   est_carre <- sum((random_points$carre)/pi)
+# }
+```

### 2024-06-26 Draft_fun.R

@@ -6,7 +6,7 @@ fun_sous <- function(x,y){
 test <- integral2(fun_sous, 0, 1000, 0, 1000)$Q #
 
 
-# x-y given to each point
+# (x>y) given to each point
 fun_ind <- function(x,y){
   as.numeric(x > y)
 }

### 2024-06-26 Bootstrap.Rmd
Mardi soir

@@
 ```{r}
+# Draft
 for (point in 1:n) {
@@
 ```{r}
-boot()
+sum((random_points$x/random_points$y)/pi)
+```
+
+```{r}
+rho <- function(df, indice){
+  d <- df[indice,] # to enable boot
+  return(sum((d$x/d$y)/pi))
+}
+```
+
+```{r}
+res_boot <- boot(data=random_points, statistic=rho, R=10)
+res_boot
+```
+
+```{r}
+boot.ci(res_boot, type = "norm")
+```
+
+```{r}
+boot.ci(res_boot, type = "basic")
+# Warning in norm.inter(t, (1 + c(conf, -conf))/2) :
+#  extreme order statistics used as endpoints
+```
+
+```{r}
+# boot.ci(res_boot, type = "stud") 
+# Error in ci.out[[4L]] : subscript out of bounds
+```
+
+```{r}
+boot.ci(res_boot, type = "perc") 
+# Error in ci.out[[4L]] : subscript out of bounds
+```
+
+```{r}
+boot.ci(res_boot, type = "bca") 
+# Error in bca.ci(boot.out, conf, index[1L], L = L, t = t.o, t0 = t0.o,  : 
+#  estimated adjustment 'a' is NA
 ```

### 2024-06-26 Draft.Rmd
Mardi soir

@@
 ```
+
+# Draft for Trees_circle
+
+```{r}
+trees_in <- data.frame(useless = rep(0,30942))
+col_names <- c()
+for (point in 1:n) {
+  new_col <- paste("point", point, sep = "")
+  a <- random_points[point,]$x
+  b <- random_points[point,]$y
+  val <- is_point_in_circle(a, b, trees$x, trees$y, 100)*point
+  # val <- is_point_in_circle(round(a, digits = 0), round(b, digits = 0), trees$x, trees$y, 100) #*point
+  # if (val != 0){
+  #  trees$Is_in_circle <- append(trees$Is_in_circle, val[val != 0])
+  # }
+  trees_in <- trees_in %>% add_column(new_col = val)
+  col_names <- append(col_names, new_col)
+}
+# unique(trees$Is_in_circle)
+trees_in[1] <- NULL
+colnames(trees_in) <- col_names
+```

### 2024-06-26 Simulation1.Rmd
Mercredi midi
Mardi soir

@@
 # Importing the database with the artificial forest
-trees <- read_excel("~/work/Sim_article2024/artificial_forest_round.xls")
+trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
 ```
@@
 # True values
-cat("Il y a au total", length(trees$x), "arbres et un volume total de", sum(trees$v), "m^3 \n", "Soit un volume moyen de", mean(trees$v), "m^3 \n", "Le diamètre moyen à hauteur de poitrine est de", mean(trees$d130), "cm")
+cat("Il y a au total", length(trees$x), "arbres et un volume total de", sum(trees$v), "m^3 \nSoit un volume moyen de", mean(trees$v), "m^3 \nLe diamètre moyen à hauteur de poitrine est de", mean(trees$d130), "cm")
 ```
@@
 ```{r}
-trees$Is_in_circle <- is_point_in_circle(a, b, trees$x, trees$y, 5)
+trees$Is_in_circle <- is_point_in_circle(a, b, trees$x, trees$y, 2)
 ```

### 2024-06-26 Test.Rmd
Mardi soir

---
title: "Test"
output:
  pdf_document: default
  html_document: default
date: "2024-06-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

$\mapsto$ 1

```{r}
vec_test <- c(0,1,2)
f <- function(data, indice){
  d <- data[indice]
  return(c((d[1]+d[2]+d[3])/3))
}
boot(data=vec_test, statistic=f, R=10)
```

### 2024-06-26 Trees_circle.Rmd
Mardi soir

---
title: "Trees in circles"
output: pdf_document
date: "2024-06-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preliminaries

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
```

```{r}
# Sample size
n <- 100
```

```{r}
# Radius
R <- 10
```

```{r}
# Marginal density: density of the uniform distribution over 1:1000
# Which leads us to the inclusion density function
# p <- sum(rep((1/1000)*(1/1000), n)) # :(
# p

# I would say that pi changes: area of each circle over total area for each marginal
# p <- sum(rep((1/1000)*(1/1000)*(R^2)*pi, n)) # :(

# p <- sum(rep((1/1000)*(1/1000)*((R^2)*pi)/2, n))
```

# With no cell

## Creating one sample

```{r}
# Dataframe containing all coordinates of n randomly chosen points
random_points <- data.frame(x = rep(0, n), y = rep(0, n))
```

```{r}
# Uniform sampling over the whole territory
random_points$x <- runif(n, 0, 1000)
random_points$y <- runif(n, 0, 1000)
```

```{r}
# Function to check if a point is inside the circle
is_point_in_circle <- function(x, y, h, k, R) {
  # Calculate the squared distance between the point and the center of the circle
  squared_distance <- (x - h)^2 + (y - k)^2
  # Check if the squared distance is less than or equal to the squared radius
  return(as.numeric(squared_distance <= R^2))
}
```

```{r}
trees_in <- data.frame(useless = rep(0,30942))
col_names <- c()
for (point in 1:n) {
  new_col <- paste("point", point, sep = "")
  a <- random_points[point,]$x
  b <- random_points[point,]$y
  val <- is_point_in_circle(a, b, trees$x, trees$y, R)*point
  trees_in <- trees_in %>% add_column(new_col = val)
  col_names <- append(col_names, new_col)
}
trees_in[1] <- NULL
colnames(trees_in) <- col_names
```

```{r}
rm(a,b,val,col_names)
```

```{r}
nb_trees <- c()

for (placette in 1:n) {
  nb_trees <- append(nb_trees, sum(trees_in[trees_in$point74 != 0,]))
}

sum((nb_trees)/p)
# 28737017 # TOO MUCH, p is (probably) wrong
# 9.028e+09 # if p unchanged i.e. sum(rep((1/1000)*(1/1000), n))
# 57474033 # TOO MUCH, p is (probably) wrong if sum(rep((1/1000)*(1/1000)*((R^2)*pi)/2, n))
```

```{r}
trees$Is_in_circle <- is_point_in_circle(500, 500, trees$x, trees$y, 100)
unique(trees$Is_in_circle)
```

```{r}
# The sample thus obtained
trees[trees$Is_in_circle == TRUE,]
```

```{r}
total_trees <- nrow(trees[trees$Is_in_circle == TRUE,])
```

```{r}
trees$Is_in_circle <- is_point_in_circle(580.869189, 797.312061, trees$x, trees$y, 100)
unique(trees$Is_in_circle)
```

```{r}

```

### 2024-06-27 Bootstrap.Rmd
Jeudi soir

@@
 
+Notes from Efron and Tibshirani (1993):
+"It is important to note that B = 100 or 200 is not adequate for confidence interval construction, see Chapter 19." (p161)
+
 # Preliminaries
@@
 # Which leads us to the inclusion density function
-pi <- sum(rep((1/1000)*(1/1000), n))
-pi
+p <- sum(rep((1/1000)*(1/1000), n))
+p
 ```
@@
 ```{r}
-sum((random_points$x/random_points$y)/pi)
+sum((random_points$x/random_points$y)/p)
 ```
@@
   d <- df[indice,] # to enable boot
-  return(sum((d$x/d$y)/pi))
+  return(sum((d$x/d$y)/p))
 }
@@
 
+# Another package
+
 ```{r}
+install.packages("bootstrap")
+library(bootstrap)
+```
 
+```{r}
+## The most simple function
+f_try <- function(x){
+  1
+}
+```
+
+```{r}
+theta <- function(x){mean(x)}
+```
+
+```{r}
+patch.boot <- bootstrap(x = random_points$x,nboot = 1000,theta = theta, func=NULL)
+```
+
+```{r}
+sd(patch.boot$thetastar) # bootstrapped standard error
+```
+
+```{r}
+bcanon(random_points$x, 1000, theta = theta)
+```
+
+```{r}
+circle <- function(x1, x2, R){
+  # Produces a local variable based on 2 coordinates (x1, x2) and a radius (R)
+
+  # Intermediary step: which trees are inside the circle?
+  trees_in <- data.frame(useless = rep(0,30942))
+  val <- is_point_in_circle(x1, x2, trees$x, trees$y, R)
+  trees_in <- trees_in %>% add_column(new_col = val)
+  trees_in[1] <- NULL
+
+  # Creation of the local variable
+  local_var <- sum(trees_in[new_col != 0,]/area_circle)
+  return(local_var) # A single number
+}
+```
+
+```{r}
+f_boot <- function(sample){
+
+}
+```
+
+```{r}
+# xdata <- matrix(rnorm(30),ncol=2)
+n <- 100
+# theta <- function(x,xdata){ cor(xdata[x,1],xdata[x,2]) }
+theta <- function(x,xdata){
+  a <- c()
+  for (i in 1:n) {
+    a <- append(a, circle(xdata[i,1], xdata[i,2], R))
+  }
+  est_nb <- sum((a)/p)
+}
+results <- bcanon(1:n,150,theta,random_points, alpha = 0.95)
+```
+
+```{r}
+results$confpoints # NaN
 ```

### 2024-06-27 Draft.Rmd
Jeudi soir

@@
 ```
+
+```{r}
+## Draft
+
+nb_trees <- c()
+
+for (placette in 1:n) {
+  nb_trees <- append(nb_trees, sum(trees_in[trees_in$point74 != 0,]))
+}
+
+sum((nb_trees)/p)
+# 28737017 # TOO MUCH, p is (probably) wrong
+# 9.028e+09 # if p unchanged i.e. sum(rep((1/1000)*(1/1000), n))
+# 57474033 # TOO MUCH, p is (probably) wrong if sum(rep((1/1000)*(1/1000)*((R^2)*pi)/2, n))
+```
+
+```{r}
+trees$Is_in_circle <- is_point_in_circle(500, 500, trees$x, trees$y, 100)
+unique(trees$Is_in_circle)
+```
+
+```{r}
+# The sample thus obtained
+trees[trees$Is_in_circle == TRUE,]
+```
+
+```{r}
+total_trees <- nrow(trees[trees$Is_in_circle == TRUE,])
+```
+
+```{r}
+trees$Is_in_circle <- is_point_in_circle(580.869189, 797.312061, trees$x, trees$y, 100)
+unique(trees$Is_in_circle)
+```
+
+```{r}
+# Marginal density: density of the uniform distribution over 1:1000
+# Which leads us to the inclusion density function
+p <- sum(rep((1/1000)*(1/1000), n)) # :(
+# p
+
+# I would say that p changes: area of each circle over total area for each marginal
+# p <- sum(rep((1/1000)*(1/1000)*(R^2)*pi, n)) # :(
+
+# p <- sum(rep((1/1000)*(1/1000)*((R^2)*pi)/2, n))
+```

### 2024-06-27 No_tree_no_grid.Rmd
Jeudi soir

---
title: "Uniform sampling across the whole territory without any cells"
output: pdf_document
date: "2024-06-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("pracma") # double integral
library(readxl) # to read the initial file
library(data.table) # for shift
library(pracma)
library(magrittr) # for pipes
library(tibble) # for add_column
```

# Preliminaries

We do not need the artificial forest for now. We just need a virtual 1000x1000 square.

```{r}
# Sample size
n <- 100
```

```{r}
# Marginal density: density of the uniform distribution over 1:1000
# Which leads us to the inclusion density function
pi <- sum(rep((1/1000)*(1/1000), n))
pi
```

# Estimates with simple functions and one sample

## Creating one sample

```{r}
# Dataframe containing all coordinates of n randomly chosen points
random_points <- data.frame(x = rep(0, n), y = rep(0, n))
```

```{r}
# Uniform sampling over the whole territory
random_points$x <- runif(n, 0, 1000)
random_points$y <- runif(n, 0, 1000)
```

## First function: (x,y) $\mapsto$ 1

```{r}
## First simple function: 1 given to each point
random_points$rho1 <- rep(1, n)
# Formula given in Cordy (1993), page 3
```

```{r}
## The most simple function
fun1 <- function(x,y){
  1
}
```

```{r}
# Value to estimate: the area of the territory
area <- 1000*1000
# integral2(fun1, 0, 1000, 0, 1000)$Q # the same
```

```{r}
# Estimated value
est_area <- sum((random_points$rho1)/pi) # Equal to 1e+06 whatever the chosen points
```

## Second function: (x,y) $\mapsto$ (x/y) with or without normalization

```{r}
# x/y given to each point
f_ratio <- function(x,y){
  x/y
}
```

```{r}
# Normalization of the ratio
f_norm <- function(x,y){
  (x/y)/(integral2(f_ratio, 0, 1000, 0, 1000)$Q)
}
```

```{r}
# random_points$rho2 <- f_norm(random_points$x,random_points$y)
```

```{r}
## Value to estimate
# ratio_norm <- integral2(f_norm, 0, 1000, 0, 1000)$Q # = 1
```

```{r}
## Estimated value
# est_ratio_norm <- sum((random_points$rho2)/pi)
## NOT SATISFACTORY: seems too low (between 0 and 1)
## 0.5449481 e.g.
```

```{r}
## Value to estimate
# ratio_norm <- integral2(f_ratio, 0, 1000, 0, 1000)$Q # = 1
```

```{r}
# Calculation of the ratio for each point
random_points$rho2 <- f_ratio(random_points$x,random_points$y)
```

```{r}
# Value to estimate
ratio <- integral2(f_ratio, 0, 1000, 0, 1000)$Q # = 3715802
ratio
```

```{r}
# Estimated value
est_ratio <- sum((random_points$rho2)/pi) # = 2024919
est_ratio
# Seems not very satisfactory
```

## Third function: (x,y) $\mapsto$ as.numeric(x>y)

```{r}
# (x>y) given to each point
f_ind <- function(x,y){
  as.numeric(x > y)
}
```

```{r}
# Value to estimate
half_area <- integral2(f_ind, 0, 1000, 0, 1000)$Q
half_area
# 509148 if x >= y; 487316.7 if x > y
```

```{r}
random_points$rho3 <- f_ind(random_points$x,random_points$y)
```

```{r}
# Estimated value
est_ind <- sum((random_points$rho3)/pi) # = 470000
est_ind
# Seems credible
```

# Variances with simple functions and one sample

Variance formula for the uniform case is based on the formula given by Cordy (1993), theorem 2 page 5 combined with the inclusion density given for example 1 page 4, which gives a simplified formula for this particular case.

```{r}
n <- 100 # Sample size
pi <- sum(rep((1/1000)*(1/1000), n))
```

## Case of the area

```{r}
# New variable: rho1^2
random_points$carre <- (random_points$rho1)^2
est_carre <- sum((random_points$carre)/pi)
# est_carre = est_area # Logical since rho1 = carre = 1
```

```{r}
var_area <- est_carre/pi - (1/n)*(est_area^2)
var_area
# The empirical variance is null as expected
```

```{r}
# fun1(x,y)^2 = fun1(x,y)
varTH_area <- integral2(fun1, 0, 1000, 0, 1000)$Q/pi - (1/n)*(integral2(fun1, 0, 1000, 0, 1000)$Q^2)
varTH_area
# The theoretical variance is null as expected
# Since the total is equal to the area
```

## Case of the ratio

```{r}
# New variable: rho2^2
random_points$carre2 <- (random_points$rho2)^2
est_carre2 <- sum((random_points$carre2)/pi)
# The new total is: 16571726
est_carre2

var_ratio <- est_carre2/pi - (1/n)*(est_ratio^2)
# Huge empirical variance: 124714284077
var_ratio
```

```{r}
f_ratio2 <- function(x,y){
  (x/y)^2
}
varTH_ratio <- integral2(f_ratio2, 1e-100, 1000, 1e-100, 1000)$Q/pi - (1/n)*(integral2(f_ratio, 1e-100, 1000, 1e-100, 1000)$Q^2)
varTH_ratio
# Huge theoretical variance: 3.216476e+97
# integral2(f_ratio2, 1, 2, 1, 2) # works
# integral2(f_ratio2, 0, 1000, 0, 1000) # doesn't work
```

## Case of half of the area

```{r}
var_ind <- est_ind/pi - (1/n)*(est_ind^2)
var_ind
# Empirical variance: 2.491e+09 (huge)
```

```{r}
# f_ind(x,y)^2 = f_ind(x,y)
varTH_ind <- integral2(f_ind, 0, 1000, 0, 1000)$Q/pi - (1/n)*(integral2(f_ind, 0, 1000, 0, 1000)$Q^2)
varTH_ind
# Theoretical variance: 2498391345, i.e. around 2.498e+09
# Close to the empirical one: great
```

# Monte Carlo

## First MC application step by step with the normalized ratio

```{r}
# Number of replications for the Monte-Carlo method
B <- 1000
```

```{r}
# Initialization with a first sample
series_MC <- data.frame(x.1 = runif(n, 0, 1000), y.1 = runif(n, 0, 1000))
col_names <- c("x1", "y1")
```

```{r}
# Making as many samples as necessary for MC (i.e. B)
for (b in 2:B) {
  x <- paste("x", b, sep = "")
  y <- paste("y", b, sep = "")
  # Uniform sampling over the whole territory
  a1 <- runif(n, 0, 1000)
  a2 <- runif(n, 0, 1000)
  # series_MC$x <- runif(n, 0, 1000)
  # series_MC$y <- runif(n, 0, 1000)
  # append()
  series_MC <- series_MC %>% add_column(x = a1, y = a2)
  col_names <- append(col_names, c(x, y))
}
colnames(series_MC) <- col_names
```

```{r}
# Calculation of rho function for each pair (x,y)
rho_MC <- data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
col_names <- c()
```

```{r}
for (c in 1:B) {
  col_ <- paste("est", c, sep = "")
  # With normalized ratio
  a <- f_norm(series_MC[(2*c)-1],series_MC[2*c])
  rho_MC <- rho_MC %>% add_column(col_ = a)
  col_names <- append(col_names, col_)
}
rho_MC$x.1 <- NULL
rho_MC$y.1 <- NULL
colnames(rho_MC) <- col_names
```

```{r}
# List of estimated totals thus obtained from each sample
est_MC <- c()
```

```{r}
for (c in 1:B) {
  est_tot <- sum((rho_MC[c])/pi)
  est_MC <- append(est_MC, est_tot)
}
```

```{r}
# Empirical mean based on MC
mean(est_MC) # should be close to 1
# 1.740544
```

```{r}
# Empirical standard deviation based on MC
sd(est_MC)
```

## Automation of the MC method with a function

```{r}
### Function to automate Monte Carlo method

true_vs_MC <- function(n, B, f){
  # n: sample size; B: number of iterations for MC; f: function to consider (with 2 variables, x and y)
  pi <- sum(rep((1/1000)*(1/1000), n))

  # 1st step: generating n samples
  series_MC <- data.frame(x.1 = runif(n, 0, 1000), y.1 = runif(n, 0, 1000))
  col_names <- c("x1", "y1")
  for (b in 2:B) {
    x <- paste("x", b, sep = "")
    y <- paste("y", b, sep = "")
    # Uniform sampling over the whole territory
    a1 <- runif(n, 0, 1000)
    a2 <- runif(n, 0, 1000)
    series_MC <- series_MC %>% add_column(x = a1, y = a2)
    col_names <- append(col_names, c(x, y))
  }
  colnames(series_MC) <- col_names

  # 2nd step: creating the values corresponding to the function
  rho_MC <- data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
  col_names <- c()
  for (c in 1:B) {
    col_ <- paste("est", c, sep = "")
    a <- f(series_MC[(2*c)-1],series_MC[2*c])
    rho_MC <- rho_MC %>% add_column(col_ = a)
    col_names <- append(col_names, col_)
  }
  rho_MC$x.1 <- NULL
  rho_MC$y.1 <- NULL
  colnames(rho_MC) <- col_names

  # 3rd step: List of estimated totals thus obtained from each sample
  est_MC <- c()
  for (c in 1:B) {
    est_tot <- sum((rho_MC[c])/pi)
    est_MC <- append(est_MC, est_tot)
  }

  true_value <- integral2(f, 0, 1000, 0, 1000)$Q # Theoretical value
  est_value <- mean(est_MC) # Estimated value
  return(c(true_value, est_value))
}
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = fun1)
cat("True integral:", res[1], "\nMean of all the estimations:", res[2])
# 1e+06 1e+06 (Equality = great)
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_norm)
cat("True integral:", res[1], "\nMean of all the estimations:", res[2])
# 1.000000 2.265018
# 1.000000 2.127999
# 1.000000 4.984275
# 1.000000 6.072692
# 1.000000 1.982327
# Satisfactory?
```

```{r}
res <- true_vs_MC(n = 1000, B = 1000, f = f_ratio)
cat("True integral:", res[1], "\nMean of all the estimations:", res[2])
# 3715802 6631207
# 3715802 10413305
# 3715802 10325197
# Satisfactory?
```

```{r}
res <- true_vs_MC(n = 10000, B = 10000, f = f_norm)
cat("True integral:", res[1], "\nMean of all the estimations:", res[2])
# 1.000000 3.353247
# Not necessarily better with a larger sample and more replications for MC
```

### 2024-06-27 Trees_no_grid.Rmd
Jeudi soir

---
title: "Uniform sampling without any cells to count trees"
output: pdf_document
date: "2024-06-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("pracma") # double integral
install.packages("boot") # for bootstrap
library(readxl) # to read the initial file
library(data.table) # for shift
library(pracma)
library(magrittr) # for pipes
library(tibble) # for add_column
library(boot)
```

# Preliminaries

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
```

For now, the variable of interest is the number of trees.

```{r}
# Sample size
n <- 100
```

```{r}
# Radius
R <- 5
area_circle <- pi*(R^2)
```

```{r}
# Marginal density: density of the uniform distribution over 1:1000
# Which leads us to the inclusion density function
p <- sum(rep((1/1000)*(1/1000), n))
```

# Creating one sample

A sample is created by uniformly sampling the whole territory except the edge, which depends on the radius (to facilitate the calculation of the local variable).

```{r}
# Dataframe containing all coordinates of n randomly chosen points
random_points <- data.frame(x = rep(0, n), y = rep(0, n))
```

```{r}
# Uniform sampling over the whole territory except the edge
random_points$x <- runif(n, 0+R, 1000-R)
random_points$y <- runif(n, 0+R, 1000-R)
```

# Creating a circle around each point

We want to target trees inside the circles defined by the sample and the radius.

```{r}
# Function to check if a point is inside a circle (indicator variable)
is_point_in_circle <- function(x, y, h, k, R) {
  # Calculate the squared distance between the point and the center of the circle
  squared_distance <- (x - h)^2 + (y - k)^2
  # Check if the squared distance is less than or equal to the squared radius
  return(as.numeric(squared_distance <= R^2))
}
```

```{r}
# New dataframe called trees_in (length = number of trees)
# Each column targets one point which was previously randomly chosen
# The value is 1 if the tree corresponding is inside the circle
trees_in <- data.frame(useless = rep(0,30942))
col_names <- c()
for (point in 1:n) {
  new_col <- paste("point", point, sep = "")
  a <- random_points[point,]$x
  b <- random_points[point,]$y
  val <- is_point_in_circle(a, b, trees$x, trees$y, R) #*point
  trees_in <- trees_in %>% add_column(new_col = val)
  col_names <- append(col_names, new_col)
}
trees_in[1] <- NULL
colnames(trees_in) <- col_names
```

```{r}
rm(a,b,val,col_names)
```

```{r}
# Creating a local variable (pages 10-11 in Trinh et alii (2024))
local_var <- c()
for (placette in 1:n) {
  local_var <- append(local_var, sum(trees_in[trees_in[placette] != 0,]/area_circle))
}

est_nb <- sum((local_var)/p)
cat("An estimation of the total number of trees based on the sample:", est_nb)
# 29921.13 e.g.
```

## Automation

A local variable is created, based on one pair of points (center of the circle) and the radius.

```{r}
circle <- function(x1, x2, R){
  # Produces a local variable based on 2 coordinates (x1, x2) and a radius (R)

  # Intermediary step: which trees are inside the circle?
  trees_in <- data.frame(useless = rep(0,30942))
  val <- is_point_in_circle(x1, x2, trees$x, trees$y, R)
  trees_in <- trees_in %>% add_column(new_col = val)
  trees_in[1] <- NULL

  # Creation of the local variable
  local_var <- sum(trees_in[new_col != 0,]/area_circle)
  return(local_var) # A single number
}
```

A mean of B estimations (Monte Carlo), each of them based on a sample of size n and using a radius R.

```{r}
### Function to automate Monte Carlo method

true_vs_MC <- function(n, B, R){
  # n: sample size; B: number of iterations for MC;
  # R: radius of the circle, taken into account for the sampling
  p <- sum(rep((1/1000)*(1/1000), n))

  # 1st step: generating n samples
  series_MC <- data.frame(x.1 = runif(n, 0+R, 1000-R), y.1 = runif(n, 0+R, 1000-R))
  col_names <- c("x1", "y1")
  for (b in 2:B) {
    x <- paste("x", b, sep = "")
    y <- paste("y", b, sep = "")
    # Uniform sampling over the whole territory except the edge
    a1 <- runif(n, 0+R, 1000-R)
    a2 <- runif(n, 0+R, 1000-R)
    series_MC <- series_MC %>% add_column(x = a1, y = a2)
    col_names <- append(col_names, c(x, y))
  }
  colnames(series_MC) <- col_names

  # 2nd step: creating the values corresponding to the function
  # Based on each sampled pair in all samples
  rho_MC <- data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
  col_names <- c()
  for (c in 1:B) {
    col_ <- paste("est", c, sep = "")
    a <- c()
    for (i in 1:n) {
      a <- append(a, circle(series_MC[i, (2*c)-1], series_MC[i, 2*c], R))
    }
    rho_MC <- rho_MC %>% add_column(col_ = a)
    col_names <- append(col_names, col_)
  }
  rho_MC$x.1 <- NULL
  rho_MC$y.1 <- NULL
  colnames(rho_MC) <- col_names

  # 3rd step: List of estimated totals thus obtained from each sample
  est_MC <- c()
  for (c in 1:B) {
    est_tot <- sum((rho_MC[c])/p)
    est_MC <- append(est_MC, est_tot)
  }

  true_value <- nrow(trees) # Theoretical value
  est_value <- mean(est_MC) # Estimated value
  return(c(true_value, est_value))
}
```

```{r}
res <- true_vs_MC(n = 100, B = 1000, R = 5)
cat("True number of trees:", res[1], "\nMean of all the estimations (Monte Carlo):", res[2])
```

### 2024-06-28 No_tree_no_grid.Rmd
TGIF

@@
 ```{r}
-install.packages("pracma") # double integral
 library(readxl) # to read the initial file
 library(data.table) # for shift
-library(pracma)
 library(magrittr) # for pipes
@@
 ```{r}
-## First simple function: 1 given to each point
-random_points$rho1 <- rep(1, n)
-# Formula given in Cordy (1993), page 3
-```
-
-```{r}
 ## The most simple function
@@
 ```{r}
+# 1 given to each sampled point
+random_points$rho1 <- rep(1, n)
+# Formula given in Cordy (1993), page 3
+```
+
+```{r}
 # Value to estimate: the area of the territory
 area <- 1000*1000
-# integral2(fun1, 0, 1000, 0, 1000)$Q # the same
 ```
@@
 # Estimated value
-est_area <- sum((random_points$rho1)/pi) # Equal to 1e+06 whatever the chosen points
+est_area <- sum((random_points$rho1)/p) 
+# Equal to 1e+06 whatever the chosen points
 ```
 
-## Second function: (x,y) $\mapsto$ (x/y) with or without normalization
+## Second function: (x,y) $\mapsto$ as.numeric(x>y)
 
 ```{r}
-# x/y given to each point
-f_ratio <- function(x,y){
-  x/y
-}
-```
-
-```{r}
-# Normalization of the ratio
-f_norm <- function(x,y){
-  (x/y)/(integral2(f_ratio, 0, 1000, 0, 1000)$Q)
-}
-```
-
-```{r}
-# random_points$rho2 <- f_norm(random_points$x,random_points$y)
-```
-
-```{r}
-## Value to estimate
-# ratio_norm <- integral2(f_norm, 0, 1000, 0, 1000)$Q # = 1
-```
-
-```{r}
-## Estimated value
-# est_ratio_norm <- sum((random_points$rho2)/pi)
-## NOT SATISFACTORY: seems too low (between 0 and 1)
-## 0.5449481 e.g.
-```
-
-```{r}
-## Value to estimate
-# ratio_norm <- integral2(f_ratio, 0, 1000, 0, 1000)$Q # = 1
-```
-
-```{r}
-# Calculation of the ratio for each point
-random_points$rho2 <- f_ratio(random_points$x,random_points$y)
-```
-
-```{r}
-# Value to estimate
-ratio <- integral2(f_ratio, 0, 1000, 0, 1000)$Q # = 3715802
-ratio
-```
-
-```{r}
-# Estimated value
-est_ratio <- sum((random_points$rho2)/pi) # = 2024919
-est_ratio
-# Seems not very satisfactory
-```
-
-## Third function: (x,y) $\mapsto$ as.numeric(x>y)
-
-```{r}
-# (x>y) given to each point
+## Indicator of (x>y)
 f_ind <- function(x,y){
@@
 # Value to estimate
-half_area <- integral2(f_ind, 0, 1000, 0, 1000)$Q
-half_area
-# 509148 if x >= y; 487316.7 if x > y
+half_area <- 1000*1000/2
 ```
@@
 ```{r}
-random_points$rho3 <- f_ind(random_points$x,random_points$y)
+# 1 given to each sampled point that satisfies x>y
+random_points$rho2 <- f_ind(random_points$x,random_points$y)
 ```
@@
 # Estimated value
-est_ind <- sum((random_points$rho3)/pi) # = 470000
+est_ind <- sum((random_points$rho2)/p)
 est_ind
-# Seems credible
+# 510000 e.g.
+```
+
+## Third function: (x,y) $\mapsto$ x
+
+```{r}
+# x given to each point
+f_x <- function(x,y){
+  x
+}
+```
+
+```{r}
+# Value to estimate
+val_x <- 500000000
+```
+
+```{r}
+# Estimated value
+est_x <- sum((random_points$x)/p) # = 
+est_x
+# 499690876 e.g.
 ```
@@
 
-```{r}
-n <- 100 # Sample size
-pi <- sum(rep((1/1000)*(1/1000), n))
-```
-
 ## Case of the area
@@
 random_points$carre <- (random_points$rho1)^2
-est_carre <- sum((random_points$carre)/pi)
+est_carre <- sum((random_points$carre)/p)
 # est_carre = est_area # Logical since rho1 = carre = 1
@@
 ```{r}
-var_area <- est_carre/pi - (1/n)*(est_area^2)
+var_area <- est_carre/p - (1/n)*(est_area^2)
 var_area
@@
 # fun1(x,y)^2 = fun1(x,y)
-varTH_area <- integral2(fun1, 0, 1000, 0, 1000)$Q/pi - (1/n)*(integral2(fun1, 0, 1000, 0, 1000)$Q^2)
+varTH_area <- area/p - (1/n)*(area^2)
 varTH_area
@@
 
-## Case of the ratio
-
-```{r}
-# New variable: rho2^2
-random_points$carre2 <- (random_points$rho2)^2
-est_carre2 <- sum((random_points$carre2)/pi)
-# The new total is: 16571726
-est_carre2
-
-var_ratio <- est_carre2/pi - (1/n)*(est_ratio^2)
-# Huge empirical variance: 124714284077
-var_ratio
-```
-
-```{r}
-f_ratio2 <- function(x,y){
-  (x/y)^2
-}
-varTH_ratio <- integral2(f_ratio2, 1e-100, 1000, 1e-100, 1000)$Q/pi - (1/n)*(integral2(f_ratio, 1e-100, 1000, 1e-100, 1000)$Q^2)
-varTH_ratio
-# Huge theoretical variance: 3.216476e+97
-# integral2(f_ratio2, 1, 2, 1, 2) # works
-# integral2(f_ratio2, 0, 1000, 0, 1000) # doesn't work
-```
-
 ## Case of half of the area
@@
 ```{r}
-var_ind <- est_ind/pi - (1/n)*(est_ind^2)
+var_ind <- est_ind/p - (1/n)*(est_ind^2)
 var_ind
@@
 # f_ind(x,y)^2 = f_ind(x,y)
-varTH_ind <- integral2(f_ind, 0, 1000, 0, 1000)$Q/pi - (1/n)*(integral2(f_ind, 0, 1000, 0, 1000)$Q^2)
+varTH_ind <- half_area/p - (1/n)*(half_area^2)
 varTH_ind
+# Theoretical variance: 2.5e+09, i.e. around 2.498e+09
+# Close to the empirical one: great
+```
+
+## Case of the function that keeps x
+
+```{r}
+f_x2 <- function(x,y){
+  x^2
+}
+```
+
+```{r}
+# Estimated value
+est_x2 <- sum(((random_points$x)^2)/p)
+est_x2
+# 499690876 e.g.
+```
+
+```{r}
+var_x <- est_x2/p - (1/n)*(est_x^2)
+var_x
+# Empirical variance: 8.407871e+14 ?!
+```
+
+```{r}
+# f_ind(x,y)^2 = f_ind(x,y)
+# varTH_x <- integral2(f_x, 0, 1000, 0, 1000)$Q/p - (1/n)*(integral2(f_x, 0, 1000, 0, 1000)$Q^2)
+# varTH_x
 # Theoretical variance: 2498391345, i.e. around 2.498e+09
@@
 
-## First MC application step by step with the normalized ratio
+## First MC application step by step with the function that keeps x
 
@@
   # With normalized ratio
-  a <- f_norm(series_MC[(2*c)-1],series_MC[2*c])
+  a <- f_x(series_MC[(2*c)-1],series_MC[2*c])
   rho_MC <- rho_MC %>% add_column(col_ = a)
@@
 for (c in 1:B) {
-  est_tot <- sum((rho_MC[c])/pi)
+  est_tot <- sum((rho_MC[c])/p)
   est_MC <- append(est_MC, est_tot)
@@
 # Empirical mean based on MC
-mean(est_MC) # should be close to 1
-# 1.740544
+mean(est_MC) # should be close to 5e+08
+# 499121662 e.g.
 ```
@@
 
-true_vs_MC <- function(n, B, f){
+true_vs_MC <- function(n, B, f, true_value){
   # n: sample size; B: number of iterations for MC; f: function to consider (with 2 variables, x and y)
-  pi <- sum(rep((1/1000)*(1/1000), n))
+  p <- sum(rep((1/1000)*(1/1000), n))
 
@@
   for (c in 1:B) {
-    est_tot <- sum((rho_MC[c])/pi)
+    est_tot <- sum((rho_MC[c])/p)
     est_MC <- append(est_MC, est_tot)
@@
 
-  true_value <- integral2(f, 0, 1000, 0, 1000)$Q # Theoretical value
   est_value <- mean(est_MC) # Estimated value
@@
 ```{r}
-res <- true_vs_MC(n = 1000, B = 1000, f = fun1)
+res <- true_vs_MC(n = 1000, B = 1000, f = fun1, true_value = 1e+06)
 cat("True integral:", res[1], "\nMean of all the estimations:", res[2])
@@
 ```{r}
-res <- true_vs_MC(n = 1000, B = 1000, f = f_norm)
+res <- true_vs_MC(n = 1000, B = 1000, f = f_ind, true_value = 500000)
 cat("True integral:", res[1], "\nMean of all the estimations:", res[2])
-# 1.000000 2.265018
-# 1.000000 2.127999
-# 1.000000 4.984275
-# 1.000000 6.072692
-# 1.000000 1.982327
-# Satisfactory?
+# True integral: 5e+05
+# Mean of all the estimations: 499600
 ```
@@
 ```{r}
-res <- true_vs_MC(n = 1000, B = 1000, f = f_ratio)
+res <- true_vs_MC(n = 1000, B = 1000, f = f_x, true_value = 5e+08)
 cat("True integral:", res[1], "\nMean of all the estimations:", res[2])
-# 3715802 6631207
-# 3715802 10413305
-# 3715802 10325197
-# Satisfactory?
+
+#True integral: 5e+08
+# Mean of all the estimations: 500189987
 ```
-
-```{r}
-res <- true_vs_MC(n = 10000, B = 10000, f = f_norm)
-cat("True integral:", res[1], "\nMean of all the estimations:", res[2])
-# 1.000000 3.353247
-# Not necessarily better with a larger sample and more replications for MC
-```

### 2024-06-28 Trees_no_grid.Rmd
TGIF

@@
 R <- 5
-area_circle <- pi*(R^2)
 ```
@@
 # Uniform sampling over the whole territory except the edge
-random_points$x <- runif(n, 0+R, 1000-R)
-random_points$y <- runif(n, 0+R, 1000-R)
+random_points$x <- runif(n, 0, 1000)
+random_points$y <- runif(n, 0, 1000)
 ```
@@
 ```{r}
-rm(a,b,val,col_names)
+rm(a,b,val,col_names, point, new_col)
 ```
@@
 local_var <- c()
+source("~/work/Sim_article2024/Inc_area.R")
 for (placette in 1:n) {
-  local_var <- append(local_var, sum(trees_in[trees_in[placette] != 0,]/area_circle))
+  local_var <- append(local_var, sum(trees_in[trees_in[placette] != 0,]/inc_area(c(random_points[placette,]$x, random_points[placette,]$y),0,0,1000,1000,R)))
 }
@@
 cat("An estimation of the total number of trees based on the sample:", est_nb)
-# 29921.13 e.g.
+# 26228.73 e.g.
+# 38197.19 e.g.
+```
+
+```{r}
+rm(placette)
 ```
@@
   trees_in <- data.frame(useless = rep(0,30942))
+  new_col <- "in_or_out"
   val <- is_point_in_circle(x1, x2, trees$x, trees$y, R)
@@
   # Creation of the local variable
-  local_var <- sum(trees_in[new_col != 0,]/area_circle)
+  local_var <- sum(trees_in[new_col != 0,]/inc_area(c(x1, x2),0,0,1000,1000,R))
   return(local_var) # A single number
@@
   # 1st step: generating n samples
-  series_MC <- data.frame(x.1 = runif(n, 0+R, 1000-R), y.1 = runif(n, 0+R, 1000-R))
+  series_MC <- data.frame(x.1 = runif(n, 0, 1000), y.1 = runif(n, 0, 1000))
   col_names <- c("x1", "y1")
@@
     # Uniform sampling over the whole territory except the edge
-    a1 <- runif(n, 0+R, 1000-R)
-    a2 <- runif(n, 0+R, 1000-R)
+    a1 <- runif(n, 0, 1000)
+    a2 <- runif(n, 0, 1000)
     series_MC <- series_MC %>% add_column(x = a1, y = a2)
@@
 cat("True number of trees:", res[1], "\nMean of all the estimations (Monte Carlo):", res[2])
+# True number of trees: 30942 
+# Mean of all the estimations (Monte Carlo): 30954.24
 ```

### 2024-06-28 Inc_area.R

@@ -1,0 +1,138 @@
+######## Translation of a SAS program ----------
+
+inc_area <- function(coord,x0F, y0F, x1F, y1F, r){
+  x <- coord[1]
+  y <- coord[2]
+  
+  ##### Case 1: the point is located s.t. the inclusion plot is completely inside the territory
+  if ((x>=x0F+r) & (x<=x1F-r) & (y>=y0F+r) & (y<=y1F-r)){
+    surf <- pi*(r^2)
+  }
+  
+  ##### Case 2: the point is located s.t. the inclusion plot is not completely inside the territory, 
+  # but intersects one side of the territory only.
+  # For the formula of the area, see https://fr.wikipedia.org/wiki/Segment_circulaire
+  ### Lower rectangle
+  if ((x>=x0F+r) & (x<=x1F-r) & (y>=y0F) & (y<y0F+r)){
+    d <- y-y0F
+    theta <- 2*acos(d/r)
+    surf <- (r^2)*(pi-0.5*theta+0.5*sin(theta))
+  }
+  ### Right rectangle
+  if ((x>x1F-r) & (x<=x1F) & (y>=y0F+r) & (y<=y1F-r)){
+      d <- x1F-x
+      theta <- 2*acos(d/r)
+      surf <- (r^2)*(pi-0.5*theta+0.5*sin(theta))
+  }
+  ### Upper rectangle
+  if ((x>=x0F+r) & (x<=x1F-r) & (y>y1F-r) & (y<=y1F)){
+      d <- y1F-y
+      theta <- 2*acos(d/r)
+      surf <- (r^2)*(pi-0.5*theta+0.5*sin(theta))
+  }
+  ### Left rectangle
+  if ((x>=x0F) & (x<x0F+r) & (y>=y0F+r) & (y<=y1F-r)){
+      d <- x-x0F
+      theta <- 2*acos(d/r)
+      surf <- (r^2)*(pi-0.5*theta+0.5*sin(theta))
+  }
+  
+  ##### Case 3: the point is located s.t. the inclusion plot is not completely inside
+  # the territory, and intersects two sides of the territory. The area is given
+  # by a rectangle triangle and a circular segment
+  ### Lower left square
+  if ((x>=x0F) & (x<x0F+r) & (y>=y0F) & (y<y0F+r)){
[…]

### 2024-07-01 Bootstrap.Rmd
Lendemain d'élection

@@
 ```{r}
-install.packages("pracma") # double integral
 install.packages("boot") # for bootstrap
@@
 library(data.table) # for shift
-library(pracma)
 library(magrittr) # for pipes
@@
 
-We do not need the artificial forest for now. We just need a virtual 1000x1000 square.
+((We do not need the artificial forest for now. We just need a virtual 1000x1000 square.))
+
+```{r}
+# Importing the database with the artificial forest
+trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
+```
 
@@
 n <- 100
-```
 
-```{r}
 # Marginal density: density of the uniform distribution over 1:1000
@@
 p <- sum(rep((1/1000)*(1/1000), n))
-p
+
+# Number of bootstrap samples
+B <- 500
+
+# Radius to consider for the circle around each sampled point
+R <- 5
 ```
@@
 # Dataframe containing all coordinates of n randomly chosen points
-random_points <- data.frame(x = rep(0, n), y = rep(0, n))
+# Uniform sampling over the whole territory
+random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
+```
+
+# Creating other samples based on the previous one
+
+```{r}
+f_boot <- function(df_sample, B){
+  # df_sample: original sample; B: number of bootstrap samples made thanks to df_sample
+  df_boot <- tibble(.rows = nrow(df_sample))
+  col_names <- c()
+  for (b in 1:B) {
+    col_ <- paste("ech", b, sep = "")
+    nb <- sample(1:nrow(df_sample), nrow(df_sample), replace = TRUE)
+    sample_b <- df_sample[nb,]
+    df_boot <- df_boot %>% add_column(b = sample_b)
+    col_names <- append(col_names, col_)
+    colnames(df_boot) <- col_names
+  }
+  return(do.call(data.frame, df_boot))
+  # as.data.frame(df_boot)
+  # Return a data frame with B samples of 2 variables and of size n
+}
+```
+do.call(data.frame, df)
+```{r}
+# Making of bootstrap samples
+df_boot <- f_boot(random_points, B)
+
+# res[(res$ech1$x == res$ech1$x[1]),]
+# res[(res$ech2$x == res$ech1$x[1]),]
+# Gives the same pair
+
+# res[(res$ech2$x == res$ech2$x[14]),]
+# Gives 1 repeated pair twice for the same sample b = 2
 ```
@@
 ```{r}
-# Uniform sampling over the whole territory
-random_points$x <- runif(n, 0, 1000)
-random_points$y <- runif(n, 0, 1000)
+# Try to do bootstrap, success
+# test <- data.frame(col = c(1:3))
+# res <- f_boot(test, 3)
 ```
 
-# Creating another sample based on the previous one
+```{r}
+# Function to check if a point is inside a circle (indicator variable)
+is_point_in_circle <- function(x, y, h, k, R) {
+  # Calculate the squared distance between the point and the center of the circle
+  squared_distance <- (x - h)^2 + (y - k)^2
+  # Check if the squared distance is less than or equal to the squared radius
+  return(as.numeric(squared_distance <= R^2))
+}
+```
 
 ```{r}
-# Draft
-for (point in 1:n) {
-  random_points$x
+circle <- function(x1, x2, R){
+  # Produces a local variable based on 2 coordinates (x1, x2) and a radius (R)
+
+  # Preliminary: area of the zone of interest
+  source("~/work/Sim_article2024/Inc_area.R")
+
+  # Intermediary step: which trees are inside the circle?
+  trees_in <- data.frame(useless = rep(0,30942))
+  val <- is_point_in_circle(x1, x2, trees$x, trees$y, R)
+  trees_in <- trees_in %>% add_column("new_col" = val)
+  trees_in[1] <- NULL
+
+  # Creation of the local variable
+  local_var <- sum(trees_in["new_col" != 0,]/inc_area(c(x1, x2),0,0,1000,1000,R))
+  return(local_var) # A single number
 }
+```
+
+```{r}
+test <- circle(500,500,10)
+```
+
+```{r}
+rho_boot <- tibble(.rows = n)
+#  data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
+col_names <- c()
+for (c in 1:B) {
+  col_ <- paste("est", c, sep = "")
+  # ech_ <- paste("ech", c, sep = "")
+  # assign(ech_, df_boot[c])
+  a <- c()
+  for (i in 1:n) {
+      a <- append(a, circle(df_boot[i, (2*c)-1], df_boot[i, 2*c], R))
+    }
+  # a <- circle(df_boot[(2*c)-1], df_boot[2*c], R)
+  # print(col_)
+  rho_boot <- rho_boot %>% add_column(col_ = a) # 
+  col_names <- append(col_names, col_)
+  colnames(rho_boot) <- col_names
+}
+# rho_MC$x.1 <- NULL
+# rho_MC$y.1 <- NULL
+colnames(rho_boot) <- col_names
+
+# 3rd step: List of estimated totals thus obtained from each sample
+est_boot <- c()
+for (c in 1:B) {
+  est_tot <- sum((rho_boot[c])/p)
+  est_boot <- append(est_boot, est_tot)
+}
+
+est_boot <- sort(est_boot)
+```
+
+```{r}
+rm(a, c, i, col_names, col_)
+```
+
+```{r}
+# Confidence Interval based on the percent approach
+lim_inf <- est_boot[floor(B*2.5/100)]
+lim_sup <- est_boot[B - floor(B*2.5/100)]
+cat("Un intervalle de confiance à 95% par la méthode des percentiles est : [", lim_inf, ";", lim_sup, "]" )
+```
+
+```{r}
+# Same result with function?
+boot.ci(rho_boot, type = "perc")
+# Doesn't work (df_boot, est_boot, rho_boot)
 ```
@@
 ```{r}
-circle <- function(x1, x2, R){
-  # Produces a local variable based on 2 coordinates (x1, x2) and a radius (R)
-
-  # Intermediary step: which trees are inside the circle?
-  trees_in <- data.frame(useless = rep(0,30942))
-  val <- is_point_in_circle(x1, x2, trees$x, trees$y, R)
-  trees_in <- trees_in %>% add_column(new_col = val)
-  trees_in[1] <- NULL
-
-  # Creation of the local variable
-  local_var <- sum(trees_in[new_col != 0,]/area_circle)
-  return(local_var) # A single number
-}
-```
-
-```{r}
-f_boot <- function(sample){
-
-}
-```
-
-```{r}
 # xdata <- matrix(rnorm(30),ncol=2)

### 2024-07-01 No_tree_no_grid.Rmd
Lendemain d'élection

@@
   col_ <- paste("est", c, sep = "")
-  # With normalized ratio
+  # With f_x
   a <- f_x(series_MC[(2*c)-1],series_MC[2*c])

### 2024-07-01 Bootstrap.Rmd
Lundi soir

@@
 library(readxl) # to read the initial file
-library(data.table) # for shift
 library(magrittr) # for pipes
@@
 # Function to check if a point is inside a circle (indicator variable)
+source("~/work/Sim_article2024/Circle.R")
+
+# Function to check if a point is inside a circle (indicator variable)
 is_point_in_circle <- function(x, y, h, k, R) {
@@
 ```{r}
-circle <- function(x1, x2, R){
+circle <- function(x1, x2, R = 5){
   # Produces a local variable based on 2 coordinates (x1, x2) and a radius (R)
@@
 ```{r}
-# Confidence Interval based on the percent approach
+# Confidence Interval based on the percentile approach
 lim_inf <- est_boot[floor(B*2.5/100)]
@@
 cat("Un intervalle de confiance à 95% par la méthode des percentiles est : [", lim_inf, ";", lim_sup, "]" )
+```
+
+```{r}
+rho_init <- tibble(.rows = n)
+# col_names <- c()
+# for (c in 1:B) {
+#   col_ <- paste("est", c, sep = "")
+  # ech_ <- paste("ech", c, sep = "")
+  # assign(ech_, df_boot[c])
+  a <- c()
+  for (i in 1:n) {
+      a <- append(a, circle(random_points[i, 1], random_points[i, 2], R))
+    }
+  # a <- circle(df_boot[(2*c)-1], df_boot[2*c], R)
+  # print(col_)
+  rho_init <- rho_init %>% add_column("ech_init" = a) # 
+  # col_names <- append(col_names, col_)
+  # colnames(rho_boot) <- col_names
+# }
+
+# colnames(rho_boot) <- "ech_init"
+
+# 3rd step: List of estimated totals thus obtained from each sample
+est_init <- c()
+
+est_tot <- sum((rho_init[1])/p)
+est_init <- append(est_init, est_tot)
+
+est_init <- sort(est_init)
+```
+
+```{r}
+# Confidence Interval based on the reverse percentile approach
+cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]" )
 ```
@@
 ```{r}
-res_boot <- boot(data=random_points, statistic=rho, R=10)
+res_boot <- boot(data=random_points, statistic=circle)
 res_boot
+# Doesn't work
 ```

### 2024-07-01 No_tree_no_grid.Rmd
Lundi soir

@@
 p
+# p may be considered simply as a numeric
+# since the inclusion density function is constant in this case
+# Otherwise, we would need a vector
 ```
@@
 
+We are looking for estimates of totals over the whole territory, i.e. double integrals of some functions.
+To make such estimations, we begin with one single sample (made by uniform sampling).
+
 ## Creating one sample
@@
 ```{r}
-# Dataframe containing all coordinates of n randomly chosen points
+# Dataframe to contain all coordinates of n randomly chosen points in a 1000x1000 square
 random_points <- data.frame(x = rep(0, n), y = rep(0, n))
@@
 ## The most simple function
-fun1 <- function(x,y){
+f_1 <- function(x,y){
   1
@@
 random_points$rho1 <- rep(1, n)
-# Formula given in Cordy (1993), page 3
 ```
@@
 # Estimated value
+# Formula given in Cordy (1993), page 3
 est_area <- sum((random_points$rho1)/p) 
 # Equal to 1e+06 whatever the chosen points
+```
+
+```{r}
+# Conclusion
+cat("Total à estimer :", area, "\nEstimation :", est_area)
 ```
@@
 est_ind <- sum((random_points$rho2)/p)
-est_ind
 # 510000 e.g.
+```
+
+```{r}
+# Conclusion
+cat("Total à estimer :", half_area, "\nEstimation :", est_ind)
 ```
@@
 # Estimated value
-est_x <- sum((random_points$x)/p) # = 
-est_x
+est_x <- sum((random_points$x)/p)
 # 499690876 e.g.
+```
+
+```{r}
+# Conclusion
+cat("Total à estimer :", val_x, "\nEstimation :", est_x)
 ```
@@
 
-Variance formula for the uniform case is based on the formula given by Cordy (1993), theorem 2 page 5 combined with the inclusion density given for example 1 page 4, which gives a simplified formula for this particular case.
+Variance formulas for the uniform case are based on the formulas given by Cordy (1993), theorem 2 page 5 combined with the inclusion density given for example 1 page 4, which gives a simplified formula for this particular case.
 
@@
 ```{r}
-var_area <- est_carre/p - (1/n)*(est_area^2)
-var_area
+var_area <- ((1000*1000)/(n-1))*est_carre - (1/(n-1))*(est_area^2)
 # The empirical variance is null as expected
@@
 ```{r}
-# fun1(x,y)^2 = fun1(x,y)
-varTH_area <- area/p - (1/n)*(area^2)
-varTH_area
+# f_1(x,y)^2 = f_1(x,y)
+varTHEO_area <- area/p - (1/n)*(area^2)
 # The theoretical variance is null as expected
 # Since the total is equal to the area
+```
+
+```{r}
+# Conclusion
+cat("Variance théorique :", varTHEO_area, "\nVariance empirique :", var_area)
 ```
@@
 ```{r}
-var_ind <- est_ind/p - (1/n)*(est_ind^2)
-var_ind
-# Empirical variance: 2.491e+09 (huge)
+var_ind <- ((1000*1000)/(n-1))*est_ind - (1/(n-1))*(est_ind^2)
+# Empirical variance: 2.491e+09 e.g.
 ```
@@
 # f_ind(x,y)^2 = f_ind(x,y)
-varTH_ind <- half_area/p - (1/n)*(half_area^2)
-varTH_ind
+varTHEO_ind <- half_area/p - (1/n)*(half_area^2)
 # Theoretical variance: 2.5e+09, i.e. around 2.498e+09
-# Close to the empirical one: great
+# Close to the empirical one
+```
+
+```{r}
+# Conclusion
+cat("Variance théorique :", varTHEO_ind, "\nVariance empirique :", var_ind)
 ```
@@
 ```{r}
+# Value to estimate for this new function
+val_x2 <- (10^12)/3
 # Estimated value
 est_x2 <- sum(((random_points$x)^2)/p)
-est_x2
 # 499690876 e.g.
@@
 ```{r}
-var_x <- est_x2/p - (1/n)*(est_x^2)
-var_x
+var_x <- ((1000*1000)/(n-1))*est_x2 - (1/(n-1))*(est_x^2)
 # Empirical variance: 8.407871e+14 ?!
@@
 # f_ind(x,y)^2 = f_ind(x,y)
-# varTH_x <- integral2(f_x, 0, 1000, 0, 1000)$Q/p - (1/n)*(integral2(f_x, 0, 1000, 0, 1000)$Q^2)
-# varTH_x
-# Theoretical variance: 2498391345, i.e. around 2.498e+09
-# Close to the empirical one: great
+varTHEO_x <- val_x2/p - (1/n)*(val_x^2)
+# Theoretical variance: 2.5e+09, i.e. around 2.498e+09
+# Close to the empirical one
+```
+
+```{r}
+# Conclusion
+cat("Variance théorique :", varTHEO_x, "\nVariance empirique :", var_x)
 ```
@@
   a2 <- runif(n, 0, 1000)
-  # series_MC$x <- runif(n, 0, 1000)
-  # series_MC$y <- runif(n, 0, 1000)
-  # append()
   series_MC <- series_MC %>% add_column(x = a1, y = a2)
@@
 colnames(series_MC) <- col_names
+```
+
+```{r}
+rm(a1, a2, x, y, b, col_, col_names) # Useless now
 ```
@@
 ```{r}
+rm(a, c, col_, col_names) # Useless now
+```
+
+```{r}
 # List of estimated totals thus obtained from each sample
@@
 ```{r}
+rm(c, est_tot) # Useless now
+```
+
+```{r}
 # Empirical mean based on MC
-mean(est_MC) # should be close to 5e+08
+cat("Total à estimer :", val_x, "\nMoyenne des estimations obtenues :", mean(est_MC)) 
+# should be close to 5e+08
 # 499121662 e.g.
@@
 # Empirical standard deviation based on MC
-sd(est_MC)
+cat("Variance associée aux échantillons de Monte Carlo :", sd(est_MC))
+# 28710306 e.g.
 ```
@@
 
-true_vs_MC <- function(n, B, f, true_value){
-  # n: sample size; B: number of iterations for MC; f: function to consider (with 2 variables, x and y)
+true_vs_MC <- function(n, B, f){
+  # n: sample size; B: number of iterations for MC; 
+  # f: function to consider (with 2 variables, x and y)
   p <- sum(rep((1/1000)*(1/1000), n))
@@
   # 2nd step: creating the values corresponding to the function
-  rho_MC <- data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
+  rho_MC <- tibble(.rows = n)
+    # data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
   col_names <- c()
@@
     col_names <- append(col_names, col_)
+    colnames(rho_MC) <- col_names
   }
-  rho_MC$x.1 <- NULL
-  rho_MC$y.1 <- NULL
+  # rho_MC$x.1 <- NULL
+  # rho_MC$y.1 <- NULL
   colnames(rho_MC) <- col_names
@@
   for (c in 1:B) {
-    est_tot <- sum((rho_MC[c])/p)
-    est_MC <- append(est_MC, est_tot)
+    est_MC <- append(est_MC, sum((rho_MC[c])/p))
   }
@@
   est_value <- mean(est_MC) # Estimated value
-  return(c(true_value, est_value))
+  return(est_value)
 }
@@
 ```{r}
-res <- true_vs_MC(n = 1000, B = 1000, f = fun1, true_value = 1e+06)
-cat("True integral:", res[1], "\nMean of all the estimations:", res[2])
-# 1e+06 1e+06 (Equality = great)
+res <- true_vs_MC(n = 1000, B = 1000, f = f_1)
+cat("True integral:", 1e+06, "\nMean of all the estimations:", res)
+# 1e+06 1e+06 (Equality as always)
 ```
@@
 ```{r}
-res <- true_vs_MC(n = 1000, B = 1000, f = f_ind, true_value = 500000)
-cat("True integral:", res[1], "\nMean of all the estimations:", res[2])
+res <- true_vs_MC(n = 1000, B = 1000, f = f_ind)
+cat("True integral:", 500000, "\nMean of all the estimations:", res)
+
+# Ex:
 # True integral: 5e+05
@@
 ```{r}
-res <- true_vs_MC(n = 1000, B = 1000, f = f_x, true_value = 5e+08)
-cat("True integral:", res[1], "\nMean of all the estimations:", res[2])
+res <- true_vs_MC(n = 1000, B = 1000, f = f_x)
+cat("True integral:", 5e+08, "\nMean of all the estimations:", res)
 
-#True integral: 5e+08
+# Ex:
+# True integral: 5e+08
 # Mean of all the estimations: 500189987

### 2024-07-01 Trees_no_grid.Rmd
Lundi soir

@@
 ```{r}
-install.packages("pracma") # double integral
 install.packages("boot") # for bootstrap
+```
+
+```{r}
 library(readxl) # to read the initial file
-library(data.table) # for shift
-library(pracma)
 library(magrittr) # for pipes
@@
 n <- 100
-```
 
-```{r}
 # Radius
 R <- 5
-```
 
-```{r}
-# Marginal density: density of the uniform distribution over 1:1000
-# Which leads us to the inclusion density function
+# Inclusion density function
 p <- sum(rep((1/1000)*(1/1000), n))
@@
 
-A sample is created by uniformly sampling the whole territory except the edge, which depends on the radius (to facilitate the calculation of the local variable).
+A sample is created by uniformly sampling the whole territory.
 
@@
 # Dataframe containing all coordinates of n randomly chosen points
-random_points <- data.frame(x = rep(0, n), y = rep(0, n))
-```
-
-```{r}
-# Uniform sampling over the whole territory except the edge
-random_points$x <- runif(n, 0, 1000)
-random_points$y <- runif(n, 0, 1000)
+# Uniform sampling over the whole territory 
+random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
 ```
@@
 # The value is 1 if the tree corresponding is inside the circle
-trees_in <- data.frame(useless = rep(0,30942))
+trees_in <- tibble(.rows = nrow(trees))
 col_names <- c()
@@
   b <- random_points[point,]$y
-  val <- is_point_in_circle(a, b, trees$x, trees$y, R) #*point
+  val <- is_point_in_circle(a, b, trees$x, trees$y, R)
   trees_in <- trees_in %>% add_column(new_col = val)
   col_names <- append(col_names, new_col)
+  colnames(trees_in) <- col_names
 }
-trees_in[1] <- NULL
 colnames(trees_in) <- col_names
@@
 ```{r}
-# Creating a local variable (pages 10-11 in Trinh et alii (2024))
+# Creating a local variable (cf pages 10-11 in Trinh et alii (2024))
 local_var <- c()
@@
     y <- paste("y", b, sep = "")
-    # Uniform sampling over the whole territory except the edge
+    # Uniform sampling over the whole territory
     a1 <- runif(n, 0, 1000)
@@
   # Based on each sampled pair in all samples
-  rho_MC <- data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
+  rho_MC <- tibble(.rows = n)
+    # data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
   col_names <- c()
@@
   }
-  rho_MC$x.1 <- NULL
-  rho_MC$y.1 <- NULL
+  # rho_MC$x.1 <- NULL
+  # rho_MC$y.1 <- NULL
   colnames(rho_MC) <- col_names

### 2024-07-01 Circle.R

@@ -1,0 +1,26 @@
+##### Functions to look for trees inside a circle --------
+
+# Function to check if a point is inside a circle (indicator variable)
+is_point_in_circle <- function(x, y, h, k, R) {
+  # Calculate the squared distance between the point and the center of the circle
+  squared_distance <- (x - h)^2 + (y - k)^2
+  # Check if the squared distance is less than or equal to the squared radius
+  return(as.numeric(squared_distance <= R^2))
+}
+
+# Function to produce a local variable
+circle <- function(x1, x2, R){
+  # 2 coordinates (x1, x2) and a radius (R)
+  
+  # Intermediary step: which trees are inside the circle?
+  trees_in <- data.frame(useless = rep(0,30942))
+  new_col <- "in_or_out"
+  val <- is_point_in_circle(x1, x2, trees$x, trees$y, R)
+  trees_in <- trees_in %>% add_column(new_col = val)
+  trees_in[1] <- NULL
+  
+  # Creation of the local variable
+  local_var <- sum(trees_in[new_col != 0,]/inc_area(c(x1, x2),0,0,1000,1000,R))
+  return(local_var) # A single number
+}
+

### 2024-07-01 Draft_fun.R

@@ -11,5 +11,16 @@ fun_ind <- function(x,y){
   as.numeric(x > y)
 }
 
+install.packages("pracma") # double integral
+library(pracma)
+library(data.table) # for shift
+
 test <- integral2(fun_ind, 0, 1000, 0, 1000)$Q 
 # 509148 if x >= y; 487316.7 if x > y
+
+
+# f_ind(x,y)^2 = f_ind(x,y)
+# varTHEO_x <- integral2(f_x, 0, 1000, 0, 1000)$Q/p - (1/n)*(integral2(f_x, 0, 1000, 0, 1000)$Q^2)
+# varTHEO_x
+# Theoretical variance: 2498391345, i.e. around 2.498e+09
+# Close to the empirical one: great

### 2024-07-02 Bootstrap.Rmd
Mardi midi

--- 2024-06-27 Bootstrap.Rmd
@@
 
-We do not need the artificial forest for now. We just need a virtual 1000x1000 square.
+((We do not need the artificial forest for now. We just need a virtual 1000x1000 square.))
 
 ```{r}
-# Sample size
-n <- 100
+# Importing the database with the artificial forest
+trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
 ```
@@
 ```{r}
+### Constant values
+
+# Sample size
+n <- 100
+
 # Marginal density: density of the uniform distribution over 1:1000
@@
 # Dataframe containing all coordinates of n randomly chosen points
-random_points <- data.frame(x = rep(0, n), y = rep(0, n))
+# Uniform sampling over the whole territory
+random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
+```
+
+# Creating other samples based on the previous one
+
+```{r}
+f_boot <- function(df_sample, B){
+  # df_sample: original sample; B: number of bootstrap samples made thanks to df_sample
+
+  df_boot <- tibble(.rows = nrow(df_sample))
+  for (b in 1:B) {
+    nb <- sample(1:nrow(df_sample), nrow(df_sample), replace = TRUE)
+    sample_b <- df_sample[nb,]
+    df_boot <- df_boot %>% add_column(new_col = sample_b)
+    colnames(df_boot)[b] <- paste("ech", b, sep = "")
+  }
+  return(do.call(data.frame, df_boot))
+  # Return a data frame with B samples of 2 variables and of size n
+}
 ```
@@
 ```{r}
-# Uniform sampling over the whole territory
-random_points$x <- runif(n, 0, 1000)
-random_points$y <- runif(n, 0, 1000)
+# Making of bootstrap samples
+df_boot <- f_boot(random_points, B)
 ```
 
-# Creating another sample based on the previous one
+```{r}
+# Function to produce a local variable
+source("~/work/Sim_article2024/Useful_functions/Circle.R")
+```
 
 ```{r}
-# Draft
-for (point in 1:n) {
-  random_points$x
+rho_boot <- tibble(.rows = n)
+for (c in 1:B) {
+  # assign(ech_, df_boot[c])
+  a <- c()
+  for (i in 1:n) {
+    a <- append(a, circle_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], R))
   }
+  rho_boot <- rho_boot %>% add_column(new_col = a)
+  colnames(rho_boot)[c] <- paste("est", c, sep = "")
+}
+
+# List of estimated totals thus obtained from each sample
+est_boot <- c()
+for (c in 1:B) {
+  est_boot <- append(est_boot, sum((rho_boot[c])/p))
+}
+
+est_boot <- sort(est_boot)
+```
+
+```{r}
+rm(a, c, i, col_names, col_)
+```
+
+```{r}
+# Confidence Interval based on the percentile approach
+lim_inf <- est_boot[floor(B*2.5/100)]
+lim_sup <- est_boot[B - floor(B*2.5/100)]
+cat("Un intervalle de confiance à 95% par la méthode des percentiles est : [", lim_inf, ";", lim_sup, "]" )
+```
+
+```{r}
+rho_init <- tibble(.rows = n)
+# col_names <- c()
+# for (c in 1:B) {
+#   col_ <- paste("est", c, sep = "")
+  # ech_ <- paste("ech", c, sep = "")
+  # assign(ech_, df_boot[c])
+  a <- c()
+  for (i in 1:n) {
+    # loc_var <- 
+    a <- append(a, circle_nb(random_points[i, 1], random_points[i, 2], R))
+    }
+  # a <- circle(df_boot[(2*c)-1], df_boot[2*c], R)
+  # print(col_)
+  rho_init <- rho_init %>% add_column("ech_init" = a) # 
+  # col_names <- append(col_names, col_)
+  # colnames(rho_boot) <- col_names
+# }
+
+# colnames(rho_boot) <- "ech_init"
+
+# 3rd step: List of estimated totals thus obtained from each sample
+est_init <- c()
+
+est_tot <- sum((rho_init[1])/p)
+est_init <- append(est_init, est_tot)
+
+est_init <- sort(est_init)
+```
+
+```{r}
+# Confidence Interval based on the reverse percentile approach
+cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]" )
+```
+
+```{r}
+# Same result with function?
+boot.ci(rho_boot, type = "perc")
+# Doesn't work (df_boot, est_boot, rho_boot)
 ```
@@
 ```{r}
-res_boot <- boot(data=random_points, statistic=rho, R=10)
+res_boot <- boot(data=random_points, statistic=circle_nb)
 res_boot
+# Doesn't work
 ```
@@
     a <- append(a, circle(xdata[i,1], xdata[i,2], R))
+    # Change: circle_nb!!!
   }
@@
 ```
+
+```{r}
+
+```
+
+```{r}
+
+```

### 2024-07-02 Draft.Rmd
Mardi midi

@@
 ```
+
+## Circle
+
+# Circle2
+
+```{r}
+  # list_trees <- c()
+  # for (plant in 1:nrow(trees)) {
+  #   if (is_point_in_circle(x1, x2, trees[plant, 1], trees[plant, 2], R)){
+  #     list_trees <- append(list_trees, plant)
+  #   }
+
+  # }
+```
+
+## Draft for bootstrap
+
+```{r}
+# res[(res$ech1$x == res$ech1$x[1]),]
+# res[(res$ech2$x == res$ech1$x[1]),]
+# Gives the same pair
+
+# res[(res$ech2$x == res$ech2$x[14]),]
+# Gives 1 repeated pair twice for the same sample b = 2
+```
+
+```{r}
+# Try to do bootstrap, success
+# test <- data.frame(col = c(1:3))
+# res <- f_boot(test, 3)
+```

### 2024-07-02 Trees_no_grid.Rmd
Mardi midi

@@
 ```{r}
-install.packages("boot") # for bootstrap
-```
-
-```{r}
 library(readxl) # to read the initial file
 library(magrittr) # for pipes
-library(tibble) # for add_column
-library(boot)
+library(tibble) # for add_column and tibble
 ```
@@
 local_var <- c()
-source("~/work/Sim_article2024/Inc_area.R")
+source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
 for (placette in 1:n) {

### 2024-07-02 Circle.R

@@ -1,26 +1,0 @@
-##### Functions to look for trees inside a circle --------
-
-# Function to check if a point is inside a circle (indicator variable)
-is_point_in_circle <- function(x, y, h, k, R) {
-  # Calculate the squared distance between the point and the center of the circle
-  squared_distance <- (x - h)^2 + (y - k)^2
-  # Check if the squared distance is less than or equal to the squared radius
-  return(as.numeric(squared_distance <= R^2))
-}
-
-# Function to produce a local variable
-circle <- function(x1, x2, R){
-  # 2 coordinates (x1, x2) and a radius (R)
-  
-  # Intermediary step: which trees are inside the circle?
-  trees_in <- data.frame(useless = rep(0,30942))
-  new_col <- "in_or_out"
-  val <- is_point_in_circle(x1, x2, trees$x, trees$y, R)
-  trees_in <- trees_in %>% add_column(new_col = val)
-  trees_in[1] <- NULL
-  
-  # Creation of the local variable
-  local_var <- sum(trees_in[new_col != 0,]/inc_area(c(x1, x2),0,0,1000,1000,R))
-  return(local_var) # A single number
-}
-

### 2024-07-02 Circle_draft.R

@@ -1,0 +1,110 @@
+##### Functions to look for trees inside a circle --------
+
+### Importing the database with the artificial forest
+trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
+
+### With 2 steps -----
+
+### Function to check if a point is inside a circle (indicator variable)
+is_point_in_circle <- function(x, y, h, k, R) {
+  # Calculate the squared distance between the point and the center of the circle
+  squared_distance <- (x - h)^2 + (y - k)^2
+  # Check if the squared distance is less than or equal to the squared radius
+  return(as.numeric(squared_distance <= R^2))
+}
+
+### Function to produce a local variable
+circle <- function(x1, x2, R){
+  # 2 coordinates (x1, x2) and a radius (R)
+  
+  # Preliminary: area of the zone of interest
+  source("~/work/Sim_article2024/Inc_area.R")
+  
+  # Intermediary step: which trees are inside the circle?
+  trees_in <- tibble(.rows = nrow(trees))
+  val <- is_point_in_circle(x1, x2, trees$x, trees$y, R)
+  trees_in <- trees_in %>% add_column("in_or_out" = val)
+  
+  # Creation of the local variable
+  local_var <- sum(trees_in["in_or_out" != 0,]/inc_area(c(x1, x2),0,0,1000,1000,R))
+  return(local_var) # A single number
+}
+
+# Ex: circle(500,500,5)
+# 0.07639437
+
+### With less computational power needed (I hope) -----
+
+# Idea: instead of keeping 1 and 0 for all the trees, just keep the identifier of trees that would have 1
+
+is_point_in_circle <- function(x, y, h, k, R) {
+  # Calculate the squared distance between the point and the center of the circle
+  squared_distance <- (x - h)^2 + (y - k)^2
+  # Check if the squared distance is less than or equal to the squared radius
+  return(as.numeric(squared_distance <= R^2))
+}
+
+circle2 <- function(x1, x2, R){
+  # 2 coordinates (x1, x2) and a radius (R)
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  list_trees <- which(is_point_in_circle(x1, x2, trees$x, trees$y, R) == 1)
[…]

### 2024-07-02 Useful_functions/Circle.R

@@ -1,0 +1,17 @@
+### Functions to produce local variables based on circles -----
+
+## Function to produce the local variable for the number of trees
+circle_nb <- function(x1, x2, R){
+  # 2 coordinates (x1, x2) and a radius (R)
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  list_trees <- which((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2)
+  local_var <- sum(length(list_trees)/inc_area(c(x1, x2),0,0,1000,1000,R))
+  return(local_var)
+  # list_trees: identifiers of targeted trees; local_var: local variable based on the number of trees
+}
+
+## Function to produce the local variable for the volume of trees
+# circle_vol <- function(x1, x2, R){}

### 2024-07-02 Bootstrap.Rmd
Before leaving ENSAI

@@
 trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
+```
+
+```{r}
+# Functions to produce a local variable
+source("~/work/Sim_article2024/Useful_functions/Circle.R")
 ```
@@
 
-```{r}
-# Function to produce a local variable
-source("~/work/Sim_article2024/Useful_functions/Circle.R")
-```
+# Estimations and confidence intervals based on the bootstrap samples
+
+## With one single circle
 
 ```{r}
-rho_boot <- tibble(.rows = n)
+# Estimation of the total number of trees for each bootstrap sample
+est_boot <- c()
 for (c in 1:B) {
-  # assign(ech_, df_boot[c])
   a <- c()
@@
   }
-  rho_boot <- rho_boot %>% add_column(new_col = a)
-  colnames(rho_boot)[c] <- paste("est", c, sep = "")
+  est_boot <- append(est_boot, sum(a/p))
 }
-
-# List of estimated totals thus obtained from each sample
-est_boot <- c()
-for (c in 1:B) {
-  est_boot <- append(est_boot, sum((rho_boot[c])/p))
-}
-
 est_boot <- sort(est_boot)
@@
 ```{r}
-rm(a, c, i, col_names, col_)
+rm(a, c, i)
 ```
@@
 ```{r}
-rho_init <- tibble(.rows = n)
-# col_names <- c()
-# for (c in 1:B) {
-#   col_ <- paste("est", c, sep = "")
-  # ech_ <- paste("ech", c, sep = "")
-  # assign(ech_, df_boot[c])
 a <- c()
 for (i in 1:n) {
-    # loc_var <- 
   a <- append(a, circle_nb(random_points[i, 1], random_points[i, 2], R))
 }
-  # a <- circle(df_boot[(2*c)-1], df_boot[2*c], R)
-  # print(col_)
-  rho_init <- rho_init %>% add_column("ech_init" = a) # 
-  # col_names <- append(col_names, col_)
-  # colnames(rho_boot) <- col_names
-# }
 
-# colnames(rho_boot) <- "ech_init"
+# Estimated total thus obtained from the initial sample
+est_init <- sum(a/p)
 
-# 3rd step: List of estimated totals thus obtained from each sample
-est_init <- c()
-
-est_tot <- sum((rho_init[1])/p)
-est_init <- append(est_init, est_tot)
-
-est_init <- sort(est_init)
 ```
@@
 cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]" )
+```
+
+## With three circles
+
+```{r}
+### With 3 circles as described in Trinh et alii (2024), page 8
+
+est_boot_3 <- c()
+for (c in 1:B) {
+  a <- c()
+  for (i in 1:n) {
+    a <- append(a, circle3_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], 15, 9, 6))
+  }
+  est_boot_3 <- append(est_boot_3, sum(a/p))
+}
+
+est_boot_3 <- sort(est_boot_3)
+
+```
+
+```{r}
+# Confidence Interval based on the percentile approach
+lim_inf <- est_boot_3[floor(B*2.5/100)]
+lim_sup <- est_boot_3[B - floor(B*2.5/100)]
+cat("Un intervalle de confiance à 95% par la méthode des percentiles est : [", lim_inf, ";", lim_sup, "]" )
+```
+
+```{r}
+a <- c()
+for (i in 1:n) {
+  a <- append(a, circle3_nb(random_points[i, 1], random_points[i, 2], 15, 9, 6))
+}
+
+# Estimated total thus obtained from the initial sample
+est_init_3 <- sum(a/p)
+
+```
+
+```{r}
+# Confidence Interval based on the reverse percentile approach
+cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : [", est_init_3*2 - lim_sup, ";", est_init_3*2 - lim_inf, "]" )
+```
+
+```{r}
+est_boot3 <- c()
+for (c in 1:B) {
+  a <- c()
+  for (i in 1:n) {
+    a <- append(a, circle_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], 15))
+  }
+  est_boot3 <- append(est_boot3, sum(a/p))
+}
+
+est_boot3 <- sort(est_boot3)
+
 ```
@@
 ```
+
+```{r}
+
+```

### 2024-07-02 Draft.Rmd
Before leaving ENSAI

@@
 ```
+
+```{r}
+# To evaluate complexity
+install.packages("cyclocomp")
+```
+
+```{r}
+library(cyclocomp)
+```
+
+```{r}
+cyclocomp(circle_nb) # 1
+```
+
+```{r}
+# Probably less efficient than the version actually used in Bootstrap.Rmd
+start.time <- Sys.time()
+
+rho_boot <- tibble(.rows = n)
+for (c in 1:B) {
+  # assign(ech_, df_boot[c])
+  a <- c()
+  for (i in 1:n) {
+    a <- append(a, circle_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], R))
+  }
+  rho_boot <- rho_boot %>% add_column(new_col = a)
+  colnames(rho_boot)[c] <- paste("est", c, sep = "")
+}
+
+# List of estimated totals thus obtained from each sample
+est_boot <- c()
+for (c in 1:B) {
+  est_boot <- append(est_boot, sum((rho_boot[c])/p))
+}
+
+est_boot <- sort(est_boot)
+
+end.time <- Sys.time()
+time.taken1 <- end.time - start.time
+
+time.taken1
+
+# Time difference of 52.57304 secs
+# Time difference of 52.57391 secs
+# Time difference of 54.01066 secs
+```
+
+```{r}
+### More efficient??? Slower than the above version
+
+start.time <- Sys.time()
+
+rho_boot <- tibble(.rows = n)
+for (c in 1:B) {
+  # assign(ech_, df_boot[c])
+  a <- c()
+  for (i in 1:n) {
+    if(circle_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], R) != 0){
+    a <- append(a, circle_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], R))
+    }
+  }
+  a2 <- append(a, rep(0, n-length(a)))
+  rho_boot <- rho_boot %>% add_column(new_col = a2)
+  colnames(rho_boot)[c] <- paste("est", c, sep = "")
+}
+
+# List of estimated totals thus obtained from each sample
+est_boot2 <- c()
+for (c in 1:B) {
+  est_boot2 <- append(est_boot2, sum((rho_boot[c])/p))
+}
+
+est_boot2 <- sort(est_boot2)
+
+end.time <- Sys.time()
+time.taken2 <- end.time - start.time
+
+time.taken2
+
+# Idea: "a" is sparse: let's simplify by shortening it
+# Time difference of 1.526216 mins :(
+# Modif: still not good
+# Time difference of 1.45528 mins
+
+# That one works (and still too long)
+# Time difference of 1.126081 mins
+# Time difference of 1.094733 mins
+```
+
+```{r}
+# For the version actually used in Bootstrap.Rmd
+start.time <- Sys.time()
+
+end.time <- Sys.time()
+time.taken3 <- end.time - start.time
+
+time.taken3
+
+# Time difference of 54.02127 secs
+# Time difference of 50.4839 secs
+# Time difference of 53.94593 secs
+```

### 2024-07-02 Circle_draft.R

@@ -107,4 +107,6 @@ time.taken3 <- end.time - start.time
 # Attention: Inc_area.R !!!
 # Time difference of 0.005484343 secs
 
+### Cyclomatic complexity?
+# cyclocomp(circle) # 1
 

### 2024-07-02 Useful_functions/Circle.R

@@ -15,3 +15,25 @@ circle_nb <- function(x1, x2, R){
 
 ## Function to produce the local variable for the volume of trees
 # circle_vol <- function(x1, x2, R){}
+
+## Function to produce the local variable for the number of trees with 3 circle
+circle3_nb <- function(x1, x2, R1, R2, R3){
+  # 2 coordinates (x1, x2) and 3 radii (R1 > R2 > R3)
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  list_trees <- trees[(x1 - trees$x)^2 + (x2 - trees$y)^2 <= R1^2,] # List with all trees inside the biggest circle
+  
+  list_trees1 <- list_trees[(pi*list_trees$d130 > 117.5),] # List with the biggest trees
+  list_trees2 <- list_trees[(pi*list_trees$d130 < 117.5) & (pi*list_trees$d130 > 70.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R2^2),] # medium trees
+  list_trees3 <- list_trees[(pi*list_trees$d130 > 23.5) & (pi*list_trees$d130 < 70.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R3^2),] # smallest trees
+  
+  local_var1 <- sum(nrow(list_trees1)/inc_area(c(x1, x2),0,0,1000,1000,R1)) # Local variable for the biggest circle and the biggest trees
+  local_var2 <- sum(nrow(list_trees2)/inc_area(c(x1, x2),0,0,1000,1000,R2)) # Local variable for the medium circle and the medium trees
+  local_var3 <- sum(nrow(list_trees3)/inc_area(c(x1, x2),0,0,1000,1000,R3)) # Local variable for the smallest circle and the smallest trees
+  local_var <- (local_var1 + local_var2 + local_var3) # Addition of the previous local variables
+  return(local_var)
+  # local_var: local variable based on the number of trees
+}
+

### 2024-07-03 Bootstrap.Rmd
Try BCa CI

@@
 ```{r}
-# Confidence Interval based on the percentile approach
+# Confidence interval based on the percentile approach
 lim_inf <- est_boot[floor(B*2.5/100)]
@@
 ```{r}
+# Target: the initial sample alone
 a <- c()
@@
 est_init <- sum(a/p)
-
 ```
@@
 ```{r}
-# Confidence Interval based on the reverse percentile approach
+rm(a, i)
+```
+
+```{r}
+# Confidence interval based on the reverse percentile approach
 cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]" )
@@
 est_boot_3 <- sort(est_boot_3)
-
 ```
@@
 ```{r}
-# Confidence Interval based on the percentile approach
+# Confidence interval based on the percentile approach
 lim_inf <- est_boot_3[floor(B*2.5/100)]
@@
 est_init_3 <- sum(a/p)
-
 ```
@@
 ```{r}
-# Confidence Interval based on the reverse percentile approach
+# Confidence interval based on the reverse percentile approach
 cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : [", est_init_3*2 - lim_sup, ";", est_init_3*2 - lim_inf, "]" )
@@
 
+# BCA and ABC bootstrap CI
+
 ```{r}
-est_boot3 <- c()
+# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
+# Function explained in Efron and Tibshirani (1993)
+bcanon <- function(x,bootsam,theta,...,alpha =
+                     c(.025,.05,.1,.16,.84,.9,.95,.975)) { 
+    if (!all(alpha < 1) || !all(alpha > 0))
+      stop("All elements of alpha must be in (0,1)")
+
+    alpha_sorted <- sort(alpha)
+    # if (nboot <= 1/min(alpha_sorted[1],1-alpha_sorted[length(alpha_sorted)]))
+    #   warning("nboot is not large enough to estimate your chosen alpha.")
+
+    call <- match.call()
+    # n <- length(x)
+    n <- nrow(x)
+    # thetahat <- theta(x,...)
+    a <- c()
+    for (i in 1:n) {
+      a <- append(a, circle3_nb(x[i, 1], x[i, 2], 15, 9, 6))
+    }
+    # Estimated total thus obtained from the initial sample
+    thetahat <- sum(a/p)
+
+    nboot <- length(bootsam)/2
+    # bootsam<- matrix(sample(x,size=n*nboot,replace=TRUE),nrow=nboot)
+
+    # thetastar <- apply(bootsam,1,theta,...)
+    thetastar <- c()
     for (c in 1:B) {
@@
       for (i in 1:n) {
-    a <- append(a, circle_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], 15))
+        a <- append(a, theta(bootsam[i, (2*c)-1], bootsam[i, 2*c], 15, 9, 6))
       }
-  est_boot3 <- append(est_boot3, sum(a/p))
+      thetastar <- append(thetastar, sum(a/p))
     }
+    thetastar <- sort(thetastar)
 
-est_boot3 <- sort(est_boot3)
+    z0 <- qnorm(sum(thetastar<thetahat)/nboot)
 
-```
+    u <- rep(0,n)
+    for(i in 1:n){
+        # u[i] <- theta(x[-i],...)
+        x_i <- x[-i]
+        a <- c()
+        for (j in 1:n) {
+          a <- append(a, theta(x_i[j, 1], x_i[j, 2], 15, 9, 6))
+        }
+        # Estimated total thus obtained from the initial sample
+        u[i] <- sum(a/p)
+    }
+    uu <- mean(u)-u
+    acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)
 
-```{r}
-# Same result with function?
-boot.ci(rho_boot, type = "perc")
-# Doesn't work (df_boot, est_boot, rho_boot)
-```
+    zalpha <- qnorm(alpha)
 
-```{r}
-sum((random_points$x/random_points$y)/p)
-```
+    tt <- pnorm(z0+ (z0+zalpha)/(1-acc*(z0+zalpha)))
 
-```{r}
-rho <- function(df, indice){
-  d <- df[indice,] # to enable boot
-  return(sum((d$x/d$y)/p))
+    confpoints <- quantile(x=thetastar,probs=tt,type=1)
+    names(confpoints) <- NULL
+    confpoints <- cbind(alpha,confpoints)
+    dimnames(confpoints)[[2]] <- c("alpha","bca point")
+    return(list(confpoints=confpoints, 
+                z0=z0, 
+                acc=acc, 
+                u=u, 
+                call=call))
 }
@@
 ```{r}
-res_boot <- boot(data=random_points, statistic=circle_nb)
-res_boot
-# Doesn't work
+bcanon(random_points,bootsam,circle_nb,...,alpha = .95)
 ```
 
-```{r}
-boot.ci(res_boot, type = "norm")
-```
+# With a grid
 
 ```{r}
-boot.ci(res_boot, type = "basic")
-# Warning in norm.inter(t, (1 + c(conf, -conf))/2) :
-#  extreme order statistics used as endpoints
-```
-
-```{r}
-# boot.ci(res_boot, type = "stud") 
-# Error in ci.out[[4L]] : subscript out of bounds
-```
-
-```{r}
-boot.ci(res_boot, type = "perc") 
-# Error in ci.out[[4L]] : subscript out of bounds
-```
-
-```{r}
-boot.ci(res_boot, type = "bca") 
-# Error in bca.ci(boot.out, conf, index[1L], L = L, t = t.o, t0 = t0.o,  : 
-#  estimated adjustment 'a' is NA
-```
-
-# Another package
-
-```{r}
-install.packages("bootstrap")
-library(bootstrap)
-```
-
-```{r}
-## The most simple function
-f_try <- function(x){
-  1
-}
-```
-
-```{r}
-theta <- function(x){mean(x)}
-```
-
-```{r}
-patch.boot <- bootstrap(x = random_points$x,nboot = 1000,theta = theta, func=NULL)
-```
-
-```{r}
-sd(patch.boot$thetastar) # bootstrapped standard error
-```
-
-```{r}
-bcanon(random_points$x, 1000, theta = theta)
-```
-
-```{r}
-# xdata <- matrix(rnorm(30),ncol=2)
-n <- 100
-# theta <- function(x,xdata){ cor(xdata[x,1],xdata[x,2]) }
-theta <- function(x,xdata){
-  a <- c()
-  for (i in 1:n) {
-    a <- append(a, circle(xdata[i,1], xdata[i,2], R))
-    # Change: circle_nb!!!
-  }
-  est_nb <- sum((a)/p)
-}
-results <- bcanon(1:n,150,theta,random_points, alpha = 0.95)
-```
-
-```{r}
-results$confpoints # NaN
+# Is it OK?
 ```
@@
 ```
-
-```{r}
-
-```
-
-```{r}
-
-```
-
-```{r}
-
-```

### 2024-07-03 Draft.Rmd
Try BCa CI

@@
 knitr::opts_chunk$set(echo = TRUE)
+```
+
+## Tessellation
+
+```{r}
+# Load necessary library
+library(ggplot2)
+
+# Define the size of the square space
+space_size <- 10
+
+# Define the size of the smaller squares
+square_size <- 1
+
+# Create a data frame to store the coordinates of the squares
+squares <- data.frame(
+  x = rep(seq(0, space_size - square_size, by = square_size), each = space_size / square_size),
+  y = rep(seq(0, space_size - square_size, by = square_size), times = space_size / square_size)
+)
+
+# Plot the tessellation
+ggplot() +
+  geom_tile(data = squares, aes(x = x, y = y), width = square_size, height = square_size, fill = "lightblue", color = "black") +
+  coord_fixed() +
+  theme_minimal() +
+  labs(title = "Square Tessellation", x = "X", y = "Y")
 ```
@@
 
+### Complexity
+
 ```{r}
@@
 ```
+
+```{r}
+est_boot3 <- c()
+for (c in 1:B) {
+  a <- c()
+  for (i in 1:n) {
+    a <- append(a, circle_nb(df_boot[i, (2*c)-1], df_boot[i, 2*c], 15))
+  }
+  est_boot3 <- append(est_boot3, sum(a/p))
+}
+
+est_boot3 <- sort(est_boot3)
+
+```
+
+### A first package
+
+```{r}
+# Same result with function?
+boot.ci(rho_boot, type = "perc")
+# Doesn't work (df_boot, est_boot, rho_boot)
+```
+
+```{r}
+sum((random_points$x/random_points$y)/p)
+```
+
+```{r}
+rho <- function(df, indice){
+  d <- df[indice,] # to enable boot
+  return(sum((d$x/d$y)/p))
+}
+```
+
+```{r}
+res_boot <- boot(data=random_points, statistic=circle_nb)
+res_boot
+# Doesn't work
+```
+
+```{r}
+boot.ci(res_boot, type = "norm")
+```
+
+```{r}
+boot.ci(res_boot, type = "basic")
+# Warning in norm.inter(t, (1 + c(conf, -conf))/2) :
+#  extreme order statistics used as endpoints
+```
+
+```{r}
+# boot.ci(res_boot, type = "stud") 
+# Error in ci.out[[4L]] : subscript out of bounds
+```
+
+```{r}
+boot.ci(res_boot, type = "perc") 
+# Error in ci.out[[4L]] : subscript out of bounds
+```
+
+```{r}
+boot.ci(res_boot, type = "bca") 
+# Error in bca.ci(boot.out, conf, index[1L], L = L, t = t.o, t0 = t0.o,  : 
+#  estimated adjustment 'a' is NA
+```
+
+### Another package
+
+```{r}
+install.packages("bootstrap")
+library(bootstrap)
+```
+
+```{r}
+## The most simple function
+f_try <- function(x){
+  1
+}
+```
+
+```{r}
+theta <- function(x){mean(x)}
+```
+
+```{r}
+patch.boot <- bootstrap(x = random_points$x,nboot = 1000,theta = theta, func=NULL)
+```
+
+```{r}
+sd(patch.boot$thetastar) # bootstrapped standard error
+```
+
+```{r}
+bcanon(random_points$x, 1000, theta = theta)
+```
+
+```{r}
+# xdata <- matrix(rnorm(30),ncol=2)
+n <- 100
+# theta <- function(x,xdata){ cor(xdata[x,1],xdata[x,2]) }
+theta <- function(x,xdata){
+  a <- c()
+  for (i in 1:n) {
+    a <- append(a, circle(xdata[i,1], xdata[i,2], R))
+    # Change: circle_nb!!!
+  }
+  est_nb <- sum((a)/p)
+}
+results <- bcanon(1:n,150,theta,random_points, alpha = 0.95)
+```
+
+```{r}
+results$confpoints # NaN
+```

### 2024-07-03 Trees_no_grid.Rmd
Try BCa CI

@@
   rho_MC <- tibble(.rows = n)
-    # data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
-  col_names <- c()
   for (c in 1:B) {
-    col_ <- paste("est", c, sep = "")
     a <- c()
@@
     rho_MC <- rho_MC %>% add_column(col_ = a)
-    col_names <- append(col_names, col_)
+    colnames(rho_MC)[c] <- paste("est", c, sep = "")
   }
-  # rho_MC$x.1 <- NULL
-  # rho_MC$y.1 <- NULL
-  colnames(rho_MC) <- col_names
 
@@
 cat("True number of trees:", res[1], "\nMean of all the estimations (Monte Carlo):", res[2])
+# Ex:
 # True number of trees: 30942 

### 2024-07-03 Test_square.R

@@ -1,21 +1,0 @@
-# Load necessary library
-library(ggplot2)
-
-# Define the size of the square space
-space_size <- 10
-
-# Define the size of the smaller squares
-square_size <- 1
-
-# Create a data frame to store the coordinates of the squares
-squares <- data.frame(
-  x = rep(seq(0, space_size - square_size, by = square_size), each = space_size / square_size),
-  y = rep(seq(0, space_size - square_size, by = square_size), times = space_size / square_size)
-)
-
-# Plot the tessellation
-ggplot() +
-  geom_tile(data = squares, aes(x = x, y = y), width = square_size, height = square_size, fill = "lightblue", color = "black") +
-  coord_fixed() +
-  theme_minimal() +
-  labs(title = "Square Tessellation", x = "X", y = "Y")

### 2024-07-03 Useful_functions/Inc_area.R

@@ -1,5 +1,12 @@
 ######## Translation of a SAS program ----------
 
+# Goal: calculate the area in common of a rectangle and a circle, 
+# given the fact that the center of the circle is inside the rectangle
+
+# coord: vector with coordinates of the center of the circle
+# x0F, y0F, x1F, y1F: define the rectangle
+# r: the radius of the circle
+
 inc_area <- function(coord,x0F, y0F, x1F, y1F, r){
   x <- coord[1]
   y <- coord[2]

### 2024-07-03 Bootstrap_draft.Rmd
BCa and grid not finished

--- 2024-07-03 Bootstrap.Rmd
@@
 ---
-title: "Bootstrap"
-output: pdf_document
-date: "2024-06-26"
+title: "Bootstrap_draft"
+output: html_document
+date: "2024-07-03"
 ---
@@
 
-((We do not need the artificial forest for now. We just need a virtual 1000x1000 square.))
-
 ```{r}
@@
 # Sample size
-n <- 100
+n <- 50
 
@@
 # Number of bootstrap samples
-B <- 500
+B <- 100
 
@@
   }
+  est_boot <- append(est_boot, sum(a/p))
+}
+est_boot <- sort(est_boot)
+```
+
+```{r}
+# Estimation of the total number of trees for each bootstrap sample
+est_boot <- c()
+for (c in 1:B) {
+  # a <- circle_nb(rbind(df_boot[, (2*c)-1], df_boot[, 2*c], c(rep(R,n))))
+  a <- apply(df_boot[, (2*c)-1], df_boot[, 2*c], c(rep(R,n)), MARGIN = 1, FUN = circle_nb)
   est_boot <- append(est_boot, sum(a/p))
@@
     for (i in 1:n) {
-      a <- append(a, circle3_nb(x[i, 1], x[i, 2], 15, 9, 6))
+      a <- append(a, theta(x[i, 1], x[i, 2]))
     }
@@
       for (i in 1:n) {
-        a <- append(a, theta(bootsam[i, (2*c)-1], bootsam[i, 2*c], 15, 9, 6))
+        a <- append(a, theta(bootsam[i, (2*c)-1], bootsam[i, 2*c]))
       }
@@
         for (j in 1:n) {
-          a <- append(a, theta(x_i[j, 1], x_i[j, 2], 15, 9, 6))
+          a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
         }
@@
 ```{r}
-bcanon(random_points,bootsam,circle_nb,...,alpha = .95)
+bcanon(random_points,df_boot,circle_nb,alpha = .95)
 ```
-
-# With a grid
-
-```{r}
-# Is it OK?
-```
-
-```{r}
-
-```

### 2024-07-03 Trees_grid.Rmd
BCa and grid not finished

---
title: "Counting trees with a grid"
output: pdf_document
date: "2024-07-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
```

# Preliminaries

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
```

```{r}
# Functions to produce a local variable
source("~/work/Sim_article2024/Useful_functions/Circle.R")
```

```{r}
### Constant values

# Sample size
n <- 50

# Marginal density: density of the uniform distribution over 1:1000
# Which leads us to the inclusion density function
p <- sum(rep((1/1000)*(1/1000), n))

# Number of bootstrap samples
B <- 100

# Radius to consider for the circle around each sampled point
R <- 5
```

# Creating a sample with a grid

```{r}
# Randomizing the positions of the numbers used to identify cells
random10 <- sample(1:10)
rank_nb <- sample(1:10, 1)
nb <- random10[rank_nb]
```

```{r}
# Shift considered to add randomization
trend <- as.numeric(sample(1:10, 1))
```

```{r}
# Dimension of a cell (length of one side of the square)
# We assume that c_dim divides 1000
c_dim <- 10
```

```{r}
# (It works a priori)
# l: toutes les lignes ; k: les cellules sur une ligne ; a: abscisse ; b: ordonnée

random_points <- data.frame(x = numeric(), y = numeric())

i <- rank_nb

list <- list_stable
for (l in 1:(1000/c_dim)) {

  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
    colnames(random_points) <- list("x", "y")
    if (length(random_points[(random_points$x > vec[(k + (l-1)*60 -1 + (nb-1)*60)%%1000 + 1])
                             & (random_points$x < vec[(k + (l-1)*60 -1 + (nb-1)*60)%%1000 + 1] + 1)
                             & (random_points$y > 200 + (l-1))
                             & (random_points$y < 200 + l) ]) == 0){ # Eviter les doublons dans chaque cellule
    a <- runif(1, vec[(k + (l-1)*60 -1 + (nb-1)*60)%%1000 + 1], vec[(k + (l-1)*60 -1 + (nb-1)*60)%%1000 + 1] + 1)
    b <- runif(1, 200 + (l-1), 200+l)
    random_points <- rbind(random_points, list(a,b))
    }
    # trees$cell <- ifelse(
    # (vec[] <= trees$x) & (trees$x < vec[k + (nb-1)*60] + 1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
    # list_stable[nb],
    # trees$cell)
  }
  # list <- shift(list, n = trend, type = "cyclic") # shift for each line
}

# 36 000 points are randomly selected if nb = 5
# Which is what we want!

```

```{r}
rm(a,b,k,l) # Useless outside loops
```

```{r}
# ESSAI
random_points <- data.frame(x = numeric(), y = numeric())

i <- rank_nb

for (l in 1:(1000/c_dim)) {
  if ((max(trend*l,c_dim*10) %% min(trend*l,c_dim*10)) < (10-i)*c_dim){
    x_init <- i
  }else{
    x_init <- (10-i)*c_dim
  }
  k <- 1
  while (x_init + 10*c_dim*k < 1000) {
    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + 1)
    b <- runif(1, (l-1)*c_dim, l*c_dim)
    random_points <- rbind(random_points, list(a,b))
    k <- k+1
  }
}
colnames(random_points) <- list("x", "y")
```

```{r}
plot(x = random_points$x, y = random_points$y, main = "Random points", panel.first=grid())
# , xlim = c(0, 1000), ylim = c(0, 1000))
```

```{r}
plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
```

```{r}
plot(x = random_points$x, y = random_points$y, main = "Random points", panel.first=grid(), ylim = c(0, 210))
```

```{r}
# ESSAI
random_points <- data.frame(x = numeric(), y = numeric())

i <- rank_nb

for (l in 0:15) {
  reste <- (max(trend*l*c_dim,c_dim*10) %% min(trend*l*c_dim,c_dim*10))
  # reste <- trend*l*c_dim %% c_dim*10
  print(reste)
  cat("trend*l:",trend*l*c_dim,"\n")
  cat("c_dim*10:",c_dim*10,"\n")
  if (l==0){
    x_init <- i*c_dim
    # trend*l*c_dim
    print("In if")
  }else if (reste < (10-i)*c_dim){
    x_init <- reste + i*c_dim
    # trend*l*c_dim
    print("In else if")
  }else{
    x_init <- reste - (10-i)*c_dim
    print("In else")
  }
  print(x_init)
  k <- 0
  while (x_init + 10*c_dim*k < 1000) {
    # a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + 1)
    # b <- runif(1, l*c_dim, (l+1)*c_dim)
    a <- ((x_init + 10*c_dim*k)+(x_init + 10*c_dim*k + 1))/2
    b <- ((l*c_dim)+(l+1)*c_dim)/2
    random_points <- rbind(random_points, list(a,b))
    k <- k+1
  }
}
colnames(random_points) <- list("x", "y")
```

```{r}
plot(x = random_points$x, y = random_points$y, main = "Regular points", panel.first=grid(), xlim = c(0, 1000), ylim = c(0, 160))
```

### 2024-07-03 Useful_functions/Circle.R

@@ -1,7 +1,7 @@
 ### Functions to produce local variables based on circles -----
 
 ## Function to produce the local variable for the number of trees
-circle_nb <- function(x1, x2, R){
+circle_nb <- function(x1, x2, R=5){
   # 2 coordinates (x1, x2) and a radius (R)
   
   # Preliminary: inclusion area
@@ -17,7 +17,7 @@ circle_nb <- function(x1, x2, R){
 # circle_vol <- function(x1, x2, R){}
 
 ## Function to produce the local variable for the number of trees with 3 circle
-circle3_nb <- function(x1, x2, R1, R2, R3){
+circle3_nb <- function(x1, x2, R1=15, R2=9, R3=6){
   # 2 coordinates (x1, x2) and 3 radii (R1 > R2 > R3)
   
   # Preliminary: inclusion area

### 2024-07-04 Bootstrap.Rmd
Sampling with grid fine but too long for CI

@@
 ---
-title: "Bootstrap"
+title: "Bootstrap approach for confidence intervals"
 output: pdf_document
@@
 ```{r}
-install.packages("boot") # for bootstrap
-```
-
-```{r}
 library(readxl) # to read the initial file
@@
 library(tibble) # for add_column
-library(boot)
 ```
@@
 # Preliminaries
-
-((We do not need the artificial forest for now. We just need a virtual 1000x1000 square.))
 
@@
 # Confidence interval based on the reverse percentile approach
-cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]" )
+cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : \n[", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]" )
 ```
@@
 # Confidence interval based on the reverse percentile approach
-cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : [", est_init_3*2 - lim_sup, ";", est_init_3*2 - lim_inf, "]" )
+cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : \n[", est_init_3*2 - lim_sup, ";", est_init_3*2 - lim_inf, "]" )
 ```
@@
 ```{r}
+## WARNING:
+## Useless function for now!
+
 # Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
@@
 
-    alpha_sorted <- sort(alpha)
+    # alpha_sorted <- sort(alpha)
     # if (nboot <= 1/min(alpha_sorted[1],1-alpha_sorted[length(alpha_sorted)]))
@@
 ```{r}
-bcanon(random_points,bootsam,circle_nb,...,alpha = .95)
+# bcanon(random_points,df_boot,circle_nb,alpha = .95)
+# Produces an error
 ```
-
-# With a grid
-
-```{r}
-# Is it OK?
-```
-
-```{r}
-
-```

### 2024-07-04 Draft.Rmd
Sampling with grid fine but too long for CI

@@
 ```
+
+# Grid for trees
+
+```{r}
+# Shift considered to add randomization
+trend <- 3
+```
+
+```{r}
+# (It works a priori)
+# l: toutes les lignes ; k: les cellules sur une ligne ; a: abscisse ; b: ordonnée
+
+random_points <- data.frame(x = numeric(), y = numeric())
+
+i <- rank_nb
+
+# list <- list_stable
+for (l in 1:(1000/c_dim)) {
+
+  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
+    colnames(random_points) <- list("x", "y")
+    if (length(random_points[(random_points$x > vec[(k + (l-1)*60 -1 + (nb-1)*60)%%1000 + 1])
+                             & (random_points$x < vec[(k + (l-1)*60 -1 + (nb-1)*60)%%1000 + 1] + 1)
+                             & (random_points$y > 200 + (l-1))
+                             & (random_points$y < 200 + l) ]) == 0){ # Eviter les doublons dans chaque cellule
+    a <- runif(1, vec[(k + (l-1)*60 -1 + (nb-1)*60)%%1000 + 1], vec[(k + (l-1)*60 -1 + (nb-1)*60)%%1000 + 1] + 1)
+    b <- runif(1, 200 + (l-1), 200+l)
+    random_points <- rbind(random_points, list(a,b))
+    }
+    # trees$cell <- ifelse(
+    # (vec[] <= trees$x) & (trees$x < vec[k + (nb-1)*60] + 1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
+    # list_stable[nb],
+    # trees$cell)
+  }
+  # list <- shift(list, n = trend, type = "cyclic") # shift for each line
+}
+
+# 36 000 points are randomly selected if nb = 5
+# Which is what we want!
+
+```
+
+```{r}
+rm(a,b,k,l) # Useless outside loops
+```
+
+```{r}
+# ESSAI
+random_points <- data.frame(x = numeric(), y = numeric())
+
+i <- rank_nb
+
+for (l in 1:(1000/c_dim)) {
+  if ((max(trend*l,c_dim*10) %% min(trend*l,c_dim*10)) < (10-i)*c_dim){
+    x_init <- i
+  }else{
+    x_init <- (10-i)*c_dim
+  }
+  k <- 1
+  while (x_init + 10*c_dim*k < 1000) {
+    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + 1)
+    b <- runif(1, (l-1)*c_dim, l*c_dim)
+    random_points <- rbind(random_points, list(a,b))
+    k <- k+1
+  }
+}
+colnames(random_points) <- list("x", "y")
+```
+
+```{r}
+plot(x = random_points$x, y = random_points$y, main = "Random points", panel.first=grid())
+# , xlim = c(0, 1000), ylim = c(0, 1000))
+```
+
+```{r}
+plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
+```
+
+```{r}
+plot(x = random_points$x, y = random_points$y, main = "Random points", panel.first=grid(), ylim = c(0, 210))
+```
+
+```{r}
+# ESSAI
+random_points <- data.frame(x = numeric(), y = numeric())
+
+# i <- rank_nb
+
+for (l in 0:15) {
+  reste <- (max(trend*l*c_dim,c_dim*10) %% min(trend*l*c_dim,c_dim*10))
+  # reste <- trend*l*c_dim %% c_dim*10
+  cat("reste:",reste,"\n")
+  cat("trend*l*c_dim:",trend*l*c_dim,"\n")
+  cat("c_dim*10:",c_dim*10,"\n")
+  if (l==0){
+    x_init <- i*c_dim
+    # trend*l*c_dim
+    print("In if")
+  }else if (reste < (10-i)*c_dim){
+    x_init <- reste + i*c_dim
+    # trend*l*c_dim
+    print("In else if")
+  }else{
+    x_init <- reste - (10-i)*c_dim
+    print("In else")
+  }
+  cat("x_init:",x_init,"\n")
+  k <- 0
+  while (x_init + 10*c_dim*k < 1000) {
+    # a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + 1)
+    # b <- runif(1, l*c_dim, (l+1)*c_dim)
+    a <- ((x_init + 10*c_dim*k)+(x_init + 10*c_dim*k + c_dim))/2
+    b <- ((l*c_dim)+(l+1)*c_dim)/2
+    random_points <- rbind(random_points, list(a,b))
+    k <- k+1
+  }
+}
+colnames(random_points) <- list("x", "y")
+```
+
+```{r}
+plot(x = random_points$x, y = random_points$y, main = "Regular points", panel.first=grid(), xlim = c(0, 1000), ylim = c(0, 160))
+```
+
+```{r}
+plot(x = random_points$x, y = random_points$y, main = "Regular points", panel.first=grid(), xlim = c(0, 150), ylim = c(0, 100))
+```
+
+Problème avec la deuxième ligne, i.e. l=1. 
+Le premier point de cette ligne a une coordonnée x trop élevée.
+
+Ex (trend=9, i=9):
+reste: 10 
+trend*l*c_dim: 90 
+c_dim*10: 100 
+[1] "In else"
+x_init: 0
+
+Ex (trend=3, i=9):
+reste: 10 
+trend*l*c_dim: 30 
+c_dim*10: 100 
+[1] "In else"
+x_init: 0
+
+Ex (trend=3, i=5):
+reste: 10 
+trend*l*c_dim: 30 
+c_dim*10: 100 
+[1] "In else if"
+x_init: 60
+
+NUL
+
+trend forcément égale à 3 (?)
+
+```{r}
+plot(x = random_points$x, y = random_points$y, main = "Regular points", panel.first=grid())
+```

### 2024-07-04 Trees_grid.Rmd
Sampling with grid fine but too long for CI

@@
 
-```{r}
-### Constant values
-
-# Sample size
-n <- 50
-
-# Marginal density: density of the uniform distribution over 1:1000
-# Which leads us to the inclusion density function
-p <- sum(rep((1/1000)*(1/1000), n))
-
-# Number of bootstrap samples
-B <- 100
-
-# Radius to consider for the circle around each sampled point
-R <- 5
-```
-
 # Creating a sample with a grid
@@
 ```{r}
-# Randomizing the positions of the numbers used to identify cells
+### Randomizing the positions of the numbers (from 1 to 10) 
+# used to identify small squares in the grid
 random10 <- sample(1:10)
-rank_nb <- sample(1:10, 1)
-nb <- random10[rank_nb]
+rank_nb <- sample(1:10, 1) # choice of the rank of the identifier we want
+nb <- random10[rank_nb] # the identifier thus chosen
 ```
@@
 ```{r}
-# Shift considered to add randomization
-trend <- as.numeric(sample(1:10, 1))
+# Dimension of a small square (length of one side of the square)
+# We assume that c_dim is a divisor of 1000
+c_dim <- 10
+```
+
+## Plotting regular points to make sure it works
+
+```{r}
+# We want to target approximately one tenth of the area, 
+# in order to reproduce figure 2.a. page 6 of Trinh et alii (2024)
+# For this step, we choose regular points
+regular_points <- data.frame(x = numeric(), y = numeric())
+
+i <- rank_nb
+
+for (l in 0:((1000/c_dim)-1)) {
+  if (l==0){
+    x_init <- i*c_dim
+  }else if ((3*l+i)*c_dim < (10)*c_dim){
+    x_init <- (3*l+i)*c_dim
+  }else{
+    x_init <- (((3*l+i)*c_dim)%%(c_dim*10))
+  }
+  k <- 0
+  while (x_init + 10*c_dim*k < 1000) {
+    # (a,b) is the center of each small square
+    a <- ((x_init + 10*c_dim*k)+(x_init + 10*c_dim*k + c_dim))/2
+    b <- ((l*c_dim)+(l+1)*c_dim)/2
+    regular_points <- rbind(regular_points, list(a,b))
+    k <- k+1
+  }
+}
+colnames(regular_points) <- list("x", "y")
 ```
@@
 ```{r}
-# Dimension of a cell (length of one side of the square)
-# We assume that c_dim divides 1000
-c_dim <- 10
+plot(x = regular_points$x, y = regular_points$y, main = "Regular points", panel.first=grid())
 ```
@@
 ```{r}
-# (It works a priori)
-# l: toutes les lignes ; k: les cellules sur une ligne ; a: abscisse ; b: ordonnée
+plot(x = regular_points$x, y = regular_points$y, main = "Regular points", panel.first=grid(), xlim = c(0, 1000), ylim = c(0, 160))
+```
 
+## Sampling in each small square of the grid
+
+```{r}
+# Now, we sample at random following the grid
 random_points <- data.frame(x = numeric(), y = numeric())
@@
 
-list <- list_stable
-for (l in 1:(1000/c_dim)) {
-
-  for (k in 1:60) { # nombre de fois où on obtient un même identifiant pour une ligne donnée
-    colnames(random_points) <- list("x", "y")
-    if (length(random_points[(random_points$x > vec[(k + (l-1)*60 -1 + (nb-1)*60)%%1000 + 1])
-                             & (random_points$x < vec[(k + (l-1)*60 -1 + (nb-1)*60)%%1000 + 1] + 1)
-                             & (random_points$y > 200 + (l-1))
-                             & (random_points$y < 200 + l) ]) == 0){ # Eviter les doublons dans chaque cellule
-    a <- runif(1, vec[(k + (l-1)*60 -1 + (nb-1)*60)%%1000 + 1], vec[(k + (l-1)*60 -1 + (nb-1)*60)%%1000 + 1] + 1)
-    b <- runif(1, 200 + (l-1), 200+l)
-    random_points <- rbind(random_points, list(a,b))
+for (l in 0:((1000/c_dim)-1)) {
+  if (l==0){
+    x_init <- i*c_dim
+  }else if ((3*l+i)*c_dim < (10)*c_dim){
+    x_init <- (3*l+i)*c_dim
+  }else{
+    x_init <- (((3*l+i)*c_dim)%%(c_dim*10))
   }
-    # trees$cell <- ifelse(
-    # (vec[] <= trees$x) & (trees$x < vec[k + (nb-1)*60] + 1) & (200 + (l-1) <= trees$y) & (trees$y < 200+l), 
-    # list_stable[nb],
-    # trees$cell)
-  }
-  # list <- shift(list, n = trend, type = "cyclic") # shift for each line
-}
-
-# 36 000 points are randomly selected if nb = 5
-# Which is what we want!
-
-```
-
-```{r}
-rm(a,b,k,l) # Useless outside loops
-```
-
-```{r}
-# ESSAI
-random_points <- data.frame(x = numeric(), y = numeric())
-
-i <- rank_nb
-
-for (l in 1:(1000/c_dim)) {
-  if ((max(trend*l,c_dim*10) %% min(trend*l,c_dim*10)) < (10-i)*c_dim){
-    x_init <- i
-  }else{
-    x_init <- (10-i)*c_dim
-  }
-  k <- 1
+  k <- 0
   while (x_init + 10*c_dim*k < 1000) {
-    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + 1)
-    b <- runif(1, (l-1)*c_dim, l*c_dim)
+    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + c_dim)
+    b <- runif(1, l*c_dim, (l+1)*c_dim)
     random_points <- rbind(random_points, list(a,b))
@@
 plot(x = random_points$x, y = random_points$y, main = "Random points", panel.first=grid())
-# , xlim = c(0, 1000), ylim = c(0, 1000))
 ```
@@
 ```{r}
-plot(x = random_points[(random_points$x < 210),]$x, y = random_points[(random_points$x < 210),]$y, main = "Random points", panel.first=grid(), xlim = c(200, 210), ylim = c(200, 220))
+plot(x = random_points$x, y = random_points$y, main = "Random points", panel.first=grid(), xlim = c(0, 1000), ylim = c(0, 160))
 ```
@@
 ```{r}
-plot(x = random_points$x, y = random_points$y, main = "Random points", panel.first=grid(), ylim = c(0, 210))
+rm(a,b,i,l,x_init,k)
 ```
@@
 ```{r}
-# ESSAI
-random_points <- data.frame(x = numeric(), y = numeric())
+### Values available after sampling
 
-i <- rank_nb
+# Sample size
+n <- nrow(random_points)
 
-for (l in 0:15) {
-  reste <- (max(trend*l*c_dim,c_dim*10) %% min(trend*l*c_dim,c_dim*10))
-  # reste <- trend*l*c_dim %% c_dim*10
-  print(reste)
-  cat("trend*l:",trend*l*c_dim,"\n")
-  cat("c_dim*10:",c_dim*10,"\n")
-  if (l==0){
-    x_init <- i*c_dim
-    # trend*l*c_dim
-    print("In if")
-  }else if (reste < (10-i)*c_dim){
-    x_init <- reste + i*c_dim
-    # trend*l*c_dim
-    print("In else if")
-  }else{
-    x_init <- reste - (10-i)*c_dim
-    print("In else")
-  }
-  print(x_init)
-  k <- 0
-  while (x_init + 10*c_dim*k < 1000) {
-    # a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + 1)
-    # b <- runif(1, l*c_dim, (l+1)*c_dim)
-    a <- ((x_init + 10*c_dim*k)+(x_init + 10*c_dim*k + 1))/2
-    b <- ((l*c_dim)+(l+1)*c_dim)/2
-    random_points <- rbind(random_points, list(a,b))
-    k <- k+1
-  }
-}
-colnames(random_points) <- list("x", "y")
+# Marginal density: density of the uniform distribution over 1:1000
+# Which leads us to the inclusion density function
+p <- sum(rep((1/1000)*(1/1000), n))
+```
+
+# Bootstrap
+
+## Creating other samples based on the previous one
+
+```{r}
+# Number of bootstrap samples
+B <- 500
 ```
@@
 ```{r}
-plot(x = random_points$x, y = random_points$y, main = "Regular points", panel.first=grid(), xlim = c(0, 1000), ylim = c(0, 160))
+f_boot <- function(df_sample, B){
+  # df_sample: original sample; B: number of bootstrap samples made thanks to df_sample
+
+  df_boot <- tibble(.rows = nrow(df_sample))
+  for (b in 1:B) {
+    nb <- sample(1:nrow(df_sample), nrow(df_sample), replace = TRUE)
+    sample_b <- df_sample[nb,]
+    df_boot <- df_boot %>% add_column(new_col = sample_b)
+    colnames(df_boot)[b] <- paste("ech", b, sep = "")
+  }
+  return(do.call(data.frame, df_boot))
+  # Return a data frame with B samples of 2 variables and of size n
+}
 ```
+
+```{r}
+# Making of bootstrap samples
+df_boot <- f_boot(random_points, B)
+```
+
+## Estimations and confidence intervals based on the bootstrap samples with three circles
+
+```{r}
+ci_boot <- function(df_init, df_boot){
+  # df: dataframe with 2*B columns and n rows
+
+  ## 1st step: 1 estimation for each sample
+  est_boot <- c()
+  for (c in 1:B) {
+    a <- mapply(circle3_nb, df_boot[, (2*c)-1], df_boot[, 2*c], MoreArgs = list(15, 9, 6))
+    est_boot <- append(est_boot, sum(a/p))
+  }
+  est_boot <- sort(est_boot)
+
+  ## 2nd step: percentile CI
+  lim_inf <- est_boot[floor(B*2.5/100)]
+  lim_sup <- est_boot[B - floor(B*2.5/100)]
+  cat("Un intervalle de confiance à 95% par la méthode des percentiles est : 
+      [", lim_inf, ";", lim_sup, "]\n" )
+
+  ## 3rd step: reverse percentile CI
+  # Target: the initial sample alone
+  a <- mapply(circle3_nb, df_init[, 1], df_init[, 2], MoreArgs = list(15, 9, 6))
+  est_init <- sum(a/p) # Estimated total thus obtained from the initial sample
+  cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : 
+      [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]\n" )
+  return(c(est_init,lim_inf,lim_sup))
+}
+```
+
+```{r}
+start.time <- Sys.time()
+
+res <- ci_boot(random_points,df_boot)
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+time.taken
+
+# Ex:
+# Un intervalle de confiance à 95% par la méthode des percentiles est : 
+#      [ 25979.59 ; 32051.31 ]
+# Un intervalle de confiance à 95% par la méthode des reverse percentiles est :
+# [ 26421.35 ; 32493.07 ]
+
+# Ex:
+# Un intervalle de confiance à 95% par la méthode des percentiles est : 
+#       [ 25979.59 ; 32051.31 ]
+# Un intervalle de confiance à 95% par la méthode des reverse percentiles est : 
+#       [ 26421.35 ; 32493.07 ]
+# Time difference of 12.57769 mins
+```

### 2024-07-04 Bootstrap.Rmd
BCa works

@@
 ```{r}
-## WARNING:
-## Useless function for now!
-
 # Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
 # Function explained in Efron and Tibshirani (1993)
+# Adapted for our particular problem
 bcanon <- function(x,bootsam,theta,...,alpha =
@@
 
-    # alpha_sorted <- sort(alpha)
-    # if (nboot <= 1/min(alpha_sorted[1],1-alpha_sorted[length(alpha_sorted)]))
-    #   warning("nboot is not large enough to estimate your chosen alpha.")
+    alpha_sorted <- sort(alpha)
+    if (nboot <= 1/min(alpha_sorted[1],1-alpha_sorted[length(alpha_sorted)]))
+    warning("nboot is not large enough to estimate your chosen alpha.")
 
     call <- match.call()
-    # n <- length(x)
     n <- nrow(x)
-    # thetahat <- theta(x,...)
-    a <- c()
-    for (i in 1:n) {
-      a <- append(a, theta(x[i, 1], x[i, 2]))
-    }
+    a <- mapply(theta, x[, 1], x[, 2])
     # Estimated total thus obtained from the initial sample
@@
     nboot <- length(bootsam)/2
-    # bootsam<- matrix(sample(x,size=n*nboot,replace=TRUE),nrow=nboot)
-
-    # thetastar <- apply(bootsam,1,theta,...)
     thetastar <- c()
     for (c in 1:B) {
-      a <- c()
-      for (i in 1:n) {
-        a <- append(a, theta(bootsam[i, (2*c)-1], bootsam[i, 2*c]))
-      }
+      a <- mapply(theta, bootsam[, (2*c)-1], bootsam[, 2*c])
       thetastar <- append(thetastar, sum(a/p))
@@
     for(i in 1:n){
-        # u[i] <- theta(x[-i],...)
-        x_i <- x[-i]
+        x_i <- x[-i,]
         a <- c()
-        for (j in 1:n) {
+        for (j in 1:(n-1)) {
           a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
         }
-        # Estimated total thus obtained from the initial sample
         u[i] <- sum(a/p)
@@
 ```{r}
-# bcanon(random_points,df_boot,circle_nb,alpha = .95)
-# Produces an error
+# Interval of intended coverage 1 - 2*alpha = .95 => alpha = .025
+res <- bcanon(random_points,df_boot,circle_nb,alpha = c(.025, .975))
 ```
+
+```{r}
+cat("Un intervalle de confiance à 95% par la méthode BCa est : [", res$confpoints[1,2], ";", res$confpoints[2,2], "]")
+```

### 2024-07-04 Bootstrap_draft.Rmd
BCa works

@@
 ```{r}
+plot(density(est_boot_3))
+```
+
+```{r}
 # Confidence interval based on the percentile approach
@@
         # u[i] <- theta(x[-i],...)
-        x_i <- x[-i]
+        x_i <- x[-i,]
         a <- c()
-        for (j in 1:n) {
+        for (j in 1:(n-1)) {
           a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
@@
 ```{r}
-bcanon(random_points,df_boot,circle_nb,alpha = .95)
+# Interval of intended coverage 1 - 2*alpha = .95 => alpha = .025
+bcanon(random_points,df_boot,circle_nb,alpha = c(.025, .975))
+# Error in if ((x >= x0F + r) & (x <= x1F - r) & (y >= y0F + r) & (y <=  : 
+#  missing value where TRUE/FALSE needed
+# Works!
 ```
+
+#### Si alpha = 0.95
+
+$confpoints
+     alpha bca point
+[1,]  0.95   42526.2
+
+$z0
+[1] 0.01504034
+
+$acc
+[1] 0.02810749
+
+$u
+  [1] 32340.28 32340.28 32340.28 32340.28 32340.28 32340.28 31449.02 32340.28 32340.28 32340.28
+ [11] 32340.28 29921.13 32340.28 31194.37 32340.28 32340.28 31321.69 32340.28 31576.34 32340.28
+ [21] 32340.28 32340.28 32340.28 32340.28 31958.31 31576.34 32085.64 32340.28 32340.28 32340.28
+ [31] 32340.28 32340.28 31194.37 31576.34 32340.28 32340.28 32340.28 32340.28 32340.28 32340.28
+ [41] 32340.28 32340.28 32340.28 31576.34 32340.28 31576.34 32340.28 32340.28 32340.28 31321.69
+ [51] 31576.34 32340.28 32340.28 30939.72 30303.10 31194.37 32340.28 32340.28 32340.28 32340.28
+ [61] 32340.28 32340.28 31067.04 32340.28 32340.28 32340.28 32340.28 30939.72 32340.28 30175.78
+ [71] 32340.28 32340.28 32340.28 32340.28 32340.28 31194.37 32340.28 32340.28 32340.28 32340.28
+ [81] 32340.28 31958.31 32340.28 32340.28 32340.28 32340.28 32340.28 31576.34 32340.28 31194.37
+ [91] 31194.37 32340.28 32340.28 32340.28 30812.40 30685.07 31067.04 32340.28 31321.69 32340.28
+
+$call
+bcanon(x = random_points, bootsam = df_boot, theta = circle_nb, 
+    alpha = 0.95)
+
+#### Si alpha = 0.25
+
+$confpoints
+     alpha bca point
+[1,]  0.25  28520.57
+
+$z0
+[1] 0.01504034
+
+$acc
+[1] 0.02810749
+
+$u
+  [1] 32340.28 32340.28 32340.28 32340.28 32340.28 32340.28 31449.02 32340.28 32340.28 32340.28
+ [11] 32340.28 29921.13 32340.28 31194.37 32340.28 32340.28 31321.69 32340.28 31576.34 32340.28
+ [21] 32340.28 32340.28 32340.28 32340.28 31958.31 31576.34 32085.64 32340.28 32340.28 32340.28
+ [31] 32340.28 32340.28 31194.37 31576.34 32340.28 32340.28 32340.28 32340.28 32340.28 32340.28
+ [41] 32340.28 32340.28 32340.28 31576.34 32340.28 31576.34 32340.28 32340.28 32340.28 31321.69
+ [51] 31576.34 32340.28 32340.28 30939.72 30303.10 31194.37 32340.28 32340.28 32340.28 32340.28
+ [61] 32340.28 32340.28 31067.04 32340.28 32340.28 32340.28 32340.28 30939.72 32340.28 30175.78
+ [71] 32340.28 32340.28 32340.28 32340.28 32340.28 31194.37 32340.28 32340.28 32340.28 32340.28
+ [81] 32340.28 31958.31 32340.28 32340.28 32340.28 32340.28 32340.28 31576.34 32340.28 31194.37
+ [91] 31194.37 32340.28 32340.28 32340.28 30812.40 30685.07 31067.04 32340.28 31321.69 32340.28
+
+$call
+bcanon(x = random_points, bootsam = df_boot, theta = circle_nb, 
+    alpha = 0.25)
+
+#### Si alpha = c(0.025, 0.975)
+
+$confpoints
+     alpha bca point
+[1,] 0.025  22154.37
+[2,] 0.975  44308.74
+
+$z0
+[1] 0.01504034
+
+$acc
+[1] 0.02810749
+
+$u
+  [1] 32340.28 32340.28 32340.28 32340.28 32340.28 32340.28 31449.02 32340.28 32340.28 32340.28
+ [11] 32340.28 29921.13 32340.28 31194.37 32340.28 32340.28 31321.69 32340.28 31576.34 32340.28
+ [21] 32340.28 32340.28 32340.28 32340.28 31958.31 31576.34 32085.64 32340.28 32340.28 32340.28
+ [31] 32340.28 32340.28 31194.37 31576.34 32340.28 32340.28 32340.28 32340.28 32340.28 32340.28
+ [41] 32340.28 32340.28 32340.28 31576.34 32340.28 31576.34 32340.28 32340.28 32340.28 31321.69
+ [51] 31576.34 32340.28 32340.28 30939.72 30303.10 31194.37 32340.28 32340.28 32340.28 32340.28
+ [61] 32340.28 32340.28 31067.04 32340.28 32340.28 32340.28 32340.28 30939.72 32340.28 30175.78
+ [71] 32340.28 32340.28 32340.28 32340.28 32340.28 31194.37 32340.28 32340.28 32340.28 32340.28
+ [81] 32340.28 31958.31 32340.28 32340.28 32340.28 32340.28 32340.28 31576.34 32340.28 31194.37
+ [91] 31194.37 32340.28 32340.28 32340.28 30812.40 30685.07 31067.04 32340.28 31321.69 32340.28
+
+$call
+bcanon(x = random_points, bootsam = df_boot, theta = circle_nb, 
+    alpha = c(0.025, 0.975))
+
+```{r}
+# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
+# Function explained in Efron and Tibshirani (1993)
+
+alpha <- .95
+x <- random_points
+bootsam <- df_boot
+theta <- circle_nb
+
+    if (!all(alpha < 1) || !all(alpha > 0))
+      stop("All elements of alpha must be in (0,1)")
+
+    # alpha_sorted <- sort(alpha)
+    # if (nboot <= 1/min(alpha_sorted[1],1-alpha_sorted[length(alpha_sorted)]))
+    #   warning("nboot is not large enough to estimate your chosen alpha.")
+
+    ### call <- match.call()
+    # n <- length(x)
+    n <- nrow(x)
+    # thetahat <- theta(x,...)
+    a <- c()
+    for (i in 1:n) {
+      a <- append(a, theta(x[i, 1], x[i, 2]))
+    }
+    # Estimated total thus obtained from the initial sample
+    thetahat <- sum(a/p)
+
+    nboot <- length(bootsam)/2
+    # bootsam<- matrix(sample(x,size=n*nboot,replace=TRUE),nrow=nboot)
+
+    # thetastar <- apply(bootsam,1,theta,...)
+    thetastar <- c()
+    for (c in 1:B) {
+      a <- c()
+      for (i in 1:n) {
+        a <- append(a, theta(bootsam[i, (2*c)-1], bootsam[i, 2*c]))
+      }
+      thetastar <- append(thetastar, sum(a/p))
+    }
+    thetastar <- sort(thetastar)
+
+    z0 <- qnorm(sum(thetastar<thetahat)/nboot)
+
+    u <- rep(0,n)
+
+    i <- 1
+    for(i in 1:n){
+        # u[i] <- theta(x[-i],...)
+        x_i <- x[-i,]
+        a <- c()
+
+        ## Bug dans cette boucle
+        j <- 1
+        for (j in 1:(n-1)) {
+          print(j)
+          a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
+        }
+        # Estimated total thus obtained from the initial sample
+        u[i] <- sum(a/p)
+    }
+    uu <- mean(u)-u
+    acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)
+
+    zalpha <- qnorm(alpha)
+
+    tt <- pnorm(z0+ (z0+zalpha)/(1-acc*(z0+zalpha)))
+
+    confpoints <- quantile(x=thetastar,probs=tt,type=1)
+    names(confpoints) <- NULL
+    confpoints <- cbind(alpha,confpoints)
+    dimnames(confpoints)[[2]] <- c("alpha","bca point")
+    return(list(confpoints=confpoints, 
+                z0=z0, 
+                acc=acc, 
+                u=u, 
+                call=call))
+```

### 2024-07-04 Draft/3Circles.Rmd
BCa works

---
title: "With three circles"
output: html_document
date: "2024-07-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
circle3_nb <- function(x1, x2, R1, R2, R3){
  # 2 coordinates (x1, x2) and 3 radii (R1 > R2 > R3)

  # Preliminary: inclusion area
  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")

  list_trees <- trees[(x1 - trees$x)^2 + (x2 - trees$y)^2 <= R1^2,] # List with all trees inside the biggest circle

  list_trees1 <- list_trees[(pi*list_trees$d130 > 117.5),] # List with the biggest trees
  list_trees2 <- list_trees[(pi*list_trees$d130 < 117.5) & (pi*list_trees$d130 > 70.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R2^2),] # medium trees
  list_trees3 <- list_trees[(pi*list_trees$d130 < 70.5) & (pi*list_trees$d130 > 23.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R3^2),] # smallest trees

  local_var1 <- sum(length(list_trees1)/inc_area(c(x1, x2),0,0,1000,1000,R1)) # Local variable for the biggest circle and the biggest trees
  local_var2 <- sum(length(list_trees2)/inc_area(c(x1, x2),0,0,1000,1000,R2)) # Local variable for the medium circle and the medium trees
  local_var3 <- sum(length(list_trees3)/inc_area(c(x1, x2),0,0,1000,1000,R3)) # Local variable for the smallest circle and the smallest trees
  local_var <- (local_var1 + local_var2 + local_var3) # Addition of the previous local variables
  # /3 # Doesn't work
  return(local_var)
  # local_var: local variable based on the number of trees
}
```

```{r}
circle3_nb(500, 500, 15, 9, 6)
# 0.08511842 e.g.
```

```{r}

```

```{r}

```

```{r}

```

### 2024-07-04 Draft/Draft.Rmd
BCa works

--- 2024-07-04 Draft.Rmd
@@
 ```
+
+# Bootstrap
+
+## ABC-BCA
+
+```{r}
+## WARNING:
+## Useless function for now!
+
+# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
+# Function explained in Efron and Tibshirani (1993)
+bcanon <- function(x,bootsam,theta,...,alpha =
+                     c(.025,.05,.1,.16,.84,.9,.95,.975)) { 
+    if (!all(alpha < 1) || !all(alpha > 0))
+      stop("All elements of alpha must be in (0,1)")
+
+    # alpha_sorted <- sort(alpha)
+    # if (nboot <= 1/min(alpha_sorted[1],1-alpha_sorted[length(alpha_sorted)]))
+    #   warning("nboot is not large enough to estimate your chosen alpha.")
+
+    call <- match.call()
+    # n <- length(x)
+    n <- nrow(x)
+    # thetahat <- theta(x,...)
+    a <- c()
+    for (i in 1:n) {
+      a <- append(a, theta(x[i, 1], x[i, 2]))
+    }
+    # Estimated total thus obtained from the initial sample
+    thetahat <- sum(a/p)
+
+    nboot <- length(bootsam)/2
+    # bootsam<- matrix(sample(x,size=n*nboot,replace=TRUE),nrow=nboot)
+
+    # thetastar <- apply(bootsam,1,theta,...)
+    thetastar <- c()
+    for (c in 1:B) {
+      a <- c()
+      for (i in 1:n) {
+        a <- append(a, theta(bootsam[i, (2*c)-1], bootsam[i, 2*c]))
+      }
+      thetastar <- append(thetastar, sum(a/p))
+    }
+    thetastar <- sort(thetastar)
+
+    z0 <- qnorm(sum(thetastar<thetahat)/nboot)
+
+    u <- rep(0,n)
+    for(i in 1:n){
+        # u[i] <- theta(x[-i],...)
+        x_i <- x[-i]
+        a <- c()
+        for (j in 1:n) {
+          a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
+        }
+        # Estimated total thus obtained from the initial sample
+        u[i] <- sum(a/p)
+    }
+    uu <- mean(u)-u
+    acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)
+
+    zalpha <- qnorm(alpha)
+
+    tt <- pnorm(z0+ (z0+zalpha)/(1-acc*(z0+zalpha)))
+
+    confpoints <- quantile(x=thetastar,probs=tt,type=1)
+    names(confpoints) <- NULL
+    confpoints <- cbind(alpha,confpoints)
+    dimnames(confpoints)[[2]] <- c("alpha","bca point")
+    return(list(confpoints=confpoints, 
+                z0=z0, 
+                acc=acc, 
+                u=u, 
+                call=call))
+}
+```
+
+```{r}
+# bcanon(random_points,df_boot,circle_nb,alpha = .95)
+# Produces an error
+```

### 2024-07-04 Draft/Draft_no_loop.R

@@ -1,0 +1,80 @@
+source("~/work/Sim_article2024/Useful_functions/Circle.R")
+
+n <- nrow(random_points)
+
+start.time <- Sys.time()
+a <- c() # Target: the initial sample alone
+for (i in 1:n) {
+  a <- append(a, circle3_nb(random_points[i, 1], random_points[i, 2], 15, 9, 6))
+}
+end.time <- Sys.time()
+time.taken1 <- end.time - start.time
+time.taken1
+
+start.time <- Sys.time()
+b <- mapply(circle3_nb, random_points[, 1], random_points[, 2], MoreArgs = list(15, 9, 6))
+end.time <- Sys.time()
+time.taken2 <- end.time - start.time
+time.taken2
+
+
+# Error
+a <- circle3_nb(random_points[, 1], random_points[, 2], 15, 9, 6)
+
+a1 <- c(1,2)
+b1 <- c(3,4)
+a2 <- c(5,6)
+b2 <- c(7,8)
+vec_try <- data.frame(x = c(a1,b1), y = c(a2,b2))
+# vec_try <- tibble(.rows = 2)
+# colnames(vec_try) <- c("x", "y")
+# vec_try$x <- c(a1,b1)
+mapply(circle_nb, vec_try)
+
+mapply(circle3_nb, vec_try[, 1], vec_try[, 2], MoreArgs = list(15, 9, 6))
+
+a <- c()
+for (i in 1:n) {
+  a <- append(a, fun(df[i, 1], df[i, 2], 15, 9, 6))
+}
+
+### apply + mapply
+
+start.time <- Sys.time()
+est_boot_b <- c()
+for (c in 1:B) {
+  a <- mapply(circle3_nb, df_boot[, (2*c)-1], df_boot[, 2*c], MoreArgs = list(15, 9, 6))
+  est_boot_b <- append(est_boot_b, sum(a/p))
+}
+est_boot_b <- sort(est_boot_b)
+end.time <- Sys.time()
+time.taken1 <- end.time - start.time
+time.taken1
+# Time difference of 11.80462 mins
+
+start.time <- Sys.time()
+est_boot <- apply(as.array(1:B), 1, function(c){
+  sum(
+    (mapply(circle3_nb, df_boot[, (2*c)-1], df_boot[, 2*c], MoreArgs = list(15, 9, 6)))
+    /p)
+      })
+est_boot <- sort(est_boot)
+end.time <- Sys.time()
[…]

### 2024-07-04 Trees_grid.Rmd
Estimation of volume

@@
 ```
+
+## The same thing with the total volume
+
+```{r}
+ci_boot_vol <- function(df_init, df_boot){
+  # df: dataframe with 2*B columns and n rows
+
+  ## 1st step: 1 estimation for each sample
+  est_boot <- c()
+  for (c in 1:B) {
+    a <- mapply(circle3_vol, df_boot[, (2*c)-1], df_boot[, 2*c], MoreArgs = list(15, 9, 6))
+    est_boot <- append(est_boot, sum(a/p))
+  }
+  est_boot <- sort(est_boot)
+
+  ## 2nd step: percentile CI
+  lim_inf <- est_boot[floor(B*2.5/100)]
+  lim_sup <- est_boot[B - floor(B*2.5/100)]
+  cat("Un intervalle de confiance à 95% par la méthode des percentiles est : 
+      [", lim_inf, ";", lim_sup, "]\n" )
+
+  ## 3rd step: reverse percentile CI
+  # Target: the initial sample alone
+  a <- mapply(circle3_vol, df_init[, 1], df_init[, 2], MoreArgs = list(15, 9, 6))
+  est_init <- sum(a/p) # Estimated total thus obtained from the initial sample
+  cat("Un intervalle de confiance à 95% par la méthode des reverse percentiles est : 
+      [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]\n" )
+  return(c(est_init,lim_inf,lim_sup))
+}
+```
+
+```{r}
+start.time <- Sys.time()
+
+res <- ci_boot_vol(random_points,df_boot)
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+time.taken
+```

### 2024-07-04 Useful_functions/Circle.R

@@ -14,7 +14,17 @@ circle_nb <- function(x1, x2, R=5){
 }
 
 ## Function to produce the local variable for the volume of trees
-# circle_vol <- function(x1, x2, R){}
+circle_vol <- function(x1, x2, R=5){
+  # 2 coordinates (x1, x2) and a radius (R)
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  list_trees <- which((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2)
+  local_var <- sum((trees[list_trees,]$v)/inc_area(c(x1, x2),0,0,1000,1000,R))
+  return(local_var)
+  # list_trees: identifiers of targeted trees; local_var: local variable based on the volume of trees
+}
 
 ## Function to produce the local variable for the number of trees with 3 circle
 circle3_nb <- function(x1, x2, R1=15, R2=9, R3=6){
@@ -35,5 +45,32 @@ circle3_nb <- function(x1, x2, R1=15, R2=9, R3=6){
   local_var <- (local_var1 + local_var2 + local_var3) # Addition of the previous local variables
   return(local_var)
   # local_var: local variable based on the number of trees
+}
+
+## Function to produce the local variable for the number of trees with 3 circle
+circle3_vol <- function(x1, x2, R1=15, R2=9, R3=6){
+  # 2 coordinates (x1, x2) and 3 radii (R1 > R2 > R3)
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  list_trees <- trees[(x1 - trees$x)^2 + (x2 - trees$y)^2 <= R1^2,] # List with all trees inside the biggest circle
+  
+  list_trees1 <- list_trees[(pi*list_trees$d130 > 117.5),] # List with the biggest trees
+  list_trees2 <- list_trees[(pi*list_trees$d130 < 117.5) & (pi*list_trees$d130 > 70.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R2^2),] # medium trees
+  list_trees3 <- list_trees[(pi*list_trees$d130 > 23.5) & (pi*list_trees$d130 < 70.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R3^2),] # smallest trees
+  
+  if (nrow(list_trees1) != 0){
[…]

### 2024-07-05 Bootstrap.Rmd
Cleaner document to sum up

@@
 cat("Un intervalle de confiance à 95% par la méthode BCa est : [", res$confpoints[1,2], ";", res$confpoints[2,2], "]")
+
+# Ex:
+# Un intervalle de confiance à 95% par la méthode BCa est : [ 22154.37 ; 44308.74 ]
 ```

### 2024-07-05 Draft/Draft.Rmd
Cleaner document to sum up

@@
 ```
+
+# Alarm / beep / message when it finishes running
+
+```{r}
+#Have R email you when it's done running.
+###Calculating - your wish is R's command.
+library(mail)
+#Send yourself an email - specify your preferred email address, subject, and message. The password is fixed at "rmail".
+sendmail("xxxxx@xxxxx.com", subject="Notification from R", message="Conditions finished running!", password="rmail")
+
+alarm()
+
+install.packages("audio")
+library(audio)
+install.packages("beepr")
+library(beepr)
+beep()
+```

### 2024-07-05 NFI_method.Rmd
Cleaner document to sum up

---
title: "NFI process: grid-based sampling"
output: html_document
date: "2024-07-05"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
```

# Preliminaries

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
```

```{r}
# Functions to produce a local variable
source("~/work/Sim_article2024/Useful_functions/Circle.R")
```

# A first sample to produce a first estimation

## Sampling in one 10th of the small squares of a grid

```{r}
### Randomizing the positions of the numbers (from 1 to 10) 
# used to identify small squares in the grid
random10 <- sample(1:10)
i <- sample(1:10, 1) # choice of the rank of the identifier we want
nb <- random10[i] # the identifier thus chosen
```

```{r}
# Dimension of a small square (length of one side of the square)
# We assume that c_dim is a divisor of 1000
c_dim <- 10
```

```{r}
# Now, we sample at random following the grid
random_points <- data.frame(x = numeric(), y = numeric())

for (l in 0:((1000/c_dim)-1)) {
  if (l==0){
    x_init <- i*c_dim
  }else if ((3*l+i)*c_dim < (10)*c_dim){
    x_init <- (3*l+i)*c_dim
  }else{
    x_init <- (((3*l+i)*c_dim)%%(c_dim*10))
  }
  k <- 0
  while (x_init + 10*c_dim*k < 1000) {
    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + c_dim)
    b <- runif(1, l*c_dim, (l+1)*c_dim)
    random_points <- rbind(random_points, list(a,b))
    k <- k+1
  }
}
colnames(random_points) <- list("x", "y")
```

```{r}
plot(x = random_points$x, y = random_points$y, xlab = "", ylab = "", main = "Random points", panel.first=grid())
```
Figure 1.**Points sampled following a grid over the whole territory**.

```{r}
rm(a,b,l,x_init,k)
```

```{r}
### Values available after sampling

# Sample size
n <- nrow(random_points)

# Marginal density: density of the uniform distribution over 1:1000
# Which leads us to the inclusion density function
p <- sum(rep((1/1000)*(1/1000), n))
```

## Estimations based on the sample previously made

```{r}
# Number of trees
a <- mapply(circle3_nb, random_points[, 1], random_points[, 2], MoreArgs = list(15, 9, 6))
est_init_nb <- sum(a/p)
rm(a)
cat("Number of trees:", nrow(trees), "\nEstimation of the number of trees:", est_init_nb)
```

```{r}
# Total volume of trees
a <- mapply(circle3_nb, random_points[, 1], random_points[, 2], MoreArgs = list(15, 9, 6))
est_init_vol <- sum(a/p)
rm(a)
cat("Volume of the forest:", sum(trees$v), "\nEstimation of the volume of the forest:", est_init_vol)
```

# Bootstrap to produce confidence intervals

## Creating other samples based on the previous one

```{r}
# Number of bootstrap samples
B <- 500
```

```{r}
f_boot <- function(df_sample, nboot){
  # df_sample: original sample
  # nboot: number of bootstrap samples made thanks to df_sample

  df_boot <- tibble(.rows = nrow(df_sample))
  for (b in 1:nboot) {
    nb <- sample(1:nrow(df_sample), nrow(df_sample), replace = TRUE)
    sample_b <- df_sample[nb,]
    df_boot <- df_boot %>% add_column(new_col = sample_b)
    colnames(df_boot)[b] <- paste("ech", b, sep = "")
  }
  return(do.call(data.frame, df_boot))
  # Return a data frame with nboot samples of 2 variables and of size n
}
```

```{r}
# Making of bootstrap samples
df_boot <- f_boot(random_points, B)
```

## Estimations and confidence intervals based on the bootstrap samples with three circles

### Number of trees

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot <- function(df_boot, fun){
  # df_boot: dataframe with 2*B columns and n rows
  # fun: function used to calculate the local variable 
  # based on one point of the sample

  nboot <- length(df_boot)/2
  vec_est <- c()
  for (c in 1:nboot) {
    a <- mapply(circle3_nb, df_boot[, (2*c)-1], df_boot[, 2*c], MoreArgs = list(15, 9, 6))
    vec_est <- append(vec_est, sum(a/p))
  }
  vec_est <- sort(vec_est)
  return(vec_est)
  # Vector with one estimation for each sample
}
```

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot_nb <- est_boot(df_init, df_boot, circle3_nb)
```

```{r}
ci_perc <- function(est_init, est_boot){
  # est_init: estimation based on the initial sample
  # est_boot: estimations based on bootstrap samples

  B <- length(est_boot)

  ## 1st step: percentile CI
  lim_inf <- est_boot[floor(B*2.5/100)]
  lim_sup <- est_boot[B - floor(B*2.5/100)]
  cat("95% confidence interval using the percentile method: 
      [", lim_inf, ";", lim_sup, "]\n" )

  ## 2nd step: reverse percentile CI
  cat("95% confidence interval using the reverse percentile method: 
      [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]\n" )
  return(c(est_init,lim_inf,lim_sup))
}
```

```{r}
print("Two intervals for the number of trees:\n")
res_nb <- ci_perc(est_init_nb,est_boot_nb)
```

```{r}
# Visualizing the density, the interval and the first estimation
plot(density(est_boot_nb), xlab="Number of trees",ylab="", main = "Distribution based on bootstrap", las = 1)
abline(v=res_nb[2], col="blue")
abline(v=res_nb[3], col="blue")
abline(v=est_init_nb*2 - res_nb[3], col="green")
abline(v=est_init_nb*2 - res_nb[2], col="green")
abline(v=est_init_nb, col="red")
abline(v=nrow(trees), col="black")
```
Figure 2.**Density based on bootstrap**. The true value (in black), the initial estimation (in red), percentile interval (in blue), reverse percentile interval (in green).

### Total volume of the forest

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot_vol <- est_boot(df_init, df_boot, circle3_vol)
```

```{r}
print("Two intervals for the volume of the forest:\n")
res_nb <- ci_perc(est_init_nb,est_boot_vol)
```

```{r}
# Visualizing the density, the interval and the first estimation
plot(density(est_boot_nb), xlab="Volume of the forest",ylab="", main = "Distribution based on bootstrap", las = 1)
abline(v=res_vol[2], col="blue")
abline(v=res_vol[3], col="blue")
abline(v=est_init_vol*2 - res_vol[3], col="green")
abline(v=est_init_vol*2 - res_vol[2], col="green")
abline(v=est_init_vol, col="red")
abline(v=sum(trees$v), col="black")
```
Figure 3.**Density based on bootstrap**. The true value (in black), the initial estimation (in red), percentile interval (in blue), reverse percentile interval (in green).

### 2024-07-05 Draft/Circle_draft.R

@@ -110,3 +110,110 @@ time.taken3 <- end.time - start.time
 ### Cyclomatic complexity?
 # cyclocomp(circle) # 1
 
+
+##### For the volume ----------
+
+### Functions ----------
+
+## Function to produce the local variable for the number of trees with 3 circle
+circle3_vol <- function(x1, x2, R1=15, R2=9, R3=6){
+  # 2 coordinates (x1, x2) and 3 radii (R1 > R2 > R3)
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  list_trees <- trees[(x1 - trees$x)^2 + (x2 - trees$y)^2 <= R1^2,] # List with all trees inside the biggest circle
+  
+  list_trees1 <- list_trees[(pi*list_trees$d130 > 117.5),] # List with the biggest trees
+  list_trees2 <- list_trees[(pi*list_trees$d130 < 117.5) & (pi*list_trees$d130 > 70.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R2^2),] # medium trees
+  list_trees3 <- list_trees[(pi*list_trees$d130 > 23.5) & (pi*list_trees$d130 < 70.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R3^2),] # smallest trees
+  
+  if (nrow(list_trees1) != 0){
+    local_var1 <- sum((list_trees1$v)/inc_area(c(x1, x2),0,0,1000,1000,R1)) # Local variable for the biggest circle and the biggest trees
+  }else{local_var1 <- 0}
+  if (nrow(list_trees2) != 0){
+    local_var2 <- sum((list_trees2$v)/inc_area(c(x1, x2),0,0,1000,1000,R2))
+  }else{local_var2 <- 0} # Local variable for the medium circle and the medium trees
+  if (nrow(list_trees3) != 0){
+    local_var3 <- sum((list_trees3$v)/inc_area(c(x1, x2),0,0,1000,1000,R3)) # Local variable for the smallest circle and the smallest trees
+  }else{local_var3 <- 0}
+  local_var <- (local_var1 + local_var2 + local_var3) # Addition of the previous local variables
+  return(local_var)
+  # local_var: local variable based on the volume of trees
+}
+
[…]

### 2024-07-05 NFI_method.Rmd
NFI better

@@
 title: "NFI process: grid-based sampling"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 date: "2024-07-05"
@@
 ```{r}
-plot(x = random_points$x, y = random_points$y, xlab = "", ylab = "", main = "Random points", panel.first=grid())
+plot(x = random_points$x, y = random_points$y, xlab = "", ylab = "", main = "Random points", panel.first=grid(), las = 1)
 ```
-Figure 1.**Points sampled following a grid over the whole territory**.
+Figure 1. **Points sampled following a grid over the whole territory**.
 
@@
 # Total volume of trees
-a <- mapply(circle3_nb, random_points[, 1], random_points[, 2], MoreArgs = list(15, 9, 6))
+a <- mapply(circle3_vol, random_points[, 1], random_points[, 2], MoreArgs = list(15, 9, 6))
 est_init_vol <- sum(a/p)
@@
   for (c in 1:nboot) {
-    a <- mapply(circle3_nb, df_boot[, (2*c)-1], df_boot[, 2*c], MoreArgs = list(15, 9, 6))
+    a <- mapply(fun, df_boot[, (2*c)-1], df_boot[, 2*c], MoreArgs = list(15, 9, 6))
     vec_est <- append(vec_est, sum(a/p))
@@
 # Making of one estimation for each sample made by the bootstrap method
-est_boot_nb <- est_boot(df_init, df_boot, circle3_nb)
+est_boot_nb <- est_boot(df_boot, circle3_nb)
 ```
@@
 ```{r}
-print("Two intervals for the number of trees:\n")
+print("Two intervals for the number of trees:")
 res_nb <- ci_perc(est_init_nb,est_boot_nb)
@@
 ```
-Figure 2.**Density based on bootstrap**. The true value (in black), the initial estimation (in red), percentile interval (in blue), reverse percentile interval (in green).
+Figure 2. **Density based on bootstrap**. The true value (in black), the initial estimation (in red), percentile interval (in blue), reverse percentile interval (in green).
 
@@
 # Making of one estimation for each sample made by the bootstrap method
-est_boot_vol <- est_boot(df_init, df_boot, circle3_vol)
+est_boot_vol <- est_boot(df_boot, circle3_vol)
 ```
@@
 ```{r}
-print("Two intervals for the volume of the forest:\n")
-res_nb <- ci_perc(est_init_nb,est_boot_vol)
+print("Two intervals for the volume of the forest:")
+res_vol <- ci_perc(est_init_vol,est_boot_vol)
 ```
@@
 # Visualizing the density, the interval and the first estimation
-plot(density(est_boot_nb), xlab="Volume of the forest",ylab="", main = "Distribution based on bootstrap", las = 1)
+plot(density(est_boot_vol), xlab="Volume of the forest",ylab="", main = "Distribution based on bootstrap", las = 1)
 abline(v=res_vol[2], col="blue")
@@
 ```
-Figure 3.**Density based on bootstrap**. The true value (in black), the initial estimation (in red), percentile interval (in blue), reverse percentile interval (in green).
+Figure 3. **Density based on bootstrap**. The true value (in black), the initial estimation (in red), percentile interval (in blue), reverse percentile interval (in green).

### 2024-07-08 No_tree_no_grid.Rmd
Mardi midi
No excluded tree

@@
 library(magrittr) # for pipes
-library(tibble) # for add_column
+library(tibble) # for add_column and tibble
 ```
@@
 # Sample size
-n <- 100
+n <- 1000
 ```
@@
 est_ind <- sum((random_points$rho2)/p)
-# 510000 e.g.
+# 492000 e.g.
 ```
@@
 est_x <- sum((random_points$x)/p)
-# 499690876 e.g.
+# 490781983 e.g.
 ```
@@
 var_area <- ((1000*1000)/(n-1))*est_carre - (1/(n-1))*(est_area^2)
-# The empirical variance is null as expected
+# The variance estimation is null as expected
 ```
@@
 # Conclusion
-cat("Variance théorique :", varTHEO_area, "\nVariance empirique :", var_area)
+cat("Variance théorique :", varTHEO_area, "\nEstimation de la variance :", var_area)
 ```
@@
 var_ind <- ((1000*1000)/(n-1))*est_ind - (1/(n-1))*(est_ind^2)
-# Empirical variance: 2.491e+09 e.g.
+# Variance estimation: 250186186 e.g.
 ```
@@
 varTHEO_ind <- half_area/p - (1/n)*(half_area^2)
-# Theoretical variance: 2.5e+09, i.e. around 2.498e+09
+# Theoretical variance: 2.5e+08, i.e. around 250186186
 # Close to the empirical one
@@
 # Conclusion
-cat("Variance théorique :", varTHEO_ind, "\nVariance empirique :", var_ind)
+cat("Variance théorique :", varTHEO_ind, "\nEstimation de la variance :", var_ind)
 ```
@@
 var_x <- ((1000*1000)/(n-1))*est_x2 - (1/(n-1))*(est_x^2)
-# Empirical variance: 8.407871e+14 ?!
+# Variance estimation: 8.341029e+13
 ```
@@
 varTHEO_x <- val_x2/p - (1/n)*(val_x^2)
-# Theoretical variance: 2.5e+09, i.e. around 2.498e+09
-# Close to the empirical one
+# Theoretical variance: 8.333333e+13, i.e. around 8.341029e+13
+# Close to the estimated one
 ```
@@
 # Conclusion
-cat("Variance théorique :", varTHEO_x, "\nVariance empirique :", var_x)
+cat("Variance théorique :", varTHEO_x, "\nEstimation de la variance :", var_x)
 ```
@@
 ```{r}
-rm(a1, a2, x, y, b, col_, col_names) # Useless now
+rm(a1, a2, x, y, b, col_names) # Useless now
 ```
@@
 # should be close to 5e+08
-# 499121662 e.g.
+# 500182431 e.g.
 ```
@@
 ```{r}
-# Empirical standard deviation based on MC
-cat("Variance associée aux échantillons de Monte Carlo :", sd(est_MC))
-# 28710306 e.g.
+# Variance estimation based on MC
+cat("Theoretical variance:", varTHEO_x, "\nVariance associée aux échantillons de Monte Carlo :", var(est_MC))
+# 8.512412e+13 e.g.
 ```
@@
   rho_MC <- tibble(.rows = n)
-    # data.frame(x.1 = rep(0, n), y.1 = rep(0, n))
   col_names <- c()
@@
   }
-  # rho_MC$x.1 <- NULL
-  # rho_MC$y.1 <- NULL
   colnames(rho_MC) <- col_names
@@
 
-  est_value <- mean(est_MC) # Estimated value
-  return(est_value)
+  return(c(mean(est_MC), var(est_MC)))
+  # Estimated value and Monte-Carlo variance
 }
@@
 res <- true_vs_MC(n = 1000, B = 1000, f = f_1)
-cat("True integral:", 1e+06, "\nMean of all the estimations:", res)
-# 1e+06 1e+06 (Equality as always)
+cat("True integral:", 1e+06, "\nMean of all the estimations:", res[1])
+cat("\n\nTheoretical variance:", varTHEO_area, "\nMonte-Carlo variance:", res[2])
+# Totals: 1e+06 and 1e+06 (Equality as always)
+# Variances: 0 and 0 (Equality as always)
 ```
@@
 res <- true_vs_MC(n = 1000, B = 1000, f = f_ind)
-cat("True integral:", 500000, "\nMean of all the estimations:", res)
-
+cat("True integral:", 500000, "\nMean of all the estimations:", res[1])
+cat("\n\nTheoretical variance:", varTHEO_ind, "\nMonte-Carlo variance:", res[2])
 # Ex:
 # True integral: 5e+05 
-# Mean of all the estimations: 499600
+# Mean of all the estimations: 499214
+
+# Theoretical variance: 2.5e+08 
+# Monte-Carlo variance: 245287491
 ```
@@
 res <- true_vs_MC(n = 1000, B = 1000, f = f_x)
-cat("True integral:", 5e+08, "\nMean of all the estimations:", res)
-
+cat("True integral:", 5e+08, "\nMean of all the estimations:", res[1])
+cat("\n\nTheoretical variance:", varTHEO_x, "\nMonte-Carlo variance:", res[2])
 # Ex:
 # True integral: 5e+08 
-# Mean of all the estimations: 500189987
+# Mean of all the estimations: 499874718
+
+# Theoretical variance: 8.333333e+13 
+# Monte-Carlo variance: 7.99389e+13
 ```

### 2024-07-08 Trees_no_grid.Rmd
No excluded tree

@@
 
+```{r}
+### Necessary step to calculate the theoretical variance
+
+# Creating a local variable (cf pages 10-11 in Trinh et alii (2024))
+local_var2 <- c()
+source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+for (placette in 1:n) {
+  local_var2 <- append(local_var2, (sum(trees_in[trees_in[placette] != 0,]/inc_area(c(random_points[placette,]$x, random_points[placette,]$y),0,0,1000,1000,R)))^2)
+}
+
+est_nb2 <- sum((local_var2)/p)
+
+cat("An estimation of the total number of trees based on the sample:", )
+```
+
 ## Automation
@@
 
-  true_value <- nrow(trees) # Theoretical value
-  est_value <- mean(est_MC) # Estimated value
-  return(c(true_value, est_value))
+  return(c(nrow(trees), mean(est_MC), var(est_MC)))
+  # Theoretical value of the total, estimated value of the total, Monte-Carlo variance
 }
@@
 cat("True number of trees:", res[1], "\nMean of all the estimations (Monte Carlo):", res[2])
+cat("\n\nTheoretical variance:", , "\nMonte-Carlo variance:", res[3])
 # Ex:

### 2024-07-08 Useful_functions/Circle.R

@@ -37,7 +37,8 @@ circle3_nb <- function(x1, x2, R1=15, R2=9, R3=6){
   
   list_trees1 <- list_trees[(pi*list_trees$d130 > 117.5),] # List with the biggest trees
   list_trees2 <- list_trees[(pi*list_trees$d130 < 117.5) & (pi*list_trees$d130 > 70.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R2^2),] # medium trees
-  list_trees3 <- list_trees[(pi*list_trees$d130 > 23.5) & (pi*list_trees$d130 < 70.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R3^2),] # smallest trees
+  list_trees3 <- list_trees[(pi*list_trees$d130 < 70.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R3^2),] # smallest trees
+  # In the real NFI process, we should have in addition: (pi*list_trees$d130 > 23.5) &
   
   local_var1 <- sum(nrow(list_trees1)/inc_area(c(x1, x2),0,0,1000,1000,R1)) # Local variable for the biggest circle and the biggest trees
   local_var2 <- sum(nrow(list_trees2)/inc_area(c(x1, x2),0,0,1000,1000,R2)) # Local variable for the medium circle and the medium trees
@@ -58,7 +59,8 @@ circle3_vol <- function(x1, x2, R1=15, R2=9, R3=6){
   
   list_trees1 <- list_trees[(pi*list_trees$d130 > 117.5),] # List with the biggest trees
   list_trees2 <- list_trees[(pi*list_trees$d130 < 117.5) & (pi*list_trees$d130 > 70.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R2^2),] # medium trees
-  list_trees3 <- list_trees[(pi*list_trees$d130 > 23.5) & (pi*list_trees$d130 < 70.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R3^2),] # smallest trees
+  list_trees3 <- list_trees[(pi*list_trees$d130 < 70.5) & ((x1 - list_trees$x)^2 + (x2 - list_trees$y)^2 <= R3^2),] # smallest trees
+  # In the real NFI process, we should have in addition: (pi*list_trees$d130 > 23.5) &
   
   if (nrow(list_trees1) != 0){
[…]

### 2024-07-09 MC_boot.Rmd
Try to merge MC and bootstrap

---
title: "Monte-Carlo and bootstrap together"
output: html_document
date: "2024-07-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
```

# Preliminaries

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
```

```{r}
# Functions to produce a local variable
source("~/work/Sim_article2024/Useful_functions/Circle.R")
```

# Useful functions

```{r}
f_boot <- function(df_sample, B){
  # df_sample: original sample; B: number of bootstrap samples made thanks to df_sample

  df_boot <- tibble(.rows = nrow(df_sample))
  for (b in 1:B) {
    nb <- sample(1:nrow(df_sample), nrow(df_sample), replace = TRUE)
    sample_b <- df_sample[nb,]
    df_boot <- df_boot %>% add_column(new_col = sample_b)
    colnames(df_boot)[b] <- paste("ech", b, sep = "")
  }
  return(do.call(data.frame, df_boot))
  # Return a data frame with B samples of 2 variables and of size n
}
```

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot <- function(df_boot, p, fun){
  # df_boot: dataframe with 2*B columns and n rows
  # fun: function used to calculate the local variable 
  # based on one point of the sample

  nboot <- length(df_boot)/2
  vec_est <- c()
  for (c in 1:nboot) {
    a <- mapply(fun, df_boot[, (2*c)-1], df_boot[, 2*c])
    vec_est <- append(vec_est, sum(a/p))
  }
  vec_est <- sort(vec_est)
  return(vec_est)
  # Vector with one estimation for each sample
}
```

# A function to plug bootstrap in a MC process

```{r}
### Function to automate Monte Carlo method

MC_boot <- function(n, B1, B2, f){
  # n: sample size; B1: number of iterations for MC;
  # B2: number of iterations for bootstrap;
  # f: function to consider (2 arguments)
  # Argument grid? (change n then)
  p <- sum(rep((1/1000)*(1/1000), n))

  est_MC <- c()
  mean_est_boot <- c()
  var_est_boot <- c()

  for (b in 2:B1) {
    # One MC iteration at a time
    random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
    a <- mapply(f, random_points[, 1], random_points[, 2])
    a <- sum(a/p)
    est_MC <- append(est_MC, a)

    # Bootstrap iterations
    df_boot <- f_boot(random_points, B2)
    est_boot_val <- est_boot(df_boot, p, f)
    mean_est_boot <- append(mean_est_boot, mean(est_boot_val))
    var_est_boot <- append(var_est_boot, var(est_boot_val))
  }
  return(c(mean(est_MC), var(est_MC), mean(var_est_boot)))
  # Estimated value of the total, Monte-Carlo variance, mean of the bootstrap variance
}
```

```{r}
MC_boot(n = 100, B1 = 1000, B2 = 200, f = circle3_nb)
```

```{r}

```

### 2024-07-10 Test.Rmd
Try to merge MC and bootstrap
A consistent bootstrap method

@@
 
-$\mapsto$ 1
-
 ```{r}
@@
 ```
+
+# Variance théorique
+
+```{r}
+for (k in 1:nrow(trees)) {
+  for (i in 1:k) {
+
+  }
+  sum_i <- sum()
+}
+```
+
+# MC_boot
+
+## Tests
+
+```{r}
+start.time <- Sys.time()
+
+MC_boot(n = 100, B1 = 1000, B2 = 200, f = circle3_nb)
+# Way too long
+```
+
+```{r}
+start.time <- Sys.time()
+
+res <- MC_boot(n = 100, B1 = 500, B2 = 100, f = circle3_nb)
+
+end.time <- Sys.time()
+time.taken1 <- end.time - start.time
+
+time.taken1
+# Way too long
+```
+
+```{r}
+start.time <- Sys.time()
+
+res <- MC_boot(n = 50, B1 = 10, B2 = 5, f = circle3_nb)
+
+end.time <- Sys.time()
+time.taken2 <- end.time - start.time
+
+time.taken2
+# Time difference of 5.522393 secs
+# 31471.63 78177624.15 53692218.51
+```
+
+```{r}
+start.time <- Sys.time()
+
+res <- MC_boot(n = 100, B1 = 100, B2 = 50, f = circle3_nb)
+
+end.time <- Sys.time()
+time.taken2 <- end.time - start.time
+
+time.taken2
+# Time difference of 5.522393 secs
+# 31471.63 78177624.15 53692218.51
+```
+
+# Volume
+
+```{r}
+# Total volume of trees
+a <- mapply(circle3_vol, random_points[, 1], random_points[, 2], MoreArgs = list(15, 9, 6))
+est_init_vol <- sum(a/p)
+rm(a)
+cat("Volume of the forest:", sum(trees$v), "\nEstimation of the volume of the forest:", est_init_vol)
+```

### 2024-07-10 adapt_boot.Rmd
A consistent bootstrap method

---
title: "Adapting bootstrap to our problem"
output: html_document
date: "2024-07-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
```

# Preliminaries

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
```

```{r}
# Functions to produce a local variable
source("~/work/Sim_article2024/Useful_functions/Circle.R")
```

# A first sample

## Sampling in one 10th of the small squares of a grid

```{r}
### Randomizing the positions of the numbers (from 1 to 10) 
# used to identify small squares in the grid
random10 <- sample(1:10)
i <- sample(1:10, 1) # choice of the rank of the identifier we want
nb <- random10[i] # the identifier thus chosen
```

```{r}
# Dimension of a small square (length of one side of the square)
# We assume that c_dim is a divisor of 1000
c_dim <- 10
```

```{r}
# Now, we sample at random following the grid
random_points <- data.frame(x = numeric(), y = numeric(), l = numeric())

# column l in addition
for (l in 0:((1000/c_dim)-1)) {
  if (l==0){
    x_init <- i*c_dim
  }else if ((3*l+i)*c_dim < (10)*c_dim){
    x_init <- (3*l+i)*c_dim
  }else{
    x_init <- (((3*l+i)*c_dim)%%(c_dim*10))
  }
  k <- 0
  while (x_init + 10*c_dim*k < 1000) {
    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + c_dim)
    b <- runif(1, l*c_dim, (l+1)*c_dim)
    random_points <- rbind(random_points, list(a,b, l))
    k <- k+1
  }
}
colnames(random_points) <- list("x", "y", "l")
```

```{r}
plot(x = random_points$x, y = random_points$y, xlab = "", ylab = "", main = "Random points", panel.first=grid(), las = 1)
```
Figure 1. **Points sampled following a grid over the whole territory**.

```{r}
rm(a,b,l,x_init,k)
```

```{r}
### Values available after sampling

# Sample size
n <- nrow(random_points)

# Marginal density: density of the uniform distribution over 1:1000
# Which leads us to the inclusion density function
p <- sum(rep((1/1000)*(1/1000), n))
```

## Estimations based on the sample previously made

```{r}
# Number of trees
random_points$var <- mapply(circle3_nb, random_points[, 1], random_points[, 2], MoreArgs = list(15, 9, 6))
est_init_nb <- sum(random_points$var/p)
cat("Number of trees:", nrow(trees), "\nEstimation of the number of trees:", est_init_nb)

# Ex:
# Number of trees: 30942 
# Estimation of the number of trees: 31066.18

# Number of trees: 30942 
# Estimation of the number of trees: 30489.25
```

```{r}
plot(x = random_points[, 1], y = random_points$var, xlab = "x", main = "Points as a function of x", las = 1)
```

```{r}
plot(x = random_points[, 2], y = random_points$var, xlab = "y", main = "Points as a function of y", las = 1)
```

# Bootstrap

```{r}
# Number of bootstrap samples
B <- 500
```

## First method to make bootstrap samples

```{r}
# We only keep x and y in the dataframe
random_points_1 <- random_points
random_points_1$l <- NULL
```

```{r}
f_boot <- function(df_sample, B){
  # df_sample: original sample; B: number of bootstrap samples made thanks to df_sample

  df_boot <- tibble(.rows = nrow(df_sample))
  for (b in 1:B) {
    nb <- sample(1:nrow(df_sample), nrow(df_sample), replace = TRUE)
    sample_b <- df_sample[nb,]
    df_boot <- df_boot %>% add_column(new_col = sample_b)
    colnames(df_boot)[b] <- paste("ech", b, sep = "")
  }
  return(do.call(data.frame, df_boot))
  # Return a data frame with B samples of 2 variables and of size n
}
```

```{r}
# Making of bootstrap samples
df_boot <- f_boot(random_points_1, B)
```

```{r}
# In case B=1
# plot(x = df_boot$ech1.x, y = df_boot$ech1.y)
```

## Second method to make bootstrap samples

```{r}
f_boot2 <- function(df_sample, nboot){
  # df_sample: original sample
  # nboot: number of bootstrap samples made thanks to df_sample

  odd_even1 <- sample(1:2, 1) # Randomly put more weight on even or odd lines
  odd_even2 <- sample(1:2, 1) # The same for "columns"
  # df_sample$prob <- (as.numeric(floor(df_sample$y/10)%%2 == odd_even1%%2)*(3/4) + as.numeric(floor(df_sample$y/10)%%2 != odd_even1%%2)*(1/4) + 
  #                      df_sample[df_sample$l]$x +
  #                      as.numeric(floor(df_sample$x/10)%%2 == odd_even2%%2)*(3/4) + as.numeric(floor(df_sample$x/10)%%2 != odd_even2%%2)*(1/4))/2

  df_sample$step <- rep(0, nrow(df_sample))
  for (line in unique(df_sample$l)) {
    df_sample$step <- (df_sample$step == 0)*(row(df_sample[df_sample$l == line,])[,1]%%2) + (df_sample$step != 0)*df_sample$step
  }
  # df_sample$prob <- ((df_sample$l+odd_even1)%%2 + (df_sample$step+odd_even2)%%2)
  df_sample$prob <- (((df_sample$l+odd_even1)%%2 + (df_sample$step+odd_even2)%%2) == 0)*(1/4) +
    (((df_sample$l+odd_even1)%%2 + (df_sample$step+odd_even2)%%2) == 1)*(1/2) +
    (((df_sample$l+odd_even1)%%2 + (df_sample$step+odd_even2)%%2) == 2)*(3/4)
  df_sample$l <- NULL
  df_sample$step <- NULL

  df_boot <- tibble(.rows = nrow(df_sample))
  for (b in 1:nboot) {
    nb <- sample(1:nrow(df_sample), nrow(df_sample), replace = TRUE, prob = df_sample$prob)
    df_sample$prob <- NULL
    sample_b <- df_sample[nb,]
    df_boot <- df_boot %>% add_column(new_col = sample_b)
    colnames(df_boot)[b] <- paste("ech", b, sep = "")
  }
  return(do.call(data.frame, df_boot))
  # Return a data frame with nboot samples of 2 variables and of size n
}
```

```{r}
# Making of bootstrap samples
df_boot2 <- f_boot2(random_points, B)
```

```{r}
# In case B=1
# plot(x = df_boot2$ech1.x, y = df_boot2$ech1.y)
```

## Number of trees

### First method

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot1 <- function(df){
  # df: dataframe with 3*B columns and n rows

  nboot <- length(df)/3
  vec_est <- c()
  for (c in 1:nboot) {
    vec_est <- append(vec_est, sum(df[,3*c]/p))
  }
  vec_est <- sort(vec_est)
  return(vec_est)
  # Vector with one estimation for each sample
}
```

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot_1 <- est_boot1(df_boot)
```

```{r}
mean(est_boot_1)
# 31055.71 e.g.
# 30488.92
```

```{r}
var(est_boot_1)
# 2791309 e.g.
# 2577277
```

### Second method

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot_2 <- est_boot1(df_boot2)
```

```{r}
mean(est_boot_2)
# 31153.14 e.g.
# 30499.57
```

```{r}
var(est_boot_2)
# 3222756 e.g.
# 2351291
```

# Comparison between both methods

```{r}
comparison <- function(ncomp, B) {
  # ncomp: number of bootstrap series to compare
  # B: number of bootstrap replications each time
  tot_mean <- c()
  tot_var <- c()
  b <- 1
  for (b in 1:ncomp) {
    ## First method
    # We only keep x and y in the dataframe
    random_points_1 <- random_points
    random_points_1$l <- NULL
    df_boot <- f_boot(random_points_1, B)
    est_boot_1 <- est_boot1(df_boot)

    ## Second method
    df_boot2 <- f_boot2(random_points, B)
    est_boot_2 <- est_boot1(df_boot2)

    tot_mean <- append(tot_mean, as.numeric(abs(mean(est_boot_2)-30942) <  abs(mean(est_boot_1)-30942)))
    # 1: the second method is better
    tot_var <- append(tot_var, as.numeric(var(est_boot_2) <  var(est_boot_1)))
    # 1: the second method is better
    b <- b+1
  }
  return(tot_mean, tot_var)
}
```

```{r}
comparison(100, 500)
```

```{r}
sum(tot_mean)
```

```{r}
sum(tot_var)
```

### 2024-07-10 Useful_functions/Circle.R

@@ -26,7 +26,7 @@ circle_vol <- function(x1, x2, R=5){
   # list_trees: identifiers of targeted trees; local_var: local variable based on the volume of trees
 }
 
-## Function to produce the local variable for the number of trees with 3 circle
+## Function to produce the local variable for the number of trees with 3 circles
 circle3_nb <- function(x1, x2, R1=15, R2=9, R3=6){
   # 2 coordinates (x1, x2) and 3 radii (R1 > R2 > R3)
   
@@ -48,7 +48,7 @@ circle3_nb <- function(x1, x2, R1=15, R2=9, R3=6){
   # local_var: local variable based on the number of trees
 }
 
-## Function to produce the local variable for the number of trees with 3 circle
+## Function to produce the local variable for the number of trees with 3 circles
 circle3_vol <- function(x1, x2, R1=15, R2=9, R3=6){
   # 2 coordinates (x1, x2) and 3 radii (R1 > R2 > R3)
   

### 2024-07-10 adapt_boot.Rmd
Adapted bootstrap is fine

@@
 title: "Adapting bootstrap to our problem"
-output: html_document
+output: pdf_document
 date: "2024-07-10"
@@
 ```
+
+The goal of this document is to create another bootstrap function that is adapted to the problem of continuous sampling with a grid.
+Indeed, we want a bootstrap function that takes into account the regularity of the sampling which is induced by the grid.
 
@@
 
-```{r}
-plot(x = random_points[, 1], y = random_points$var, xlab = "x", main = "Points as a function of x", las = 1)
-```
-
-```{r}
-plot(x = random_points[, 2], y = random_points$var, xlab = "y", main = "Points as a function of y", las = 1)
-```
-
 # Bootstrap
@@
 ```
+
+Here, two methods are used: a naive one and an adapted one.
 
@@
 
-    tot_mean <- append(tot_mean, as.numeric(abs(mean(est_boot_2)-30942) <  abs(mean(est_boot_1)-30942)))
+    tot_mean <- append(tot_mean, as.numeric(abs(mean(est_boot_2)-30942) <  abs(mean(est_boot_1)-30942))*2-1)
     # 1: the second method is better
-    tot_var <- append(tot_var, as.numeric(var(est_boot_2) <  var(est_boot_1)))
+    tot_var <- append(tot_var, as.numeric(var(est_boot_2) <  var(est_boot_1))*2-1)
     # 1: the second method is better
@@
   }
-  return(tot_mean, tot_var)
+  return(list(tot_mean, tot_var))
 }
@@
 ```{r}
-comparison(100, 500)
+res <- comparison(100, 500)
 ```
@@
 ```{r}
-sum(tot_mean)
+# If it is positive, the second method is the best to estimate the total
+sum(res[[1]])
+# 10 e.g.
+# 18
 ```
@@
 ```{r}
-sum(tot_var)
+# If it is positive, the second method is the best to minimize the variance
+sum(res[[2]])
+# 2 e.g.
+# 12
 ```
+
+# Conclusion
+
+Adapting bootstrap to the problem seems relevant.

### 2024-07-10 adapt_boot.Rmd
Variance much better for adapted bootstrap

@@
 ```{r}
-res <- comparison(100, 500)
+res <- comparison(1000, 800)
 ```
@@
 sum(res[[1]])
+# With ncomp = 100 and B = 500
 # 10 e.g.
 # 18
+
+# With ncomp = 1000 and B = 800
+# -4
 ```
@@
 sum(res[[2]])
+# With ncomp = 100 and B = 500
 # 2 e.g.
 # 12
+
+# With ncomp = 1000 and B = 800
+# 56
 ```
@@
 
-Adapting bootstrap to the problem seems relevant.
+Adapting bootstrap to the problem seems relevant: it does not improve much the estimator but it reduces its variance.

### 2024-07-11 adapt_boot2.Rmd
Not done yet

--- 2024-07-10 adapt_boot.Rmd
@@
 ---
-title: "Adapting bootstrap to our problem"
+title: "Adapting bootstrap to our problem - Part 2"
 output: pdf_document
-date: "2024-07-10"
+date: "2024-07-11"
 ---
@@
 library(tibble) # for add_column
+library(ggplot2)
 ```
@@
 
-```{r}
-# Number of bootstrap samples
-B <- 500
-```
-
 Here, two methods are used: a naive one and an adapted one.
@@
 
-```{r}
-# Making of bootstrap samples
-df_boot <- f_boot(random_points_1, B)
-```
-
-```{r}
-# In case B=1
-# plot(x = df_boot$ech1.x, y = df_boot$ech1.y)
-```
-
 ## Second method to make bootstrap samples
@@
 f_boot2 <- function(df_sample, nboot){
-  # df_sample: original sample
+  # df_sample: original sample (4 variables: x,y,l,var)
   # nboot: number of bootstrap samples made thanks to df_sample
@@
   odd_even2 <- sample(1:2, 1) # The same for "columns"
-  # df_sample$prob <- (as.numeric(floor(df_sample$y/10)%%2 == odd_even1%%2)*(3/4) + as.numeric(floor(df_sample$y/10)%%2 != odd_even1%%2)*(1/4) + 
-  #                      df_sample[df_sample$l]$x +
-  #                      as.numeric(floor(df_sample$x/10)%%2 == odd_even2%%2)*(3/4) + as.numeric(floor(df_sample$x/10)%%2 != odd_even2%%2)*(1/4))/2
 
@@
   for (line in unique(df_sample$l)) {
-    df_sample$step <- (df_sample$step == 0)*(row(df_sample[df_sample$l == line,])[,1]%%2) + (df_sample$step != 0)*df_sample$step
+    df_sample$step <- as.numeric(df_sample$step == 0)*(row(df_sample[df_sample$l == line,])[,1]%%2) + as.numeric(df_sample$step != 0)*df_sample$step
   }
-  # df_sample$prob <- ((df_sample$l+odd_even1)%%2 + (df_sample$step+odd_even2)%%2)
+
   df_sample$prob <- (((df_sample$l+odd_even1)%%2 + (df_sample$step+odd_even2)%%2) == 0)*(1/4) +
@@
 
-```{r}
-# Making of bootstrap samples
-df_boot2 <- f_boot2(random_points, B)
-```
-
-```{r}
-# In case B=1
-# plot(x = df_boot2$ech1.x, y = df_boot2$ech1.y)
-```
-
 ## Number of trees
-
-### First method
 
@@
 
-```{r}
-# Making of one estimation for each sample made by the bootstrap method
-est_boot_1 <- est_boot1(df_boot)
-```
-
-```{r}
-mean(est_boot_1)
-# 31055.71 e.g.
-# 30488.92
-```
-
-```{r}
-var(est_boot_1)
-# 2791309 e.g.
-# 2577277
-```
-
-### Second method
-
-```{r}
-# Making of one estimation for each sample made by the bootstrap method
-est_boot_2 <- est_boot1(df_boot2)
-```
-
-```{r}
-mean(est_boot_2)
-# 31153.14 e.g.
-# 30499.57
-```
-
-```{r}
-var(est_boot_2)
-# 3222756 e.g.
-# 2351291
-```
-
 # Comparison between both methods
@@
 ```{r}
-comparison <- function(ncomp, B) {
-  # ncomp: number of bootstrap series to compare
+comparison2 <- function(B) {
   # B: number of bootstrap replications each time
-  tot_mean <- c()
-  tot_var <- c()
-  b <- 1
-  for (b in 1:ncomp) {
+  mean_vec1 <- c()
+  mean_vec2 <- c()
+  var_vec1 <- c()
+  var_vec2 <- c()
+  b1 <- 100
+  while (b1  < B) {
     ## First method
@@
     random_points_1$l <- NULL
-    df_boot <- f_boot(random_points_1, B)
+    df_boot <- f_boot(random_points_1, b1)
     est_boot_1 <- est_boot1(df_boot)
@@
     ## Second method
-    df_boot2 <- f_boot2(random_points, B)
+    df_boot2 <- f_boot2(random_points, b1)
     est_boot_2 <- est_boot1(df_boot2)
 
-    tot_mean <- append(tot_mean, as.numeric(abs(mean(est_boot_2)-30942) <  abs(mean(est_boot_1)-30942))*2-1)
+    mean_vec1 <- append(mean_vec1, abs(mean(est_boot_1)-30942))
+    mean_vec2 <- append(mean_vec2, abs(mean(est_boot_2)-30942))
+
+    var_vec1 <- append(var_vec1, var(est_boot_1))
+    var_vec2 <- append(var_vec2, var(est_boot_2))
+
+    # tot_mean <- append(tot_mean, as.numeric(abs(mean(est_boot_2)-30942) <  abs(mean(est_boot_1)-30942))*2-1)
     # 1: the second method is better
-    tot_var <- append(tot_var, as.numeric(var(est_boot_2) <  var(est_boot_1))*2-1)
+    # tot_var <- append(tot_var, as.numeric(var(est_boot_2) <  var(est_boot_1))*2-1)
     # 1: the second method is better
-    b <- b+1
+    b1 <- b1+10
   }
-  return(list(tot_mean, tot_var))
+  return(list(mean_vec1, mean_vec2, var_vec1, var_vec2))
 }
@@
 ```{r}
-res <- comparison(1000, 800)
+res2 <- comparison2(500)
 ```
@@
 ```{r}
-# If it is positive, the second method is the best to estimate the total
-sum(res[[1]])
-# With ncomp = 100 and B = 500
-# 10 e.g.
-# 18
+res <- comparison2(500)
+```
 
-# With ncomp = 1000 and B = 800
-# -4
+```{r}
+data = as.data.frame(cbind(1:length(res2[[1]]), res2[[1]], res2[[2]]))
+p1 <- ggplot(data, aes(data[,1], data[,2]))
+p2 <- ggplot(data, aes(data[,1], data[,3]))
+p1 + p2 + geom_point()
+p1 + geom_point
+
+# p <- ggplot(data, aes(data[,1], cbind(data[,2], data[,3])))
+# p + geom_point()
+
+p <- ggplot(data, aes(data[,1], data[,3] - data[,2]))
+p + geom_point()
+```
+
+```{r}
+data_var = as.data.frame(cbind(1:length(res2[[1]]), res2[[3]], res2[[4]]))
+
+p <- ggplot(data_var, aes(data_var[,1], data_var[,3] - data_var[,2]))
+p + geom_point()
+```
+
+```{r}
+data_var = as.data.frame(cbind(1:length(res2[[1]]), res2[[3]], res2[[4]]))
+
+p <- ggplot(data_var, aes(data_var[,1], data_var[,3] - data_var[,2]))
+p + geom_point()
+```
+
+```{r}
+ggplot(x = 1:length(res[[1]]), y = res[[1]]) +
+  plot(x = 1:length(res[[1]]), y = res[[2]], col = "red")
+geom_point(
+    mapping = aes(y = group_mean), data = group_means_df,
+    colour = 'red', size = 3)
+
 ```
@@
 # Conclusion
-
-Adapting bootstrap to the problem seems relevant: it does not improve much the estimator but it reduces its variance.

### 2024-07-11 adapt_boot2.Rmd
Not done yet v2

@@
   for (line in unique(df_sample$l)) {
+    print(line)
     df_sample$step <- as.numeric(df_sample$step == 0)*(row(df_sample[df_sample$l == line,])[,1]%%2) + as.numeric(df_sample$step != 0)*df_sample$step

### 2024-07-11 adapt_boot2.Rmd
Better comparison

--- 2024-07-11 adapt_boot2.Rmd
@@
 library(tibble) # for add_column
-library(ggplot2)
+library(ggplot2) # To plot scatterplots
+library(dplyr) # for select
 ```
@@
     nb <- sample(1:nrow(df_sample), nrow(df_sample), replace = TRUE, prob = df_sample$prob)
-    df_sample$prob <- NULL
     sample_b <- df_sample[nb,]
@@
   }
-  return(do.call(data.frame, df_boot))
-  # Return a data frame with nboot samples of 2 variables and of size n
+  df_boot <- do.call(data.frame, df_boot)
+  df_boot <- df_boot %>% select(-contains("prob")) # Probabilities are useless now
+  return(df_boot)
+  # Return a data frame with nboot samples of 2 variables (x,y,local variable) and of size n
 }
@@
 ```{r}
-comparison2 <- function(B) {
+comparison2 <- function(df_init, B, small_step) {
+  # df_init: initial data frame with 4 variables, just as random_points
   # B: number of bootstrap replications each time
+  # small_step: step to decide how many bootstrap series will be computed
+  # large small_step => a few bootstrap series
   mean_vec1 <- c()
@@
     # We only keep x and y in the dataframe
-    random_points_1 <- random_points
-    random_points_1$l <- NULL
-    df_boot <- f_boot(random_points_1, b1)
+    df_init_1 <- df_init
+    df_init_1$l <- NULL
+    df_boot <- f_boot(df_init_1, b1)
     est_boot_1 <- est_boot1(df_boot)
@@
     ## Second method
-    df_boot2 <- f_boot2(random_points, b1)
+    df_boot2 <- f_boot2(df_init, b1)
     est_boot_2 <- est_boot1(df_boot2)
@@
     # 1: the second method is better
-    b1 <- b1+10
+    b1 <- b1+small_step
   }
@@
 ```{r}
-res2 <- comparison2(500)
+B_test <- 800
 ```
@@
 ```{r}
-res <- comparison2(500)
+df_test <- random_points
+res2 <- comparison2(df_test, B_test, 1)
 ```
@@
 ```{r}
+# We look at the mean of estimators
 data = as.data.frame(cbind(1:length(res2[[1]]), res2[[1]], res2[[2]]))
-p1 <- ggplot(data, aes(data[,1], data[,2]))
-p2 <- ggplot(data, aes(data[,1], data[,3]))
-p1 + p2 + geom_point()
-p1 + geom_point
 
-# p <- ggplot(data, aes(data[,1], cbind(data[,2], data[,3])))
-# p + geom_point()
-
-p <- ggplot(data, aes(data[,1], data[,3] - data[,2]))
-p + geom_point()
+p <- ggplot(data, aes(data[,1], data[,2] - data[,3]))
+p + geom_point() +ggtitle("Comparison of the mean of estimators") + xlab("Number of bootstrap replications") + ylab("First method minus Second method")
 ```
@@
 
-p <- ggplot(data_var, aes(data_var[,1], data_var[,3] - data_var[,2]))
-p + geom_point()
+p <- ggplot(data_var, aes(data_var[,1], data_var[,2] - data_var[,3]))
+p + geom_point() + ggtitle("Comparison of the variance of estimators") + xlab("Number of bootstrap replications") + ylab("First method minus Second method")
+
+# If it is positive, method 2 is better
 ```
@@
 ```{r}
-data_var = as.data.frame(cbind(1:length(res2[[1]]), res2[[3]], res2[[4]]))
+# To what extent does the second method improve variance?
+cat("If it is positive, it indicates that the second method improve reducing the variance.")
+cat("\nWith all bootstrap samples:", mean(data_var[,2] - data_var[,3]))
+cat("\nWith the first half of bootstrap series (between 100 and ", floor((B_test+100)/2)," samples): ", mean(data_var[1:(floor((B_test+100)/2)-100),2] - data_var[1:(floor((B_test+100)/2)-100),3]), sep = "")
+cat("\nWith the last half of bootstrap series (between ", floor((B_test+100)/2)," and ", B_test, " samples): ", mean(data_var[(floor((B_test+100)/2)-100):(B_test-100),2] - data_var[(floor((B_test+100)/2)-100):(B_test-100),3]), sep = "")
 
-p <- ggplot(data_var, aes(data_var[,1], data_var[,3] - data_var[,2]))
-p + geom_point()
+# Ex:
+# With all bootstrap samples: 13172.49
+# With the first half of bootstrap series (between 100 and 300): -3856.388
+# With the last half of bootstrap series (between 300 and 500 samples): 27526.69
 ```
-
-```{r}
-ggplot(x = 1:length(res[[1]]), y = res[[1]]) +
-  plot(x = 1:length(res[[1]]), y = res[[2]], col = "red")
-geom_point(
-    mapping = aes(y = group_mean), data = group_means_df,
-    colour = 'red', size = 3)
-
-```
-
-```{r}
-# If it is positive, the second method is the best to minimize the variance
-sum(res[[2]])
-# With ncomp = 100 and B = 500
-# 2 e.g.
-# 12
-
-# With ncomp = 1000 and B = 800
-# 56
-```
-
-# Conclusion

### 2024-07-12 MC_boot2.Rmd
Faster MC_boot

--- 2024-07-09 MC_boot.Rmd
@@
 ---
-title: "Monte-Carlo and bootstrap together"
-output: html_document
-date: "2024-07-09"
+title: "Monte-Carlo and bootstrap together - Part 2"
+output:
+  pdf_document: default
+  html_document: default
+date: "2024-07-11"
 ---
@@
 # Making of one estimation for each sample made by the bootstrap method
-est_boot <- function(df_boot, p, fun){
-  # df_boot: dataframe with 2*B columns and n rows
-  # fun: function used to calculate the local variable 
-  # based on one point of the sample
+est_boot <- function(df, p){
+  # df: dataframe with 3*B columns and n rows
 
-  nboot <- length(df_boot)/2
+  nboot <- length(df)/3
   vec_est <- c()
   for (c in 1:nboot) {
-    a <- mapply(fun, df_boot[, (2*c)-1], df_boot[, 2*c])
-    vec_est <- append(vec_est, sum(a/p))
+    vec_est <- append(vec_est, sum(df[,3*c]/p))
   }
@@
     random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
-    a <- mapply(f, random_points[, 1], random_points[, 2])
-    a <- sum(a/p)
+    random_points$var <- mapply(f, random_points[, 1], random_points[, 2])
+    a <- sum(random_points$var/p)
     est_MC <- append(est_MC, a)
@@
     df_boot <- f_boot(random_points, B2)
-    est_boot_val <- est_boot(df_boot, p, f)
+    est_boot_val <- est_boot(df_boot, p)
     mean_est_boot <- append(mean_est_boot, mean(est_boot_val))
@@
 
+# Test
+
 ```{r}
-MC_boot(n = 100, B1 = 1000, B2 = 200, f = circle3_nb)
+start.time <- Sys.time()
+
+res <- MC_boot(n = 100, B1 = 1000, B2 = 200, f = circle3_nb)
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
 ```
@@
 ```{r}
-
+cat("Mean of Monte-Carlo samples:", res[1], "\nMonte-Carlo variance:", res[2], "\nMean of the variance of bootstrap samples:", res[3])
 ```

### 2024-07-12 Two_var.Rmd
Doc to compare variances

--- 2024-07-12 MC_boot2.Rmd
@@
 ---
-title: "Monte-Carlo and bootstrap together - Part 2"
-output:
-  pdf_document: default
-  html_document: default
-date: "2024-07-11"
+title: "Making sure the variances converge"
+output: html_document
+date: "2024-07-12"
 ---
@@
 
-# Useful functions
+```{r}
+# Sample size
+n <- 1000
+```
+
+# Monte Carlo alone
+
+10 000 Monte Carlo iterations would be fine
+
+```{r}
+
+```
+
+# Bootstrap for each Monte Carlo iteration
+
+1 000 Monte Carlo iterations should be fine
+400 bootstrap iterations for each would be fine (200 to begin with if it is too much)
 
@@
 
-# A function to plug bootstrap in a MC process
-
 ```{r}
@@
 ```
-
-# Test
-
-```{r}
-start.time <- Sys.time()
-
-res <- MC_boot(n = 100, B1 = 1000, B2 = 200, f = circle3_nb)
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Mean of Monte-Carlo samples:", res[1], "\nMonte-Carlo variance:", res[2], "\nMean of the variance of bootstrap samples:", res[3])
-```

### 2024-07-12 Two_var.Rmd
Before a commit night

@@
 title: "Making sure the variances converge"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 date: "2024-07-12"
@@
 ```{r}
+### Function to automate Monte Carlo method
 
+MonteCarlo <- function(n, B, f){
+  # n: sample size; B: number of iterations for MC; 
+  # f: function to consider (with 2 variables, x and y)
+  p <- sum(rep((1/1000)*(1/1000), n))
+
+  # 1st step: generating n samples
+  # series_MC <- data.frame(x.1 = runif(n, 0, 1000), y.1 = runif(n, 0, 1000))
+  col_names <- c()
+
+  series_MC <- data.frame(rep(0,n))
+  est_MC <- c()
+  for (b in 2:B) {
+    x <- paste("x", b, sep = "")
+    y <- paste("y", b, sep = "")
+    z <- paste("est", b, sep = "")
+    # Uniform sampling over the whole territory
+    a1 <- runif(n, 0, 1000)
+    a2 <- runif(n, 0, 1000)
+    a <- mapply(f, a1, a2)
+    est_MC <- append(est_MC, sum(a/p))
+    series_MC <- series_MC %>% add_column(x = a1, y = a2, z = a)
+    col_names <- append(col_names, c(x, y, z))
+  }
+  series_MC <- series_MC[,-1]
+  colnames(series_MC) <- col_names
+
+  return(c(mean(est_MC), var(est_MC)))
+  # Estimated value and Monte-Carlo variance
+}
+```
+rho_MC <- tibble(.rows = n)
+
+```{r}
+start.time <- Sys.time()
+
+MC1 <- MonteCarlo(n, 10000, circle_nb)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+
+MC1
 ```
@@
 ```
+
+```{r}
+start.time <- Sys.time()
+
+res <- MC_boot(n = 100, B1 = 1000, B2 = 400, f = circle_nb)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```
+
+```{r}
+cat("Mean of Monte-Carlo samples:", res[1], "\nMonte-Carlo variance:", res[2], "\nMean of the variance of bootstrap samples:", res[3])
+```

### 2024-07-15 Two_var.Rmd
Two_var cleaner

@@
 ```
-rho_MC <- tibble(.rows = n)
 
@@
 time.taken
+```
 
-MC1
+```{r}
+cat("Monte Carlo variance:", MC1[2])
 ```
@@
 
-  df_boot <- tibble(.rows = nrow(df_sample))
+  df_boot <- tibble(.rows = (nrow(df_sample)-1))
   for (b in 1:B) {
-    nb <- sample(1:nrow(df_sample), nrow(df_sample), replace = TRUE)
+    nb <- sample(1:(nrow(df_sample)-1), nrow(df_sample), replace = TRUE)
+    # (n-1) points at random
     sample_b <- df_sample[nb,]
@@
 
-res <- MC_boot(n = 100, B1 = 1000, B2 = 400, f = circle_nb)
+res <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_nb)
 # Just one circle to begin with
@@
 ```{r}
-cat("Mean of Monte-Carlo samples:", res[1], "\nMonte-Carlo variance:", res[2], "\nMean of the variance of bootstrap samples:", res[3])
+cat("Mean of the variance of bootstrap samples:", res[3])
 ```

### 2024-07-15 Two_var.Rmd
Better version of Two_var

--- 2024-07-12 Two_var.Rmd
@@
 
-10 000 Monte Carlo iterations would be fine
+10 000 Monte Carlo iterations are appropriated.
 
 ```{r}
+### Function to automate Monte Carlo method, to produce a variance
+MonteCarlo <- function(n, B, f){
+  # n: sample size; 
+  # B: number of iterations for MC; 
+  # f: function to consider (with 2 variables, x and y)
 
+  p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
+  col_names <- c()
+  series_MC <- data.frame(rep(0,n))
+  est_MC <- c() # Vector containing all estimations
+  for (b in 2:B) { # All in one "for" loop
+    x <- paste("x", b, sep = "")
+    y <- paste("y", b, sep = "")
+    z <- paste("est", b, sep = "")
+    # Uniform sampling over the whole territory
+    a1 <- runif(n, 0, 1000)
+    a2 <- runif(n, 0, 1000)
+    # Variable of interest derived from the sample
+    a <- mapply(f, a1, a2)
+    est_MC <- append(est_MC, sum(a/p))
+    series_MC <- series_MC %>% add_column(x = a1, y = a2, z = a)
+    col_names <- append(col_names, c(x, y, z))
+  }
+  series_MC <- series_MC[,-1]
+  colnames(series_MC) <- col_names
+
+  return(var(est_MC))
+  # Monte-Carlo variance
+}
+```
+
+```{r}
+start.time <- Sys.time()
+
+res1 <- MonteCarlo(n, 10000, circle_nb)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```
+
+```{r}
+cat("Monte Carlo variance:", res1)
 ```
@@
 
-1 000 Monte Carlo iterations should be fine
-400 bootstrap iterations for each would be fine (200 to begin with if it is too much)
+1 000 Monte Carlo iterations and 400 bootstrap iterations for each one are appropriated.
 
@@
 f_boot <- function(df_sample, B){
-  # df_sample: original sample; B: number of bootstrap samples made thanks to df_sample
+  # df_sample: original sample; 
+  # B: number of bootstrap samples made thanks to df_sample
 
-  df_boot <- tibble(.rows = nrow(df_sample))
+  df_boot <- tibble(.rows = (nrow(df_sample)-1))
   for (b in 1:B) {
-    nb <- sample(1:nrow(df_sample), nrow(df_sample), replace = TRUE)
+    nb <- sample(1:(nrow(df_sample)-1), nrow(df_sample), replace = TRUE)
+    # (n-1) points at random
     sample_b <- df_sample[nb,]
@@
 
-  nboot <- length(df)/3
+  n <- nrow(df) + 1 # sample size of the initial sample
+  nboot <- length(df)/3 # number of bootstrap samples
   vec_est <- c()
   for (c in 1:nboot) {
-    vec_est <- append(vec_est, sum(df[,3*c]/p))
+    vec_est <- append(vec_est, (n/(n-1))*sum(df[,3*c]/p))
+    # (n/(n-1)) is the correction needed since we choose only (n-1) points
   }
@@
 ```{r}
-### Function to automate Monte Carlo method
+### Function to automate Monte Carlo + bootstrap method
 
@@
   # f: function to consider (2 arguments)
-  # Argument grid? (change n then)
   p <- sum(rep((1/1000)*(1/1000), n))
@@
   }
-  return(c(mean(est_MC), var(est_MC), mean(var_est_boot)))
-  # Estimated value of the total, Monte-Carlo variance, mean of the bootstrap variance
+  return(mean(var_est_boot))
+  # Mean of the bootstrap variance
 }
 ```
+
+```{r}
+start.time <- Sys.time()
+
+res2 <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_nb)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```
+
+```{r}
+cat("Mean of the variance of bootstrap samples:", res2)
+```
+
+# Conclusion
+
+```{r}
+cat("We get a difference of: ", 100*(max(res1,res2)-min(res1,res2))/min(res1,res2), "%", sep = "")
+```

### 2024-07-15 Two_var.Rmd
More simple

@@
   p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
-  col_names <- c()
-  series_MC <- data.frame(rep(0,n))
   est_MC <- c() # Vector containing all estimations
   for (b in 2:B) { # All in one "for" loop
-    x <- paste("x", b, sep = "")
-    y <- paste("y", b, sep = "")
-    z <- paste("est", b, sep = "")
     # Uniform sampling over the whole territory
@@
     est_MC <- append(est_MC, sum(a/p))
-    series_MC <- series_MC %>% add_column(x = a1, y = a2, z = a)
-    col_names <- append(col_names, c(x, y, z))
   }
-  series_MC <- series_MC[,-1]
-  colnames(series_MC) <- col_names
 
@@
   for (b in 1:B) {
-    nb <- sample(1:(nrow(df_sample)-1), nrow(df_sample), replace = TRUE)
+    nb <- sample(1:nrow(df_sample), (nrow(df_sample)-1), replace = TRUE)
     # (n-1) points at random

### 2024-07-15 Two_var.Rmd
With one example

@@
 ### Function to automate Monte Carlo method, to produce a variance
+
 MonteCarlo <- function(n, B, f){
@@
 cat("Monte Carlo variance:", res1)
+# Ex:
+# Monte Carlo variance: 2789037
 ```
@@
   # f: function to consider (2 arguments)
+
   p <- sum(rep((1/1000)*(1/1000), n))
-
-  est_MC <- c()
-  mean_est_boot <- c()
   var_est_boot <- c()
-
   for (b in 2:B1) {
@@
     a <- sum(random_points$var/p)
-    est_MC <- append(est_MC, a)
 
@@
     est_boot_val <- est_boot(df_boot, p)
-    mean_est_boot <- append(mean_est_boot, mean(est_boot_val))
     var_est_boot <- append(var_est_boot, var(est_boot_val))
@@
 cat("Mean of the variance of bootstrap samples:", res2)
+# Ex:
+# Mean of the variance of bootstrap samples: 2845120
 ```
@@
 cat("We get a difference of: ", 100*(max(res1,res2)-min(res1,res2))/min(res1,res2), "%", sep = "")
+# Ex:
+# We get a difference of: 2.01084%
 ```

### 2024-07-18 Ratio_boot.Rmd
Bootstrap with volume and ratio

--- 2024-07-15 Two_var.Rmd
@@
 ---
-title: "Making sure the variances converge"
-output:
-  pdf_document: default
-  html_document: default
-date: "2024-07-12"
+title: "Bootstrap method with estimated ratios"
+output: pdf_document
+date: "2024-07-18"
 ---
@@
 ```
-
-# Monte Carlo alone
-
-10 000 Monte Carlo iterations are appropriated.
-
-```{r}
-### Function to automate Monte Carlo method, to produce a variance
-MonteCarlo <- function(n, B, f){
-  # n: sample size; 
-  # B: number of iterations for MC; 
-  # f: function to consider (with 2 variables, x and y)
-
-  p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
-  est_MC <- c() # Vector containing all estimations
-  for (b in 2:B) { # All in one "for" loop
-    # Uniform sampling over the whole territory
-    a1 <- runif(n, 0, 1000)
-    a2 <- runif(n, 0, 1000)
-    # Variable of interest derived from the sample
-    a <- mapply(f, a1, a2)
-    est_MC <- append(est_MC, sum(a/p))
-  }
-
-  return(var(est_MC))
-  # Monte-Carlo variance
-}
-```
-
-```{r}
-start.time <- Sys.time()
-
-res1 <- MonteCarlo(n, 10000, circle_nb)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Monte Carlo variance:", res1)
-```
-
-# Bootstrap for each Monte Carlo iteration
-
-1 000 Monte Carlo iterations and 400 bootstrap iterations for each one are appropriated.
-
-```{r}
-f_boot <- function(df_sample, B){
-  # df_sample: original sample; 
-  # B: number of bootstrap samples made thanks to df_sample
-
-  df_boot <- tibble(.rows = (nrow(df_sample)-1))
-  for (b in 1:B) {
-    nb <- sample(1:nrow(df_sample), (nrow(df_sample)-1), replace = TRUE)
-    # (n-1) points at random
-    sample_b <- df_sample[nb,]
-    df_boot <- df_boot %>% add_column(new_col = sample_b)
-    colnames(df_boot)[b] <- paste("ech", b, sep = "")
-  }
-  return(do.call(data.frame, df_boot))
-  # Return a data frame with B samples of 2 variables and of size n
-}
-```
-
-```{r}
-# Making of one estimation for each sample made by the bootstrap method
-est_boot <- function(df, p){
-  # df: dataframe with 3*B columns and n rows
-
-  n <- nrow(df) + 1 # sample size of the initial sample
-  nboot <- length(df)/3 # number of bootstrap samples
-  vec_est <- c()
-  for (c in 1:nboot) {
-    vec_est <- append(vec_est, (n/(n-1))*sum(df[,3*c]/p))
-    # (n/(n-1)) is the correction needed since we choose only (n-1) points
-  }
-  vec_est <- sort(vec_est)
-  return(vec_est)
-  # Vector with one estimation for each sample
-}
-```
-
-```{r}
-### Function to automate Monte Carlo + bootstrap method
-
-MC_boot <- function(n, B1, B2, f){
-  # n: sample size; B1: number of iterations for MC;
-  # B2: number of iterations for bootstrap;
-  # f: function to consider (2 arguments)
-  p <- sum(rep((1/1000)*(1/1000), n))
-
-  est_MC <- c()
-  mean_est_boot <- c()
-  var_est_boot <- c()
-
-  for (b in 2:B1) {
-    # One MC iteration at a time
-    random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
-    random_points$var <- mapply(f, random_points[, 1], random_points[, 2])
-    a <- sum(random_points$var/p)
-    est_MC <- append(est_MC, a)
-
-    # Bootstrap iterations
-    df_boot <- f_boot(random_points, B2)
-    est_boot_val <- est_boot(df_boot, p)
-    mean_est_boot <- append(mean_est_boot, mean(est_boot_val))
-    var_est_boot <- append(var_est_boot, var(est_boot_val))
-  }
-  return(mean(var_est_boot))
-  # Mean of the bootstrap variance
-}
-```
-
-```{r}
-start.time <- Sys.time()
-
-res2 <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_nb)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Mean of the variance of bootstrap samples:", res2)
-```
-
-# Conclusion
-
-```{r}
-cat("We get a difference of: ", 100*(max(res1,res2)-min(res1,res2))/min(res1,res2), "%", sep = "")
-```

### 2024-07-18 Two_var.Rmd
Bootstrap with volume and ratio

@@
 }
-```
-
-```{r}
-start.time <- Sys.time()
-
-res1 <- MonteCarlo(n, 10000, circle_nb)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Monte Carlo variance:", res1)
-# Ex:
-# Monte Carlo variance: 2789037
 ```
@@
 
+# First example: number of trees
+
 ```{r}
@@
 
-res2 <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_nb)
+res1_nb <- MonteCarlo(n, 10000, circle_nb)
 # Just one circle to begin with
@@
 ```{r}
-cat("Mean of the variance of bootstrap samples:", res2)
-# Ex:
-# Mean of the variance of bootstrap samples: 2845120
+cat("Monte Carlo variance:", res1_nb)
+# Examples:
+# Monte Carlo variance: 2789037
+# Monte Carlo variance: 2827317
 ```
 
-# Conclusion
+```{r}
+start.time <- Sys.time()
+
+res2_nb <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_nb)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```
 
 ```{r}
-cat("We get a difference of: ", 100*(max(res1,res2)-min(res1,res2))/min(res1,res2), "%", sep = "")
+cat("Mean of the variance of bootstrap samples:", res2_nb)
+# Examples:
+# Mean of the variance of bootstrap samples: 2845120
+# Mean of the variance of bootstrap samples: 2851631
+```
+
+```{r}
+cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
+# Examples:
+# We get a difference of: 2.01084%
+# We get a difference of: 0.8599411%
+```
+
+# Second example: volume of the forest
+
+```{r}
+start.time <- Sys.time()
+
+res1_vol <- MonteCarlo(n, 10000, circle_vol)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```
+
+```{r}
+cat("Monte Carlo variance:", res1_vol)
 # Ex:
-# We get a difference of: 2.01084%
+# Monte Carlo variance: 
 ```
+
+```{r}
+start.time <- Sys.time()
+
+res2_vol <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_vol)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```
+
+```{r}
+cat("Mean of the variance of bootstrap samples:", res2_vol)
+# Ex:
+# Mean of the variance of bootstrap samples: 
+```
+
+```{r}
+cat("We get a difference of: ", 100*(max(res1_vol,res2_vol)-min(res1_vol,res2_vol))/min(res1_vol,res2_vol), "%", sep = "")
+# Ex:
+# We get a difference of:
+```

### 2024-07-18 Intermediary.Rmd
Intermediary

--- 2024-07-18 Two_var.Rmd
@@
 ---
-title: "Making sure the variances converge"
+title: "Intermediary"
 output:
   pdf_document: default
-  html_document: default
-date: "2024-07-12"
+date: "2024-07-18"
 ---
@@
 
-# First example: number of trees
-
-```{r}
-start.time <- Sys.time()
-
-res1_nb <- MonteCarlo(n, 10000, circle_nb)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Monte Carlo variance:", res1_nb)
-# Examples:
-# Monte Carlo variance: 2789037
-# Monte Carlo variance: 2827317
-```
-
-```{r}
-start.time <- Sys.time()
-
-res2_nb <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_nb)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Mean of the variance of bootstrap samples:", res2_nb)
-# Examples:
-# Mean of the variance of bootstrap samples: 2845120
-# Mean of the variance of bootstrap samples: 2851631
-```
-
-```{r}
-cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
-# Examples:
-# We get a difference of: 2.01084%
-# We get a difference of: 0.8599411%
-```
-
 # Second example: volume of the forest

### 2024-07-19 Useful_functions/Circle.R
Biblio plain text + ratio

@@ -1,4 +1,6 @@
-### Functions to produce local variables based on circles -----
+####### Functions to produce local variables based on circles -------
+
+### With one single circle -----
 
 ## Function to produce the local variable for the number of trees
 circle_nb <- function(x1, x2, R=5){
@@ -25,6 +27,75 @@ circle_vol <- function(x1, x2, R=5){
   return(local_var)
   # list_trees: identifiers of targeted trees; local_var: local variable based on the volume of trees
 }
+
+## Function to produce 3 local variables for the volume of trees in 3 categories
+circle_nb_3cats <- function(x1, x2, R=5, bounds = c(0, 70.5, 117.5)){
+  # 2 coordinates (x1, x2) and a radius (R)
+  # bounds: to make 3 categories of trees based on circumference
+  # 23.5: lowest limit for the NFI
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  # From circumference to diameter (d130)
+  d <- bounds/pi
+  
+  list_trees <- trees[(x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2,] 
+  # list_trees1 <- ifelse(nrow(list_trees) != 0, list_trees[(list_trees$d130 > d[3]),], list_trees) # List with the biggest trees
+  # list_trees2 <- ifelse(nrow(list_trees) != 0, list_trees[(list_trees$d130 < d[3]) & (list_trees$d130 > d[2]),], list_trees) # medium trees
+  # list_trees3 <- ifelse(nrow(list_trees) != 0, list_trees[(list_trees$d130 > d[1]) & (list_trees$d130 < d[2]),], list_trees) # smallest trees
+  
+  list_trees1 <- list_trees[(list_trees$d130 > d[3]),] # List with the biggest trees
+  list_trees2 <- list_trees[(list_trees$d130 < d[3]) & (list_trees$d130 > d[2]),] # medium trees
+  list_trees3 <- list_trees[(list_trees$d130 > d[1]) & (list_trees$d130 < d[2]),] # smallest trees
+  
+  inc_areaR <- inc_area(c(x1, x2),0,0,1000,1000,R)
+  local_var1 <- sum(nrow(list_trees1)/inc_areaR) # Local variable for the biggest circle and the biggest trees
[…]

### 2024-07-22 Two_var3.Rmd
Two_var with 3 circles

--- 2024-07-18 Two_var.Rmd
@@
 ---
-title: "Making sure the variances converge"
+title: "Making sure the variances converge with 3 circles"
 output: 
   pdf_document: default
-  html_document: default
-date: "2024-07-12"
+date: "2024-07-22"
 ---
@@
 
-res1_nb <- MonteCarlo(n, 10000, circle_nb)
-# Just one circle to begin with
+res1_nb <- MonteCarlo(n, 10000, circle3_nb)
+# 3 circles
 
@@
 # Examples:
-# Monte Carlo variance: 2789037
-# Monte Carlo variance: 2827317
+# Monte Carlo variance: 
 ```
@@
 
-res2_nb <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_nb)
-# Just one circle to begin with
+res2_nb <- MC_boot(n, B1 = 1000, B2 = 400, f = circle3_nb)
+# 3 circles
 
@@
 # Examples:
-# Mean of the variance of bootstrap samples: 2845120
-# Mean of the variance of bootstrap samples: 2851631
+# Mean of the variance of bootstrap samples:
 ```
@@
 # Examples:
-# We get a difference of: 2.01084%
-# We get a difference of: 0.8599411%
+# We get a difference of: 
 ```
@@
 
-res1_vol <- MonteCarlo(n, 10000, circle_vol)
-# Just one circle to begin with
+res1_vol <- MonteCarlo(n, 10000, circle3_vol)
+# 3 circles
 
@@
 
-res2_vol <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_vol)
-# Just one circle to begin with
+res2_vol <- MC_boot(n, B1 = 1000, B2 = 400, f = circle3_vol)
+# 3 circles
 

### 2024-07-22 Boot_grid.Rmd
Useless pdf and boot with grid

--- 2024-07-18 Two_var.Rmd
@@
 ---
-title: "Making sure the variances converge"
+title: "Bootstrap with a grid"
 output:
   pdf_document: default
-  html_document: default
-date: "2024-07-12"
+date: "2024-07-22"
 ---
@@
 # Ex:
-# Monte Carlo variance: 
+# Monte Carlo variance: 98332.87
 ```
@@
 # Ex:
-# Mean of the variance of bootstrap samples: 
+# Mean of the variance of bootstrap samples: 98594.44
 ```
@@
 # Ex:
-# We get a difference of:
+# We get a difference of: 0.2660091%
 ```

### 2024-07-22 Two_var3.Rmd
Two_var3 with example

@@
 # Examples:
-# Monte Carlo variance: 
+# Monte Carlo variance: 2717279
 ```
@@
 # Examples:
-# Mean of the variance of bootstrap samples:
+# Mean of the variance of bootstrap samples: 2684541
 ```
@@
 # Examples:
-# We get a difference of: 
+# We get a difference of: 1.21952%
 ```
@@
 # Ex:
-# Monte Carlo variance: 
+# Monte Carlo variance: 84693.99
 ```
@@
 # Ex:
-# Mean of the variance of bootstrap samples: 
+# Mean of the variance of bootstrap samples: 83681.51
 ```
@@
 # Ex:
-# We get a difference of: 
+# We get a difference of: 1.209916%
 ```

### 2024-07-22 Two_var3.Rmd
Finition

@@
 cat("Monte Carlo variance:", res1_nb)
-# Examples:
+# Example:
 # Monte Carlo variance: 2717279
@@
 cat("Mean of the variance of bootstrap samples:", res2_nb)
-# Examples:
+# Example:
 # Mean of the variance of bootstrap samples: 2684541
@@
 cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
-# Examples:
+# Example:
 # We get a difference of: 1.21952%

### 2024-07-23 Boot_grid.Rmd
Correct bootstrap with grid

--- 2024-07-18 Two_var.Rmd
@@
 ```{r}
-# Sample size
-n <- 1000
+i <- sample(1:10, 1) # choice of the rank of the identifier we want
+i
+```
+
+```{r}
+# Dimension of a small square (length of one side of the square)
+# We assume that c_dim is a divisor of 1000
+c_dim <- 10
+```
+
+```{r}
+# Function to sample at random following the grid
+sampling_grid <- function(i,c_dim){
+random_points <- data.frame(x = numeric(), y = numeric())
+
+for (l in 0:((1000/c_dim)-1)) {
+  if (l==0){
+    x_init <- i*c_dim
+  }else if ((3*l+i)*c_dim < (10)*c_dim){
+    x_init <- (3*l+i)*c_dim
+  }else{
+    x_init <- (((3*l+i)*c_dim)%%(c_dim*10))
+  }
+  k <- 0
+  while (x_init + 10*c_dim*k < 1000) {
+    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + c_dim)
+    b <- runif(1, l*c_dim, (l+1)*c_dim)
+    random_points <- rbind(random_points, list(a,b))
+    k <- k+1
+  }
+}
+colnames(random_points) <- list("x", "y")
+return(random_points)
+}
 ```
@@
 
-MonteCarlo <- function(n, B, f){
-  # n: sample size; 
+MonteCarlo <- function(B, f){
   # B: number of iterations for MC; 
@@
 
-  p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
   est_MC <- c() # Vector containing all estimations
   for (b in 2:B) { # All in one "for" loop
-    # Uniform sampling over the whole territory
-    a1 <- runif(n, 0, 1000)
-    a2 <- runif(n, 0, 1000)
+    # Sampling over the whole territory
+    df_grid <- sampling_grid(i,c_dim)
     # Variable of interest derived from the sample
-    a <- mapply(f, a1, a2)
+    a <- mapply(f, df_grid$x, df_grid$y)
+    n <- nrow(df_grid)
+    p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
     est_MC <- append(est_MC, sum(a/p))
@@
 
-MC_boot <- function(n, B1, B2, f){
-  # n: sample size; B1: number of iterations for MC;
+MC_boot <- function(B1, B2, f){
+  # B1: number of iterations for MC;
   # B2: number of iterations for bootstrap;
@@
 
-  p <- sum(rep((1/1000)*(1/1000), n))
   var_est_boot <- c()
@@
     # One MC iteration at a time
-    random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
+    random_points <- sampling_grid(i,c_dim)
     random_points$var <- mapply(f, random_points[, 1], random_points[, 2])
+    n <- nrow(random_points)
+    p <- sum(rep((1/1000)*(1/1000), n))
     a <- sum(random_points$var/p)
@@
 
-res1_nb <- MonteCarlo(n, 10000, circle_nb)
+res1_nb <- MonteCarlo(10000, circle_nb)
 # Just one circle to begin with
@@
 
-res2_nb <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_nb)
+res2_nb <- MC_boot(B1 = 1000, B2 = 400, f = circle_nb)
 # Just one circle to begin with
@@
 cat("Mean of the variance of bootstrap samples:", res2_nb)
-# Examples:
-# Mean of the variance of bootstrap samples: 2845120
-# Mean of the variance of bootstrap samples: 2851631
+# Example:
+# Mean of the variance of bootstrap samples: 
 ```
@@
 cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
-# Examples:
-# We get a difference of: 2.01084%
-# We get a difference of: 0.8599411%
+# Example:
+# We get a difference of: 
 ```
@@
 
-res1_vol <- MonteCarlo(n, 10000, circle_vol)
+res1_vol <- MonteCarlo(10000, circle_vol)
 # Just one circle to begin with
@@
 
-res2_vol <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_vol)
+res2_vol <- MC_boot(B1 = 1000, B2 = 400, f = circle_vol)
 # Just one circle to begin with

### 2024-07-23 Ratios.Rmd
Ratios and bootstrap

---
title: "Ratios"
output: pdf_document
date: "2024-07-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
```

# Preliminaries

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
```

```{r}
# Functions to produce a local variable
source("~/work/Sim_article2024/Useful_functions/Circle.R")
```

```{r}
# Sample size
n <- 1000

# Inclusion density
p <- sum(rep((1/1000)*(1/1000), n))
```

```{r}
random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
```

# Bootstrap for each Monte Carlo iteration

1 000 Monte Carlo iterations and 400 bootstrap iterations for each one are appropriated.

```{r}
f_boot <- function(df_sample, B){
  # df_sample: original sample; 
  # B: number of bootstrap samples made thanks to df_sample

  df_boot <- tibble(.rows = (nrow(df_sample)-1))
  for (b in 1:B) {
    nb <- sample(1:nrow(df_sample), (nrow(df_sample)-1), replace = TRUE)
    # (n-1) points at random
    sample_b <- df_sample[nb,]
    df_boot <- df_boot %>% add_column(new_col = sample_b)
    colnames(df_boot)[b] <- paste("ech", b, sep = "")
  }
  return(do.call(data.frame, df_boot))
  # Return a data frame with B samples of 2 (or more) variables and of size n
}
```

```{r}
# Making of one estimation for each sample made by the bootstrap method
est_boot <- function(df, p){
  # df: dataframe with 4*B columns and n rows

  n <- nrow(df) + 1 # sample size of the initial sample
  nboot <- length(df)/4 # number of bootstrap samples
  vec_est1 <- c()
  vec_est2 <- c()
  for (c in 1:nboot) {
    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3*c]/p))
    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,4*c]/p))
    # (n/(n-1)) is the correction needed since we choose only (n-1) points
  }
  # vec_est1 <- sort(vec_est1)
  # vec_est2 <- sort(vec_est2)
  vec_est <- data.frame(est1 = vec_est1, est2 = vec_est2)
  return(vec_est)
  # Vector with one estimation for each sample
}
```

```{r}
### Function to automate Monte Carlo + bootstrap method

MC_boot <- function(n, B1, B2, f1, f2){
  # n: sample size; B1: number of iterations for MC;
  # B2: number of iterations for bootstrap;
  # f1: function to consider (2 arguments) on the numerator
  # f2: function to consider (2 arguments) on the denominator

  p <- sum(rep((1/1000)*(1/1000), n))
  var_est_boot <- c()
  for (b in 2:B1) {
    # One MC iteration at a time
    random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
    random_points$var1 <- mapply(f1, random_points[, 1], random_points[, 2])
    random_points$var2 <- mapply(f2, random_points[, 1], random_points[, 2])
    # a1 <- sum(random_points$var1/p)

    # Bootstrap iterations
    df_boot <- f_boot(random_points, B2)
    # est_boot_val <- mapply(est_boot, df_boot[, 1], df_boot[, 2])
    est_boot_val <- est_boot(df_boot, p)
    est_boot_ratio <- est_boot_val[,1]/est_boot_val[,2]
    var_est_boot <- append(var_est_boot, var(est_boot_ratio))
  }
  return(mean(var_est_boot))
  # Mean of the bootstrap variance
}
```

# Global estimations with one circle

```{r}
tot_nb <- mapply(circle_nb, random_points[, 1], random_points[, 2])
tot_vol <- mapply(circle_vol, random_points[, 1], random_points[, 2])
```

```{r}
tot_nb_vol <- data.frame(nb = tot_nb, vol = tot_vol)
a1 <- sum(tot_nb/p)
a2 <- sum(tot_vol/p)
est_ratio <- a2/a1
```

```{r}
cat("True ratio \"total volume over number of trees\":", sum(trees$v)/nrow(trees), "\nEstimation of this ratio:", est_ratio)
# Ex:
# True ratio "total volume over number of trees": 0.1749312 
# Estimation of this ratio: 0.1693595
```

```{r}
start.time <- Sys.time()

res_ratio1 <- MC_boot(n, B1 = 1000, B2 = 400, f1 = circle_nb, f2 = circle_vol)
# Just one circle to begin with

end.time <- Sys.time()
time.taken <- end.time - start.time

time.taken
```

```{r}
cat("Mean of the variance of bootstrap samples:", res_ratio1)
# Ex:
# Mean of the variance of bootstrap samples: 
```

# Various circumferences

```{r}
y1 <- mapply(circle_vol_size, random_points[, 1], random_points[, 2])
Y1 <- sum(y1/p)
```

```{r}
cat("True ratio \"volume of the smallest over total volume\":", sum(trees[(trees$d130 > 23.5/pi) & (trees$d130 < 70.5/pi),]$v)/sum(trees$v), "\nEstimation of this ratio:", Y1/a2)
```

```{r}
y2 <- mapply(circle_vol_size, random_points[, 1], random_points[, 2], MoreArgs = list(5, c(70.5, 117.5)))
Y2 <- sum(y2/p)
```

```{r}
cat("True ratio \"volume of the medium over total volume\":", sum(trees[(trees$d130 > 70.5/pi) & (trees$d130 < 117.5/pi),]$v)/sum(trees$v), "\nEstimation of this ratio:", Y2/a2)
```

```{r}
y3 <- mapply(circle_vol_size, random_points[, 1], random_points[, 2], MoreArgs = list(5, c(117.5, 500)))
Y3 <- sum(y3/p)
```

```{r}
cat("True ratio \"volume of the biggest over total volume\":", sum(trees[(trees$d130 > 117.5/pi) & (trees$d130 < 500/pi),]$v)/sum(trees$v), "\nEstimation of this ratio:", Y3/a2)
```

```{r}

```

### 2024-07-23 Useful_functions/Circle.R

@@ -28,6 +28,50 @@ circle_vol <- function(x1, x2, R=5){
   # list_trees: identifiers of targeted trees; local_var: local variable based on the volume of trees
 }
 
+circle_nb_size <- function(x1, x2, R=5, bounds = c(23.5, 70.5)){
+  # 2 coordinates (x1, x2) and a radius (R)
+  # bounds: to target a category of trees based on circumference
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  # From circumference to diameter (d130)
+  d <- bounds/pi
+  
+  list_trees <- trees[(x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2,] 
+  # list_trees1 <- ifelse(nrow(list_trees) != 0, list_trees[(list_trees$d130 > d[3]),], list_trees) # List with the biggest trees
+  
+  list_trees_size <- list_trees[(list_trees$d130 > d[1]) & (list_trees$d130 < d[2]),] # smallest trees
+  
+  inc_areaR <- inc_area(c(x1, x2),0,0,1000,1000,R)
+  local_var <- sum(nrow(list_trees_size)/inc_areaR) # Local variable for the specific category of trees
+  
+  return(local_var)
+  # local_var: local variable based on the number of trees
+}
+
+circle_vol_size <- function(x1, x2, R=5, bounds = c(23.5, 70.5)){
+  # 2 coordinates (x1, x2) and a radius (R)
+  # bounds: to target a category of trees based on circumference
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  # From circumference to diameter (d130)
+  d <- bounds/pi
+  
+  list_trees <- trees[(x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2,] 
+  # list_trees1 <- ifelse(nrow(list_trees) != 0, list_trees[(list_trees$d130 > d[3]),], list_trees) # List with the biggest trees
+  
+  list_trees_size <- list_trees[(list_trees$d130 > d[1]) & (list_trees$d130 < d[2]),] # smallest trees
+  
+  inc_areaR <- inc_area(c(x1, x2),0,0,1000,1000,R)
+  local_var <- sum(list_trees_size$v/inc_areaR) # Local variable for the specific category of trees
+  
+  return(local_var)
[…]

### 2024-07-23 Ratios.Rmd
Just a few changes
Ratio with example

@@
 ---
-title: "Ratios"
+title: "Various ratios and their estimations"
 output: pdf_document
@@
     random_points$var2 <- mapply(f2, random_points[, 1], random_points[, 2])
-    # a1 <- sum(random_points$var1/p)
 
@@
     df_boot <- f_boot(random_points, B2)
-    # est_boot_val <- mapply(est_boot, df_boot[, 1], df_boot[, 2])
     est_boot_val <- est_boot(df_boot, p)
@@
 # True ratio "total volume over number of trees": 0.1749312 
-# Estimation of this ratio: 0.1693595
+# Estimation of this ratio: 0.1714633
 ```
@@
 
-res_ratio1 <- MC_boot(n, B1 = 1000, B2 = 400, f1 = circle_nb, f2 = circle_vol)
+res_ratio1 <- MC_boot(n, B1 = 1000, B2 = 400, f1 = circle_vol, f2 = circle_nb)
 # Just one circle to begin with
@@
 # Ex:
-# Mean of the variance of bootstrap samples: 
+# Mean of the variance of bootstrap samples: 2190764978
 ```
@@
 cat("True ratio \"volume of the smallest over total volume\":", sum(trees[(trees$d130 > 23.5/pi) & (trees$d130 < 70.5/pi),]$v)/sum(trees$v), "\nEstimation of this ratio:", Y1/a2)
+# Ex:
+# True ratio "volume of the smallest over total volume": 0.5741108
+# Estimation of this ratio: 0.5846677
+```
+
+```{r}
+start.time <- Sys.time()
+
+res_ratio2 <- MC_boot(n, B1 = 1000, B2 = 400, f1 = circle_vol_size, f2 = circle_vol)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```
+
+```{r}
+cat("Mean of the variance of bootstrap samples:", res_ratio2)
 ```
@@
 cat("True ratio \"volume of the medium over total volume\":", sum(trees[(trees$d130 > 70.5/pi) & (trees$d130 < 117.5/pi),]$v)/sum(trees$v), "\nEstimation of this ratio:", Y2/a2)
+# Ex:
+# True ratio "volume of the medium over total volume": 0.3628267
+# Estimation of this ratio: 0.3623958
 ```
@@
 cat("True ratio \"volume of the biggest over total volume\":", sum(trees[(trees$d130 > 117.5/pi) & (trees$d130 < 500/pi),]$v)/sum(trees$v), "\nEstimation of this ratio:", Y3/a2)
+# True ratio "volume of the biggest over total volume": 0.06306254
+# Estimation of this ratio: 0.0529365
 ```
-
-```{r}
-
-```

### 2024-07-24 Boot_grid.Rmd
Boot_grid without empty examples

@@
   pdf_document: default
-date: "2024-07-22"
+date: "2024-07-23"
 ---
@@
 cat("Monte Carlo variance:", res1_nb)
-# Examples:
-# Monte Carlo variance: 
 ```
@@
 cat("Mean of the variance of bootstrap samples:", res2_nb)
-# Example:
-# Mean of the variance of bootstrap samples: 
 ```
@@
 cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
-# Example:
-# We get a difference of: 
 ```
@@
 cat("Monte Carlo variance:", res1_vol)
-# Ex:
-# Monte Carlo variance: 
 ```
@@
 cat("Mean of the variance of bootstrap samples:", res2_vol)
-# Ex:
-# Mean of the variance of bootstrap samples: 
 ```
@@
 cat("We get a difference of: ", 100*(max(res1_vol,res2_vol)-min(res1_vol,res2_vol))/min(res1_vol,res2_vol), "%", sep = "")
-# Ex:
-# We get a difference of: 
 ```

### 2024-07-24 Test_local_dens.R
Test new local density

@@ -1,0 +1,62 @@
+##### Test for the correction of the local density ----------
+
+# frontier <- c(500, 500, 510, 510)
+
+frontier <- c(600, 610, 610, 620)
+
+## Function to produce the local variable for the number of trees
+circle_nb_old <- function(x1, x2, R=4){
+  # 2 coordinates (x1, x2) and a radius (R)
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  list_trees <- which(((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2) & (trees$x > frontier[1]) & (trees$x < frontier[3]) & (trees$y > frontier[2]) & (trees$y < frontier[4]))
+  local_var <- sum(length(list_trees)/inc_area(c(x1, x2),frontier[1],frontier[2],frontier[3],frontier[4],R))
+  return(local_var)
+  # list_trees: identifiers of targeted trees; local_var: local variable based on the number of trees
+}
+
+## Function to produce the local variable for the number of trees
+circle_nb_new <- function(x1, x2, R=4){
+  # 2 coordinates (x1, x2) and a radius (R)
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  list_trees <- which(((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2) & (trees$x > frontier[1]) & (trees$x < frontier[3]) & (trees$y > frontier[2]) & (trees$y < frontier[4]))
+  trees1 <- trees
+  trees1$var1 <- rep(1,nrow(trees1))
+  if (length(list_trees) != 0){
+  local_var <- sum(trees1[list_trees,]$var1/inc_area(c(trees1[list_trees,]$x, trees1[list_trees,]$y),frontier[1],frontier[2],frontier[3],frontier[4],R))
+  }
+  else{local_var <- 0}
+  return(local_var)
+  # list_trees: identifiers of targeted trees; local_var: local variable based on the number of trees
+}
+
+plot(trees$x, trees$y, xlim = c(frontier[1], frontier[3]), ylim = c(frontier[2], frontier[4]))
+
+p <- (1/(frontier[3] - frontier[1]))*(1/(frontier[4] - frontier[2]))
+
+# est_old <- circle_nb_old(505,505)/p # 5.96831
[…]

### 2024-07-24 Test_local_dens.R
Unsuccessful test for now

@@ -1,8 +1,9 @@
-##### Test for the correction of the local density ----------
+##### Test for the correction of the local density #####
 
-# frontier <- c(500, 500, 510, 510)
+library(readxl) # to read the initial file
+trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
 
-frontier <- c(600, 610, 610, 620)
+##### Two functions ----------
 
 ## Function to produce the local variable for the number of trees
 circle_nb_old <- function(x1, x2, R=4){
@@ -28,24 +29,28 @@ circle_nb_new <- function(x1, x2, R=4){
   trees1 <- trees
   trees1$var1 <- rep(1,nrow(trees1))
   if (length(list_trees) != 0){
-  local_var <- sum(trees1[list_trees,]$var1/inc_area(c(trees1[list_trees,]$x, trees1[list_trees,]$y),frontier[1],frontier[2],frontier[3],frontier[4],R))
+    combined_list <- mapply(function(x, y) c(x, y), trees1[list_trees,]$x, trees1[list_trees,]$y, SIMPLIFY = FALSE)
+    df_coord <- data.frame(id = list_trees, coord = I(combined_list)) # Create a new df with a single column containing these lists
+    local_var <- sum((trees1[df_coord$id,]$var1)/mapply(inc_area, df_coord$coord, MoreArgs = list(frontier[1],frontier[2],frontier[3],frontier[4],R)))
   }
   else{local_var <- 0}
   return(local_var)
   # list_trees: identifiers of targeted trees; local_var: local variable based on the number of trees
 }
 
+##### First test ----------
+
+frontier <- c(500, 500, 510, 510)
+
+# frontier <- c(600, 610, 610, 620)
+
 plot(trees$x, trees$y, xlim = c(frontier[1], frontier[3]), ylim = c(frontier[2], frontier[4]))
 
-p <- (1/(frontier[3] - frontier[1]))*(1/(frontier[4] - frontier[2]))
-
-# est_old <- circle_nb_old(505,505)/p # 5.96831
-# est_new <- circle_nb_new(505,505)/p # 7.270723
 true_val <- nrow(trees[(trees$x > frontier[1]) & (trees$x < frontier[3]) & (trees$y > frontier[2]) & (trees$y < frontier[4]),]) # 10
 
[…]

### 2024-07-24 Useful_functions/Inc_area_test.R

@@ -1,0 +1,113 @@
+# Just a test
+
+inc_area_test <- function(x, y, x0F, y0F, x1F, y1F, r){
+  # x <- coord[1]
+  # y <- coord[2]
+  
+  ##### Case 1: the point is located s.t. the inclusion plot is completely inside the territory
+  if ((x>=x0F+r) & (x<=x1F-r) & (y>=y0F+r) & (y<=y1F-r)){
+    surf <- pi*(r^2)
+  }
+  
+  ##### Case 2: the point is located s.t. the inclusion plot is not completely inside the territory, 
+  # but intersects one side of the territory only.
+  # For the formula of the area, see https://fr.wikipedia.org/wiki/Segment_circulaire
+  ### Lower rectangle
+  if ((x>=x0F+r) & (x<=x1F-r) & (y>=y0F) & (y<y0F+r)){
+    d <- y-y0F
+    theta <- 2*acos(d/r)
+    surf <- (r^2)*(pi-0.5*theta+0.5*sin(theta))
+  }
+  ### Right rectangle
+  if ((x>x1F-r) & (x<=x1F) & (y>=y0F+r) & (y<=y1F-r)){
+    d <- x1F-x
+    theta <- 2*acos(d/r)
+    surf <- (r^2)*(pi-0.5*theta+0.5*sin(theta))
+  }
+  ### Upper rectangle
+  if ((x>=x0F+r) & (x<=x1F-r) & (y>y1F-r) & (y<=y1F)){
+    d <- y1F-y
+    theta <- 2*acos(d/r)
+    surf <- (r^2)*(pi-0.5*theta+0.5*sin(theta))
+  }
+  ### Left rectangle
+  if ((x>=x0F) & (x<x0F+r) & (y>=y0F+r) & (y<=y1F-r)){
+    d <- x-x0F
+    theta <- 2*acos(d/r)
+    surf <- (r^2)*(pi-0.5*theta+0.5*sin(theta))
+  }
+  
+  ##### Case 3: the point is located s.t. the inclusion plot is not completely inside
+  # the territory, and intersects two sides of the territory. The area is given
+  # by a rectangle triangle and a circular segment
+  ### Lower left square
+  if ((x>=x0F) & (x<x0F+r) & (y>=y0F) & (y<y0F+r)){
+    # Lower intersection point between the plot and the rectangle
+    xa <- x+sqrt(r^2-(y-y0F)^2);ya <- y0F
[…]

### 2024-07-25 MC_all.Rmd
Failure with local density for now

--- 2024-07-18 Two_var.Rmd
@@
 ---
-title: "Making sure the variances converge"
-output:
-  pdf_document: default
-  html_document: default
-date: "2024-07-12"
+title: "Monte Carlo for all parameters"
+output: pdf_document
+date: "2024-07-24"
 ---
@@
 
-MonteCarlo <- function(n, B, f){
+MonteCarlo <- function(n, B){
   # n: sample size;
-  # B: number of iterations for MC; 
-  # f: function to consider (with 2 variables, x and y)
+  # B: number of iterations for MC
 
   p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
-  est_MC <- c() # Vector containing all estimations
-  for (b in 2:B) { # All in one "for" loop
+
+  MC_df <- data.frame(useless = rep(0, n))
+  MC_est <- data.frame(useless = rep(0, 3), row.names = c("est_nb", "est_vol", "est_ratio"))
+
+  for (b in 1:B) { # All in one "for" loop
     # Uniform sampling over the whole territory
@@
     a2 <- runif(n, 0, 1000)
-    # Variable of interest derived from the sample
-    a <- mapply(f, a1, a2)
-    est_MC <- append(est_MC, sum(a/p))
+    # Variables of interest derived from the sample
+    var_nb <- mapply(circle_nb, a1, a2)
+    var_vol <- mapply(circle_vol, a1, a2)
+    MC_b <- data.frame(x = a1, y = a2, z = var_nb, t = var_vol)
+    MC_df <- cbind(MC_df, MC_b)
+    colnames(MC_df)[4*(b-1)+2] <- paste("x", b, sep = "")
+    colnames(MC_df)[4*(b-1)+2+1] <- paste("y", b, sep = "")
+    colnames(MC_df)[4*(b-1)+2+2] <- paste("nb", b, sep = "")
+    colnames(MC_df)[4*(b-1)+2+3] <- paste("vol", b, sep = "")
+    est_b <- t(data.frame(x = sum(MC_df[4*(b-1)+2+2] /p), y = sum(MC_df[4*(b-1)+2+3] /p), z = (sum(MC_df[4*(b-1)+2+3] /p))/(sum(MC_df[4*(b-1)+2+2]/p))))
+    MC_est <- cbind(MC_est, est_b)
+    colnames(MC_est)[b+1] <- paste("ech", b, sep = "") 
   }
+  MC_df$useless <- NULL
+  MC_est$useless <- NULL
+  MC_var <- c(var(as.vector(t(MC_est[1,]))), var(as.vector(t(MC_est[2,]))), var(as.vector(t(MC_est[3,]))))
+  return(list(MC_df, MC_est, MC_var))
+}
+```
 
-  return(var(est_MC))
-  # Monte-Carlo variance
-}
+```{r}
+# Small test
+
+start.time <- Sys.time()
+
+res_MC <- MonteCarlo(100, 200)
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
 ```

### 2024-07-25 Test_local_dens.R

@@ -95,7 +95,7 @@ circle_nb_new2 <- function(x1, x2, R=4){
 
 est_new1 <- circle_nb_new(501,507)/p
 est_new2 <- circle_nb_new2(501,507)/p
-# est_new1 = est_new2
+# est_new1 == est_new2 # TRUE
 
 
 ##### Automation ----------

### 2024-07-25 MC_all.Rmd
More global MC and function for local variables

@@
 # Importing the database with the artificial forest
-trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
+all_trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
+# To get closer to the NFI process, trees whose circumference is under 23.5 cm are not considered
+trees <- trees[(pi*trees$d130 > 23.5),]
 ```
@@
 n <- 1000
+```
+
+```{r}
+# True values
+cat("Number of trees:", length(trees$x), "\nTotal volume:", sum(trees$v), "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees))
 ```
@@
     # Variables of interest derived from the sample
-    var_nb <- mapply(circle_nb, a1, a2)
-    var_vol <- mapply(circle_vol, a1, a2)
-    MC_b <- data.frame(x = a1, y = a2, z = var_nb, t = var_vol)
+    var <- mapply(circle_all, a1, a2)
+    MC_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
     MC_df <- cbind(MC_df, MC_b)
@@
   MC_var <- c(var(as.vector(t(MC_est[1,]))), var(as.vector(t(MC_est[2,]))), var(as.vector(t(MC_est[3,]))))
-  return(list(MC_df, MC_est, MC_var))
+  return(list(Data = MC_df, Estimators = MC_est, Variances = MC_var))
+  # Data: local variables (number and voume) for each point in each sample
+  # Estimators: 3 estimators (number, volume, ratio volume / number) for each sample
+  # Variances: Monte Carlo variance for each of the totals / ratio
 }
@@
 time.taken
+```
+
+```{r}
+# mean(as.vector(res_MC$Estimators[1,]))
+```
+
+```{r}
+# mean(res_MC$Estimators[1,])
 ```
@@
 ```{r}
-# Making of one estimation for each sample made by the bootstrap method
+# Making of estimations for each sample made by the bootstrap method
 est_boot <- function(df, p){
-  # df: dataframe with 3*B columns and n rows
+  # df: dataframe with 4*B columns and n rows
 
   n <- nrow(df) + 1 # sample size of the initial sample
-  nboot <- length(df)/3 # number of bootstrap samples
-  vec_est <- c()
+  nboot <- length(df)/4 # number of bootstrap samples
+  vec_est1 <- c()
+  vec_est2 <- c()
   for (c in 1:nboot) {
-    vec_est <- append(vec_est, (n/(n-1))*sum(df[,3*c]/p))
+    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3*c]/p))
+    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,4*c]/p))
     # (n/(n-1)) is the correction needed since we choose only (n-1) points
   }
-  vec_est <- sort(vec_est)
+  vec_est <- data.frame(est1 = vec_est1, est2 = vec_est2)
   return(vec_est)
@@
 
-MC_boot <- function(n, B1, B2, f){
+MC_boot <- function(n, B1, B2){
   # n: sample size; B1: number of iterations for MC;
@@
   return(mean(var_est_boot))
-  # Mean of the bootstrap variance
+  # Variances: mean of the bootstrap variance for each estimator
 }
@@
 
-# First example: number of trees
+# Example
 
@@
 
-res1_nb <- MonteCarlo(n, 10000, circle_nb)
+res1 <- MonteCarlo(n, 10000)
 # Just one circle to begin with
@@
 ```{r}
-cat("Monte Carlo variance:", res1_nb)
-# Examples:
-# Monte Carlo variance: 2789037
-# Monte Carlo variance: 2827317
+cat("Monte Carlo means of estimators: \n - for the number of trees:", mean(as.vector(res1$Estimators[1,])), "\n - for the volume of trees:", mean(as.vector(res1$Estimators[1,])), "\n - for the ratio volume / number of trees:", mean(as.vector(res1$Estimators[1,])))
+# Example:
+```
+
+```{r}
+cat("Monte Carlo variance: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[2], "\n - for the ratio volume / number of trees:", res1$Variances[3])
+# Example:
 ```
@@
 
-res2_nb <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_nb)
+res2 <- MC_boot(n, B1 = 1000, B2 = 400)
 # Just one circle to begin with
@@
 cat("Mean of the variance of bootstrap samples:", res2_nb)
+cat("Mean of the variance of bootstrap samples: \n - for the number of trees:", res2$Variances[1], "\n - for the volume of trees:", res2$Variances[2], "\n - for the ratio volume / number of trees:", res2$Variances[3])
 # Examples:
 # Mean of the variance of bootstrap samples: 2845120
-# Mean of the variance of bootstrap samples: 2851631
+
 ```
@@
 ```{r}
-cat("We get a difference of: ", 100*(max(res1_nb,res2_nb)-min(res1_nb,res2_nb))/min(res1_nb,res2_nb), "%", sep = "")
+diff_percent <- function(x,y)100*(max(x,y)-min(x,y))/min(x,y)
+cat("We get a difference of: ", diff_percent(), "%", sep = "")
 # Examples:

### 2024-07-25 Test_dens.Rmd
More global MC and function for local variables

---
title: "Test_dens"
output: pdf_document
date: "2024-07-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The goal of this file is to correct a mistake made on previous versions of functions to create local variables (those previous versions may be found in Old_Circle.R).

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column and tibble
```

# Preliminaries

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
```

The variable of interest is the number of trees.

```{r}
# Sample size
n <- 100

# Radius
R <- 4
```

# Two functions

```{r}
## Function to produce the local variable for the number of trees
circle_nb_old <- function(x1, x2, R=4){
  # 2 coordinates (x1, x2) and a radius (R)

  # Preliminary: inclusion area
  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")

  list_trees <- which(((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2) & (trees$x > frontier[1]) & (trees$x < frontier[3]) & (trees$y > frontier[2]) & (trees$y < frontier[4]))
  local_var <- sum(length(list_trees)/inc_area(c(x1, x2),frontier[1],frontier[2],frontier[3],frontier[4],R))
  return(local_var)
  # list_trees: identifiers of targeted trees; local_var: local variable based on the number of trees
}
```

```{r}
## Function to produce the local variable for the number of trees
circle_nb_new2 <- function(x1, x2, R=4){
  # 2 coordinates (x1, x2) and a radius (R)

  # Preliminary: inclusion area
  source("~/work/Sim_article2024/Useful_functions/Inc_area_2.R")

  list_trees <- which(((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2) & (trees$x > frontier[1]) & (trees$x < frontier[3]) & (trees$y > frontier[2]) & (trees$y < frontier[4]))
  trees1 <- trees
  trees1$var1 <- rep(1,nrow(trees1))
  if (length(list_trees) != 0){
    local_var <- sum((trees1[list_trees,]$var1)/mapply(inc_area_test, trees1[list_trees,]$x, trees1[list_trees,]$y, MoreArgs = list(frontier[1],frontier[2],frontier[3],frontier[4],R)))
  }
  else{local_var <- 0}
  return(local_var)
  # list_trees: identifiers of targeted trees; local_var: local variable based on the number of trees
}
```

# Tests

```{r}
# Small square
frontier <- c(500, 568, 510, 578)
# Ex: frontier <- c(500, 516, 510, 526)
# frontier <- c(500, 557, 510, 567)
# frontier <- c(500, 568, 510, 578)
```

```{r}
plot(trees$x, trees$y, xlim = c(frontier[1], frontier[3]), ylim = c(frontier[2], frontier[4]))
```

```{r}
true_val <- nrow(trees[(trees$x > frontier[1]) & (trees$x < frontier[3]) & (trees$y > frontier[2]) & (trees$y < frontier[4]),])
true_val
# Ex: 19
# 7
# 12
```

```{r}
# Inclusion density function
p1 <- (1/(frontier[3] - frontier[1]))*(1/(frontier[4] - frontier[2]))
p <- sum(rep(p1, n))
```

```{r}
gap_old <- c()
gap_new <- c()
i = 1
for (i in 1:1000) {
  sampling <- data.frame(x.1 = runif(n, frontier[1], frontier[3]), y.1 = runif(n, frontier[2], frontier[4]))
  est_old <- sum(mapply(circle_nb_old, sampling[, 1], sampling[, 2])/p)
  est_new <- sum(mapply(circle_nb_new2, sampling[, 1], sampling[, 2])/p)
  gap_old <- append(gap_old, abs(est_old-true_val))
  gap_new <- append(gap_new, abs(est_new-true_val))
  i <- i+1
}
```

```{r}
sum(gap_new - gap_old)
# Ex: -0.6188775
# -546.3402
# -97.20414
```

```{r}
sum(as.numeric(gap_new > gap_old) - as.numeric(gap_new < gap_old))
# Ex: 8
# -918
# -188
```

### 2024-07-25 Draft/Old_Circle.R

@@ -1,0 +1,194 @@
+####### OLD functions to produce local variables based on circles -------
+
+# Copy-paste from Circle.R on the 25th of July 2024
+
+### With one single circle -----
+
+## Function to produce the local variable for the number of trees
+circle_nb <- function(x1, x2, R=5){
+  # 2 coordinates (x1, x2) and a radius (R)
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  list_trees <- which((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2)
+  local_var <- sum(length(list_trees)/inc_area(c(x1, x2),0,0,1000,1000,R))
+  return(local_var)
+  # list_trees: identifiers of targeted trees; local_var: local variable based on the number of trees
+}
+
+## Function to produce the local variable for the volume of trees
+circle_vol <- function(x1, x2, R=5){
+  # 2 coordinates (x1, x2) and a radius (R)
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  list_trees <- which((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2)
+  local_var <- sum((trees[list_trees,]$v)/inc_area(c(x1, x2),0,0,1000,1000,R))
+  return(local_var)
+  # list_trees: identifiers of targeted trees; local_var: local variable based on the volume of trees
+}
+
+circle_nb_size <- function(x1, x2, R=5, bounds = c(23.5, 70.5)){
+  # 2 coordinates (x1, x2) and a radius (R)
+  # bounds: to target a category of trees based on circumference
+  
+  # Preliminary: inclusion area
+  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
+  
+  # From circumference to diameter (d130)
+  d <- bounds/pi
+  
+  list_trees <- trees[(x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2,] 
+  # list_trees1 <- ifelse(nrow(list_trees) != 0, list_trees[(list_trees$d130 > d[3]),], list_trees) # List with the biggest trees
+  
+  list_trees_size <- list_trees[(list_trees$d130 > d[1]) & (list_trees$d130 < d[2]),] # smallest trees
+  
[…]

### 2024-07-25 Useful_functions/Circle.R

@@ -1,16 +1,39 @@
 ####### Functions to produce local variables based on circles -------
 
+##### Preliminary: inclusion area ----------
+
+source("~/work/Sim_article2024/Useful_functions/Inc_area_2.R")
+
 ### With one single circle -----
+
+## Function to produce all local variable from one point
+circle_all <- function(x1, x2, R=5){
+  # 2 coordinates (x1, x2) and a radius (R)
+  
+  list_trees <- which(((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2))
+  if (length(list_trees) != 0){
+    local_var_nb <- sum(1/mapply(inc_area, trees[list_trees,]$x, trees[list_trees,]$y, MoreArgs = list(0,0,1000,1000,R)))
+    local_var_vol <- sum((trees[list_trees,]$v)/mapply(inc_area, trees[list_trees,]$x, trees[list_trees,]$y, MoreArgs = list(0,0,1000,1000,R)))
+  }
+  else{
+    local_var_nb <- 0
+    local_var_vol <- 0
+  }
+  return(c(local_var_nb,local_var_vol))
+  # local_var_nb: local variable based on the number of trees; local_var_vol: local variable based on the volume of trees
+}
 
 ## Function to produce the local variable for the number of trees
 circle_nb <- function(x1, x2, R=5){
   # 2 coordinates (x1, x2) and a radius (R)
   
-  # Preliminary: inclusion area
-  source("~/work/Sim_article2024/Useful_functions/Inc_area.R")
-  
-  list_trees <- which((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2)
-  local_var <- sum(length(list_trees)/inc_area(c(x1, x2),0,0,1000,1000,R))
+  list_trees <- which(((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2))
+  trees1 <- trees
+  trees1$var1 <- rep(1,nrow(trees1))
+  if (length(list_trees) != 0){
+    local_var <- sum((trees1[list_trees,]$var1)/mapply(inc_area, trees1[list_trees,]$x, trees1[list_trees,]$y, MoreArgs = list(0,0,1000,1000,R)))
+  }
+  else{local_var <- 0}
   return(local_var)
   # list_trees: identifiers of targeted trees; local_var: local variable based on the number of trees
 }
@@ -19,11 +42,11 @@ circle_nb <- function(x1, x2, R=5){
[…]

### 2024-07-25 Useful_functions/Inc_area_2.R

@@ -1,6 +1,6 @@
-# Just a test
+# More than a test
 
-inc_area_test <- function(x, y, x0F, y0F, x1F, y1F, r){
+inc_area <- function(x, y, x0F, y0F, x1F, y1F, r){
   # x <- coord[1]
   # y <- coord[2]
   

### 2024-07-25 MC_all.Rmd
Adding CI etc

@@
     MC_df <- cbind(MC_df, MC_b)
-    colnames(MC_df)[4*(b-1)+2] <- paste("x", b, sep = "")
-    colnames(MC_df)[4*(b-1)+2+1] <- paste("y", b, sep = "")
-    colnames(MC_df)[4*(b-1)+2+2] <- paste("nb", b, sep = "")
-    colnames(MC_df)[4*(b-1)+2+3] <- paste("vol", b, sep = "")
+    colnames(MC_df)[(4*(b-1)+2):(4*(b-1)+2+3)] <- c(paste("x", b, sep = ""), paste("y", b, sep = ""), paste("nb", b, sep = ""), paste("vol", b, sep = ""))
     est_b <- t(data.frame(x = sum(MC_df[4*(b-1)+2+2] /p), y = sum(MC_df[4*(b-1)+2+3] /p), z = (sum(MC_df[4*(b-1)+2+3] /p))/(sum(MC_df[4*(b-1)+2+2]/p))))
@@
   MC_var <- c(var(as.vector(t(MC_est[1,]))), var(as.vector(t(MC_est[2,]))), var(as.vector(t(MC_est[3,]))))
-  return(list(Data = MC_df, Estimators = MC_est, Variances = MC_var))
-  # Data: local variables (number and voume) for each point in each sample
+
+  # Confidence intervals
+  norm_CI <- data.frame(useless = rep(0, 2))
+  perc_CI <- data.frame(useless = rep(0, 2))
+  rev_perc_CI <- data.frame(useless = rep(0, 2))
+  for (l in 1:3) { # Loop: one estimator each time
+    est_init <- as.vector(t(MC_est[l,]))[1]
+    sorted_est <- sort(as.vector(t(MC_est[l,])))
+    lim_inf <- sorted_est[floor(B*2.5/100)]
+    lim_sup <- sorted_est[B - floor(B*2.5/100)]
+    perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
+    rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_init*2 - lim_sup, est_init*2 - lim_inf)))
+    norm_CI <- cbind(norm_CI, data.frame(c(est_init-qnorm(0.975)*sqrt(MC_var[l]), est_init+qnorm(0.975)*sqrt(MC_var[l]))))
+  }
+  norm_CI$useless <- NULL
+  perc_CI$useless <- NULL
+  rev_perc_CI$useless <- NULL
+  colnames(norm_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
+  colnames(perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
+  colnames(rev_perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
+  all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI)
+
+  return(list(`Local Variables` = MC_df, Estimators = MC_est, Variances = MC_var, `Confidence Intervals` = all_CI))
+  # Local Variables: local variables (number and volume) for each point in each sample
   # Estimators: 3 estimators (number, volume, ratio volume / number) for each sample
   # Variances: Monte Carlo variance for each of the totals / ratio
+  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
 }
@@
 ```{r}
-# mean(as.vector(res_MC$Estimators[1,]))
-```
+# mean(as.vector(t(res_MC$Estimators[1,])))
 
-```{r}
-# mean(res_MC$Estimators[1,])
+cat("95% confidence interval using the percentile method: 
+      [", res_MC$`Confidence Intervals`$Percentile[1,1], ";", res_MC$`Confidence Intervals`$Percentile[2,1], "]\n" )
+
+# cat("95% confidence interval using the reverse percentile method: 
+#       [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]\n" )
 ```
@@
   return(do.call(data.frame, df_boot))
-  # Return a data frame with B samples of 2 variables and of size n
+  # Return a data frame with B samples of as many variables as we want (in this application, 4) and of size n
 }
@@
   vec_est2 <- c()
+  vec_est3 <- c()
   for (c in 1:nboot) {
@@
     vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,4*c]/p))
+    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,4*c]/p))/((n/(n-1))*sum(df[,3*c]/p)))
     # (n/(n-1)) is the correction needed since we choose only (n-1) points
   }
-  vec_est <- data.frame(est1 = vec_est1, est2 = vec_est2)
+  vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
   return(vec_est)
-  # Vector with one estimation for each sample
+  # Vector with 3 estimations for each sample
 }
@@
   p <- sum(rep((1/1000)*(1/1000), n))
+  local_var <- list() # All 
   var_est_boot <- c()
@@
     var_est_boot <- append(var_est_boot, var(est_boot_val))
+
+    local_var <- c(local_var, data_init = random_points, data_boot = est_boot_val)
   }
-  return(mean(var_est_boot))
+  return(list(`Local Variables` = local_var, Variances = boot_var))
+  # Local Variables: local variables (number and volume) for each point in each sample
   # Variances: mean of the bootstrap variance for each estimator
@@
 # Example
+
+## Monte Carlo alone
 
@@
 ```{r}
-cat("Monte Carlo means of estimators: \n - for the number of trees:", mean(as.vector(res1$Estimators[1,])), "\n - for the volume of trees:", mean(as.vector(res1$Estimators[1,])), "\n - for the ratio volume / number of trees:", mean(as.vector(res1$Estimators[1,])))
+cat("Monte Carlo means of estimators: \n - for the number of trees:", mean(as.vector(t(res1$Estimators[1,]))), "\n - for the volume of trees:", mean(as.vector(t(res1$Estimators[2,]))), "\n - for the ratio volume / number of trees:", mean(as.vector(t(res1$Estimators[3,]))))
 # Example:
@@
 ```{r}
-cat("Monte Carlo variance: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[2], "\n - for the ratio volume / number of trees:", res1$Variances[3])
+cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[2], "\n - for the ratio volume / number of trees:", res1$Variances[3])
 # Example:
 ```
+
+```{r}
+cat("95% confidence intervals using the normal method: 
+    \n - for the number of trees: [", res1$`Confidence Intervals`$Normal[1,1], ";", res1$`Confidence Intervals`$Normal[2,1], 
+    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Normal[1,2], ";", res1$`Confidence Intervals`$Normal[2,2], 
+    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$Normal[1,3], ";", res1$`Confidence Intervals`$Normal[2,3],
+    "]")
+```
+
+```{r}
+cat("95% confidence intervals using the percentile method: 
+    \n - for the number of trees: [", res1$`Confidence Intervals`$Percentile[1,1], ";", res1$`Confidence Intervals`$Percentile[2,1], 
+    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Percentile[1,2], ";", res1$`Confidence Intervals`$Percentile[2,2], 
+    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$Percentile[1,3], ";", res1$`Confidence Intervals`$Percentile[2,3],
+    "]"
+    )
+```
+
+```{r}
+cat("95% confidence intervals using the reverse percentile method: 
+    \n - for the number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,1], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,1], 
+    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,2], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,2], 
+    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,3], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,3],
+    "]"
+    )
+```
+
+## Monte Carlo and bootstrap
 
@@
 cat("Mean of the variance of bootstrap samples: \n - for the number of trees:", res2$Variances[1], "\n - for the volume of trees:", res2$Variances[2], "\n - for the ratio volume / number of trees:", res2$Variances[3])
-# Examples:
-# Mean of the variance of bootstrap samples: 2845120
+# Example:
+```
 
-```
+## Comparison of the variances
 
@@
 diff_percent <- function(x,y)100*(max(x,y)-min(x,y))/min(x,y)
-cat("We get a difference of: ", diff_percent(), "%", sep = "")
-# Examples:
-# We get a difference of: 2.01084%
-# We get a difference of: 0.8599411%
+cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(res1$Variances[1], res2$Variances[1]), "%", "\n - for the volume of trees: ", diff_percent(res1$Variances[2], res2$Variances[2]), "\n - for the ratio volume / number of trees: ", diff_percent(res1$Variances[3], res2$Variances[3]), sep = "")
+# Example:
 ```
-
-# Second example: volume of the forest
-
-```{r}
-start.time <- Sys.time()
-
-res1_vol <- MonteCarlo(n, 10000, circle_vol)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Monte Carlo variance:", res1_vol)
-# Ex:
-# Monte Carlo variance: 98332.87
-```
-
-```{r}
-start.time <- Sys.time()
-
-res2_vol <- MC_boot(n, B1 = 1000, B2 = 400, f = circle_vol)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Mean of the variance of bootstrap samples:", res2_vol)
-# Ex:
-# Mean of the variance of bootstrap samples: 98594.44
-```
-
-```{r}
-cat("We get a difference of: ", 100*(max(res1_vol,res2_vol)-min(res1_vol,res2_vol))/min(res1_vol,res2_vol), "%", sep = "")
-# Ex:
-# We get a difference of: 0.2660091%
-```

### 2024-07-25 MC_all.Rmd
MC + boot almost done

@@
 
-  return(list(`Local Variables` = MC_df, Estimators = MC_est, Variances = MC_var, `Confidence Intervals` = all_CI))
+  return(list(`Local Variables` = MC_df, Estimations = MC_est, Variances = MC_var, `Confidence Intervals` = all_CI))
   # Local Variables: local variables (number and volume) for each point in each sample
@@
   return(do.call(data.frame, df_boot))
-  # Return a data frame with B samples of as many variables as we want (in this application, 4) and of size n
+  # Return a data frame with B samples of as many variables as we want (in this application, 4) and of size (n-1)
 }
@@
 MC_boot <- function(n, B1, B2){
-  # n: sample size; B1: number of iterations for MC;
-  # B2: number of iterations for bootstrap;
-  # f: function to consider (2 arguments)
+  # n: sample size;
+  # B1: number of iterations for MC;
+  # B2: number of iterations for bootstrap
 
   p <- sum(rep((1/1000)*(1/1000), n))
-  local_var <- list() # All 
-  var_est_boot <- c()
-  for (b in 2:B1) {
-    # One MC iteration at a time
-    random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
-    random_points$var <- mapply(f, random_points[, 1], random_points[, 2])
-    a <- sum(random_points$var/p)
+  BOOT_df <- list() # All local variables
+  BOOT_est <- list() # All estimations
+  BOOT_var <- list() # Variances
+  BOOT_CI <- list() # Confidence Intervals
+  for (b in 1:B1) { # One MC iteration at a time
+    # Uniform sampling over the whole territory
+    a1 <- runif(n, 0, 1000)
+    a2 <- runif(n, 0, 1000)
+    var <- mapply(circle_all, a1, a2)
+    df_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
+    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
+    est_b <- t(data.frame(x = sum(df_b[3] /p), y = sum(df_b[4] /p), z = (sum(df_b[4] /p))/(sum(df_b[3]/p))))
 
     # Bootstrap iterations
-    df_boot <- f_boot(random_points, B2)
+    df_boot <- f_boot(df_b, B2)
     est_boot_val <- est_boot(df_boot, p)
-    var_est_boot <- append(var_est_boot, var(est_boot_val))
 
-    local_var <- c(local_var, data_init = random_points, data_boot = est_boot_val)
+    BOOT_var[[b]] <- list(var_nb = var(est_boot_val$est_nb), var_vol = var(est_boot_val$est_vol), var_ratio = var(est_boot_val$est_ratio))
+    names(BOOT_var)[b] <- paste("Variance", b, sep = "")
+    BOOT_df <- c(BOOT_df, list(data_init = df_b, data_boot = df_boot))
+    names(BOOT_df)[(2*b-1):(2*b)] <- c(paste("df_MC", b, sep = ""), paste("df_boot", b, sep = ""))
+    BOOT_est <- c(BOOT_est, list(est_init_b = est_b, est_boot_b = est_boot_val))
+    names(BOOT_est)[(2*b-1):(2*b)] <- c(paste("est_MC", b, sep = ""), paste("est_boot", b, sep = ""))
+
+    # Confidence intervals
+    norm_CI <- data.frame(useless = rep(0, 2))
+    perc_CI <- data.frame(useless = rep(0, 2))
+    rev_perc_CI <- data.frame(useless = rep(0, 2))
+    for (l in 1:3) { # Loop: one estimator each time
+      sorted_est <- sort(est_boot_val[,l])
+      lim_inf <- sorted_est[floor(B2*2.5/100)]
+      lim_sup <- sorted_est[B2 - floor(B2*2.5/100)]
+      perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
+      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_b[l,]*2 - lim_sup, est_b[l,]*2 - lim_inf)))
+      norm_CI <- cbind(norm_CI, data.frame(c(est_b[l,]-qnorm(0.975)*sqrt(var(est_boot_val[,l])), est_b[l,]+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
     }
-  return(list(`Local Variables` = local_var, Variances = boot_var))
+    norm_CI$useless <- NULL
+    perc_CI$useless <- NULL
+    rev_perc_CI$useless <- NULL
+    colnames(norm_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
+    colnames(perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
+    colnames(rev_perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
+    all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI)
+    # BOOT_CI <- c(BOOT_CI, CI_b = all_CI)
+    BOOT_CI[[b]] <- all_CI
+    names(BOOT_CI)[b] <- paste("CI", b, sep = "")
+  }
+  return(list(`Local Variables` = BOOT_df, Estimations = BOOT_est, Variances = BOOT_var, `Confidence Intervals` = BOOT_CI))
   # Local Variables: local variables (number and volume) for each point in each sample
+  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
   # Variances: mean of the bootstrap variance for each estimator
+  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
 }
+```
+
+```{r}
+# Small test
+
+start.time <- Sys.time()
+
+res_MC_boot <- MC_boot(100, 200, 100)
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
 ```
@@
 ```{r}
-cat("Mean of the variance of bootstrap samples:", res2_nb)
+# PROBLEM NOW: MEAN of variance for each estimation
+# How to extract it without a loop? mapply with function made up
+
 cat("Mean of the variance of bootstrap samples: \n - for the number of trees:", res2$Variances[1], "\n - for the volume of trees:", res2$Variances[2], "\n - for the ratio volume / number of trees:", res2$Variances[3])

### 2024-07-25 Draft/Draft.Rmd
Better version of Two_var
More global MC and function for local variables
Obviously a pb with variances

@@
 
-## Tessellation
+## Tessellation ----------
 
@@
 
-## Draft
+## Draft ----------
 
@@
 
-## Circle
+## Circle ----------
 
@@
 
-## Draft for bootstrap
+## Draft for bootstrap ----------
 
@@
 
-### Complexity
+### Complexity ----------
 
@@
 
-### A first package
+### A first package ----------
 
@@
 
-### Another package
+### Another package ----------
 
@@
 
-# Grid for trees
+# Grid for trees ----------
 
@@
 
-# Bootstrap
+# Bootstrap ----------
 
@@
 
-# Alarm / beep / message when it finishes running
+# Alarm / beep / message when it finishes running ----------
 
@@
 ```
+
+# Variance ----------
+
+```{r}
+# Unbiased variance
+
+# Test
+test <- c(1,2,3,5)
+var(test) # 2.916667
+
+varbis <- function(x){
+
+}
+```
+
+# Print LaTeX code as output of R code (failure) ----------
+
+```{r}
+print("* $H_o = `r 1 + 1`$")
+b0 = "$\\beta_0$"
+m3 = "$m^3$"
+cat("thing:",m3)
+cat("thing:",`b0`)
+```
+
+```{r}
+print(bquote(m^2))
+```
+
+# Small examples for MC_all.Rmd ----------
+
+```{r}
+# Small test
+
+start.time <- Sys.time()
+
+res_MC <- MonteCarlo(100, 200)
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```
+
+```{r}
+# mean(as.vector(t(res_MC$Estimators[1,])))
+
+cat("95% confidence interval using the percentile method: 
+      [", res_MC$`Confidence Intervals`$Percentile[1,1], ";", res_MC$`Confidence Intervals`$Percentile[2,1], "]\n" )
+
+# cat("95% confidence interval using the reverse percentile method: 
+#       [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]\n" )
+```
+
+```{r}
+# Small test
+
+start.time <- Sys.time()
+
+res_MC_boot <- MC_boot(100, 200, 100)
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```

### 2024-07-25 MC_all.Rmd
Obviously a pb with variances

@@
 # To get closer to the NFI process, trees whose circumference is under 23.5 cm are not considered
-trees <- trees[(pi*trees$d130 > 23.5),]
+trees <- all_trees[(pi*all_trees$d130 > 23.5),]
 ```
@@
   # Local Variables: local variables (number and volume) for each point in each sample
-  # Estimators: 3 estimators (number, volume, ratio volume / number) for each sample
+  # Estimations: 3 Estimations (number, volume, ratio volume / number) for each sample
   # Variances: Monte Carlo variance for each of the totals / ratio
@@
 }
-```
-
-```{r}
-# Small test
-
-start.time <- Sys.time()
-
-res_MC <- MonteCarlo(100, 200)
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-# mean(as.vector(t(res_MC$Estimators[1,])))
-
-cat("95% confidence interval using the percentile method: 
-      [", res_MC$`Confidence Intervals`$Percentile[1,1], ";", res_MC$`Confidence Intervals`$Percentile[2,1], "]\n" )
-
-# cat("95% confidence interval using the reverse percentile method: 
-#       [", est_init*2 - lim_sup, ";", est_init*2 - lim_inf, "]\n" )
 ```
@@
 
-```{r}
-# Small test
-
-start.time <- Sys.time()
-
-res_MC_boot <- MC_boot(100, 200, 100)
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
 # Example
@@
 ```{r}
-cat("Monte Carlo means of estimators: \n - for the number of trees:", mean(as.vector(t(res1$Estimators[1,]))), "\n - for the volume of trees:", mean(as.vector(t(res1$Estimators[2,]))), "\n - for the ratio volume / number of trees:", mean(as.vector(t(res1$Estimators[3,]))))
+cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(as.vector(t(res1$Estimations[1,]))), "\n - for the volume of trees:", mean(as.vector(t(res1$Estimations[2,]))), "\n - for the ratio volume / number of trees:", mean(as.vector(t(res1$Estimations[3,]))))
+
 # Example:
+# Monte Carlo means of estimations: 
+#  - for the number of trees: 29299.58 
+#  - for the volume of trees: 5418.03 
+#  - for the ratio volume / number of trees: 0.1849162
 ```
@@
 cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[2], "\n - for the ratio volume / number of trees:", res1$Variances[3])
+
 # Example:
+# Monte Carlo variances: 
+#  - for the number of trees: 2531530 
+#  - for the volume of trees: 96840.38 
+#  - for the ratio volume / number of trees: 1.116039e-05
 ```
@@
 ```{r}
-cat("95% confidence intervals using the normal method: 
-    \n - for the number of trees: [", res1$`Confidence Intervals`$Normal[1,1], ";", res1$`Confidence Intervals`$Normal[2,1], 
+cat("95% confidence intervals using the normal method:\n - for the number of trees: [", res1$`Confidence Intervals`$Normal[1,1], ";", res1$`Confidence Intervals`$Normal[2,1], 
     "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Normal[1,2], ";", res1$`Confidence Intervals`$Normal[2,2], 
@@
     "]")
+
+# Example:
+# 95% confidence intervals using the normal method: 
+#  - for the number of trees: [ 25885.94 ; 32122.85 ]
+#  - for the volume of trees: [ 4727.737 ; 5947.587 ]
+#  - for the ratio volume / number of trees: [ 0.1774817 ; 0.1905771 ]
 ```
@@
 ```{r}
-cat("95% confidence intervals using the percentile method: 
-    \n - for the number of trees: [", res1$`Confidence Intervals`$Percentile[1,1], ";", res1$`Confidence Intervals`$Percentile[2,1], 
+cat("95% confidence intervals using the percentile method:\n - for the number of trees: [", res1$`Confidence Intervals`$Percentile[1,1], ";", res1$`Confidence Intervals`$Percentile[2,1], 
     "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Percentile[1,2], ";", res1$`Confidence Intervals`$Percentile[2,2], 
     "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$Percentile[1,3], ";", res1$`Confidence Intervals`$Percentile[2,3],
-    "]"
-    )
+    "]")
+
+# Example:
+# 95% confidence intervals using the percentile method: 
+#  - for the number of trees: [ 26203.27 ; 32429.41 ]
+#  - for the volume of trees: [ 4817.327 ; 6027.707 ]
+#  - for the ratio volume / number of trees: [ 0.1786038 ; 0.1915195 ]
 ```
@@
 ```{r}
-cat("95% confidence intervals using the reverse percentile method: 
-    \n - for the number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,1], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,1], 
+cat("95% confidence intervals using the reverse percentile method:\n - for the number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,1], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,1],
     "]\n - for the volume of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,2], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,2], 
@@
     )
+
+# Example:
+# 95% confidence intervals using the reverse percentile method:
+#  - for the number of trees: [ 25579.38 ; 31805.52 ]
+#  - for the volume of trees: [ 4647.617 ; 5857.997 ]
+#  - for the ratio volume / number of trees: [ 0.1765393 ; 0.189455 ]
 ```
@@
 ```{r}
-# PROBLEM NOW: MEAN of variance for each estimation
-# How to extract it without a loop? mapply with function made up
+VAR_nb <- c()
+for (elt in res2$Variances) {
+  VAR_nb <- append(VAR_nb, elt$var_nb)
+}
 
-cat("Mean of the variance of bootstrap samples: \n - for the number of trees:", res2$Variances[1], "\n - for the volume of trees:", res2$Variances[2], "\n - for the ratio volume / number of trees:", res2$Variances[3])
+VAR_vol <- c()
+for (elt in res2$Variances) {
+  VAR_vol <- append(VAR_vol, elt$var_vol)
+}
+
+VAR_ratio <- c()
+for (elt in res2$Variances) {
+  VAR_ratio <- append(VAR_ratio, elt$var_ratio)
+}
+```
+
+```{r}
+cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", mean(VAR_nb), "\n - for the volume of trees:", mean(VAR_vol), "\n - for the ratio volume / number of trees:", mean(VAR_ratio))
+
 # Example:
+# Mean of the variance of bootstrap samples:
+#  - for the number of trees: 6.273237e+16 
+#  - for the volume of trees: 98861.68 
+#  - for the ratio volume / number of trees: 0.1741024
 ```
@@
 diff_percent <- function(x,y)100*(max(x,y)-min(x,y))/min(x,y)
-cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(res1$Variances[1], res2$Variances[1]), "%", "\n - for the volume of trees: ", diff_percent(res1$Variances[2], res2$Variances[2]), "\n - for the ratio volume / number of trees: ", diff_percent(res1$Variances[3], res2$Variances[3]), sep = "")
+cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(res1$Variances[1], mean(VAR_nb)), "%", "\n - for the volume of trees: ", diff_percent(res1$Variances[2], mean(VAR_vol)), "%\n - for the ratio volume / number of trees: ", diff_percent(res1$Variances[3], mean(VAR_ratio)), "%", sep = "")
+
 # Example:
+# Difference between the two estimations of variance: 
+#  - for the number of trees: 2.478042e+12%
+#  - for the volume of trees: 2.087256%
+#  - for the ratio volume / number of trees: 1559903%
 ```

### 2024-07-26 MC_all.Rmd
Found and resolved a pb

@@
 
-  df_boot <- tibble(.rows = (nrow(df_sample)-1))
+  # df_boot <- tibble(.rows = (nrow(df_sample)-1))
+  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-1))
   for (b in 1:B) {
@@
     sample_b <- df_sample[nb,]
-    df_boot <- df_boot %>% add_column(new_col = sample_b)
-    colnames(df_boot)[b] <- paste("ech", b, sep = "")
+    # df_boot <- df_boot %>% add_column(new_col = sample_b)
+    df_boot <- cbind(df_boot, sample_b)
+    colnames(df_boot)[((b-1)*4+1 + 1):(b*4+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""))
   }
-  return(do.call(data.frame, df_boot))
+  df_boot$useless <- NULL
+  # return(do.call(data.frame, df_boot))
+  return(df_boot)
   # Return a data frame with B samples of as many variables as we want (in this application, 4) and of size (n-1)
@@
   for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3*c]/p))
+    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + (4*(c-1))]/p))
     vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,4*c]/p))
-    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,4*c]/p))/((n/(n-1))*sum(df[,3*c]/p)))
+    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,4*c]/p))/((n/(n-1))*sum(df[,3 + (4*(c-1))]/p)))
     # (n/(n-1)) is the correction needed since we choose only (n-1) points

### 2024-07-26 Draft/Draft.Rmd
Clean file to knit

@@
 ```
+
+# Old f_boot with the tibble point of view still readable for MC_all.Rmd ----------
+
+```{r}
+f_boot <- function(df_sample, B){
+  # df_sample: original sample; 
+  # B: number of bootstrap samples made thanks to df_sample
+
+  # df_boot <- tibble(.rows = (nrow(df_sample)-1))
+  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-1))
+  for (b in 1:B) {
+    nb <- sample(1:nrow(df_sample), (nrow(df_sample)-1), replace = TRUE)
+    # (n-1) points at random
+    sample_b <- df_sample[nb,]
+    # df_boot <- df_boot %>% add_column(new_col = sample_b)
+    df_boot <- cbind(df_boot, sample_b)
+    colnames(df_boot)[((b-1)*4+1 + 1):(b*4+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""))
+  }
+  df_boot$useless <- NULL
+  # return(do.call(data.frame, df_boot))
+  return(df_boot)
+  # Return a data frame with B samples of as many variables as we want (in this application, 4) and of size (n-1)
+}
+```
+
+VAR_vol <- c()
+for (elt in res2$Variances) {
+  VAR_vol <- append(VAR_vol, elt$var_vol)
+}
+
+VAR_ratio <- c()
+for (elt in res2$Variances) {
+  VAR_ratio <- append(VAR_ratio, elt$var_ratio)
+}

### 2024-07-26 MC_all.Rmd
Clean file to knit

@@
 
-  # df_boot <- tibble(.rows = (nrow(df_sample)-1))
   df_boot <- data.frame(useless = rep(0, nrow(df_sample)-1))
@@
     sample_b <- df_sample[nb,]
-    # df_boot <- df_boot %>% add_column(new_col = sample_b)
     df_boot <- cbind(df_boot, sample_b)
@@
   df_boot$useless <- NULL
-  # return(do.call(data.frame, df_boot))
   return(df_boot)
@@
 ```{r}
+# We want all the variances obtained for each parameter of interest, 
+# to find the mean for each of these series
+EST_nb <- c()
+EST_vol <- c()
+EST_ratio <- c()
+for (elt in res2$Estimations) {
+  if ("data.frame" %in% class(elt)){ # we target bootstrap samples made from each MC iteration
+    EST_nb <- append(EST_nb, mean(elt$est_nb))
+    EST_vol <- append(EST_vol, mean(elt$est_vol))
+    EST_ratio <- append(EST_ratio, mean(elt$est_ratio))
+  }
+}
+```
+
+```{r}
+cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(EST_nb), "\n - for the volume of trees:", mean(EST_vol), "\n - for the ratio volume / number of trees:", mean(EST_ratio))
+
+# Example:
+
+```
+
+```{r}
+# We want all the variances obtained for each parameter of interest, 
+# to find the mean for each of these series
 VAR_nb <- c()
+VAR_vol <- c()
+VAR_ratio <- c()
 for (elt in res2$Variances) {
   VAR_nb <- append(VAR_nb, elt$var_nb)
-}
-
-VAR_vol <- c()
-for (elt in res2$Variances) {
   VAR_vol <- append(VAR_vol, elt$var_vol)
-}
-
-VAR_ratio <- c()
-for (elt in res2$Variances) {
   VAR_ratio <- append(VAR_ratio, elt$var_ratio)
@@
 # Example:
-# Mean of the variance of bootstrap samples:
-#  - for the number of trees: 6.273237e+16 
-#  - for the volume of trees: 98861.68 
-#  - for the ratio volume / number of trees: 0.1741024
+
 ```
@@
 # Example:
-# Difference between the two estimations of variance: 
-#  - for the number of trees: 2.478042e+12%
-#  - for the volume of trees: 2.087256%
-#  - for the ratio volume / number of trees: 1559903%
+
 ```

### 2024-07-26 MC_all.Rmd
With example

@@
 ---
-title: "Monte Carlo for all parameters"
+title: "Monte Carlo and bootstrap for all parameters"
 output: pdf_document
-date: "2024-07-24"
+date: "2024-07-26"
 ---
@@
 ```
+
+The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees and the ratio volume of trees / number of trees), variances of these estimators and confidence intervals.
+The same elements are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations.
+By comparing the two results, we may ensure the validity of the bootstrap strategy to find the estimation of the variances.
+In this document, one single circle with a radius of 5 is used to compute local variables.
 
@@
 # Example:
-# Monte Carlo means of estimations: 
-#  - for the number of trees: 29299.58 
-#  - for the volume of trees: 5418.03 
-#  - for the ratio volume / number of trees: 0.1849162
+## Monte Carlo means of estimations:
+##  - for the number of trees: 29251.69
+##  - for the volume of trees: 5407.967
+##  - for the ratio volume / number of trees: 0.184873
 ```
@@
 # Example:
-# Monte Carlo variances: 
-#  - for the number of trees: 2531530 
-#  - for the volume of trees: 96840.38 
-#  - for the ratio volume / number of trees: 1.116039e-05
+## Monte Carlo variances:
+##  - for the number of trees: 2604340
+##  - for the volume of trees: 99936.6
+##  - for the ratio volume / number of trees: 1.122037e-05
 ```
@@
 # Example:
-# 95% confidence intervals using the normal method: 
-#  - for the number of trees: [ 25885.94 ; 32122.85 ]
-#  - for the volume of trees: [ 4727.737 ; 5947.587 ]
-#  - for the ratio volume / number of trees: [ 0.1774817 ; 0.1905771 ]
+## 95% confidence intervals using the normal method:
+##  - for the number of trees: [ 23345.86 ; 29671.83 ]
+##  - for the volume of trees: [ 4320.113 ; 5559.31 ]
+##  - for the ratio volume / number of trees: [ 0.1797767 ; 0.1929072 ]
 ```
@@
 # Example:
-# 95% confidence intervals using the percentile method: 
-#  - for the number of trees: [ 26203.27 ; 32429.41 ]
-#  - for the volume of trees: [ 4817.327 ; 6027.707 ]
-#  - for the ratio volume / number of trees: [ 0.1786038 ; 0.1915195 ]
+## 95% confidence intervals using the percentile method:
+##  - for the number of trees: [ 26139.61 ; 32467.61 ]
+##  - for the volume of trees: [ 4798.827 ; 6037.256 ]
+##  - for the ratio volume / number of trees: [ 0.1783755 ; 0.1915082 ]
 ```
@@
 # Example:
-# 95% confidence intervals using the reverse percentile method:
-#  - for the number of trees: [ 25579.38 ; 31805.52 ]
-#  - for the volume of trees: [ 4647.617 ; 5857.997 ]
-#  - for the ratio volume / number of trees: [ 0.1765393 ; 0.189455 ]
+## 95% confidence intervals using the reverse percentile method:
+##  - for the number of trees: [ 20550.09 ; 26878.09 ]
+##  - for the volume of trees: [ 3842.166 ; 5080.595 ]
+##  - for the ratio volume / number of trees: [ 0.1811758 ; 0.1943085 ]
 ```
@@
 # Example:
-
+## Mean of the means of estimations obtained through each bootstrap process:
+##  - for the number of trees: 29280.52
+##  - for the volume of trees: 5411.916
+##  - for the ratio volume / number of trees: 0.1848212
 ```
@@
 # Example:
-
+## Mean of the variance of bootstrap samples:
+##  - for the number of trees: 2562574
+##  - for the volume of trees: 98333.62
+##  - for the ratio volume / number of trees: 1.121868e-05
 ```
@@
 # Example:
-
+## Difference between the two estimations of variance:
+##  - for the number of trees: 1.629866%
+##  - for the volume of trees: 1.630143%
+##  - for the ratio volume / number of trees: 0.01505727%
 ```

### 2024-07-26 MC_grid.Rmd
Big MC and boot functions with grid

--- 2024-07-26 MC_all.Rmd
@@
 ---
-title: "Monte Carlo for all parameters"
+title: "Monte Carlo and bootstrap for all parameteres with a grid"
 output: pdf_document
-date: "2024-07-24"
+date: "2024-07-26"
 ---
@@
 ```
+
+The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees and the ratio volume of trees / number of trees), variances of these estimators and confidence intervals.
+The same elements are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations.
+By comparing the two results, we may verify the invalidity of the bootstrap strategy to find the estimation of the variances.
+\\
+In this document, one single circle with a radius of 5 is used to compute local variables. Besides, and more importantly, a grid is used for sampling.
 
@@
 ```{r}
+i <- sample(1:10, 1) # choice of the rank of the identifier we want
+i
+```
+
+```{r}
+# Dimension of a small square (length of one side of the square)
+# We assume that c_dim is a divisor of 1000
+c_dim <- 10
+```
+
+```{r}
+# Function to sample at random following the grid
+sampling_grid <- function(i,c_dim){
+random_points <- data.frame(x = numeric(), y = numeric())
+
+for (l in 0:((1000/c_dim)-1)) {
+  if (l==0){
+    x_init <- i*c_dim
+  }else if ((3*l+i)*c_dim < (10)*c_dim){
+    x_init <- (3*l+i)*c_dim
+  }else{
+    x_init <- (((3*l+i)*c_dim)%%(c_dim*10))
+  }
+  k <- 0
+  while (x_init + 10*c_dim*k < 1000) {
+    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + c_dim)
+    b <- runif(1, l*c_dim, (l+1)*c_dim)
+    random_points <- rbind(random_points, list(a,b))
+    k <- k+1
+  }
+}
+colnames(random_points) <- list("x", "y")
+return(random_points)
+}
+```
+
+```{r}
 # True values
@@
 ```{r}
-### Function to automate Monte Carlo method, to produce a variance
+### Function to automate Monte Carlo method
 
 MonteCarlo <- function(n, B){
-  # n: sample size;
   # B: number of iterations for MC
@@
   p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
-
   MC_df <- data.frame(useless = rep(0, n))
@@
   for (b in 1:B) { # All in one "for" loop
-    # Uniform sampling over the whole territory
-    a1 <- runif(n, 0, 1000)
-    a2 <- runif(n, 0, 1000)
+    # Sampling over the whole territory
+    df_grid <- sampling_grid(i,c_dim)
+    a1 <- df_grid$x
+    a2 <- df_grid$y
+    # n <- nrow(df_grid) # sample size
+    # p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
     # Variables of interest derived from the sample
@@
   return(vec_est)
-  # Vector with 3 estimations for each sample
+  # Data frame with 3 estimations for each sample
 }
@@
 MC_boot <- function(n, B1, B2){
-  # n: sample size;
   # B1: number of iterations for MC;
@@
     # Uniform sampling over the whole territory
-    a1 <- runif(n, 0, 1000)
-    a2 <- runif(n, 0, 1000)
+    df_grid <- sampling_grid(i,c_dim)
+    a1 <- df_grid$x
+    a2 <- df_grid$y
+    # n <- nrow(df_grid) # sample size
+    # p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
     var <- mapply(circle_all, a1, a2)
@@
 # Example:
-# Monte Carlo means of estimations: 
-#  - for the number of trees: 29299.58 
-#  - for the volume of trees: 5418.03 
-#  - for the ratio volume / number of trees: 0.1849162
+
 ```
@@
 # Example:
-# Monte Carlo variances: 
-#  - for the number of trees: 2531530 
-#  - for the volume of trees: 96840.38 
-#  - for the ratio volume / number of trees: 1.116039e-05
+
 ```
@@
 # Example:
-# 95% confidence intervals using the normal method: 
-#  - for the number of trees: [ 25885.94 ; 32122.85 ]
-#  - for the volume of trees: [ 4727.737 ; 5947.587 ]
-#  - for the ratio volume / number of trees: [ 0.1774817 ; 0.1905771 ]
+
 ```
@@
 # Example:
-# 95% confidence intervals using the percentile method: 
-#  - for the number of trees: [ 26203.27 ; 32429.41 ]
-#  - for the volume of trees: [ 4817.327 ; 6027.707 ]
-#  - for the ratio volume / number of trees: [ 0.1786038 ; 0.1915195 ]
+
 ```
@@
 # Example:
-# 95% confidence intervals using the reverse percentile method:
-#  - for the number of trees: [ 25579.38 ; 31805.52 ]
-#  - for the volume of trees: [ 4647.617 ; 5857.997 ]
-#  - for the ratio volume / number of trees: [ 0.1765393 ; 0.189455 ]
+
 ```

### 2024-07-26 Useful_functions/Circle.R
The same with 3 circles

@@ -6,7 +6,7 @@ source("~/work/Sim_article2024/Useful_functions/Inc_area_2.R")
 
 ### With one single circle -----
 
-## Function to produce all local variable from one point
+## Function to produce all local variables from one point
 circle_all <- function(x1, x2, R=5){
   # 2 coordinates (x1, x2) and a radius (R)
   
@@ -90,6 +90,51 @@ circle_vol_size <- function(x1, x2, R=5, bounds = c(23.5, 70.5)){
 }
 
 ### With three circles -----
+
+## Function to produce all local variables from one point
+circle3_all <- function(x1, x2, R1=15, R2=9, R3=6){
+  # 2 coordinates (x1, x2) and a radius (R)
+  
+  list_trees <- which(((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R1^2))
+  
+  list_trees1 <- list_trees[pi*trees[list_trees,]$d130 > 117.5] # List with the biggest trees
+  list_trees2 <- list_trees[(pi*trees[list_trees,]$d130 < 117.5) & (pi*trees[list_trees,]$d130 > 70.5) & ((x1 - trees[list_trees,]$x)^2 + (x2 - trees[list_trees,]$y)^2 <= R2^2)] # medium trees
+  list_trees3 <- list_trees[(pi*trees[list_trees,]$d130 < 70.5) & ((x1 - trees[list_trees,]$x)^2 + (x2 - trees[list_trees,]$y)^2 <= R3^2)] # smallest trees
+  # (pi*trees[list_trees,]$d130 > 23.5) & = useless since trees already excludes the little ones
+  
+  if (length(list_trees1) != 0){
+    local_var_nb1 <- sum(1/mapply(inc_area, trees[list_trees1,]$x, trees[list_trees1,]$y, MoreArgs = list(0,0,1000,1000,R1)))
+    local_var_vol1 <- sum((trees[list_trees1,]$v)/mapply(inc_area, trees[list_trees1,]$x, trees[list_trees1,]$y, MoreArgs = list(0,0,1000,1000,R1)))
+  }
+  else{
+    local_var_nb1 <- 0
+    local_var_vol1 <- 0
+  }
+  
+  if (length(list_trees2) != 0){
+    local_var_nb2 <- sum(1/mapply(inc_area, trees[list_trees2,]$x, trees[list_trees2,]$y, MoreArgs = list(0,0,1000,1000,R2)))
[…]

### 2024-07-27 MC_grid.Rmd
With an example

@@
 ---
-title: "Monte Carlo and bootstrap for all parameteres with a grid"
+title: "Monte Carlo and bootstrap for all parameters with a grid"
 output: pdf_document
@@
 By comparing the two results, we may verify the invalidity of the bootstrap strategy to find the estimation of the variances.
-\\
+
 In this document, one single circle with a radius of 5 is used to compute local variables. Besides, and more importantly, a grid is used for sampling.
@@
 # Example:
-
+## Monte Carlo means of estimations:
+##  - for the number of trees: 29529.27
+##  - for the volume of trees: 5428.676
+##  - for the ratio volume / number of trees: 0.1838376
 ```
@@
 # Example:
-
+## Monte Carlo variances:
+##  - for the number of trees: 263478.6
+##  - for the volume of trees: 15475.27
+##  - for the ratio volume / number of trees: 6.470082e-06
 ```
@@
 # Example:
-
+## 95% confidence intervals using the normal method:
+##  - for the number of trees: [ 28787.75 ; 30799.86 ]
+##  - for the volume of trees: [ 5115.539 ; 5603.177 ]
+##  - for the ratio volume / number of trees: [ 0.1748962 ; 0.1848671 ]
 ```
@@
 # Example:
-
+## 95% confidence intervals using the percentile method:
+##  - for the number of trees: [ 28533.3 ; 30557.75 ]
+##  - for the volume of trees: [ 5188.069 ; 5673.772 ]
+##  - for the ratio volume / number of trees: [ 0.1787598 ; 0.1888164 ]
 ```
@@
 # Example:
-
+## 95% confidence intervals using the reverse percentile method:
+##  - for the number of trees: [ 29029.86 ; 31054.31 ]
+##  - for the volume of trees: [ 5044.944 ; 5530.647 ]
+##  - for the ratio volume / number of trees: [ 0.1709469 ; 0.1810035 ]
 ```
@@
 # Example:
-
+## Mean of the means of estimations obtained through each bootstrap process:
+##  - for the number of trees: 29546.03
+##  - for the volume of trees: 5431.112
+##  - for the ratio volume / number of trees: 0.1838134
 ```
@@
 # Example:
-
+## Mean of the variance of bootstrap samples:
+##  - for the number of trees: 2630037
+##  - for the volume of trees: 99634.96
+##  - for the ratio volume / number of trees: 1.033748e-05
 ```
@@
 # Example:
-
+## Difference between the two estimations of variance:
+##  - for the number of trees: 898.1975%
+##  - for the volume of trees: 543.8335%
+##  - for the ratio volume / number of trees: 59.77348%
 ```

### 2024-07-29 MC_adagrid.Rmd
Stratified bootstrap

--- 2024-07-26 MC_grid.Rmd
@@
 ---
-title: "Monte Carlo and bootstrap for all parameteres with a grid"
+title: "Monte Carlo and non-uniform bootstrap"
 output: pdf_document
-date: "2024-07-26"
+date: "2024-07-29"
 ---
@@
 sampling_grid <- function(i,c_dim){
-random_points <- data.frame(x = numeric(), y = numeric())
+random_points <- data.frame(x = numeric(), y = numeric(), z = numeric())
 
@@
     b <- runif(1, l*c_dim, (l+1)*c_dim)
-    random_points <- rbind(random_points, list(a,b))
+    random_points <- rbind(random_points, list(a,b, l))
     k <- k+1
@@
 }
-colnames(random_points) <- list("x", "y")
+colnames(random_points) <- list("x", "y", "line")
 return(random_points)
@@
     a2 <- df_grid$y
+    a3 <- df_grid$line
     # n <- nrow(df_grid) # sample size
@@
     var <- mapply(circle_all, a1, a2)
-    MC_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
+    MC_b <- data.frame(x = a1, y = a2, w = a3, z = t(var)[,1], t = t(var)[,2])
     MC_df <- cbind(MC_df, MC_b)
-    colnames(MC_df)[(4*(b-1)+2):(4*(b-1)+2+3)] <- c(paste("x", b, sep = ""), paste("y", b, sep = ""), paste("nb", b, sep = ""), paste("vol", b, sep = ""))
-    est_b <- t(data.frame(x = sum(MC_df[4*(b-1)+2+2] /p), y = sum(MC_df[4*(b-1)+2+3] /p), z = (sum(MC_df[4*(b-1)+2+3] /p))/(sum(MC_df[4*(b-1)+2+2]/p))))
+    colnames(MC_df)[(5*(b-1)+2):(5*(b-1)+2+4)] <- c(paste("x", b, sep = ""), paste("y", b, sep = ""), paste("l", b, sep = ""), paste("nb", b, sep = ""), paste("vol", b, sep = ""))
+    est_b <- t(data.frame(x = sum(MC_df[5*(b-1)+2+3] /p), y = sum(MC_df[5*(b-1)+2+4] /p), z = (sum(MC_df[5*(b-1)+2+4] /p))/(sum(MC_df[5*(b-1)+2+3]/p))))
     MC_est <- cbind(MC_est, est_b)
@@
 
-  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-1))
+  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-10))
   for (b in 1:B) {
-    nb <- sample(1:nrow(df_sample), (nrow(df_sample)-1), replace = TRUE)
-    # (n-1) points at random
-    sample_b <- df_sample[nb,]
+    nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
+    # (H-1) lines at random
+    sample_b <- data.frame(x = numeric(), y = numeric(), z = numeric(), t = numeric(), w = numeric())
+    for (number in nb){
+      sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
+    }
     df_boot <- cbind(df_boot, sample_b)
-    colnames(df_boot)[((b-1)*4+1 + 1):(b*4+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""))
+    colnames(df_boot)[((b-1)*5+1 + 1):(b*5+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""), paste("ech", b, colnames(df_sample)[5], sep = ""))
   }
@@
   return(df_boot)
-  # Return a data frame with B samples of as many variables as we want (in this application, 4) and of size (n-1)
+  # Return a data frame with B samples of as many variables as we want (in this application, 5)
 }
@@
 est_boot <- function(df, p){
-  # df: dataframe with 4*B columns and n rows
+  # df: dataframe with 5*B columns and n rows
 
   n <- nrow(df) + 1 # sample size of the initial sample
-  nboot <- length(df)/4 # number of bootstrap samples
+  nboot <- length(df)/5 # number of bootstrap samples
   vec_est1 <- c()
@@
   for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + (4*(c-1))]/p))
-    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,4*c]/p))
-    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,4*c]/p))/((n/(n-1))*sum(df[,3 + (4*(c-1))]/p)))
+    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,4 + (5*(c-1))]/p))
+    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,5*c]/p))
+    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,5*c]/p))/((n/(n-1))*sum(df[,4 + (5*(c-1))]/p)))
     # (n/(n-1)) is the correction needed since we choose only (n-1) points
@@
     a2 <- df_grid$y
-    # n <- nrow(df_grid) # sample size
-    # p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
+    a3 <- df_grid$line
     var <- mapply(circle_all, a1, a2)
-    df_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
-    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
-    est_b <- t(data.frame(x = sum(df_b[3] /p), y = sum(df_b[4] /p), z = (sum(df_b[4] /p))/(sum(df_b[3]/p))))
+    df_b <- data.frame(x = a1, y = a2, w = a3, z = t(var)[,1], t = t(var)[,2])
+    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("l.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
+    est_b <- t(data.frame(x = sum(df_b[4] /p), y = sum(df_b[5] /p), z = (sum(df_b[5] /p))/(sum(df_b[4]/p))))
 

### 2024-07-30 MC_adagrid.Rmd
Correction for bootstrap 1

@@
 The same elements are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations.
-By comparing the two results, we may verify the invalidity of the bootstrap strategy to find the estimation of the variances.
+By comparing the two results, we may verify the (in)validity of the bootstrap strategy to find the estimation of the variances.
 
@@
     colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("l.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
-    est_b <- t(data.frame(x = sum(df_b[4] /p), y = sum(df_b[5] /p), z = (sum(df_b[5] /p))/(sum(df_b[4]/p))))
+    est_b <- t(data.frame(x = (100/99)*sum(df_b[4] /p), y = (100/99)*sum(df_b[5] /p), z = (100/99)*(sum(df_b[5] /p))/(sum(df_b[4]/p))))
 

### 2024-07-30 MC_adagrid.Rmd
Correction changed

--- 2024-07-29 MC_adagrid.Rmd
@@
   for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,4 + (5*(c-1))]/p))
-    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,5*c]/p))
-    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,5*c]/p))/((n/(n-1))*sum(df[,4 + (5*(c-1))]/p)))
+    vec_est1 <- append(vec_est1, (100/99)*sum(df[,4 + (5*(c-1))]/p))
+    vec_est2 <- append(vec_est2, (100/99)*sum(df[,5*c]/p))
+    vec_est3 <- append(vec_est3, ((100/99)*sum(df[,5*c]/p))/((100/99)*sum(df[,4 + (5*(c-1))]/p)))
     # (n/(n-1)) is the correction needed since we choose only (n-1) points

### 2024-07-30 test_boot_short.Rmd
Test for better bootstrap variance

--- 2024-07-30 MC_adagrid.Rmd
@@
 ---
-title: "Monte Carlo and non-uniform bootstrap"
+title: "Another stratification"
 output: pdf_document
@@
     b <- runif(1, l*c_dim, (l+1)*c_dim)
-    random_points <- rbind(random_points, list(a,b, l))
+    h <- nrow(random_points)%%100 # 100 strata
+    random_points <- rbind(random_points, list(a,b, h))
     k <- k+1
@@
 }
-colnames(random_points) <- list("x", "y", "line")
+colnames(random_points) <- list("x", "y", "Stratum")
 return(random_points)
@@
 cat("Number of trees:", length(trees$x), "\nTotal volume:", sum(trees$v), "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees))
-```
-
-# Monte Carlo alone
-
-10 000 Monte Carlo iterations are appropriated.
-
-```{r}
-### Function to automate Monte Carlo method
-
-MonteCarlo <- function(n, B){
-  # B: number of iterations for MC
-
-  p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
-  MC_df <- data.frame(useless = rep(0, n))
-  MC_est <- data.frame(useless = rep(0, 3), row.names = c("est_nb", "est_vol", "est_ratio"))
-
-  for (b in 1:B) { # All in one "for" loop
-    # Sampling over the whole territory
-    df_grid <- sampling_grid(i,c_dim)
-    a1 <- df_grid$x
-    a2 <- df_grid$y
-    a3 <- df_grid$line
-    # n <- nrow(df_grid) # sample size
-    # p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
-    # Variables of interest derived from the sample
-    var <- mapply(circle_all, a1, a2)
-    MC_b <- data.frame(x = a1, y = a2, w = a3, z = t(var)[,1], t = t(var)[,2])
-    MC_df <- cbind(MC_df, MC_b)
-    colnames(MC_df)[(5*(b-1)+2):(5*(b-1)+2+4)] <- c(paste("x", b, sep = ""), paste("y", b, sep = ""), paste("l", b, sep = ""), paste("nb", b, sep = ""), paste("vol", b, sep = ""))
-    est_b <- t(data.frame(x = sum(MC_df[5*(b-1)+2+3] /p), y = sum(MC_df[5*(b-1)+2+4] /p), z = (sum(MC_df[5*(b-1)+2+4] /p))/(sum(MC_df[5*(b-1)+2+3]/p))))
-    MC_est <- cbind(MC_est, est_b)
-    colnames(MC_est)[b+1] <- paste("ech", b, sep = "") 
-  }
-  MC_df$useless <- NULL
-  MC_est$useless <- NULL
-  MC_var <- c(var(as.vector(t(MC_est[1,]))), var(as.vector(t(MC_est[2,]))), var(as.vector(t(MC_est[3,]))))
-
-  # Confidence intervals
-  norm_CI <- data.frame(useless = rep(0, 2))
-  perc_CI <- data.frame(useless = rep(0, 2))
-  rev_perc_CI <- data.frame(useless = rep(0, 2))
-  for (l in 1:3) { # Loop: one estimator each time
-    est_init <- as.vector(t(MC_est[l,]))[1]
-    sorted_est <- sort(as.vector(t(MC_est[l,])))
-    lim_inf <- sorted_est[floor(B*2.5/100)]
-    lim_sup <- sorted_est[B - floor(B*2.5/100)]
-    perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
-    rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_init*2 - lim_sup, est_init*2 - lim_inf)))
-    norm_CI <- cbind(norm_CI, data.frame(c(est_init-qnorm(0.975)*sqrt(MC_var[l]), est_init+qnorm(0.975)*sqrt(MC_var[l]))))
-  }
-  norm_CI$useless <- NULL
-  perc_CI$useless <- NULL
-  rev_perc_CI$useless <- NULL
-  colnames(norm_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-  colnames(perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-  colnames(rev_perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-  all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI)
-
-  return(list(`Local Variables` = MC_df, Estimations = MC_est, Variances = MC_var, `Confidence Intervals` = all_CI))
-  # Local Variables: local variables (number and volume) for each point in each sample
-  # Estimations: 3 Estimations (number, volume, ratio volume / number) for each sample
-  # Variances: Monte Carlo variance for each of the totals / ratio
-  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
-}
 ```
@@
     nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
-    # (H-1) lines at random
+    # (H-1) strata at random
     sample_b <- data.frame(x = numeric(), y = numeric(), z = numeric(), t = numeric(), w = numeric())
@@
     a2 <- df_grid$y
-    a3 <- df_grid$line
+    a3 <- df_grid$Stratum
     var <- mapply(circle_all, a1, a2)
     df_b <- data.frame(x = a1, y = a2, w = a3, z = t(var)[,1], t = t(var)[,2])
-    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("l.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
+    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("h.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
     est_b <- t(data.frame(x = sum(df_b[4] /p), y = sum(df_b[5] /p), z = (sum(df_b[5] /p))/(sum(df_b[4]/p))))
@@
 # Example
-
-## Monte Carlo alone
-
-```{r}
-start.time <- Sys.time()
-
-res1 <- MonteCarlo(n, 10000)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(as.vector(t(res1$Estimations[1,]))), "\n - for the volume of trees:", mean(as.vector(t(res1$Estimations[2,]))), "\n - for the ratio volume / number of trees:", mean(as.vector(t(res1$Estimations[3,]))))
-
-# Example:
-
-```
-
-```{r}
-cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[2], "\n - for the ratio volume / number of trees:", res1$Variances[3])
-
-# Example:
-
-```
-
-```{r}
-cat("95% confidence intervals using the normal method:\n - for the number of trees: [", res1$`Confidence Intervals`$Normal[1,1], ";", res1$`Confidence Intervals`$Normal[2,1], 
-    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Normal[1,2], ";", res1$`Confidence Intervals`$Normal[2,2], 
-    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$Normal[1,3], ";", res1$`Confidence Intervals`$Normal[2,3],
-    "]")
-
-# Example:
-
-```
-
-```{r}
-cat("95% confidence intervals using the percentile method:\n - for the number of trees: [", res1$`Confidence Intervals`$Percentile[1,1], ";", res1$`Confidence Intervals`$Percentile[2,1], 
-    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Percentile[1,2], ";", res1$`Confidence Intervals`$Percentile[2,2], 
-    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$Percentile[1,3], ";", res1$`Confidence Intervals`$Percentile[2,3],
-    "]")
-
-# Example:
-
-```
-
-```{r}
-cat("95% confidence intervals using the reverse percentile method:\n - for the number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,1], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,1],
-    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,2], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,2], 
-    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,3], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,3],
-    "]"
-    )
-
-# Example:
-
-```
 
@@
 diff_percent <- function(x,y)100*(max(x,y)-min(x,y))/min(x,y)
-cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(res1$Variances[1], mean(VAR_nb)), "%", "\n - for the volume of trees: ", diff_percent(res1$Variances[2], mean(VAR_vol)), "%\n - for the ratio volume / number of trees: ", diff_percent(res1$Variances[3], mean(VAR_ratio)), "%", sep = "")
+cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(240516.7, mean(VAR_nb)), "%", "\n - for the volume of trees: ", diff_percent(14084.96, mean(VAR_vol)), "%\n - for the ratio volume / number of trees: ", diff_percent(6.397115e-06, mean(VAR_ratio)), "%", sep = "")
 

### 2024-07-30 test_boot_short_2.Rmd
2nd test for better bootstrap variance

--- 2024-07-30 test_boot_short.Rmd
@@
 ---
-title: "Another stratification"
+title: "Testing bootstrap processes"
 output: pdf_document
-date: "2024-07-29"
+date: "2024-07-30"
 ---
@@
   for (b in 1:B) {
-    nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
+    # nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
     # (H-1) strata at random
     sample_b <- data.frame(x = numeric(), y = numeric(), z = numeric(), t = numeric(), w = numeric())
-    for (number in nb){
-      sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
+    for (number in unique(df_sample[,3])){
+      truc <- sample(df_sample[df_sample[,3] == number,], nrow(df_sample[df_sample[,3] == number,]) -1, replace = TRUE)
+      sample_b <- rbind(sample_b, truc)
+      # sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
     }
@@
   for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (100/99)*sum(df[,4 + (5*(c-1))]/p))
-    vec_est2 <- append(vec_est2, (100/99)*sum(df[,5*c]/p))
-    vec_est3 <- append(vec_est3, ((100/99)*sum(df[,5*c]/p))/((100/99)*sum(df[,4 + (5*(c-1))]/p)))
+    vec_est1 <- append(vec_est1, (900/899)*sum(df[,4 + (5*(c-1))]/p))
+    vec_est2 <- append(vec_est2, (900/899)*sum(df[,5*c]/p))
+    vec_est3 <- append(vec_est3, ((900/899)*sum(df[,5*c]/p))/((900/899)*sum(df[,4 + (5*(c-1))]/p)))
     # (n/(n-1)) is the correction needed since we choose only (n-1) points

### 2024-07-30 test_boot_short_2.Rmd
Able to knit

@@
 
-  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-10))
+  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-100))
   for (b in 1:B) {
@@
     for (number in unique(df_sample[,3])){
-      truc <- sample(df_sample[df_sample[,3] == number,], nrow(df_sample[df_sample[,3] == number,]) -1, replace = TRUE)
-      sample_b <- rbind(sample_b, truc)
+      truc <- sample(rownames(df_sample[df_sample[,3] == number,]), (nrow(df_sample[df_sample[,3] == number,])-1), replace = TRUE)
+      muche <- mapply(function(RRRRR){df_sample[rownames(df_sample) == RRRRR,]}, truc)
+      sample_b <- rbind(sample_b, t(muche))
       # sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])

### 2024-07-30 test_boot_short_2.Rmd
Ready to knit I hope

@@
   for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (900/899)*sum(df[,4 + (5*(c-1))]/p))
-    vec_est2 <- append(vec_est2, (900/899)*sum(df[,5*c]/p))
-    vec_est3 <- append(vec_est3, ((900/899)*sum(df[,5*c]/p))/((900/899)*sum(df[,4 + (5*(c-1))]/p)))
+    vec_est1 <- append(vec_est1, (900/899)*sum(unlist(df[,4 + (5*(c-1))])/p))
+    vec_est2 <- append(vec_est2, (900/899)*sum(unlist(df[,5*c])/p))
+    vec_est3 <- append(vec_est3, ((900/899)*sum(unlist(df[,5*c])/p))/((900/899)*sum(unlist(df[,4 + (5*(c-1))])/p)))
     # (n/(n-1)) is the correction needed since we choose only (n-1) points

### 2024-07-31 First_steps/Trees_grid.Rmd
Re organization

--- 2024-07-04 Trees_grid.Rmd
@@
 ```{r}
+cat("Volume total de la forêt :", sum(trees$v), "m^3")
+```
+
+```{r}
 ci_boot_vol <- function(df_init, df_boot){
@@
 time.taken
+
+# Ex:
+# Un intervalle de confiance à 95% par la méthode des percentiles est : 
+#       [ 3819.372 ; 7249.115 ]
+# Un intervalle de confiance à 95% par la méthode des reverse percentiles est : 
+#       [ 3794.295 ; 7224.039 ]
+# Time difference of 30.0428 mins
 ```

### 2024-07-31 First_steps/Trees_no_grid.Rmd
Re organization

--- 2024-07-08 Trees_no_grid.Rmd
@@
 
-  # 1st step: generating n samples
+  # 1st step: generating B samples
   series_MC <- data.frame(x.1 = runif(n, 0, 1000), y.1 = runif(n, 0, 1000))

### 2024-07-31 Untitled_.Rmd
Re organization

--- 2024-07-30 MC_adagrid.Rmd
@@
 ---
-title: "Monte Carlo and non-uniform bootstrap"
+title: "Testing bootstrap processes"
 output: pdf_document
-date: "2024-07-29"
+date: "2024-07-30"
 ---
@@
     a2 <- df_grid$y
-    a3 <- df_grid$line
+    a3 <- df_grid$Stratum
     # n <- nrow(df_grid) # sample size
@@
     MC_df <- cbind(MC_df, MC_b)
-    colnames(MC_df)[(5*(b-1)+2):(5*(b-1)+2+4)] <- c(paste("x", b, sep = ""), paste("y", b, sep = ""), paste("l", b, sep = ""), paste("nb", b, sep = ""), paste("vol", b, sep = ""))
+    colnames(MC_df)[(5*(b-1)+2):(5*(b-1)+2+4)] <- c(paste("x", b, sep = ""), paste("y", b, sep = ""), paste("h", b, sep = ""), paste("nb", b, sep = ""), paste("vol", b, sep = ""))
     est_b <- t(data.frame(x = sum(MC_df[5*(b-1)+2+3] /p), y = sum(MC_df[5*(b-1)+2+4] /p), z = (sum(MC_df[5*(b-1)+2+4] /p))/(sum(MC_df[5*(b-1)+2+3]/p))))
@@
   for (b in 1:B) {
-    nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
-    # (H-1) lines at random
+    # nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
+    # (H-1) strata at random
     sample_b <- data.frame(x = numeric(), y = numeric(), z = numeric(), t = numeric(), w = numeric())
-    for (number in nb){
-      sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
+    for (number in unique(df_sample[,3])){
+      truc <- sample(df_sample[df_sample[,3] == number,], nrow(df_sample[df_sample[,3] == number,]) -1, replace = TRUE)
+      sample_b <- rbind(sample_b, truc)
+      # sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
     }

### 2024-07-31 test_boot_short_3.Rmd
Another test for better bootstrap variance

--- 2024-07-30 test_boot_short_2.Rmd
@@
 ---
-title: "Testing bootstrap processes"
+title: "Testing some bootstrap process"
 output: pdf_document
-date: "2024-07-30"
+date: "2024-07-31"
 ---
@@
 ```
+
+Idea for the bootstrap: for each line l, containing $n_l$ sampled points, $n_l - 1$ points are sampled with replacement.
+As a result, $100(n_l-1)$ points are sampled from the initial sample.
+In this case, 900 points are sampled.
 
@@
     b <- runif(1, l*c_dim, (l+1)*c_dim)
-    h <- nrow(random_points)%%100 # 100 strata
+    h <- l # 100 lines = 100 strata
     random_points <- rbind(random_points, list(a,b, h))
@@
   for (b in 1:B) {
-    # nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
-    # (H-1) strata at random
     sample_b <- data.frame(x = numeric(), y = numeric(), z = numeric(), t = numeric(), w = numeric())
     for (number in unique(df_sample[,3])){
-      truc <- sample(rownames(df_sample[df_sample[,3] == number,]), (nrow(df_sample[df_sample[,3] == number,])-1), replace = TRUE)
-      muche <- mapply(function(RRRRR){df_sample[rownames(df_sample) == RRRRR,]}, truc)
-      sample_b <- rbind(sample_b, t(muche))
-      # sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
+      names_h <- sample(rownames(df_sample[df_sample[,3] == number,]), (nrow(df_sample[df_sample[,3] == number,])-1), replace = TRUE)
+      sample_h <- mapply(function(some_names){df_sample[rownames(df_sample) == some_names,]}, names_h)
+      sample_b <- rbind(sample_b, t(sample_h))
     }
@@
   return(df_boot)
-  # Return a data frame with B samples of as many variables as we want (in this application, 5)
+  # Return a data frame with B samples of 5 variables
 }

### 2024-07-31 Useful_functions/Inc_area_2.R
A few explanations

@@ -1,8 +1,9 @@
-# More than a test
+# A very similar function to the one in Inc_area.R
+# The only difference is that (x,y) is considered directly instead of coord (which was a vector containing x and y)
 
 inc_area <- function(x, y, x0F, y0F, x1F, y1F, r){
-  # x <- coord[1]
-  # y <- coord[2]
+  # x <- coord[1] # Useless step: x is an argument
+  # y <- coord[2] # Useless step: y is an argument
   
   ##### Case 1: the point is located s.t. the inclusion plot is completely inside the territory
   if ((x>=x0F+r) & (x<=x1F-r) & (y>=y0F+r) & (y<=y1F-r)){

### 2024-07-31 LPM_test.Rmd
First test with LPM

---
title: "LPM_test"
output: pdf_document
date: "2024-07-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
N <- 10000 # Number of small squares in the grid
```

```{r}
vec <- runif(N, min = 0, max = 1) # initial vector pi
```

```{r}
# LPM process
new_vec <- rep(5, N)
while(vec != truc){
  i <- sample(1:10000, 1)
  pi_i <- vec[i]
  pi_j <- vec[(i+1)%%10000]
  pi_w <- min(1,pi_i+pi_j)
  pi_l <- pi_i+pi_j - pi_w
  new_pi_i <- sample(c(pi_w, pi_l), 1, prob = c((pi_w - pi_j)/(pi_w - pi_l), (pi_w - pi_i)/(pi_w - pi_l)))
  new_pi_j <- pi_w + pi_l - new_pi_i
  new_vec[i] <- as.numeric((new_pi_i == 1) |  (new_pi_i == 0))*new_pi_i + as.numeric(xor((new_pi_i != 1),  (new_pi_i != 0)))*new_vec[i]

}
```

### 2024-08-01 test_boot_short_2.Rmd
Corrections

--- 2024-07-30 test_boot_short_2.Rmd
@@
 ```
+
+Idea for the bootstrap: for each stratum $h$, containing $n_h$ sampled points, $n_h - 1$ points are sampled with replacement.
+As a result, $100(n_h-1)$ points are sampled from the initial sample.
+In this case, 900 points are sampled.
 
@@
   for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (900/899)*sum(df[,4 + (5*(c-1))]/p))
-    vec_est2 <- append(vec_est2, (900/899)*sum(df[,5*c]/p))
-    vec_est3 <- append(vec_est3, ((900/899)*sum(df[,5*c]/p))/((900/899)*sum(df[,4 + (5*(c-1))]/p)))
-    # (n/(n-1)) is the correction needed since we choose only (n-1) points
+    vec_est1 <- append(vec_est1, (900/9)*sum(unlist(df[,4 + (5*(c-1))])/p))
+    vec_est2 <- append(vec_est2, (900/9)*sum(unlist(df[,5*c])/p))
+    vec_est3 <- append(vec_est3, ((900/9)*sum(unlist(df[,5*c])/p))/((900/9)*sum(unlist(df[,4 + (5*(c-1))])/p)))
+    # (n_h/(n_h-1))*(n/n_h) is the correction needed since we choose only (n_h-1) points per strata
   }
@@
 ```{r}
+start.time <- Sys.time()
+
+res2 <- MC_boot(n, B1 = 10, B2 = 4)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```
+
+```{r}
 # We want all the variances obtained for each parameter of interest, 

### 2024-08-01 test_boot_short_3.Rmd
Corrections

@@
   for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (900/899)*sum(unlist(df[,4 + (5*(c-1))])/p))
-    vec_est2 <- append(vec_est2, (900/899)*sum(unlist(df[,5*c])/p))
-    vec_est3 <- append(vec_est3, ((900/899)*sum(unlist(df[,5*c])/p))/((900/899)*sum(unlist(df[,4 + (5*(c-1))])/p)))
-    # (n/(n-1)) is the correction needed since we choose only (n-1) points
+    vec_est1 <- append(vec_est1, (900/9)*sum(unlist(df[,4 + (5*(c-1))])/p))
+    vec_est2 <- append(vec_est2, (900/9)*sum(unlist(df[,5*c])/p))
+    vec_est3 <- append(vec_est3, ((900/9)*sum(unlist(df[,5*c])/p))/((900/9)*sum(unlist(df[,4 + (5*(c-1))])/p)))
+    # (n_h/(n_h-1))*(n/n_h) is the correction needed since we choose only (n_h-1) points per strata
   }

### 2024-08-01 CopyOfMC_all.Rmd
MC_all without CI for MC and with coverage rate

--- 2024-07-26 MC_all.Rmd
@@
 By comparing the two results, we may ensure the validity of the bootstrap strategy to find the estimation of the variances.
-In this document, one single circle with a radius of 5 is used to compute local variables.
+
+In this document, uniform sampling is used to create a sample and one single circle with a radius of 5 is used to compute local variables.
 
@@
 ```{r}
-### Function to automate Monte Carlo method, to produce a variance
+### Function to automate Monte Carlo method
 
@@
 
-  # Confidence intervals
-  norm_CI <- data.frame(useless = rep(0, 2))
-  perc_CI <- data.frame(useless = rep(0, 2))
-  rev_perc_CI <- data.frame(useless = rep(0, 2))
-  for (l in 1:3) { # Loop: one estimator each time
-    est_init <- as.vector(t(MC_est[l,]))[1]
-    sorted_est <- sort(as.vector(t(MC_est[l,])))
-    lim_inf <- sorted_est[floor(B*2.5/100)]
-    lim_sup <- sorted_est[B - floor(B*2.5/100)]
-    perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
-    rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_init*2 - lim_sup, est_init*2 - lim_inf)))
-    norm_CI <- cbind(norm_CI, data.frame(c(est_init-qnorm(0.975)*sqrt(MC_var[l]), est_init+qnorm(0.975)*sqrt(MC_var[l]))))
-  }
-  norm_CI$useless <- NULL
-  perc_CI$useless <- NULL
-  rev_perc_CI$useless <- NULL
-  colnames(norm_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-  colnames(perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-  colnames(rev_perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-  all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI)
-
-  return(list(`Local Variables` = MC_df, Estimations = MC_est, Variances = MC_var, `Confidence Intervals` = all_CI))
+  return(list(`Local Variables` = MC_df, Estimations = MC_est, Variances = MC_var))
   # Local Variables: local variables (number and volume) for each point in each sample
@@
   # Variances: Monte Carlo variance for each of the totals / ratio
-  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
 }
@@
 
-```{r}
-cat("95% confidence intervals using the normal method:\n - for the number of trees: [", res1$`Confidence Intervals`$Normal[1,1], ";", res1$`Confidence Intervals`$Normal[2,1], 
-    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Normal[1,2], ";", res1$`Confidence Intervals`$Normal[2,2], 
-    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$Normal[1,3], ";", res1$`Confidence Intervals`$Normal[2,3],
-    "]")
-
-# Example:
-## 95% confidence intervals using the normal method:
-##  - for the number of trees: [ 23345.86 ; 29671.83 ]
-##  - for the volume of trees: [ 4320.113 ; 5559.31 ]
-##  - for the ratio volume / number of trees: [ 0.1797767 ; 0.1929072 ]
-```
-
-```{r}
-cat("95% confidence intervals using the percentile method:\n - for the number of trees: [", res1$`Confidence Intervals`$Percentile[1,1], ";", res1$`Confidence Intervals`$Percentile[2,1], 
-    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Percentile[1,2], ";", res1$`Confidence Intervals`$Percentile[2,2], 
-    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$Percentile[1,3], ";", res1$`Confidence Intervals`$Percentile[2,3],
-    "]")
-
-# Example:
-## 95% confidence intervals using the percentile method:
-##  - for the number of trees: [ 26139.61 ; 32467.61 ]
-##  - for the volume of trees: [ 4798.827 ; 6037.256 ]
-##  - for the ratio volume / number of trees: [ 0.1783755 ; 0.1915082 ]
-```
-
-```{r}
-cat("95% confidence intervals using the reverse percentile method:\n - for the number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,1], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,1],
-    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,2], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,2], 
-    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,3], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,3],
-    "]"
-    )
-
-# Example:
-## 95% confidence intervals using the reverse percentile method:
-##  - for the number of trees: [ 20550.09 ; 26878.09 ]
-##  - for the volume of trees: [ 3842.166 ; 5080.595 ]
-##  - for the ratio volume / number of trees: [ 0.1811758 ; 0.1943085 ]
-```
-
 ## Monte Carlo and bootstrap
@@
 
+```{r}
+## We want all the CI based on Normal distribution obtained for each parameter of interest, 
+# to find the coverage rate
+CI_nb <- data.frame(useless = c(0,0))
+CI_vol <- data.frame(useless = c(0,0))
+CI_ratio <- data.frame(useless = c(0,0))
+for (elt in res2$`Confidence Intervals`) {
+  CI_nb <- cbind(CI_nb, elt$Normal$lim_nb)
+  CI_vol <- cbind(CI_vol, elt$Normal$lim_vol)
+  CI_ratio <- cbind(CI_ratio, elt$Normal$lim_ratio)
+}
+CI_nb$useless <- NULL
+CI_vol$useless <- NULL
+CI_ratio$useless <- NULL
+
+CI_nb <- as.data.frame(t(CI_nb))
+rownames(CI_nb) <- 1:(nrow(CI_nb))
+colnames(CI_nb) <- c("x", "y")
+
+CI_vol <- as.data.frame(t(CI_vol))
+rownames(CI_vol) <- 1:(nrow(CI_vol))
+colnames(CI_vol) <- c("x", "y")
+
+CI_ratio <- as.data.frame(t(CI_ratio))
+rownames(CI_ratio) <- 1:(nrow(CI_ratio))
+colnames(CI_ratio) <- c("x", "y")
+```
+
+```{r}
+# Check the coverage rate
+TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb$x, CI_nb$y) )
+TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol$x, CI_vol$y) )
+TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio$x, CI_ratio$y) )
+cat("Concerning the normal approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
+```
+
+```{r}
+## We want all the Percentile CI obtained for each parameter of interest, 
+# to find the coverage rate
+CI_perc_nb <- data.frame(useless = c(0,0))
+CI_perc_vol <- data.frame(useless = c(0,0))
+CI_perc_ratio <- data.frame(useless = c(0,0))
+for (elt in res2$`Confidence Intervals`) {
+  CI_perc_nb <- cbind(CI_perc_nb, elt$Percentile$lim_nb)
+  CI_perc_vol <- cbind(CI_perc_vol, elt$Percentile$lim_vol)
+  CI_perc_ratio <- cbind(CI_perc_ratio, elt$Percentile$lim_ratio)
+}
+CI_perc_nb$useless <- NULL
+CI_perc_vol$useless <- NULL
+CI_perc_ratio$useless <- NULL
+
+CI_perc_nb <- as.data.frame(t(CI_perc_nb))
+rownames(CI_perc_nb) <- 1:(nrow(CI_perc_nb))
+colnames(CI_perc_nb) <- c("x", "y")
+
+CI_perc_vol <- as.data.frame(t(CI_perc_vol))
+rownames(CI_perc_vol) <- 1:(nrow(CI_perc_vol))
+colnames(CI_perc_vol) <- c("x", "y")
+
+CI_perc_ratio <- as.data.frame(t(CI_perc_ratio))
+rownames(CI_perc_ratio) <- 1:(nrow(CI_perc_ratio))
+colnames(CI_perc_ratio) <- c("x", "y")
+```
+
+```{r}
+# Check the coverage rate
+TC_nb <- (1/nrow(CI_perc_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_perc_nb$x, CI_perc_nb$y) )
+TC_vol <- (1/nrow(CI_perc_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_perc_vol$x, CI_perc_vol$y) )
+TC_ratio <- (1/nrow(CI_perc_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_perc_ratio$x, CI_perc_ratio$y) )
+cat("Concerning the percentile approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
+```
+
+```{r}
+## We want all the Reverse Percentile CI obtained for each parameter of interest, 
+# to find the coverage rate
+CI_nb <- data.frame(useless = c(0,0))
+CI_vol <- data.frame(useless = c(0,0))
+CI_ratio <- data.frame(useless = c(0,0))
+for (elt in res2$`Confidence Intervals`) {
+  CI_nb <- cbind(CI_nb, elt$`Reverse percentile`$lim_nb)
+  CI_vol <- cbind(CI_vol, elt$`Reverse percentile`$lim_vol)
+  CI_ratio <- cbind(CI_ratio, elt$`Reverse percentile`$lim_ratio)
+}
+CI_nb$useless <- NULL
+CI_vol$useless <- NULL
+CI_ratio$useless <- NULL
+
+CI_nb <- as.data.frame(t(CI_nb))
+rownames(CI_nb) <- 1:(nrow(CI_nb))
+colnames(CI_nb) <- c("x", "y")
+
+CI_vol <- as.data.frame(t(CI_vol))
+rownames(CI_vol) <- 1:(nrow(CI_vol))
+colnames(CI_vol) <- c("x", "y")
+
+CI_ratio <- as.data.frame(t(CI_ratio))
+rownames(CI_ratio) <- 1:(nrow(CI_ratio))
+colnames(CI_ratio) <- c("x", "y")
+```
+
+```{r}
+# Check the coverage rate
+TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb$x, CI_nb$y) )
+TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol$x, CI_vol$y) )
+TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio$x, CI_ratio$y) )
+cat("Concerning the reverse percentile approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
+```
+
 ## Comparison of the variances

### 2024-08-01 test_boot_short_3.Rmd
Test stratified bootstrap

--- 2024-07-31 test_boot_short_3.Rmd
@@
   for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (900/899)*sum(unlist(df[,4 + (5*(c-1))])/p))
-    vec_est2 <- append(vec_est2, (900/899)*sum(unlist(df[,5*c])/p))
-    vec_est3 <- append(vec_est3, ((900/899)*sum(unlist(df[,5*c])/p))/((900/899)*sum(unlist(df[,4 + (5*(c-1))])/p)))
-    # (n/(n-1)) is the correction needed since we choose only (n-1) points
+    vec_est1 <- append(vec_est1, (1000/9)*sum(unlist(df[,4 + (5*(c-1))])/p))
+    vec_est2 <- append(vec_est2, (1000/9)*sum(unlist(df[,5*c])/p))
+    vec_est3 <- append(vec_est3, ((1000/9)*sum(unlist(df[,5*c])/p))/((100/9)*sum(unlist(df[,4 + (5*(c-1))])/p)))
+    # (n_h/(n_h-1))*(n/n_h) is the correction needed since we choose only (n_h-1) points per strata
   }

### 2024-08-01 Boot_grid_ter.Rmd
A third way to use the grid

--- 2024-07-26 MC_grid.Rmd
@@
 ---
-title: "Monte Carlo and bootstrap for all parameteres with a grid"
+title: "Monte Carlo and bootstrap for all parameters with a grid"
 output: pdf_document
-date: "2024-07-26"
+date: "2024-08-01"
 ---
@@
 
-The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees and the ratio volume of trees / number of trees), variances of these estimators and confidence intervals.
-The same elements are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations.
+Motivation: specific sampling from a grid, random small square inside a first bunch of 10 small squares, for a beginning. Then, systematic sampling without any shifts when changing line.
+
+The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees and the ratio volume of trees / number of trees) and variances of these estimators.
+The same elements, along with confidence intervals, are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations.
 By comparing the two results, we may verify the invalidity of the bootstrap strategy to find the estimation of the variances.
-\\
+We reuse the results from another file for the function that exploits Monte Carlo alone.
+
 In this document, one single circle with a radius of 5 is used to compute local variables. Besides, and more importantly, a grid is used for sampling.
@@
 for (l in 0:((1000/c_dim)-1)) {
-  if (l==0){
   x_init <- i*c_dim
-  }else if ((3*l+i)*c_dim < (10)*c_dim){
-    x_init <- (3*l+i)*c_dim
-  }else{
-    x_init <- (((3*l+i)*c_dim)%%(c_dim*10))
-  }
   k <- 0
@@
 ```{r}
+# Small example
+ex_grid <- sampling_grid(i, c_dim)
+```
+
+```{r}
+plot(ex_grid, xlab="", ylab="", main = "Random points within the grid", las = 1)
+```
+
+```{r}
+plot(ex_grid, xlab="", ylab="", main = "Only one point", xlim = c(0, 100), ylim = c(0, 10), las = 1)
+```
+
+```{r}
 # True values
 cat("Number of trees:", length(trees$x), "\nTotal volume:", sum(trees$v), "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees))
-```
-
-# Monte Carlo alone
-
-10 000 Monte Carlo iterations are appropriated.
-
-```{r}
-### Function to automate Monte Carlo method
-
-MonteCarlo <- function(n, B){
-  # B: number of iterations for MC
-
-  p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
-  MC_df <- data.frame(useless = rep(0, n))
-  MC_est <- data.frame(useless = rep(0, 3), row.names = c("est_nb", "est_vol", "est_ratio"))
-
-  for (b in 1:B) { # All in one "for" loop
-    # Sampling over the whole territory
-    df_grid <- sampling_grid(i,c_dim)
-    a1 <- df_grid$x
-    a2 <- df_grid$y
-    # n <- nrow(df_grid) # sample size
-    # p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
-    # Variables of interest derived from the sample
-    var <- mapply(circle_all, a1, a2)
-    MC_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
-    MC_df <- cbind(MC_df, MC_b)
-    colnames(MC_df)[(4*(b-1)+2):(4*(b-1)+2+3)] <- c(paste("x", b, sep = ""), paste("y", b, sep = ""), paste("nb", b, sep = ""), paste("vol", b, sep = ""))
-    est_b <- t(data.frame(x = sum(MC_df[4*(b-1)+2+2] /p), y = sum(MC_df[4*(b-1)+2+3] /p), z = (sum(MC_df[4*(b-1)+2+3] /p))/(sum(MC_df[4*(b-1)+2+2]/p))))
-    MC_est <- cbind(MC_est, est_b)
-    colnames(MC_est)[b+1] <- paste("ech", b, sep = "") 
-  }
-  MC_df$useless <- NULL
-  MC_est$useless <- NULL
-  MC_var <- c(var(as.vector(t(MC_est[1,]))), var(as.vector(t(MC_est[2,]))), var(as.vector(t(MC_est[3,]))))
-
-  # Confidence intervals
-  norm_CI <- data.frame(useless = rep(0, 2))
-  perc_CI <- data.frame(useless = rep(0, 2))
-  rev_perc_CI <- data.frame(useless = rep(0, 2))
-  for (l in 1:3) { # Loop: one estimator each time
-    est_init <- as.vector(t(MC_est[l,]))[1]
-    sorted_est <- sort(as.vector(t(MC_est[l,])))
-    lim_inf <- sorted_est[floor(B*2.5/100)]
-    lim_sup <- sorted_est[B - floor(B*2.5/100)]
-    perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
-    rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_init*2 - lim_sup, est_init*2 - lim_inf)))
-    norm_CI <- cbind(norm_CI, data.frame(c(est_init-qnorm(0.975)*sqrt(MC_var[l]), est_init+qnorm(0.975)*sqrt(MC_var[l]))))
-  }
-  norm_CI$useless <- NULL
-  perc_CI$useless <- NULL
-  rev_perc_CI$useless <- NULL
-  colnames(norm_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-  colnames(perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-  colnames(rev_perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-  all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI)
-
-  return(list(`Local Variables` = MC_df, Estimations = MC_est, Variances = MC_var, `Confidence Intervals` = all_CI))
-  # Local Variables: local variables (number and volume) for each point in each sample
-  # Estimations: 3 Estimations (number, volume, ratio volume / number) for each sample
-  # Variances: Monte Carlo variance for each of the totals / ratio
-  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
-}
 ```
@@
     # Uniform sampling over the whole territory
-    df_grid <- sampling_grid(i,c_dim)
+    df_grid <- sampling_grid(i, c_dim)
     a1 <- df_grid$x
@@
 
-## Monte Carlo alone
-
-```{r}
-start.time <- Sys.time()
-
-res1 <- MonteCarlo(n, 10000)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(as.vector(t(res1$Estimations[1,]))), "\n - for the volume of trees:", mean(as.vector(t(res1$Estimations[2,]))), "\n - for the ratio volume / number of trees:", mean(as.vector(t(res1$Estimations[3,]))))
-
-# Example:
-
-```
-
-```{r}
-cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[2], "\n - for the ratio volume / number of trees:", res1$Variances[3])
-
-# Example:
-
-```
-
-```{r}
-cat("95% confidence intervals using the normal method:\n - for the number of trees: [", res1$`Confidence Intervals`$Normal[1,1], ";", res1$`Confidence Intervals`$Normal[2,1], 
-    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Normal[1,2], ";", res1$`Confidence Intervals`$Normal[2,2], 
-    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$Normal[1,3], ";", res1$`Confidence Intervals`$Normal[2,3],
-    "]")
-
-# Example:
-
-```
-
-```{r}
-cat("95% confidence intervals using the percentile method:\n - for the number of trees: [", res1$`Confidence Intervals`$Percentile[1,1], ";", res1$`Confidence Intervals`$Percentile[2,1], 
-    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$Percentile[1,2], ";", res1$`Confidence Intervals`$Percentile[2,2], 
-    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$Percentile[1,3], ";", res1$`Confidence Intervals`$Percentile[2,3],
-    "]")
-
-# Example:
-
-```
-
-```{r}
-cat("95% confidence intervals using the reverse percentile method:\n - for the number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,1], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,1],
-    "]\n - for the volume of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,2], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,2], 
-    "]\n - for the ratio volume / number of trees: [", res1$`Confidence Intervals`$`Reverse percentile`[1,3], ";", res1$`Confidence Intervals`$`Reverse percentile`[2,3],
-    "]"
-    )
-
-# Example:
-
-```
-
 ## Monte Carlo and bootstrap
@@
 cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(EST_nb), "\n - for the volume of trees:", mean(EST_vol), "\n - for the ratio volume / number of trees:", mean(EST_ratio))
-
-# Example:
-
 ```
@@
 cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", mean(VAR_nb), "\n - for the volume of trees:", mean(VAR_vol), "\n - for the ratio volume / number of trees:", mean(VAR_ratio))
-
-# Example:
-
 ```
@@
 diff_percent <- function(x,y)100*(max(x,y)-min(x,y))/min(x,y)
-cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(res1$Variances[1], mean(VAR_nb)), "%", "\n - for the volume of trees: ", diff_percent(res1$Variances[2], mean(VAR_vol)), "%\n - for the ratio volume / number of trees: ", diff_percent(res1$Variances[3], mean(VAR_ratio)), "%", sep = "")
-
-# Example:
-
+cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(240516.7, mean(VAR_nb)), "%", "\n - for the volume of trees: ", diff_percent(14084.96, mean(VAR_vol)), "%\n - for the ratio volume / number of trees: ", diff_percent(6.397115e-06, mean(VAR_ratio)), "%", sep = "")
 ```

### 2024-08-02 MC_all.Rmd
Function for coverage rate

@@
 
-The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees and the ratio volume of trees / number of trees), variances of these estimators and confidence intervals.
-The same elements are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations.
+The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees and the ratio volume of trees / number of trees) and variances of these estimators.
+The same elements, along with confidence intervals, are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations.
 By comparing the two results, we may ensure the validity of the bootstrap strategy to find the estimation of the variances.
-In this document, one single circle with a radius of 5 is used to compute local variables.
+We may also compare the coverage rates of each type of confidence interval.
+
+In this document, *uniform sampling* is used to create a sample and *one single circle* with a radius of 5 is used to compute local variables.
 
@@
 # True values
-cat("Number of trees:", length(trees$x), "\nTotal volume:", sum(trees$v), "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees))
+cat("Number of trees:", length(trees$x), "\nTotal volume:", sum(trees$v), 
+    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees))
 ```
@@
 
-  # Confidence intervals
-  norm_CI <- data.frame(useless = rep(0, 2))
-  perc_CI <- data.frame(useless = rep(0, 2))
-  rev_perc_CI <- data.frame(useless = rep(0, 2))
-  for (l in 1:3) { # Loop: one estimator each time
-    est_init <- as.vector(t(MC_est[l,]))[1]
-    sorted_est <- sort(as.vector(t(MC_est[l,])))
-    lim_inf <- sorted_est[floor(B*2.5/100)]
-    lim_sup <- sorted_est[B - floor(B*2.5/100)]
-    perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
-    rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_init*2 - lim_sup, est_init*2 - lim_inf)))
-    norm_CI <- cbind(norm_CI, data.frame(c(est_init-qnorm(0.975)*sqrt(MC_var[l]), est_init+qnorm(0.975)*sqrt(MC_var[l]))))
-  }
-  norm_CI$useless <- NULL
-  perc_CI$useless <- NULL
-  rev_perc_CI$useless <- NULL
-  colnames(norm_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-  colnames(perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-  colnames(rev_perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-  all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI)
-
-  return(list(`Local Variables` = MC_df, Estimations = MC_est, Variances = MC_var, `Confidence Intervals` = all_CI))
+  return(list(`Local Variables` = MC_df, Estimations = MC_est, Variances = MC_var))
   # Local Variables: local variables (number and volume) for each point in each sample
-  # Estimations: 3 Estimations (number, volume, ratio volume / number) for each sample
+  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
   # Variances: Monte Carlo variance for each of the totals / ratio
-  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
 }
@@
 ```{r}
+## Making of bootstrap samples based on an initial sample
 f_boot <- function(df_sample, B){
-  # df_sample: original sample; 
+  # df_sample: initial sample with 4 variables and of size n; 
   # B: number of bootstrap samples made thanks to df_sample
@@
   return(df_boot)
-  # Return a data frame with B samples of as many variables as we want (in this application, 4) and of size (n-1)
+  # Return a data frame with B samples of 4 variables and of size (n-1)
 }
@@
 ```{r}
-# Making of estimations for each sample made by the bootstrap method
+## Making of estimations for each sample made by the bootstrap method
 est_boot <- function(df, p){
-  # df: dataframe with 4*B columns and n rows
+  # df: data frame with 4*B columns and (n-1) rows
+  # p: inclusion density function (constant in the uniform case)
 
@@
 
+```{r}
+coverage_rate <- function(nb){
+  CI_nb <- data.frame(useless = c(0,0))
+  CI_vol <- data.frame(useless = c(0,0))
+  CI_ratio <- data.frame(useless = c(0,0))
+  for (elt in res2$`Confidence Intervals`) {
+    CI_nb <- cbind(CI_nb, c(unlist(res2$`Confidence Intervals`$CI1[1])[1], unlist(res2$`Confidence Intervals`$CI1[1])[2]))
+    CI_vol <- cbind(CI_nb, c(unlist(res2$`Confidence Intervals`$CI1[1])[3], unlist(res2$`Confidence Intervals`$CI1[1])[4]))
+    CI_ratio <- cbind(CI_nb, c(unlist(res2$`Confidence Intervals`$CI1[1])[5], unlist(res2$`Confidence Intervals`$CI1[1])[6]))
+  }
+  CI_nb$useless <- NULL
+  rownames(CI_nb) <- 1:(nrow(CI_nb))
+  colnames(CI_nb) <- c("x", "y")
+  CI_vol$useless <- NULL
+  CI_ratio$useless <- NULL
+
+  CI_nb <- as.data.frame(t(CI_nb))
+  CI_vol <- as.data.frame(t(CI_vol))
+  CI_ratio <- as.data.frame(t(CI_ratio))
+
+  # Coverage rate
+  TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb[1], CI_nb[2]) )
+  TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol[1], CI_vol[2]) )
+  TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio[1], CI_ratio[2]) )
+
+  # Lower tail
+  low_tail_nb <- (1/nrow(CI_nb))*sum( mapply(function(a){as.numeric(29272 < a)}, CI_nb[1]) )
+  low_tail_vol <- (1/nrow(CI_vol))*sum( mapply(function(a){as.numeric(5412.722 < a)}, CI_vol[1]) )
+  low_tail_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a){as.numeric(0.1849112 < a)}, CI_ratio[1]) )
+
+  # Upper tail
+  up_tail_nb <- (1/nrow(CI_nb))*sum( mapply(function(b){as.numeric(29272 > b)}, CI_nb[2]) )
+  up_tail_vol <- (1/nrow(CI_vol))*sum( mapply(function(b){as.numeric(5412.722 > b)}, CI_vol[2]) )
+  up_tail_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(b){as.numeric(0.1849112 > b)}, CI_ratio[2]) )
+
+  # Mean length of CIs
+  length_nb <- mean( mapply(function(a,b){b-a}, CI_nb[1], CI_nb[2]) )
+  length_vol <- mean( mapply(function(a,b){b-a}, CI_vol[1], CI_vol[2]) )
+  length_ratio <- mean( mapply(function(a,b){b-a}, CI_ratio[1], CI_ratio[2]) )
+
+  df_TC <- data.frame(TC = c(TC_nb, TC_vol, TC_ratio), Upper = c(low_tail_nb, low_tail_vol, low_tail_ratio), Lower = c(up_tail_nb, up_tail_vol, up_tail_ratio), Mean_length = c(length_nb, length_vol, length_ratio))
+
+  return(df_TC)
+}
+```
+
+```{r}
+TC_normal <- coverage_rate(1)
+cat("Concerning the normal approach, the coverage rates are the following: \n - for the number of trees: ", 
+    TC_normal[1,1], "\n - for the volume of trees: ", TC_normal[2,1], "\n - for the ratio volume / number of trees: ", TC_normal[3,1],
+    " \n \nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_normal[1,2], "\n - for the volume of trees: ", TC_normal[2,2], "\n - for the ratio volume / number of trees: ", TC_normal[3,2],
+    " \n \nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_normal[1,3], "\n - for the volume of trees: ", TC_normal[2,3], "\n - for the ratio volume / number of trees: ", TC_normal[3,3],
+    " \n \nThe mean length of coverage rates are the following: \n - for the number of trees: ",
+    TC_normal[1,4], "\n - for the volume of trees: ", TC_normal[2,4], "\n - for the ratio volume / number of trees: ", TC_normal[3,4])
+```
+
+```{r}
+## We want all the CI based on Normal distribution obtained for each parameter of interest, 
+# to find the coverage rate
+CI_nb <- data.frame(useless = c(0,0))
+CI_vol <- data.frame(useless = c(0,0))
+CI_ratio <- data.frame(useless = c(0,0))
+for (elt in res2$`Confidence Intervals`) {
+  CI_nb <- cbind(CI_nb, elt$Normal$lim_nb)
+  CI_vol <- cbind(CI_vol, elt$Normal$lim_vol)
+  CI_ratio <- cbind(CI_ratio, elt$Normal$lim_ratio)
+}
+CI_nb$useless <- NULL
+CI_vol$useless <- NULL
+CI_ratio$useless <- NULL
+
+CI_nb <- as.data.frame(t(CI_nb))
+rownames(CI_nb) <- 1:(nrow(CI_nb))
+colnames(CI_nb) <- c("x", "y")
+
+CI_vol <- as.data.frame(t(CI_vol))
+rownames(CI_vol) <- 1:(nrow(CI_vol))
+colnames(CI_vol) <- c("x", "y")
+
+CI_ratio <- as.data.frame(t(CI_ratio))
+rownames(CI_ratio) <- 1:(nrow(CI_ratio))
+colnames(CI_ratio) <- c("x", "y")
+```
+
+```{r}
+# Check the coverage rate
+TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb$x, CI_nb$y) )
+TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol$x, CI_vol$y) )
+TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio$x, CI_ratio$y) )
+cat("Concerning the normal approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
+```
+
+```{r}
+## We want all the Percentile CI obtained for each parameter of interest, 
+# to find the coverage rate
+CI_perc_nb <- data.frame(useless = c(0,0))
+CI_perc_vol <- data.frame(useless = c(0,0))
+CI_perc_ratio <- data.frame(useless = c(0,0))
+for (elt in res2$`Confidence Intervals`) {
+  CI_perc_nb <- cbind(CI_perc_nb, elt$Percentile$lim_nb)
+  CI_perc_vol <- cbind(CI_perc_vol, elt$Percentile$lim_vol)
+  CI_perc_ratio <- cbind(CI_perc_ratio, elt$Percentile$lim_ratio)
+}
+CI_perc_nb$useless <- NULL
+CI_perc_vol$useless <- NULL
+CI_perc_ratio$useless <- NULL
+
+CI_perc_nb <- as.data.frame(t(CI_perc_nb))
+rownames(CI_perc_nb) <- 1:(nrow(CI_perc_nb))
+colnames(CI_perc_nb) <- c("x", "y")
+
+CI_perc_vol <- as.data.frame(t(CI_perc_vol))
+rownames(CI_perc_vol) <- 1:(nrow(CI_perc_vol))
+colnames(CI_perc_vol) <- c("x", "y")
+
+CI_perc_ratio <- as.data.frame(t(CI_perc_ratio))
+rownames(CI_perc_ratio) <- 1:(nrow(CI_perc_ratio))
+colnames(CI_perc_ratio) <- c("x", "y")
+```
+
+```{r}
+# Check the coverage rate
+TC_nb <- (1/nrow(CI_perc_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_perc_nb$x, CI_perc_nb$y) )
+TC_vol <- (1/nrow(CI_perc_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_perc_vol$x, CI_perc_vol$y) )
+TC_ratio <- (1/nrow(CI_perc_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_perc_ratio$x, CI_perc_ratio$y) )
+cat("Concerning the percentile approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
+```
+
+```{r}
+## We want all the Reverse Percentile CI obtained for each parameter of interest, 
+# to find the coverage rate
+CI_nb <- data.frame(useless = c(0,0))
+CI_vol <- data.frame(useless = c(0,0))
+CI_ratio <- data.frame(useless = c(0,0))
+for (elt in res2$`Confidence Intervals`) {
+  CI_nb <- cbind(CI_nb, elt$`Reverse percentile`$lim_nb)
+  CI_vol <- cbind(CI_vol, elt$`Reverse percentile`$lim_vol)
+  CI_ratio <- cbind(CI_ratio, elt$`Reverse percentile`$lim_ratio)
+}
+CI_nb$useless <- NULL
+CI_vol$useless <- NULL
+CI_ratio$useless <- NULL
+
+CI_nb <- as.data.frame(t(CI_nb))
+rownames(CI_nb) <- 1:(nrow(CI_nb))
+colnames(CI_nb) <- c("x", "y")
+
+CI_vol <- as.data.frame(t(CI_vol))
+rownames(CI_vol) <- 1:(nrow(CI_vol))
+colnames(CI_vol) <- c("x", "y")
+
+CI_ratio <- as.data.frame(t(CI_ratio))
+rownames(CI_ratio) <- 1:(nrow(CI_ratio))
+colnames(CI_ratio) <- c("x", "y")
+```
+
+```{r}
+# Check the coverage rate
+TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb$x, CI_nb$y) )
+TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol$x, CI_vol$y) )
+TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio$x, CI_ratio$y) )
+cat("Concerning the reverse percentile approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
+```
+
 ## Comparison of the variances

### 2024-08-02 MC_all_old.Rmd
Function for coverage rate

--- 2024-07-26 MC_all.Rmd
@@
 By comparing the two results, we may ensure the validity of the bootstrap strategy to find the estimation of the variances.
+
 In this document, one single circle with a radius of 5 is used to compute local variables.

### 2024-08-02 Draft/Draft.Rmd
Clean MC_all for CI

@@
 }
+
+## Non-optimal version of coverage rates in MC_all.Rmd ----------
+
+```{r}
+## We want all the CI based on Normal distribution obtained for each parameter of interest, 
+# to find the coverage rate
+CI_nb <- data.frame(useless = c(0,0))
+CI_vol <- data.frame(useless = c(0,0))
+CI_ratio <- data.frame(useless = c(0,0))
+for (elt in res2$`Confidence Intervals`) {
+  CI_nb <- cbind(CI_nb, elt$Normal$lim_nb)
+  CI_vol <- cbind(CI_vol, elt$Normal$lim_vol)
+  CI_ratio <- cbind(CI_ratio, elt$Normal$lim_ratio)
+}
+CI_nb$useless <- NULL
+CI_vol$useless <- NULL
+CI_ratio$useless <- NULL
+
+CI_nb <- as.data.frame(t(CI_nb))
+rownames(CI_nb) <- 1:(nrow(CI_nb))
+colnames(CI_nb) <- c("x", "y")
+
+CI_vol <- as.data.frame(t(CI_vol))
+rownames(CI_vol) <- 1:(nrow(CI_vol))
+colnames(CI_vol) <- c("x", "y")
+
+CI_ratio <- as.data.frame(t(CI_ratio))
+rownames(CI_ratio) <- 1:(nrow(CI_ratio))
+colnames(CI_ratio) <- c("x", "y")
+```
+
+```{r}
+# Check the coverage rate
+TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb$x, CI_nb$y) )
+TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol$x, CI_vol$y) )
+TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio$x, CI_ratio$y) )
+cat("Concerning the normal approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
+```
+
+```{r}
+## We want all the Percentile CI obtained for each parameter of interest, 
+# to find the coverage rate
+CI_perc_nb <- data.frame(useless = c(0,0))
+CI_perc_vol <- data.frame(useless = c(0,0))
+CI_perc_ratio <- data.frame(useless = c(0,0))
+for (elt in res2$`Confidence Intervals`) {
+  CI_perc_nb <- cbind(CI_perc_nb, elt$Percentile$lim_nb)
+  CI_perc_vol <- cbind(CI_perc_vol, elt$Percentile$lim_vol)
+  CI_perc_ratio <- cbind(CI_perc_ratio, elt$Percentile$lim_ratio)
+}
+CI_perc_nb$useless <- NULL
+CI_perc_vol$useless <- NULL
+CI_perc_ratio$useless <- NULL
+
+CI_perc_nb <- as.data.frame(t(CI_perc_nb))
+rownames(CI_perc_nb) <- 1:(nrow(CI_perc_nb))
+colnames(CI_perc_nb) <- c("x", "y")
+
+CI_perc_vol <- as.data.frame(t(CI_perc_vol))
+rownames(CI_perc_vol) <- 1:(nrow(CI_perc_vol))
+colnames(CI_perc_vol) <- c("x", "y")
+
+CI_perc_ratio <- as.data.frame(t(CI_perc_ratio))
+rownames(CI_perc_ratio) <- 1:(nrow(CI_perc_ratio))
+colnames(CI_perc_ratio) <- c("x", "y")
+```
+
+```{r}
+# Check the coverage rate
+TC_nb <- (1/nrow(CI_perc_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_perc_nb$x, CI_perc_nb$y) )
+TC_vol <- (1/nrow(CI_perc_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_perc_vol$x, CI_perc_vol$y) )
+TC_ratio <- (1/nrow(CI_perc_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_perc_ratio$x, CI_perc_ratio$y) )
+cat("Concerning the percentile approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
+```
+
+```{r}
+## We want all the Reverse Percentile CI obtained for each parameter of interest, 
+# to find the coverage rate
+CI_nb <- data.frame(useless = c(0,0))
+CI_vol <- data.frame(useless = c(0,0))
+CI_ratio <- data.frame(useless = c(0,0))
+for (elt in res2$`Confidence Intervals`) {
+  CI_nb <- cbind(CI_nb, elt$`Reverse percentile`$lim_nb)
+  CI_vol <- cbind(CI_vol, elt$`Reverse percentile`$lim_vol)
+  CI_ratio <- cbind(CI_ratio, elt$`Reverse percentile`$lim_ratio)
+}
+CI_nb$useless <- NULL
+CI_vol$useless <- NULL
+CI_ratio$useless <- NULL
+
+CI_nb <- as.data.frame(t(CI_nb))
+rownames(CI_nb) <- 1:(nrow(CI_nb))
+colnames(CI_nb) <- c("x", "y")
+
+CI_vol <- as.data.frame(t(CI_vol))
+rownames(CI_vol) <- 1:(nrow(CI_vol))
+colnames(CI_vol) <- c("x", "y")
+
+CI_ratio <- as.data.frame(t(CI_ratio))
+rownames(CI_ratio) <- 1:(nrow(CI_ratio))
+colnames(CI_ratio) <- c("x", "y")
+```
+
+```{r}
+# Check the coverage rate
+TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb$x, CI_nb$y) )
+TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol$x, CI_vol$y) )
+TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio$x, CI_ratio$y) )
+cat("Concerning the reverse percentile approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
+```

### 2024-08-02 MC_all.Rmd
Clean MC_all for CI

@@
 output: pdf_document
-date: "2024-07-26"
+date: "2024-08-02"
 ---
@@
 ```{r}
-coverage_rate <- function(nb){
+coverage_rate <- function(k){
   CI_nb <- data.frame(useless = c(0,0))
@@
   for (elt in res2$`Confidence Intervals`) {
-    CI_nb <- cbind(CI_nb, c(unlist(res2$`Confidence Intervals`$CI1[1])[1], unlist(res2$`Confidence Intervals`$CI1[1])[2]))
-    CI_vol <- cbind(CI_nb, c(unlist(res2$`Confidence Intervals`$CI1[1])[3], unlist(res2$`Confidence Intervals`$CI1[1])[4]))
-    CI_ratio <- cbind(CI_nb, c(unlist(res2$`Confidence Intervals`$CI1[1])[5], unlist(res2$`Confidence Intervals`$CI1[1])[6]))
+    CI_nb <- cbind(CI_nb, c(unlist(elt[k])[1], unlist(elt[k])[2]))
+    CI_vol <- cbind(CI_vol, c(unlist(elt[k])[3], unlist(elt[k])[4]))
+    CI_ratio <- cbind(CI_ratio, c(unlist(elt[k])[5], unlist(elt[k])[6]))
   }
   CI_nb$useless <- NULL
-  rownames(CI_nb) <- 1:(nrow(CI_nb))
-  colnames(CI_nb) <- c("x", "y")
+  # rownames(CI_nb) <- 1:(nrow(CI_nb))
+  # colnames(CI_nb) <- c("x", "y")
   CI_vol$useless <- NULL
@@
     TC_normal[1,1], "\n - for the volume of trees: ", TC_normal[2,1], "\n - for the ratio volume / number of trees: ", TC_normal[3,1],
-    " \n \nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
+    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
     TC_normal[1,2], "\n - for the volume of trees: ", TC_normal[2,2], "\n - for the ratio volume / number of trees: ", TC_normal[3,2],
-    " \n \nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
+    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
     TC_normal[1,3], "\n - for the volume of trees: ", TC_normal[2,3], "\n - for the ratio volume / number of trees: ", TC_normal[3,3],
-    " \n \nThe mean length of coverage rates are the following: \n - for the number of trees: ",
+    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
     TC_normal[1,4], "\n - for the volume of trees: ", TC_normal[2,4], "\n - for the ratio volume / number of trees: ", TC_normal[3,4])
@@
 ```{r}
-## We want all the CI based on Normal distribution obtained for each parameter of interest, 
-# to find the coverage rate
-CI_nb <- data.frame(useless = c(0,0))
-CI_vol <- data.frame(useless = c(0,0))
-CI_ratio <- data.frame(useless = c(0,0))
-for (elt in res2$`Confidence Intervals`) {
-  CI_nb <- cbind(CI_nb, elt$Normal$lim_nb)
-  CI_vol <- cbind(CI_vol, elt$Normal$lim_vol)
-  CI_ratio <- cbind(CI_ratio, elt$Normal$lim_ratio)
-}
-CI_nb$useless <- NULL
-CI_vol$useless <- NULL
-CI_ratio$useless <- NULL
-
-CI_nb <- as.data.frame(t(CI_nb))
-rownames(CI_nb) <- 1:(nrow(CI_nb))
-colnames(CI_nb) <- c("x", "y")
-
-CI_vol <- as.data.frame(t(CI_vol))
-rownames(CI_vol) <- 1:(nrow(CI_vol))
-colnames(CI_vol) <- c("x", "y")
-
-CI_ratio <- as.data.frame(t(CI_ratio))
-rownames(CI_ratio) <- 1:(nrow(CI_ratio))
-colnames(CI_ratio) <- c("x", "y")
+TC_perc <- coverage_rate(2)
+cat("Concerning the percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
+    TC_perc[1,1], "\n - for the volume of trees: ", TC_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_perc[3,1],
+    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_perc[1,2], "\n - for the volume of trees: ", TC_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_perc[3,2],
+    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_perc[1,3], "\n - for the volume of trees: ", TC_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_perc[3,3],
+    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
+    TC_perc[1,4], "\n - for the volume of trees: ", TC_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_perc[3,4])
 ```
@@
 ```{r}
-# Check the coverage rate
-TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb$x, CI_nb$y) )
-TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol$x, CI_vol$y) )
-TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio$x, CI_ratio$y) )
-cat("Concerning the normal approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
-```
-
-```{r}
-## We want all the Percentile CI obtained for each parameter of interest, 
-# to find the coverage rate
-CI_perc_nb <- data.frame(useless = c(0,0))
-CI_perc_vol <- data.frame(useless = c(0,0))
-CI_perc_ratio <- data.frame(useless = c(0,0))
-for (elt in res2$`Confidence Intervals`) {
-  CI_perc_nb <- cbind(CI_perc_nb, elt$Percentile$lim_nb)
-  CI_perc_vol <- cbind(CI_perc_vol, elt$Percentile$lim_vol)
-  CI_perc_ratio <- cbind(CI_perc_ratio, elt$Percentile$lim_ratio)
-}
-CI_perc_nb$useless <- NULL
-CI_perc_vol$useless <- NULL
-CI_perc_ratio$useless <- NULL
-
-CI_perc_nb <- as.data.frame(t(CI_perc_nb))
-rownames(CI_perc_nb) <- 1:(nrow(CI_perc_nb))
-colnames(CI_perc_nb) <- c("x", "y")
-
-CI_perc_vol <- as.data.frame(t(CI_perc_vol))
-rownames(CI_perc_vol) <- 1:(nrow(CI_perc_vol))
-colnames(CI_perc_vol) <- c("x", "y")
-
-CI_perc_ratio <- as.data.frame(t(CI_perc_ratio))
-rownames(CI_perc_ratio) <- 1:(nrow(CI_perc_ratio))
-colnames(CI_perc_ratio) <- c("x", "y")
-```
-
-```{r}
-# Check the coverage rate
-TC_nb <- (1/nrow(CI_perc_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_perc_nb$x, CI_perc_nb$y) )
-TC_vol <- (1/nrow(CI_perc_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_perc_vol$x, CI_perc_vol$y) )
-TC_ratio <- (1/nrow(CI_perc_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_perc_ratio$x, CI_perc_ratio$y) )
-cat("Concerning the percentile approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
-```
-
-```{r}
-## We want all the Reverse Percentile CI obtained for each parameter of interest, 
-# to find the coverage rate
-CI_nb <- data.frame(useless = c(0,0))
-CI_vol <- data.frame(useless = c(0,0))
-CI_ratio <- data.frame(useless = c(0,0))
-for (elt in res2$`Confidence Intervals`) {
-  CI_nb <- cbind(CI_nb, elt$`Reverse percentile`$lim_nb)
-  CI_vol <- cbind(CI_vol, elt$`Reverse percentile`$lim_vol)
-  CI_ratio <- cbind(CI_ratio, elt$`Reverse percentile`$lim_ratio)
-}
-CI_nb$useless <- NULL
-CI_vol$useless <- NULL
-CI_ratio$useless <- NULL
-
-CI_nb <- as.data.frame(t(CI_nb))
-rownames(CI_nb) <- 1:(nrow(CI_nb))
-colnames(CI_nb) <- c("x", "y")
-
-CI_vol <- as.data.frame(t(CI_vol))
-rownames(CI_vol) <- 1:(nrow(CI_vol))
-colnames(CI_vol) <- c("x", "y")
-
-CI_ratio <- as.data.frame(t(CI_ratio))
-rownames(CI_ratio) <- 1:(nrow(CI_ratio))
-colnames(CI_ratio) <- c("x", "y")
-```
-
-```{r}
-# Check the coverage rate
-TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb$x, CI_nb$y) )
-TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol$x, CI_vol$y) )
-TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio$x, CI_ratio$y) )
-cat("Concerning the reverse percentile approach, the coverage rate are the following: \n - for the number of trees: ", TC_nb, "\n - for the volume of trees: ", TC_vol, "\n - for the ratio volume / number of trees: ", TC_ratio)
+TC_rev_perc <- coverage_rate(3)
+cat("Concerning the percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
+    TC_rev_perc[1,1], "\n - for the volume of trees: ", TC_rev_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,1],
+    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_rev_perc[1,2], "\n - for the volume of trees: ", TC_rev_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,2],
+    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_rev_perc[1,3], "\n - for the volume of trees: ", TC_rev_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,3],
+    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
+    TC_rev_perc[1,4], "\n - for the volume of trees: ", TC_rev_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,4])
 ```

### 2024-08-02 test_boot_short_3.Rmd
Alternative bootstrap method ready to knit

--- 2024-07-31 test_boot_short_3.Rmd
@@
 output: pdf_document
-date: "2024-07-31"
+date: "2024-08-02"
 ---
@@
 
-  n <- nrow(df) + 1 # sample size of the initial sample
+  n <- nrow(df) + 100 # sample size of the initial sample
   nboot <- length(df)/5 # number of bootstrap samples
@@
   for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (900/899)*sum(unlist(df[,4 + (5*(c-1))])/p))
-    vec_est2 <- append(vec_est2, (900/899)*sum(unlist(df[,5*c])/p))
-    vec_est3 <- append(vec_est3, ((900/899)*sum(unlist(df[,5*c])/p))/((900/899)*sum(unlist(df[,4 + (5*(c-1))])/p)))
-    # (n/(n-1)) is the correction needed since we choose only (n-1) points
+    vec_est1 <- append(vec_est1, (1/100)*(1000/9)*sum(as.vector(unlist(df[,4 + (5*(c-1))]))/p))
+    vec_est2 <- append(vec_est2, (1/100)*(1000/9)*sum(as.vector(unlist(df[,5*c]))/p))
+    vec_est3 <- append(vec_est3, ((1000/9)*sum(as.vector(unlist(df[,5*c])/p)))/((1000/9)*sum(as.vector(unlist(df[,4 + (5*(c-1))]))/p)))
+    # (n_h/(n_h-1))*(n/n_h) is the correction needed since we choose only (n_h-1) points per strata
   }
@@
     names(BOOT_est)[(2*b-1):(2*b)] <- c(paste("est_MC", b, sep = ""), paste("est_boot", b, sep = ""))
+    est_b <- as.vector(est_b)
 
@@
       perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
-      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_b[l,]*2 - lim_sup, est_b[l,]*2 - lim_inf)))
-      norm_CI <- cbind(norm_CI, data.frame(c(est_b[l,]-qnorm(0.975)*sqrt(var(est_boot_val[,l])), est_b[l,]+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
+      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_b[l]*2 - lim_sup, est_b[l]*2 - lim_inf)))
+      norm_CI <- cbind(norm_CI, data.frame(c(est_b[l]-qnorm(0.975)*sqrt(var(est_boot_val[,l])), est_b[l]+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
     }

### 2024-08-05 Draft/Draft.Rmd
Ready to knit

@@
 ```
+
+# Old version of tes_boot_short_2.Rmd (strata different from lines)
+
+```{r}
+f_boot <- function(df_sample, B){
+  # df_sample: original sample; 
+  # B: number of bootstrap samples made thanks to df_sample
+
+  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-100))
+  for (b in 1:B) {
+    # nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
+    # (H-1) strata at random
+    sample_b <- data.frame(x = numeric(), y = numeric(), z = numeric(), t = numeric(), w = numeric())
+    for (number in unique(df_sample[,3])){
+      truc <- sample(rownames(df_sample[df_sample[,3] == number,]), (nrow(df_sample[df_sample[,3] == number,])-1), replace = TRUE)
+      muche <- mapply(function(RRRRR){df_sample[rownames(df_sample) == RRRRR,]}, truc)
+      sample_b <- rbind(sample_b, t(muche))
+      # sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
+    }
+    df_boot <- cbind(df_boot, sample_b)
+    colnames(df_boot)[((b-1)*5+1 + 1):(b*5+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""), paste("ech", b, colnames(df_sample)[5], sep = ""))
+  }
+  df_boot$useless <- NULL
+  return(df_boot)
+  # Return a data frame with B samples of as many variables as we want (in this application, 5)
+}
+```
+
+```{r}
+# Making of estimations for each sample made by the bootstrap method
+est_boot <- function(df, p){
+  # df: dataframe with 5*B columns and n rows
+
+  n <- nrow(df) + 1 # sample size of the initial sample
+  nboot <- length(df)/5 # number of bootstrap samples
+  vec_est1 <- c()
+  vec_est2 <- c()
+  vec_est3 <- c()
+  for (c in 1:nboot) {
+    vec_est1 <- append(vec_est1, (900/9)*sum(unlist(df[,4 + (5*(c-1))])/p))
+    vec_est2 <- append(vec_est2, (900/9)*sum(unlist(df[,5*c])/p))
+    vec_est3 <- append(vec_est3, ((900/9)*sum(unlist(df[,5*c])/p))/((900/9)*sum(unlist(df[,4 + (5*(c-1))])/p)))
+    # (n_h/(n_h-1))*(n/n_h) is the correction needed since we choose only (n_h-1) points per strata
+  }
+  vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
+  return(vec_est)
+  # Data frame with 3 estimations for each sample
+}
+```
+
+```{r}
+### Function to automate Monte Carlo + bootstrap method
+
+MC_boot <- function(n, B1, B2){
+  # B1: number of iterations for MC;
+  # B2: number of iterations for bootstrap
+
+  p <- sum(rep((1/1000)*(1/1000), n))
+  BOOT_df <- list() # All local variables
+  BOOT_est <- list() # All estimations
+  BOOT_var <- list() # Variances
+  BOOT_CI <- list() # Confidence Intervals
+  for (b in 1:B1) { # One MC iteration at a time
+    # Uniform sampling over the whole territory
+    df_grid <- sampling_grid(i,c_dim)
+    a1 <- df_grid$x
+    a2 <- df_grid$y
+    a3 <- df_grid$Stratum
+    var <- mapply(circle_all, a1, a2)
+    df_b <- data.frame(x = a1, y = a2, w = a3, z = t(var)[,1], t = t(var)[,2])
+    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("h.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
+    est_b <- t(data.frame(x = sum(df_b[4] /p), y = sum(df_b[5] /p), z = (sum(df_b[5] /p))/(sum(df_b[4]/p))))
+
+    # Bootstrap iterations
+    df_boot <- f_boot(df_b, B2)
+    est_boot_val <- est_boot(df_boot, p)
+
+    BOOT_var[[b]] <- list(var_nb = var(est_boot_val$est_nb), var_vol = var(est_boot_val$est_vol), var_ratio = var(est_boot_val$est_ratio))
+    names(BOOT_var)[b] <- paste("Variance", b, sep = "")
+    BOOT_df <- c(BOOT_df, list(data_init = df_b, data_boot = df_boot))
+    names(BOOT_df)[(2*b-1):(2*b)] <- c(paste("df_MC", b, sep = ""), paste("df_boot", b, sep = ""))
+    BOOT_est <- c(BOOT_est, list(est_init_b = est_b, est_boot_b = est_boot_val))
+    names(BOOT_est)[(2*b-1):(2*b)] <- c(paste("est_MC", b, sep = ""), paste("est_boot", b, sep = ""))
+
+    # Confidence intervals
+    norm_CI <- data.frame(useless = rep(0, 2))
+    perc_CI <- data.frame(useless = rep(0, 2))
+    rev_perc_CI <- data.frame(useless = rep(0, 2))
+    for (l in 1:3) { # Loop: one estimator each time
+      sorted_est <- sort(est_boot_val[,l])
+      lim_inf <- sorted_est[floor(B2*2.5/100)]
+      lim_sup <- sorted_est[B2 - floor(B2*2.5/100)]
+      perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
+      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_b[l,]*2 - lim_sup, est_b[l,]*2 - lim_inf)))
+      norm_CI <- cbind(norm_CI, data.frame(c(est_b[l,]-qnorm(0.975)*sqrt(var(est_boot_val[,l])), est_b[l,]+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
+    }
+    norm_CI$useless <- NULL
+    perc_CI$useless <- NULL
+    rev_perc_CI$useless <- NULL
+    colnames(norm_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
+    colnames(perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
+    colnames(rev_perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
+    all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI)
+    # BOOT_CI <- c(BOOT_CI, CI_b = all_CI)
+    BOOT_CI[[b]] <- all_CI
+    names(BOOT_CI)[b] <- paste("CI", b, sep = "")
+  }
+  return(list(`Local Variables` = BOOT_df, Estimations = BOOT_est, Variances = BOOT_var, `Confidence Intervals` = BOOT_CI))
+  # Local Variables: local variables (number and volume) for each point in each sample
+  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
+  # Variances: mean of the bootstrap variance for each estimator
+  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
+}
+```
+
+```{r}
+start.time <- Sys.time()
+
+res2 <- MC_boot(n, B1 = 10, B2 = 4)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```

### 2024-08-05 Plot_grids.R
Plotting grids

@@ -1,0 +1,141 @@
+##### To plot grids (for the report) ----------
+
+install.packages("ggplot2")
+library(ggplot2)
+
+### Version 1 -----------
+
+# Create a data frame with the coordinates and colors
+grid_data <- expand.grid(x = 1:30, y = 1:30)  # 10x10 grid
+grid_data$color <- "white"  # Default color for all squares
+
+# Specify the squares to be colored
+colored_squares <- data.frame(
+  x = c(rep(3, 30), rep(13, 30), rep(23, 30)),
+  y = rep(1:30, 3),
+  color = c(rep("orange", 90))
+)
+
+# Merge the colored squares into the grid data
+grid_data <- merge(grid_data, colored_squares, by = c("x", "y"), all.x = TRUE)
+grid_data$color.y[is.na(grid_data$color.y)] <- "white" # Set NA colors to white
+# c(rep("white", 100))
+
+ggplot(grid_data, aes(x = x, y = y, fill = color.y)) +
+  geom_tile(colour = "black") +  # Draw the squares with black borders # 
+  scale_fill_identity() +  # Use the colors specified in the data
+  theme_minimal() +  # Minimal theme for better visualization
+  theme(
+    axis.title = element_blank(),  # Remove axis titles
+    axis.text = element_blank(),   # Remove axis text
+    axis.ticks = element_blank(),  # Remove axis ticks
+    panel.grid = element_blank()   # Remove grid lines
+  ) +
+  coord_fixed()  # Ensure squares are not stretched
+
+### Version 2 -----------
+
+# Create a data frame with the coordinates and colors
+grid_data <- expand.grid(x = 1:30, y = 1:30)  # 10x10 grid
+grid_data$color <- "white"  # Default color for all squares
+
+# Function to sample at random following the grid
+sampling_grid <- function(i){
+  cells_x <- c()
+  cells_y <- c()
+  
+  for (l in 0:29) {
+    if (l==0){
+      x_init <- i
+    }else if ((3*l+i) < 10){
+      x_init <- (3*l+i)
+    }else{
+      x_init <- (((3*l+i))%%(10))
+    }
+    k <- 0
+    while (x_init + 10*k < 30) {
+      a <- x_init + 10*k
+      b <- l
+      cells_x <- append(cells_x, a)
+      print(a)
+      cells_y <- append(cells_y, b)
+      print(b)
+      k <- k+1
+    }
+  }
+  return(data.frame(x = cells_x, y = cells_y))
+}
+
[…]

### 2024-08-05 Draft/Draft.Rmd
Draft with plots

@@
 ```
+
+## Plots ----------
+
+```{r}
+install.packages("ggplot2")
+library(ggplot2)
+
+# Setup the data
+m <- matrix(c(8,3,4,1,5,9,6,7,2), nrow=3, ncol=3)
+df <- expand.grid(x=1:ncol(m),y=1:nrow(m))
+df$val <- m[as.matrix(df[c('y','x')])]
+
+library(ggplot2)
+library(scales)
+test <- ggplot(df, aes(x=x, y=y, label=val)) + 
+  geom_tile(fill='transparent', colour = 'black') + 
+  geom_text(size = 14) + 
+  scale_y_reverse() +
+  theme_classic() + 
+  theme(axis.text  = element_blank(),
+        panel.grid = element_blank(),
+        axis.line  = element_blank(),
+        axis.ticks = element_blank(),
+        axis.title = element_blank())
+
+plot(test)
+```
+
+```{r}
+# Create a data frame with the coordinates and colors
+grid_data <- expand.grid(x = 1:10, y = 1:10)  # 10x10 grid
+grid_data$color <- "white"  # Default color for all squares
+
+# Specify the squares to be colored
+colored_squares <- data.frame(
+  x = c(2, 4, 6, 8),
+  y = c(3, 5, 7, 9),
+  color = c("red", "blue", "green", "yellow")
+)
+
+# Merge the colored squares into the grid data
+grid_data <- merge(grid_data, colored_squares, by = c("x", "y"), all.x = TRUE)
+grid_data$color.y[is.na(grid_data$color.y)] <- "white" # Set NA colors to white
+# c(rep("white", 100))
+
+ggplot(grid_data, aes(x = x, y = y, fill = color.y)) +
+  geom_tile(colour = "black") +  # Draw the squares with black borders # 
+  scale_fill_identity() +  # Use the colors specified in the data
+  theme_minimal() +  # Minimal theme for better visualization
+  theme(
+    axis.title = element_blank(),  # Remove axis titles
+    axis.text = element_blank(),   # Remove axis text
+    axis.ticks = element_blank(),  # Remove axis ticks
+    panel.grid = element_blank()   # Remove grid lines
+  ) +
+  coord_fixed()  # Ensure squares are not stretched
+```

### 2024-08-06 MC_all.Rmd
BCa not finished

@@
 1 000 Monte Carlo iterations and 400 bootstrap iterations for each one are appropriated.
+
+```{r}
+## BCa nonparametric
+# Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
+# Function explained in Efron and Tibshirani (1993)
+# Adapted for our particular problem
+bcanon <- function(df_init,est_init,est_boot_val,p,...,alpha =
+                     c(.025,.975)) { 
+    # n <- nrow(x)
+    # a <- mapply(theta, x[, 1], x[, 2])
+    # Estimated total thus obtained from the initial sample
+    # thetahat <- sum(a/p)
+
+    nboot <- nrow(est_boot_val)
+    # thetastar <- c()
+    # for (c in 1:B) {
+    #   a <- mapply(theta, est_boot[, (2*c)-1], est_boot[, 2*c])
+    #   thetastar <- append(thetastar, sum(a/p))
+    # }
+    thetastar <- as.data.frame(mapply(sort, est_boot_val))
+
+    z0 <- mapply(function(one, long){qnorm(sum(long<one)/nboot)}, t(est_init),est_boot_val)
+
+    # z0 <- qnorm(sum(thetastar<thetahat)/nboot)
+
+    u <- data.frame(x = numeric(), y = numeric())
+    for(i in 1:n){
+        x_i <- df_init[-i,]
+        # a <- c()
+        # for (j in 1:(n-1)) {
+        #   a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
+        # }
+        u <- rbind(u, c(sum(x_i[3]/p), sum(x_i[4]/p)))
+    }
+    u <- cbind(u, mapply(function(x,y){x/y}, u[2], u[1]))
+    uu <- as.data.frame( mapply(function(some_vec){mean(some_vec)-some_vec}, u) )
+    # uu <- mean(u)-u
+    acc <- mapply(function(some_vec){sum(some_vec**3)/(6*(sum(some_vec**2))^1.5)}, uu)
+    # acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)
+
+    zalpha <- qnorm(alpha)
+
+    tt <- as.data.frame( mapply(function(z0, acc){pnorm(z0+ (z0+zalpha)/(1-acc*(z0+zalpha)))}, z0, acc) )
+    # tt <- pnorm(z0+ (z0+zalpha)/(1-acc*(z0+zalpha)))
+
+    confpoints <- as.data.frame( mapply(function(tt, thetastar){quantile(x=thetastar,probs=tt,type=1)}, tt, thetastar) )
+    # confpoints <- quantile(x=thetastar,probs=tt,type=1)
+    # confpoints <- quantile(x=thetastar,probs=tt,type=1)
+    rownames(confpoints) <- NULL
+    # confpoints <- cbind(alpha,confpoints)
+    # dimnames(confpoints)[[2]] <- c("alpha","bca point")
+    return(confpoints)
+}
+```
+
+```{r}
+# Test
+# bcanon(df_b,est_boot_val,circle_all())
+```
 
@@
     colnames(rev_perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-    all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI)
-    # BOOT_CI <- c(BOOT_CI, CI_b = all_CI)
+    BCa_CI <- bcanon(df_b, est_b, est_boot_val,p)
+    colnames(BCa_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
+    all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI, BCa = BCa_CI)
     BOOT_CI[[b]] <- all_CI

### 2024-08-06 MC_all.Rmd
Ready to knit with BCa

@@
 
-In this document, *uniform sampling* is used to create a sample and *one single circle* with a radius of 5 is used to compute local variables.
+In this document, \textbf{uniform sampling} is used to create a sample and \textbf{one single circle} with a radius of 5 is used to compute local variables.
 
@@
                      c(.025,.975)) { 
-    # n <- nrow(x)
-    # a <- mapply(theta, x[, 1], x[, 2])
-    # Estimated total thus obtained from the initial sample
-    # thetahat <- sum(a/p)
+    # df_init: initial sample
+    # est_init: estimation made thanks to the initial sample
+    # est_boot_val: estimations made thanks to bootstrap samples
+    # p: inclusion density
 
     nboot <- nrow(est_boot_val)
-    # thetastar <- c()
-    # for (c in 1:B) {
-    #   a <- mapply(theta, est_boot[, (2*c)-1], est_boot[, 2*c])
-    #   thetastar <- append(thetastar, sum(a/p))
-    # }
     thetastar <- as.data.frame(mapply(sort, est_boot_val))
@@
 
-    # z0 <- qnorm(sum(thetastar<thetahat)/nboot)
-
     u <- data.frame(x = numeric(), y = numeric())
@@
         x_i <- df_init[-i,]
-        # a <- c()
-        # for (j in 1:(n-1)) {
-        #   a <- append(a, theta(x_i[j, 1], x_i[j, 2]))
-        # }
         u <- rbind(u, c(sum(x_i[3]/p), sum(x_i[4]/p)))
@@
     uu <- as.data.frame( mapply(function(some_vec){mean(some_vec)-some_vec}, u) )
-    # uu <- mean(u)-u
     acc <- mapply(function(some_vec){sum(some_vec**3)/(6*(sum(some_vec**2))^1.5)}, uu)
-    # acc <- sum(uu*uu*uu)/(6*(sum(uu*uu))^1.5)
 
@@
     tt <- as.data.frame( mapply(function(z0, acc){pnorm(z0+ (z0+zalpha)/(1-acc*(z0+zalpha)))}, z0, acc) )
-    # tt <- pnorm(z0+ (z0+zalpha)/(1-acc*(z0+zalpha)))
 
     confpoints <- as.data.frame( mapply(function(tt, thetastar){quantile(x=thetastar,probs=tt,type=1)}, tt, thetastar) )
-    # confpoints <- quantile(x=thetastar,probs=tt,type=1)
-    # confpoints <- quantile(x=thetastar,probs=tt,type=1)
     rownames(confpoints) <- NULL
-    # confpoints <- cbind(alpha,confpoints)
-    # dimnames(confpoints)[[2]] <- c("alpha","bca point")
     return(confpoints)
@@
 
+```{r}
+TC_bca <- coverage_rate(4)
+cat("Concerning the BCa approach, the coverage rates are the following: \n - for the number of trees: ", 
+    TC_bca[1,1], "\n - for the volume of trees: ", TC_bca[2,1], "\n - for the ratio volume / number of trees: ", TC_bca[3,1],
+    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_bca[1,2], "\n - for the volume of trees: ", TC_bca[2,2], "\n - for the ratio volume / number of trees: ", TC_bca[3,2],
+    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_bca[1,3], "\n - for the volume of trees: ", TC_bca[2,3], "\n - for the ratio volume / number of trees: ", TC_bca[3,3],
+    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
+    TC_bca[1,4], "\n - for the volume of trees: ", TC_bca[2,4], "\n - for the ratio volume / number of trees: ", TC_bca[3,4])
+```
+
 ## Comparison of the variances

### 2024-08-07 MC3_all.Rmd
3 circles and cleaner

--- 2024-08-06 MC_all.Rmd
@@
 output: pdf_document
-date: "2024-08-02"
+date: "2024-08-07"
 ---
@@
 
-In this document, \textbf{uniform sampling} is used to create a sample and \textbf{one single circle} with a radius of 5 is used to compute local variables.
+In this document, \textbf{uniform sampling} is used to create a sample and \textbf{three circles} with a radii of 6, 9 and 15 are used to compute local variables.
 
@@
     # Variables of interest derived from the sample
-    var <- mapply(circle_all, a1, a2)
+    var <- mapply(circle3_all, a1, a2)
     MC_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
@@
 }
-```
-
-```{r}
-# Test
-# bcanon(df_b,est_boot_val,circle_all())
 ```
@@
     a2 <- runif(n, 0, 1000)
-    var <- mapply(circle_all, a1, a2)
+    var <- mapply(circle3_all, a1, a2)
     df_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
@@
 res1 <- MonteCarlo(n, 10000)
-# Just one circle to begin with
+# Three concentric circles
 
@@
 # Example:
-## Monte Carlo means of estimations:
-##  - for the number of trees: 29251.69
-##  - for the volume of trees: 5407.967
-##  - for the ratio volume / number of trees: 0.184873
 ```
@@
 # Example:
-## Monte Carlo variances:
-##  - for the number of trees: 2604340
-##  - for the volume of trees: 99936.6
-##  - for the ratio volume / number of trees: 1.122037e-05
 ```
@@
 res2 <- MC_boot(n, B1 = 1000, B2 = 400)
-# Just one circle to begin with
+# Three concentric circles
 
@@
 # Example:
-## Mean of the means of estimations obtained through each bootstrap process:
-##  - for the number of trees: 29280.52
-##  - for the volume of trees: 5411.916
-##  - for the ratio volume / number of trees: 0.1848212
 ```
@@
 # Example:
-## Mean of the variance of bootstrap samples:
-##  - for the number of trees: 2562574
-##  - for the volume of trees: 98333.62
-##  - for the ratio volume / number of trees: 1.121868e-05
 ```
@@
   CI_nb$useless <- NULL
-  # rownames(CI_nb) <- 1:(nrow(CI_nb))
-  # colnames(CI_nb) <- c("x", "y")
   CI_vol$useless <- NULL
@@
 TC_rev_perc <- coverage_rate(3)
-cat("Concerning the percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
+cat("Concerning the reverse percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
     TC_rev_perc[1,1], "\n - for the volume of trees: ", TC_rev_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,1],
@@
 # Example:
-## Difference between the two estimations of variance:
-##  - for the number of trees: 1.629866%
-##  - for the volume of trees: 1.630143%
-##  - for the ratio volume / number of trees: 0.01505727%
 ```

### 2024-08-07 MC3_all.Rmd
Radii

@@
 
-In this document, \textbf{uniform sampling} is used to create a sample and \textbf{three circles} with a radii of 6, 9 and 15 are used to compute local variables.
+In this document, \textbf{uniform sampling} is used to create a sample and \textbf{three circles} with radii of 6, 9 and 15 are used to compute local variables.
 

### 2024-08-07 Plot_grids.R
With strata

@@ -139,3 +139,140 @@ ggplot(grid_data, aes(x = x, y = y, fill = color.y)) +
   ) +
   coord_fixed()  # Ensure squares are not stretched
 
+
+
+### Strata 1 -----------
+
+# Create a data frame with the coordinates and colors
+grid_data <- expand.grid(x = 1:30, y = 1:30)  # 10x10 grid
+grid_data$color <- "white"  # Default color for all squares
+
+# Function to sample at random following the grid
+sampling_grid <- function(i){
+  cells_x <- c()
+  cells_y <- c()
+  
+  for (l in 0:29) {
+    if (l==0){
+      x_init <- i
+    }else if ((3*l+i) < 10){
+      x_init <- (3*l+i)
+    }else{
+      x_init <- (((3*l+i))%%(10))
+    }
+    k <- 0
+    while (x_init + 10*k < 30) {
+      a <- x_init + 10*k
+      b <- l
+      cells_x <- append(cells_x, a)
+      # print(a)
+      cells_y <- append(cells_y, b)
+      # print(b)
+      k <- k+1
+    }
+  }
+  return(data.frame(x = cells_x, y = cells_y))
+}
+
+test <- sampling_grid(3)
+
+# Specify the squares to be colored
+colored_squares <- data.frame(
+  x = test$x,
+  y = test$y +1,
+  color = c(rep("orange", 90))
+)
+
+colored_stratum <- data.frame(
+  x = test[test$y == 2,]$x,
+  y = test[test$y == 2,]$y +1,
+  color = c(rep("red", nrow(test[test$y == 2,])))
+)
+
+# Merge the colored squares into the grid data
+grid_data <- merge(grid_data, colored_squares, by = c("x", "y"), all.x = TRUE)
+grid_data <- merge(grid_data, colored_stratum, by = c("x", "y"), all.x = TRUE)
+grid_data$color[(is.na(grid_data$color)) & (grid_data$color.y == "orange")] <- "orange" 
+grid_data$color[is.na(grid_data$color)] <- "white" # Set NA colors to white
+
+ggplot(grid_data, aes(x = x, y = y, fill = color)) +
+  geom_tile(colour = "black") +  # Draw the squares with black borders # 
+  scale_fill_identity() +  # Use the colors specified in the data
+  theme_minimal() +  # Minimal theme for better visualization
+  theme(
+    axis.title = element_blank(),  # Remove axis titles
+    axis.text = element_blank(),   # Remove axis text
[…]

### 2024-08-08 Useful_functions/Circle.R
Towards a very complete function for local var

@@ -6,6 +6,30 @@ source("~/work/Sim_article2024/Useful_functions/Inc_area_2.R")
 
 ### With one single circle -----
 
+circle_ALL <- function(x1, x2, R=5){
+  # 2 coordinates (x1, x2) and a radius (R)
+  
+  list_trees <- which(((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2))
+  if (length(list_trees) != 0){
+    local_var_nb <- sum(1/mapply(inc_area, trees[list_trees,]$x, trees[list_trees,]$y, MoreArgs = list(0,0,1000,1000,R)))
+    local_var_nb_small <- sum(1/mapply(inc_area, trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 < 70.5),]$x, 
+                                       trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 < 70.5),]$y, MoreArgs = list(0,0,1000,1000,R)))
+    local_var_nb_medium <- sum(1/mapply(inc_area, trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$x, 
+                                        trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$y, MoreArgs = list(0,0,1000,1000,R)))
+    local_var_nb_big <- sum(1/mapply(inc_area, trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 > 117.5),]$x, 
+                                     trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 > 117.5),]$y, MoreArgs = list(0,0,1000,1000,R)))
+    local_var_vol <- sum((trees[list_trees,]$v)/mapply(inc_area, trees[list_trees,]$x, trees[list_trees,]$y, MoreArgs = list(0,0,1000,1000,R)))
+  }
+  else{
+    local_var_nb <- 0
+    local_var_nb_small <- 0
+    local_var_nb_medium <- 0
+    local_var_vol <- 0
+  }
+  return(c(local_var_nb,local_var_vol))
+  # local_var_nb: local variable based on the number of trees; local_var_vol: local variable based on the volume of trees
+}
+
 ## Function to produce all local variables from one point
 circle_all <- function(x1, x2, R=5){
   # 2 coordinates (x1, x2) and a radius (R)

### 2024-08-08 Draft/Old_Circle.R
1 circle and many var

@@ -192,3 +192,21 @@ circle3_vol <- function(x1, x2, R1=15, R2=9, R3=6){
   return(local_var)
   # local_var: local variable based on the volume of trees
 }
+
+##### Rubbish ----------
+
+var_nb_small <- sum(1/mapply(inc_area, trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 < 70.5),]$x, 
+                             trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 < 70.5),]$y, MoreArgs = list(0,0,1000,1000,R)))
+var_nb_medium <- sum(1/mapply(inc_area, trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$x, 
+                              trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$y, MoreArgs = list(0,0,1000,1000,R)))
+var_nb_big <- sum(1/mapply(inc_area, trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 > 117.5),]$x, 
+                           trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 > 117.5),]$y, MoreArgs = list(0,0,1000,1000,R)))
+var_nb <- 0
+var_nb_small <- 0
+var_nb_medium <- 0
+var_nb_big <- 0
+var_vol <- 0
+var_vol_small <- 0
+var_vol_medium <- 0
+var_vol_big <- 0
+

### 2024-08-08 Useful_functions/Circle.R

@@ -11,23 +11,49 @@ circle_ALL <- function(x1, x2, R=5){
   
   list_trees <- which(((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2))
   if (length(list_trees) != 0){
-    local_var_nb <- sum(1/mapply(inc_area, trees[list_trees,]$x, trees[list_trees,]$y, MoreArgs = list(0,0,1000,1000,R)))
-    local_var_nb_small <- sum(1/mapply(inc_area, trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 < 70.5),]$x, 
-                                       trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 < 70.5),]$y, MoreArgs = list(0,0,1000,1000,R)))
-    local_var_nb_medium <- sum(1/mapply(inc_area, trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$x, 
-                                        trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$y, MoreArgs = list(0,0,1000,1000,R)))
-    local_var_nb_big <- sum(1/mapply(inc_area, trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 > 117.5),]$x, 
-                                     trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 > 117.5),]$y, MoreArgs = list(0,0,1000,1000,R)))
-    local_var_vol <- sum((trees[list_trees,]$v)/mapply(inc_area, trees[list_trees,]$x, trees[list_trees,]$y, MoreArgs = list(0,0,1000,1000,R)))
+    var_nb <- sum(1/mapply(inc_area, trees[list_trees,]$x, trees[list_trees,]$y, MoreArgs = list(0,0,1000,1000,R)))
+    var_vol <- sum((trees[list_trees,]$v)/mapply(inc_area, trees[list_trees,]$x, trees[list_trees,]$y, MoreArgs = list(0,0,1000,1000,R)))
+    small_trees <- trees[(rownames(trees) %in% list_trees) & (pi*trees$d130 < 70.5),]
+    if (nrow(small_trees) != 0){
+      var_nb_small <- sum(1/mapply(inc_area, small_trees$x, 
+                                   small_trees$y, MoreArgs = list(0,0,1000,1000,R)))
[…]

### 2024-08-08 All_param.Rmd
Towards a lot of ratios

--- 2024-08-07 MC3_all.Rmd
@@
 ---
-title: "Monte Carlo and bootstrap for all parameters"
+title: "Monte Carlo and bootstrap for ALL parameters"
 output: pdf_document
-date: "2024-08-07"
+date: "2024-08-02"
 ---
@@
 
-The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees and the ratio volume of trees / number of trees) and variances of these estimators.
+The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees, the ratio volume of trees / number of trees and \textbf{other ratios}) and variances of these estimators.
 The same elements, along with confidence intervals, are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations.
@@
 
-In this document, \textbf{uniform sampling} is used to create a sample and \textbf{three circles} with radii of 6, 9 and 15 are used to compute local variables.
+In this document, \textbf{uniform sampling} is used to create a sample and \textbf{one single circle} with a radius of 5 is used to compute local variables.
 
@@
 # True values
-cat("Number of trees:", length(trees$x), "\nTotal volume:", sum(trees$v), 
-    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees))
+cat("True integrals are the following:\n\nNumber of trees:", nrow(trees), "\nTotal volume:", sum(trees$v), 
+    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees),
+    "\n\nNumber of small trees:", nrow(trees[(pi*trees$d130 < 70.5),]), "\nVolume of small trees:", sum(trees[(pi*trees$d130 < 70.5),]$v), 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]),
+    "\n\nNumber of medium trees:", nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), "\nVolume of medium trees:", sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]),
+    "\n\nNumber of big trees:", nrow(trees[(pi*trees$d130 > 117.5),]), "\nVolume of big trees:", sum(trees[(pi*trees$d130 > 117.5),]$v), 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),])
+    )
 ```
@@
     # Variables of interest derived from the sample
-    var <- mapply(circle3_all, a1, a2)
+    var <- mapply(circle_ALL_, a1, a2)
     MC_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
@@
     a2 <- runif(n, 0, 1000)
-    var <- mapply(circle3_all, a1, a2)
+    var <- mapply(circle_ALL_, a1, a2)
     df_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
@@
 res1 <- MonteCarlo(n, 10000)
-# Three concentric circles
+# Just one circle to begin with
 
@@
 res2 <- MC_boot(n, B1 = 1000, B2 = 400)
-# Three concentric circles
+# Just one circle to begin with
 

### 2024-08-08 Useful_functions/Circle.R

@@ -6,7 +6,7 @@ source("~/work/Sim_article2024/Useful_functions/Inc_area_2.R")
 
 ### With one single circle -----
 
-circle_ALL <- function(x1, x2, R=5){
+circle_ALL_ <- function(x1, x2, R=5){
   # 2 coordinates (x1, x2) and a radius (R)
   
   list_trees <- which(((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R^2))

### 2024-08-08 All_param.Rmd
Complexification in progress

@@
   MC_df <- data.frame(useless = rep(0, n))
-  MC_est <- data.frame(useless = rep(0, 3), row.names = c("est_nb", "est_vol", "est_ratio"))
+  MC_est <- data.frame()
 
   for (b in 1:B) { # All in one "for" loop
+    print(b) ### To delete in the end!!! 
     # Uniform sampling over the whole territory
-    a1 <- runif(n, 0, 1000)
-    a2 <- runif(n, 0, 1000)
+    xy <- data.frame(a1 = runif(n, 0, 1000), a2 = runif(n, 0, 1000))
     # Variables of interest derived from the sample
-    var <- mapply(circle_ALL_, a1, a2)
-    MC_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
-    MC_df <- cbind(MC_df, MC_b)
-    colnames(MC_df)[(4*(b-1)+2):(4*(b-1)+2+3)] <- c(paste("x", b, sep = ""), paste("y", b, sep = ""), paste("nb", b, sep = ""), paste("vol", b, sep = ""))
-    est_b <- t(data.frame(x = sum(MC_df[4*(b-1)+2+2] /p), y = sum(MC_df[4*(b-1)+2+3] /p), z = (sum(MC_df[4*(b-1)+2+3] /p))/(sum(MC_df[4*(b-1)+2+2]/p))))
-    MC_est <- cbind(MC_est, est_b)
-    colnames(MC_est)[b+1] <- paste("ech", b, sep = "") 
+    var <- as.data.frame(t(mapply(circle_ALL_, xy$a1, xy$a2)))
+    nb_var <- length(var) # number of variables of interest
+    MC_df <- cbind(MC_df, xy, var)
+    colnames(MC_df)[((nb_var+2)*(b-1)+2):((nb_var+2)*(b)+2-1)] <- c(paste("x", b, sep = ""), paste("y", b, sep = ""), paste("nb", b, sep = ""), paste("nb_s", b, sep = ""), paste("nb_m", b, sep = ""), paste("nb_b", b, sep = ""), paste("vol", b, sep = ""), paste("vol_s", b, sep = ""), paste("vol_m", b, sep = ""), paste("vol_b", b, sep = ""))
+    from_local <- function(j){sum(MC_df[(nb_var+2)*(b-1)+3+j] /p)}
+    est_b <- data.frame(from_local(1), from_local(5), (from_local(5))/(from_local(1)), from_local(2), from_local(6), (from_local(6))/(from_local(2)), 
+                           from_local(3), from_local(7), (from_local(7))/(from_local(3)), from_local(4), from_local(8), (from_local(8))/(from_local(4)))
+    nb_est <- length(est_b) # number of estimations
+    MC_est <- rbind(MC_est, est_b)
+    rownames(MC_est)[b] <- paste("ech", b, sep = "") 
   }
   MC_df$useless <- NULL
-  MC_est$useless <- NULL
-  MC_var <- c(var(as.vector(t(MC_est[1,]))), var(as.vector(t(MC_est[2,]))), var(as.vector(t(MC_est[3,]))))
+  MC_est <- t(MC_est)
+  row.names(MC_est) <- NULL
+  var_est <- function(j){var(as.vector(MC_est[j,]))}
+  MC_var <- mapply(var_est, 1:nb_est)
 
   return(list(`Local Variables` = MC_df, Estimations = MC_est, Variances = MC_var))
-  # Local Variables: local variables (number and volume) for each point in each sample
-  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
-  # Variances: Monte Carlo variance for each of the totals / ratio
+  # Local Variables: local variables (numbers and volumes) for each point in each sample
+  # Estimations: all estimations (numbers, volumes, ratios) for each sample
+  # Variances: Monte Carlo variance for each of the totals / ratios
 }
@@
 # Adapted for our particular problem
-bcanon <- function(df_init,est_init,est_boot_val,p,...,alpha =
+bcanon <- function(df_init,est_init,est_boot_val,p,nb_est,alpha =
                      c(.025,.975)) { 
@@
         x_i <- df_init[-i,]
-        u <- rbind(u, c(sum(x_i[3]/p), sum(x_i[4]/p)))
+        # u <- rbind(u, c(sum(x_i[3]/p), sum(x_i[4]/p)))
+        u <- rbind(u, as.vector(mapply(function(j){mapply(sum(x_i[j]/p))}, 1:nb_est)))
     }
@@
 ## Making of bootstrap samples based on an initial sample
-f_boot <- function(df_sample, B){
+f_boot <- function(df_sample, B, nb_est){
   # df_sample: initial sample with 4 variables and of size n; 
@@
     df_boot <- cbind(df_boot, sample_b)
-    colnames(df_boot)[((b-1)*4+1 + 1):(b*4+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""))
+    colnames(df_boot)[((b-1)*4+1 + 1):(b*4+1)] <- as.vector(mapply(function(j){paste("ech", b, colnames(df_sample)[j], sep = "")}, 1:nb_est))
+      # c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""))
   }
@@
     # Uniform sampling over the whole territory
-    a1 <- runif(n, 0, 1000)
-    a2 <- runif(n, 0, 1000)
-    var <- mapply(circle_ALL_, a1, a2)
-    df_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
-    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
-    est_b <- t(data.frame(x = sum(df_b[3] /p), y = sum(df_b[4] /p), z = (sum(df_b[4] /p))/(sum(df_b[3]/p))))
+    xy <- data.frame(a1 = runif(n, 0, 1000), a2 = runif(n, 0, 1000))
+    # Variables of interest derived from the sample
+    var <- as.data.frame(t(mapply(circle_ALL_, xy$a1, xy$a2)))
+    nb_var <- length(var) # number of variables of interest
+    df_b <- cbind(xy, var)
+
+    colnames(df_b)[((nb_var+2)*(b-1)+2):((nb_var+2)*(b)+2-1)] <- 
+      c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("nb_s.MC", b, sep = ""), paste("nb_m.MC", b, sep = ""), paste("nb_b.MC", b, sep = ""), paste("vol.MC", b, sep = ""), paste("vol_s.MC", b, sep = ""), paste("vol_m.MC", b, sep = ""), paste("vol_b.MC", b, sep = ""))
+    from_local <- function(j){sum(df_b[(nb_var+2)*(b-1)+3+j] /p)}
+    est_b <- data.frame(from_local(1), from_local(5), (from_local(5))/(from_local(1)), from_local(2), from_local(6), (from_local(6))/(from_local(2)), 
+                           from_local(3), from_local(7), (from_local(7))/(from_local(3)), from_local(4), from_local(8), (from_local(8))/(from_local(4)))
+    nb_est <- length(est_b) # number of estimations
+    rownames(MC_est)[b] <- paste("ech", b, sep = "")
+
+    # colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
+    # est_b <- t(data.frame(x = sum(df_b[3] /p), y = sum(df_b[4] /p), z = (sum(df_b[4] /p))/(sum(df_b[3]/p))))
 
     # Bootstrap iterations
-    df_boot <- f_boot(df_b, B2)
+    df_boot <- f_boot(df_b, B2, nb_est)
     est_boot_val <- est_boot(df_boot, p)
@@
     rev_perc_CI <- data.frame(useless = rep(0, 2))
-    for (l in 1:3) { # Loop: one estimator each time
+    for (l in 1:length(est_boot_val)) { # Loop: one estimator each time
       sorted_est <- sort(est_boot_val[,l])
@@
     rev_perc_CI$useless <- NULL
-    colnames(norm_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-    colnames(perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-    colnames(rev_perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-    BCa_CI <- bcanon(df_b, est_b, est_boot_val,p)
-    colnames(BCa_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
+    nam_lim <- c("lim_nb", "lim_vol", "lim_ratio", "lim_nb_s", "lim_vol_s", "lim_ratio_s", 
+                 "lim_nb_m", "lim_vol_m", "lim_ratio_m", 
+                 "lim_nb_b", "lim_vol_b", "lim_ratio_b")
+    colnames(norm_CI) <- nam_lim
+    colnames(perc_CI) <- nam_lim
+    colnames(rev_perc_CI) <- nam_lim
+    BCa_CI <- bcanon(df_b, est_b, est_boot_val,p, nb_est)
+    colnames(BCa_CI) <- nam_lim
     all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI, BCa = BCa_CI)
@@
 ```{r}
-cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(as.vector(t(res1$Estimations[1,]))), "\n - for the volume of trees:", mean(as.vector(t(res1$Estimations[2,]))), "\n - for the ratio volume / number of trees:", mean(as.vector(t(res1$Estimations[3,]))))
+cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(as.vector(res1$Estimations[1,])), "\n - for the volume of trees:", mean(as.vector(res1$Estimations[2,])), "\n - for the ratio volume / number of trees:", mean(as.vector(res1$Estimations[3,])),
+    "\n\n - for the number of small trees:", mean(as.vector(res1$Estimations[4,])), "\n - for the volume of small trees:", mean(as.vector(res1$Estimations[5,])), "\n - for the ratio volume / number of trees:", mean(as.vector(res1$Estimations[6,])),
+    "\n\n - for the number of medium trees:", mean(as.vector(res1$Estimations[7,])), "\n - for the volume of medium trees:", mean(as.vector(res1$Estimations[8,])), "\n - for the ratio volume / number of trees:", mean(as.vector(res1$Estimations[9,])),
+    "\n\n - for the number of big trees:", mean(as.vector(res1$Estimations[10,])), "\n - for the volume of big trees:", mean(as.vector(res1$Estimations[11,])), "\n - for the ratio volume / number of trees:", mean(as.vector(res1$Estimations[12,]))
+    )
 

### 2024-08-08 All_param.Rmd
Pb in f_boot

@@
 # Adapted for our particular problem
-bcanon <- function(df_init,est_init,est_boot_val,p,nb_est,alpha =
+bcanon <- function(df_init,est_init,est_boot_val,p,nb_var,alpha =
                      c(.025,.975)) { 
@@
         # u <- rbind(u, c(sum(x_i[3]/p), sum(x_i[4]/p)))
-        u <- rbind(u, as.vector(mapply(function(j){mapply(sum(x_i[j]/p))}, 1:nb_est)))
+        u <- rbind(u, as.vector(mapply(function(j){mapply(sum(x_i[j]/p))}, 3:nb_var)))
     }
-    u <- cbind(u, mapply(function(x,y){x/y}, u[2], u[1]))
+    # u <- cbind(u, mapply(function(x,y){x/y}, u[2], u[1]))
+    u <- cbind(u, mapply(function(j){mapply(function(x,y){x/y}, u[j+4], u[j])}, 3:6) )
     uu <- as.data.frame( mapply(function(some_vec){mean(some_vec)-some_vec}, u) )
@@
     colnames(rev_perc_CI) <- nam_lim
-    BCa_CI <- bcanon(df_b, est_b, est_boot_val,p, nb_est)
+    BCa_CI <- bcanon(df_b, est_b, est_boot_val,p, nb_var)
     colnames(BCa_CI) <- nam_lim

### 2024-08-08 All_param.Rmd
Pb in f_boot bis

@@
 f_boot <- function(df_sample, B, nb_est){
-  # df_sample: initial sample with 4 variables and of size n; 
+  # df_sample: initial sample with nb_est variables and of size n; 
   # B: number of bootstrap samples made thanks to df_sample
@@
     df_boot <- cbind(df_boot, sample_b)
-    colnames(df_boot)[((b-1)*4+1 + 1):(b*4+1)] <- as.vector(mapply(function(j){paste("ech", b, colnames(df_sample)[j], sep = "")}, 1:nb_est))
+    colnames(df_boot)[((b-1)*(nb_var+2)+1 + 1):(b*(nb_var+2)+1)] <- as.vector(mapply(function(j){paste("ech", b, colnames(df_sample)[j], sep = "")}, 1:nb_est))
       # c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""))
@@
   n <- nrow(df) + 1 # sample size of the initial sample
-  nboot <- length(df)/4 # number of bootstrap samples
+  nboot <- length(df)/(nb_var+2) # number of bootstrap samples
   vec_est1 <- c()
@@
   for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + (4*(c-1))]/p))
-    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,4*c]/p))
-    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,4*c]/p))/((n/(n-1))*sum(df[,3 + (4*(c-1))]/p)))
+    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p))
+    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,(nb_var+2)*c]/p))
+    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,(nb_var+2)*c]/p))/((n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p)))
     # (n/(n-1)) is the correction needed since we choose only (n-1) points
@@
 
-    colnames(df_b)[((nb_var+2)*(b-1)+2):((nb_var+2)*(b)+2-1)] <- 
+    colnames(df_b)[((nb_var+2)*(b-1)+1):((nb_var+2)*(b)-1)] <- 
       c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("nb_s.MC", b, sep = ""), paste("nb_m.MC", b, sep = ""), paste("nb_b.MC", b, sep = ""), paste("vol.MC", b, sep = ""), paste("vol_s.MC", b, sep = ""), paste("vol_m.MC", b, sep = ""), paste("vol_b.MC", b, sep = ""))
-    from_local <- function(j){sum(df_b[(nb_var+2)*(b-1)+3+j] /p)}
+    from_local <- function(j){sum(df_b[(nb_var+2)*(b-1)+2+j] /p)}
     est_b <- data.frame(from_local(1), from_local(5), (from_local(5))/(from_local(1)), from_local(2), from_local(6), (from_local(6))/(from_local(2)), 
@@
     nb_est <- length(est_b) # number of estimations
-    rownames(MC_est)[b] <- paste("ech", b, sep = "")
+    rownames(est_b)[b] <- paste("ech", b, sep = "")
 

### 2024-08-08 All_param.Rmd
Need to extend est_boot

@@
 ## Making of bootstrap samples based on an initial sample
-f_boot <- function(df_sample, B, nb_est){
+f_boot <- function(df_sample, B, nb_var){
   # df_sample: initial sample with nb_est variables and of size n; 
@@
     df_boot <- cbind(df_boot, sample_b)
-    colnames(df_boot)[((b-1)*(nb_var+2)+1 + 1):(b*(nb_var+2)+1)] <- as.vector(mapply(function(j){paste("ech", b, colnames(df_sample)[j], sep = "")}, 1:nb_est))
+    colnames(df_boot)[((b-1)*(nb_var+2)+1 + 1):(b*(nb_var+2)+1)] <- as.vector(mapply(function(j){paste("ech", b, colnames(df_sample)[j], sep = "")}, 1:(nb_var+2)))
       # c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""))
@@
 ## Making of estimations for each sample made by the bootstrap method
-est_boot <- function(df, p){
-  # df: data frame with 4*B columns and (n-1) rows
+est_boot <- function(df, p, nb_var){
+  # df: data frame with (nb_var+2)*B columns and (n-1) rows
   # p: inclusion density function (constant in the uniform case)
@@
 
-    colnames(df_b)[((nb_var+2)*(b-1)+1):((nb_var+2)*(b)-1)] <- 
+    colnames(df_b)[((nb_var+2)*(b-1)+1):((nb_var+2)*(b))] <- 
       c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("nb_s.MC", b, sep = ""), paste("nb_m.MC", b, sep = ""), paste("nb_b.MC", b, sep = ""), paste("vol.MC", b, sep = ""), paste("vol_s.MC", b, sep = ""), paste("vol_m.MC", b, sep = ""), paste("vol_b.MC", b, sep = ""))
@@
 
-    # colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
-    # est_b <- t(data.frame(x = sum(df_b[3] /p), y = sum(df_b[4] /p), z = (sum(df_b[4] /p))/(sum(df_b[3]/p))))
-
     # Bootstrap iterations
-    df_boot <- f_boot(df_b, B2, nb_est)
-    est_boot_val <- est_boot(df_boot, p)
+    df_boot <- f_boot(df_b, B2, nb_var)
+    est_boot_val <- est_boot(df_boot, p, nb_var)
 

### 2024-08-08 All_param.Rmd
est_boot not finished

@@
   vec_est3 <- c()
+  # big_vec <- rep(c(), 12)
   for (c in 1:nboot) {
+    # mapply(function(vec_, c){append(vec_, (n/(n-1))*sum(df[, 2 + c + ((nb_var+2)*(c-1))]/p))}, big_vec, )
     vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p))

### 2024-08-09 All_param.Rmd
est_boot not good yet

--- 2024-08-08 All_param.Rmd
@@
   vec_est3 <- c()
+  big_est <- as.data.frame(matrix(NA, ncol = nb_var, nrow = nboot))
+
+  # Estimations of totals
   for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p))
-    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,(nb_var+2)*c]/p))
-    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,(nb_var+2)*c]/p))/((n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p)))
+    big_est <- mapply(function(vec_, j){
+        vec_[c] <- (n/(n-1))*sum(df[, 2 + j + ((nb_var+2)*(c-1))]/p)
+        return(as.data.frame(vec_))
+        }, big_est, 1:nb_var)
     # (n/(n-1)) is the correction needed since we choose only (n-1) points
+
+        # big_est2 <- mapply(function(vec_, j){
+        # vec_[c] <- (n/(n-1))*sum(df[, 2 + j + ((nb_var+2)*(c-1))]/p)
+        # return(as.data.frame(vec_))
+        # }, big_est2, 1:nb_var) 
+    # mapply(function(vec_, c){append(vec_, (n/(n-1))*sum(df[, 2 + c + ((nb_var+2)*(c-1))]/p))}, big_vec, 1:nboot)
+    # vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p))
+    # vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,(nb_var+2)*c]/p))
+    # vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,(nb_var+2)*c]/p))/((n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p)))
   }
-  vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
-  return(vec_est)
+  # Estimations of ratios
+  l_big_est <- length(big_est)
+  big_est <- as.data.frame(big_est)
+  for (k in 1:4) {
+    big_est <- add_column(big_est, rep(NA, nrow(big_est)))
+  }
+  big_est2 <- big_est
+  for (c in 1:nboot) {
+    # add_column()
+    big_est2 <- mapply(function(j){big_est2[c, l_big_est+j] <- big_est2[c,j+4]/big_est2[c,j]
+      return(as.data.frame(big_est2))
+    }, 1) # 4 ratios
+    # big_est2[l_big_est+1] <- big_est2[c,1]/big_est2[c,1+4]
+
+    test <- function(j){big_est2[c, l_big_est+j] <- big_est2[c,j+4]/big_est2[c,j]     
+    return(as.data.frame(big_est2))
+    }
+  }
+  big_est <- t(big_est)
+  colnames(big_est) <- c("est_nb", "est_nb_s","est_nb_m", "est_nb_b", "est_vol", "est_vol_s", "est_vol_m", "est_vol_b")
+  # vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
+  return(big_est)
   # Data frame with 3 estimations for each sample

### 2024-08-09 All_param.Rmd
Work to do on bcanon

--- 2024-08-08 All_param.Rmd
@@
   for (b in 1:B) { # All in one "for" loop
-    print(b) ### To delete in the end!!! 
+    # print(b) ### To delete in the end!!! 
     # Uniform sampling over the whole territory
@@
   nboot <- length(df)/(nb_var+2) # number of bootstrap samples
-  vec_est1 <- c()
-  vec_est2 <- c()
-  vec_est3 <- c()
+  big_est <- as.data.frame(matrix(NA, ncol = nb_var, nrow = nboot))
+
+  # Estimations of totals
   for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p))
-    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,(nb_var+2)*c]/p))
-    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,(nb_var+2)*c]/p))/((n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p)))
+    big_est <- mapply(function(vec_, j){
+        vec_[c] <- (n/(n-1))*sum(df[, 2 + j + ((nb_var+2)*(c-1))]/p)
+        return(as.data.frame(vec_))
+        }, big_est, 1:nb_var)
     # (n/(n-1)) is the correction needed since we choose only (n-1) points
+
+        # big_est2 <- mapply(function(vec_, j){
+        # vec_[c] <- (n/(n-1))*sum(df[, 2 + j + ((nb_var+2)*(c-1))]/p)
+        # return(as.data.frame(vec_))
+        # }, big_est2, 1:nb_var) 
   }
-  vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
-  return(vec_est)
+  # Estimations of ratios
+  l_big_est <- length(big_est)
+  big_est <- as.data.frame(big_est)
+  for (k in 1:4) {
+    big_est <- add_column(big_est, rep(NA, nrow(big_est)))
+  }
+  for (c in 1:nboot) {
+    ratio_c <- mapply(function(j){big_est[c,j+4]/big_est[c,j]
+      # return(as.data.frame(big_est2))
+    }, 1:4) # 4 ratios
+    big_est[c, (l_big_est+1):(l_big_est+4) ] <- ratio_c
+    # as.data.frame(split(as.data.frame(big_est2), ","))
+    # big_est2[c, j] <- 
+    # big_est2[l_big_est+1] <- big_est2[c,1]/big_est2[c,1+4]
+    }
+  colnames(big_est) <- c("est_nb", "est_nb_s","est_nb_m", "est_nb_b", "est_vol", "est_vol_s", "est_vol_m", "est_vol_b", "est_ratio", "est_ratio_s", "est_ratio_m", "est_ratio_b")
+  # vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
+  return(big_est)
   # Data frame with 3 estimations for each sample
@@
     from_local <- function(j){sum(df_b[(nb_var+2)*(b-1)+2+j] /p)}
-    est_b <- data.frame(from_local(1), from_local(5), (from_local(5))/(from_local(1)), from_local(2), from_local(6), (from_local(6))/(from_local(2)), 
-                           from_local(3), from_local(7), (from_local(7))/(from_local(3)), from_local(4), from_local(8), (from_local(8))/(from_local(4)))
+    # est_b <- data.frame(from_local(1), from_local(5), (from_local(5))/(from_local(1)), from_local(2), from_local(6), (from_local(6))/(from_local(2)), 
+    #                        from_local(3), from_local(7), (from_local(7))/(from_local(3)), from_local(4), from_local(8), (from_local(8))/(from_local(4)))
+    est_b <- data.frame(from_local(1), from_local(2), from_local(3), from_local(4), from_local(5), from_local(6), from_local(7), from_local(8), 
+                        (from_local(5))/(from_local(1)), (from_local(6))/(from_local(2)), 
+                        (from_local(7))/(from_local(3)), (from_local(8))/(from_local(4)))
     nb_est <- length(est_b) # number of estimations
@@
       perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
-      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_b[l,]*2 - lim_sup, est_b[l,]*2 - lim_inf)))
-      norm_CI <- cbind(norm_CI, data.frame(c(est_b[l,]-qnorm(0.975)*sqrt(var(est_boot_val[,l])), est_b[l,]+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
+      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(as.numeric(est_b[l])*2 - lim_sup, as.numeric(est_b[l])*2 - lim_inf)))
+      norm_CI <- cbind(norm_CI, data.frame(c(as.numeric(est_b[l])-qnorm(0.975)*sqrt(var(est_boot_val[,l])), as.numeric(est_b[l])+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
     }
@@
     rev_perc_CI$useless <- NULL
-    nam_lim <- c("lim_nb", "lim_vol", "lim_ratio", "lim_nb_s", "lim_vol_s", "lim_ratio_s", 
-                 "lim_nb_m", "lim_vol_m", "lim_ratio_m", 
-                 "lim_nb_b", "lim_vol_b", "lim_ratio_b")
+    nam_lim <- c("lim_nb", "lim_nb_s", "lim_nb_m", "lim_nb_b", 
+                 "lim_vol", "lim_vol_s", "lim_vol_m", "lim_vol_b", 
+                 "lim_ratio", "lim_ratio_s", "lim_ratio_m", "lim_ratio_b")
     colnames(norm_CI) <- nam_lim
@@
     colnames(rev_perc_CI) <- nam_lim
-    BCa_CI <- bcanon(df_b, est_b, est_boot_val,p, nb_var)
+    BCa_CI <- bcanon(df_b, est_b, est_boot_val, p, nb_var)
     colnames(BCa_CI) <- nam_lim

### 2024-08-12 All_param.Rmd
Still a long way to go

@@
 
-    z0 <- mapply(function(one, long){qnorm(sum(long<one)/nboot)}, t(est_init),est_boot_val)
+    z0 <- mapply( function(j){qnorm(sum(mapply(function(long){long<est_init[,j]},est_boot_val[,j]))/nboot)} , 1:12) # length: nb_est
+    # Same as: mapply(function(one, long){qnorm(sum(long<one)/nboot)}, t(est_init),est_boot_val)
+      # qnorm(sum(mapply(function(one, long){long<one}, t(est_init),est_boot_val))/nboot)
 
-    u <- data.frame(x = numeric(), y = numeric())
+    u <- data.frame(replicate(nb_var, numeric(0)))
     for(i in 1:n){
@@
         # u <- rbind(u, c(sum(x_i[3]/p), sum(x_i[4]/p)))
-        u <- rbind(u, as.vector(mapply(function(j){mapply(sum(x_i[j]/p))}, 3:nb_var)))
+        u <- rbind(u, as.vector(mapply(function(j){sum(x_i[,j]/p)}, 3:(nb_var+2))))
     }
     # u <- cbind(u, mapply(function(x,y){x/y}, u[2], u[1]))
-    u <- cbind(u, mapply(function(j){mapply(function(x,y){x/y}, u[j+4], u[j])}, 3:6) )
+    u <- cbind(u, mapply(function(j){mapply(function(x,y){x/y}, u[j+4], u[j])}, 1:3) )
     uu <- as.data.frame( mapply(function(some_vec){mean(some_vec)-some_vec}, u) )

### 2024-08-12 All_param.Rmd
Ready to knit I hope

@@
     # u <- cbind(u, mapply(function(x,y){x/y}, u[2], u[1]))
-    u <- cbind(u, mapply(function(j){mapply(function(x,y){x/y}, u[j+4], u[j])}, 1:3) )
+    u <- cbind(u, mapply(function(j){mapply(function(x,y){x/y}, u[j+4], u[j])}, 1:4) )
     uu <- as.data.frame( mapply(function(some_vec){mean(some_vec)-some_vec}, u) )
@@
 
-    colnames(df_b)[((nb_var+2)*(b-1)+1):((nb_var+2)*(b))] <- 
+    # [((nb_var+2)*(b-1)+1):((nb_var+2)*(b))]
+    colnames(df_b) <- 
       c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("nb_s.MC", b, sep = ""), paste("nb_m.MC", b, sep = ""), paste("nb_b.MC", b, sep = ""), paste("vol.MC", b, sep = ""), paste("vol_s.MC", b, sep = ""), paste("vol_m.MC", b, sep = ""), paste("vol_b.MC", b, sep = ""))
-    from_local <- function(j){sum(df_b[(nb_var+2)*(b-1)+2+j] /p)}
+    from_local <- function(j){sum(df_b[2+j] /p)} # (nb_var+2)*(b-1)
     # est_b <- data.frame(from_local(1), from_local(5), (from_local(5))/(from_local(1)), from_local(2), from_local(6), (from_local(6))/(from_local(2)), 
@@
     nb_est <- length(est_b) # number of estimations
-    rownames(est_b)[b] <- paste("ech", b, sep = "")
+    rownames(est_b) <- paste("ech", b, sep = "")
 

### 2024-08-12 All_param.Rmd
Cleaner file before knit

--- 2024-08-09 All_param.Rmd
@@
   for (b in 1:B) { # All in one "for" loop
-    # print(b) ### To delete in the end!!! 
     # Uniform sampling over the whole territory
@@
 
-    z0 <- mapply(function(one, long){qnorm(sum(long<one)/nboot)}, t(est_init),est_boot_val)
+    # Bias-correction
+    z0 <- mapply( function(j){qnorm(sum(mapply(function(long){long<est_init[,j]},est_boot_val[,j]))/nboot)} , 1:12)
+    # Same as: mapply(function(one, long){qnorm(sum(long<one)/nboot)}, t(est_init),est_boot_val)
 
-    u <- data.frame(x = numeric(), y = numeric())
+    # Acceleration
+    u <- data.frame(replicate(nb_var, numeric(0)))
     for(i in 1:n){
         x_i <- df_init[-i,]
-        # u <- rbind(u, c(sum(x_i[3]/p), sum(x_i[4]/p)))
-        u <- rbind(u, as.vector(mapply(function(j){mapply(sum(x_i[j]/p))}, 3:nb_var)))
+        u <- rbind(u, as.vector(mapply(function(j){sum(x_i[,j]/p)}, 3:(nb_var+2))))
     }
-    # u <- cbind(u, mapply(function(x,y){x/y}, u[2], u[1]))
-    u <- cbind(u, mapply(function(j){mapply(function(x,y){x/y}, u[j+4], u[j])}, 3:6) )
+    u <- cbind(u, mapply(function(j){mapply(function(x,y){x/y}, u[j+4], u[j])}, 1:4) )
     uu <- as.data.frame( mapply(function(some_vec){mean(some_vec)-some_vec}, u) )
@@
     colnames(df_boot)[((b-1)*(nb_var+2)+1 + 1):(b*(nb_var+2)+1)] <- as.vector(mapply(function(j){paste("ech", b, colnames(df_sample)[j], sep = "")}, 1:(nb_var+2)))
-      # c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""))
   }
@@
     # (n/(n-1)) is the correction needed since we choose only (n-1) points
-
-        # big_est2 <- mapply(function(vec_, j){
-        # vec_[c] <- (n/(n-1))*sum(df[, 2 + j + ((nb_var+2)*(c-1))]/p)
-        # return(as.data.frame(vec_))
-        # }, big_est2, 1:nb_var) 
   }
@@
     ratio_c <- mapply(function(j){big_est[c,j+4]/big_est[c,j]
-      # return(as.data.frame(big_est2))
     }, 1:4) # 4 ratios
     big_est[c, (l_big_est+1):(l_big_est+4) ] <- ratio_c
-    # as.data.frame(split(as.data.frame(big_est2), ","))
-    # big_est2[c, j] <- 
-    # big_est2[l_big_est+1] <- big_est2[c,1]/big_est2[c,1+4]
     }
   colnames(big_est) <- c("est_nb", "est_nb_s","est_nb_m", "est_nb_b", "est_vol", "est_vol_s", "est_vol_m", "est_vol_b", "est_ratio", "est_ratio_s", "est_ratio_m", "est_ratio_b")
-  # vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
   return(big_est)
@@
 
-    colnames(df_b)[((nb_var+2)*(b-1)+1):((nb_var+2)*(b))] <- 
+    colnames(df_b) <- 
       c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("nb_s.MC", b, sep = ""), paste("nb_m.MC", b, sep = ""), paste("nb_b.MC", b, sep = ""), paste("vol.MC", b, sep = ""), paste("vol_s.MC", b, sep = ""), paste("vol_m.MC", b, sep = ""), paste("vol_b.MC", b, sep = ""))
-    from_local <- function(j){sum(df_b[(nb_var+2)*(b-1)+2+j] /p)}
-    # est_b <- data.frame(from_local(1), from_local(5), (from_local(5))/(from_local(1)), from_local(2), from_local(6), (from_local(6))/(from_local(2)), 
-    #                        from_local(3), from_local(7), (from_local(7))/(from_local(3)), from_local(4), from_local(8), (from_local(8))/(from_local(4)))
+    from_local <- function(j){sum(df_b[2+j] /p)} # (nb_var+2)*(b-1)
     est_b <- data.frame(from_local(1), from_local(2), from_local(3), from_local(4), from_local(5), from_local(6), from_local(7), from_local(8), 

### 2024-08-12 All_param.Rmd
Better All_param

@@
 
+  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
   p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
 
-  MC_df <- data.frame(useless = rep(0, n))
+  # MC_df <- data.frame(useless = rep(0, n))
+  MC_df <- data.frame(matrix(numeric(0), nrow = n))
   MC_est <- data.frame()
@@
     MC_df <- cbind(MC_df, xy, var)
-    colnames(MC_df)[((nb_var+2)*(b-1)+2):((nb_var+2)*(b)+2-1)] <- c(paste("x", b, sep = ""), paste("y", b, sep = ""), paste("nb", b, sep = ""), paste("nb_s", b, sep = ""), paste("nb_m", b, sep = ""), paste("nb_b", b, sep = ""), paste("vol", b, sep = ""), paste("vol_s", b, sep = ""), paste("vol_m", b, sep = ""), paste("vol_b", b, sep = ""))
+    colnames(MC_df)[((nb_var+2)*(b-1)+2):((nb_var+2)*(b)+2-1)] <- paste0(raw_names, b)[-(11:14)]
     from_local <- function(j){sum(MC_df[(nb_var+2)*(b-1)+3+j] /p)}
@@
   }
-  MC_df$useless <- NULL
+  # MC_df$useless <- NULL
   MC_est <- t(MC_est)
@@
 
+  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
   n <- nrow(df) + 1 # sample size of the initial sample
@@
   }
-  colnames(big_est) <- c("est_nb", "est_nb_s","est_nb_m", "est_nb_b", "est_vol", "est_vol_s", "est_vol_m", "est_vol_b", "est_ratio", "est_ratio_s", "est_ratio_m", "est_ratio_b")
+  colnames(big_est) <- paste0("est_", raw_names)[-(1:2)]
   return(big_est)
@@
 
+  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
   p <- sum(rep((1/1000)*(1/1000), n))
@@
     # Variables of interest derived from the sample
-    var <- as.data.frame(t(mapply(circle_ALL_, xy$a1, xy$a2)))
-    nb_var <- length(var) # number of variables of interest
-    df_b <- cbind(xy, var)
+    all_var <- as.data.frame(t(mapply(circle_ALL_, xy$a1, xy$a2)))
+    nb_var <- length(all_var) # number of variables of interest
+    df_b <- cbind(xy, all_var)
 
-    colnames(df_b) <- 
-      c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("nb_s.MC", b, sep = ""), paste("nb_m.MC", b, sep = ""), paste("nb_b.MC", b, sep = ""), paste("vol.MC", b, sep = ""), paste("vol_s.MC", b, sep = ""), paste("vol_m.MC", b, sep = ""), paste("vol_b.MC", b, sep = ""))
+    colnames(df_b) <- paste0(raw_names, ".MC", b)[-(11:14)]
+      # c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("nb_s.MC", b, sep = ""), paste("nb_m.MC", b, sep = ""), paste("nb_b.MC", b, sep = ""), paste("vol.MC", b, sep = ""), paste("vol_s.MC", b, sep = ""), paste("vol_m.MC", b, sep = ""), paste("vol_b.MC", b, sep = ""))
     from_local <- function(j){sum(df_b[2+j] /p)} # (nb_var+2)*(b-1)
@@
 
-    BOOT_var[[b]] <- list(var_nb = var(est_boot_val$est_nb), var_vol = var(est_boot_val$est_vol), var_ratio = var(est_boot_val$est_ratio))
+    BOOT_var[[b]] <- mapply(var, est_boot_val)
+      # list(var_nb = var(est_boot_val$est_nb), var_vol = var(est_boot_val$est_vol), var_ratio = var(est_boot_val$est_ratio))
     names(BOOT_var)[b] <- paste("Variance", b, sep = "")
@@
     rev_perc_CI$useless <- NULL
-    nam_lim <- c("lim_nb", "lim_nb_s", "lim_nb_m", "lim_nb_b", 
-                 "lim_vol", "lim_vol_s", "lim_vol_m", "lim_vol_b", 
-                 "lim_ratio", "lim_ratio_s", "lim_ratio_m", "lim_ratio_b")
+    test <- paste0("lim_", raw_names)[-(1:2)]
+    # nam_lim <- c("lim_nb", "lim_nb_s", "lim_nb_m", "lim_nb_b", 
+    #              "lim_vol", "lim_vol_s", "lim_vol_m", "lim_vol_b", 
+    #              "lim_ratio", "lim_ratio_s", "lim_ratio_m", "lim_ratio_b")
     colnames(norm_CI) <- nam_lim

### 2024-08-12 All_param.Rmd
Small modifications

@@
 
-  # MC_df <- data.frame(useless = rep(0, n))
   MC_df <- data.frame(matrix(numeric(0), nrow = n))
@@
     # Variables of interest derived from the sample
-    var <- as.data.frame(t(mapply(circle_ALL_, xy$a1, xy$a2)))
-    nb_var <- length(var) # number of variables of interest
-    MC_df <- cbind(MC_df, xy, var)
-    colnames(MC_df)[((nb_var+2)*(b-1)+2):((nb_var+2)*(b)+2-1)] <- paste0(raw_names, b)[-(11:14)]
-    from_local <- function(j){sum(MC_df[(nb_var+2)*(b-1)+3+j] /p)}
-    est_b <- data.frame(from_local(1), from_local(5), (from_local(5))/(from_local(1)), from_local(2), from_local(6), (from_local(6))/(from_local(2)), 
-                           from_local(3), from_local(7), (from_local(7))/(from_local(3)), from_local(4), from_local(8), (from_local(8))/(from_local(4)))
+    all_var <- as.data.frame(t(mapply(circle_ALL_, xy$a1, xy$a2)))
+    nb_var <- length(all_var) # number of variables of interest
+    MC_df <- cbind(MC_df, xy, all_var)
+    colnames(MC_df)[((nb_var+2)*(b-1)+1):((nb_var+2)*(b))] <- paste0(raw_names, b)[-(11:14)]
+    from_local <- function(j){sum(MC_df[(nb_var+2)*(b-1)+2+j] /p)}
+    est_b <- append(as.vector(mapply(from_local, 1:8)), as.vector(mapply(function(j){(from_local(j+4))/(from_local(j))}, 1:4)))
     nb_est <- length(est_b) # number of estimations
@@
   }
-  # MC_df$useless <- NULL
-  MC_est <- t(MC_est)
-  row.names(MC_est) <- NULL
-  var_est <- function(j){var(as.vector(MC_est[j,]))}
+
+  var_est <- function(j){var(as.vector(MC_est[,j]))}
   MC_var <- mapply(var_est, 1:nb_est)
+  MC_var <- t(as.data.frame(MC_var))
+  colnames(MC_est) <- paste0("est_", raw_names)[-(1:2)]
+  colnames(MC_var) <- paste0("var_", raw_names)[-(1:2)]
+  row.names(MC_var) <- NULL
 
@@
 ```{r}
-## BCa nonparametric
+## Nonparametric BCa
 # Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
@@
     colnames(df_b) <- paste0(raw_names, ".MC", b)[-(11:14)]
-      # c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("nb_s.MC", b, sep = ""), paste("nb_m.MC", b, sep = ""), paste("nb_b.MC", b, sep = ""), paste("vol.MC", b, sep = ""), paste("vol_s.MC", b, sep = ""), paste("vol_m.MC", b, sep = ""), paste("vol_b.MC", b, sep = ""))
     from_local <- function(j){sum(df_b[2+j] /p)} # (nb_var+2)*(b-1)
@@
     nb_est <- length(est_b) # number of estimations
-    rownames(est_b) <- paste("ech", b, sep = "")
+    rownames(est_b) <- paste0("ech", b)
+    colnames(est_b) <- paste0("est_", b)
 
@@
     BOOT_var[[b]] <- mapply(var, est_boot_val)
-      # list(var_nb = var(est_boot_val$est_nb), var_vol = var(est_boot_val$est_vol), var_ratio = var(est_boot_val$est_ratio))
     names(BOOT_var)[b] <- paste("Variance", b, sep = "")
@@
     rev_perc_CI$useless <- NULL
-    test <- paste0("lim_", raw_names)[-(1:2)]
-    # nam_lim <- c("lim_nb", "lim_nb_s", "lim_nb_m", "lim_nb_b", 
-    #              "lim_vol", "lim_vol_s", "lim_vol_m", "lim_vol_b", 
-    #              "lim_ratio", "lim_ratio_s", "lim_ratio_m", "lim_ratio_b")
+    nam_lim <- paste0("lim_", raw_names)[-(1:2)]
     colnames(norm_CI) <- nam_lim
@@
     BOOT_CI[[b]] <- all_CI
-    names(BOOT_CI)[b] <- paste("CI", b, sep = "")
+    names(BOOT_CI)[b] <- paste0("CI", b)
   }

### 2024-08-12 All_param.Rmd
Work to do on EST with MC_boot

@@
 for (elt in res2$Estimations) {
-  if ("data.frame" %in% class(elt)){ # we target bootstrap samples made from each MC iteration
+  if (grepl("boot", names(elt)) ){ # we target bootstrap samples made from each MC iteration
     EST_nb <- append(EST_nb, mean(elt$est_nb))
@@
 ```{r}
-diff_percent <- function(x,y)100*(max(x,y)-min(x,y))/min(x,y)
-cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(res1$Variances[1], mean(VAR_nb)), "%", "\n - for the volume of trees: ", diff_percent(res1$Variances[2], mean(VAR_vol)), "%\n - for the ratio volume / number of trees: ", diff_percent(res1$Variances[3], mean(VAR_ratio)), "%", sep = "")
+diff_percent <- function(x,y){100*(max(res1$Variances[x],mean(y))-min(res1$Variances[x],mean(y)))/min(res1$Variances[x],mean(y))}
+cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1, VAR_nb), "%", "\n - for the volume of trees: ", diff_percent(2, VAR_vol), "%\n - for the ratio volume / number of trees: ", diff_percent(3, VAR_ratio), "%", sep = "")
 

### 2024-08-13 All_param.Rmd
CI more general

@@
 
-    BOOT_var[[b]] <- mapply(var, est_boot_val)
+    BOOT_var[[b]] <- as.data.frame(mapply(var, est_boot_val))
     names(BOOT_var)[b] <- paste("Variance", b, sep = "")
@@
     colnames(BCa_CI) <- nam_lim
-    all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI, BCa = BCa_CI)
+    all_CI <- list(Normal = as.data.frame(norm_CI), Percentile = as.data.frame(perc_CI), `Reverse percentile` = as.data.frame(rev_perc_CI), BCa = as.data.frame(BCa_CI))
     BOOT_CI[[b]] <- all_CI
@@
 
-res1 <- MonteCarlo(n, 10000)
+# res1 <- MonteCarlo(n, 10000)
+res1 <- MonteCarlo(n, 10)
 # Just one circle to begin with
@@
 
-res2 <- MC_boot(n, B1 = 1000, B2 = 400)
+# res2 <- MC_boot(n, B1 = 1000, B2 = 400)
+res2 <- MC_boot(n, B1 = 10, B2 = 4)
 # Just one circle to begin with
@@
 for (elt in res2$Estimations) {
-  if (grepl("boot", names(elt)) ){ # we target bootstrap samples made from each MC iteration
+  if ( nrow(elt) != 1){ # we target bootstrap samples made from each MC iteration
     EST_nb <- append(EST_nb, mean(elt$est_nb))
@@
 coverage_rate <- function(k){
-  CI_nb <- data.frame(useless = c(0,0))
-  CI_vol <- data.frame(useless = c(0,0))
-  CI_ratio <- data.frame(useless = c(0,0))
-  for (elt in res2$`Confidence Intervals`) {
-    CI_nb <- cbind(CI_nb, c(unlist(elt[k])[1], unlist(elt[k])[2]))
-    CI_vol <- cbind(CI_vol, c(unlist(elt[k])[3], unlist(elt[k])[4]))
-    CI_ratio <- cbind(CI_ratio, c(unlist(elt[k])[5], unlist(elt[k])[6]))
+  # k: integer to target one specific method to create confidence intervals
+
+  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
+  CI_names <- paste0("CI_", raw_names)[-(1:2)]
+  TC_names <- paste0("TC_", raw_names)[-(1:2)]
+  low_names <- paste0("low_", raw_names)[-(1:2)]
+  up_names <- paste0("up_", raw_names)[-(1:2)]
+  length_names <- paste0("length_", raw_names)[-(1:2)]
+
+  real_val <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
+  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
+  sum(trees$v)/nrow(trees), sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),])
+  )
+
+  for (j in CI_names) {
+    assign(j, data.frame(matrix(numeric(0), nrow = 2)))
   }
-  CI_nb$useless <- NULL
-  CI_vol$useless <- NULL
-  CI_ratio$useless <- NULL
+  # CI_nb <- data.frame(matrix(numeric(0), nrow = 2))
+  # CI_vol <- data.frame(matrix(numeric(0), nrow = 2))
+  # CI_ratio <- data.frame(matrix(numeric(0), nrow = 2))
+  for (elt in res2$`Confidence Intervals`) { # For each MC iteration
+    for (j in CI_names) { # For each estimation
+      x <- cbind(get(x = j), elt[k])
+      assign(j, x)
+    }
+    # elt2 <- as.data.frame(elt[k])
+    # CI_nb <- cbind(CI_nb, elt2[k])
+      # cbind(CI_nb2, c(elt2[k][1,], elt2[k][2,]))
 
-  CI_nb <- as.data.frame(t(CI_nb))
-  CI_vol <- as.data.frame(t(CI_vol))
-  CI_ratio <- as.data.frame(t(CI_ratio))
+    # CI_nb <- cbind(CI_nb, c(unlist(elt[k])[1], unlist(elt[k])[2]))
+    # CI_vol <- cbind(CI_vol, c(unlist(elt[k])[3], unlist(elt[k])[4]))
+    # CI_ratio <- cbind(CI_ratio, c(unlist(elt[k])[5], unlist(elt[k])[6]))
+  }
+
+  TC <- c()
+  Lower <- c()
+  Upper <- c()
+  Mean_length <- c()
+  for (j in 1:(length(CI_names))) {
+    x <- as.data.frame(t(get(x = CI_names[j])))
+    # Coverage rate
+    assign( TC_names[j], (1/nrow(x))*sum( mapply(function(a,b){as.numeric((real_val[j] > a) & (real_val[j] < b))}, x[1], x[2]) ))
+    TC <- append(TC, get(TC_names[j]))
+    # Lower tail
+    assign( low_names[j], (1/nrow(x))*sum( mapply(function(a){as.numeric(real_val[j] < a)}, x[1]) ))
+    Lower <- append(Lower, get(low_names[j]))
+    # Upper tail
+    assign( up_names[j], (1/nrow(x))*sum( mapply(function(b){as.numeric(real_val[j] > b)}, x[2]) ))
+    Upper <- append(Upper, get(up_names[j]))
+    # Mean length of CIs
+    assign( length_names[j], (1/nrow(x))*sum( mapply(function(a,b){b-a}, x[1], x[2]) ))
+    Mean_length <- append(Mean_length, get(length_names[j]))
+  }
+  # CI_nb <- as.data.frame(t(CI_nb))
+  # CI_vol <- as.data.frame(t(CI_vol))
+  # CI_ratio <- as.data.frame(t(CI_ratio))
+
+  df_TC <- data.frame(TC, Lower, Upper, Mean_length)
+
+  return(df_TC)
+}
+```
+
+```{r eval=FALSE, include=FALSE}
+### DRAFT
 
@@
   df_TC <- data.frame(TC = c(TC_nb, TC_vol, TC_ratio), Upper = c(low_tail_nb, low_tail_vol, low_tail_ratio), Lower = c(up_tail_nb, up_tail_vol, up_tail_ratio), Mean_length = c(length_nb, length_vol, length_ratio))
-
-  return(df_TC)
-}
 ```

### 2024-08-13 All_param.Rmd
MC alone good

@@
 ```{r}
-cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(as.vector(res1$Estimations[1,])), "\n - for the volume of trees:", mean(as.vector(res1$Estimations[2,])), "\n - for the ratio volume / number of trees:", mean(as.vector(res1$Estimations[3,])),
-    "\n\n - for the number of small trees:", mean(as.vector(res1$Estimations[4,])), "\n - for the volume of small trees:", mean(as.vector(res1$Estimations[5,])), "\n - for the ratio volume / number of trees:", mean(as.vector(res1$Estimations[6,])),
-    "\n\n - for the number of medium trees:", mean(as.vector(res1$Estimations[7,])), "\n - for the volume of medium trees:", mean(as.vector(res1$Estimations[8,])), "\n - for the ratio volume / number of trees:", mean(as.vector(res1$Estimations[9,])),
-    "\n\n - for the number of big trees:", mean(as.vector(res1$Estimations[10,])), "\n - for the volume of big trees:", mean(as.vector(res1$Estimations[11,])), "\n - for the ratio volume / number of trees:", mean(as.vector(res1$Estimations[12,]))
+cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(unlist(res1$Estimations[1])), "\n - for the volume of trees:", mean(unlist(res1$Estimations[5])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[9])),
+    "\n\n - for the number of small trees:", mean(unlist(res1$Estimations[2])), "\n - for the volume of small trees:", mean(unlist(res1$Estimations[6])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[10])),
+    "\n\n - for the number of medium trees:", mean(unlist(res1$Estimations[3])), "\n - for the volume of medium trees:", mean(unlist(res1$Estimations[7])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[11])),
+    "\n\n - for the number of big trees:", mean(unlist(res1$Estimations[4])), "\n - for the volume of big trees:", mean(unlist(res1$Estimations[8])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[12]))
     )
@@
 ```{r}
-cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[2], "\n - for the ratio volume / number of trees:", res1$Variances[3])
+cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[5], "\n - for the ratio volume / number of trees:", res1$Variances[9],
+    "\n\n - for the number of small trees:", res1$Variances[2], "\n - for the volume of small trees:", res1$Variances[6], "\n - for the ratio volume / number of trees:", res1$Variances[10],
+    "\n\n - for the number of medium trees:", res1$Variances[3], "\n - for the volume of medium trees:", res1$Variances[7], "\n - for the ratio volume / number of trees:", res1$Variances[11],
+    "\n\n - for the number of big trees:", res1$Variances[4], "\n - for the volume of big trees:", res1$Variances[8], "\n - for the ratio volume / number of trees:", res1$Variances[12])
 

### 2024-08-13 All_param.Rmd
Ready to knit I hope

@@
     nb_est <- length(est_b) # number of estimations
-    rownames(est_b) <- paste0("ech", b)
-    colnames(est_b) <- paste0("est_", b)
+    colnames(est_b) <- paste0("est_", raw_names)[-(1:2)]
 
@@
 
-    BOOT_var[[b]] <- as.data.frame(mapply(var, est_boot_val))
+    BOOT_var[[b]] <- as.data.frame(t(mapply(var, est_boot_val)))
+    colnames(BOOT_var[[b]]) <- paste0("var_", raw_names)[-(1:2)]
     names(BOOT_var)[b] <- paste("Variance", b, sep = "")
@@
     # Confidence intervals
-    norm_CI <- data.frame(useless = rep(0, 2))
-    perc_CI <- data.frame(useless = rep(0, 2))
-    rev_perc_CI <- data.frame(useless = rep(0, 2))
+    norm_CI <- data.frame(matrix(numeric(0), nrow = 2))
+    perc_CI <- data.frame(matrix(numeric(0), nrow = 2))
+    rev_perc_CI <- data.frame(matrix(numeric(0), nrow = 2))
+    # norm_CI <- data.frame(useless = rep(0, 2))
+    # perc_CI <- data.frame(useless = rep(0, 2))
+    # rev_perc_CI <- data.frame(useless = rep(0, 2))
     for (l in 1:length(est_boot_val)) { # Loop: one estimator each time
@@
     }
-    norm_CI$useless <- NULL
-    perc_CI$useless <- NULL
-    rev_perc_CI$useless <- NULL
+    # norm_CI$useless <- NULL
+    # perc_CI$useless <- NULL
+    # rev_perc_CI$useless <- NULL
     nam_lim <- paste0("lim_", raw_names)[-(1:2)]
@@
 # to find the mean for each of these series
-EST_nb <- c()
-EST_vol <- c()
-EST_ratio <- c()
+raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
+EST_names <- paste0("EST_", raw_names)[-(1:2)]
+# est_names <- paste0("est_", raw_names)[-(1:2)]
+
+for (j in EST_names) {
+  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
+}
+
 for (elt in res2$Estimations) {
-  if ( nrow(elt) != 1){ # we target bootstrap samples made from each MC iteration
-    EST_nb <- append(EST_nb, mean(elt$est_nb))
-    EST_vol <- append(EST_vol, mean(elt$est_vol))
-    EST_ratio <- append(EST_ratio, mean(elt$est_ratio))
+  if ( nrow(elt) != 1 ){ # we target bootstrap samples made from each MC iteration
+    for (j in 1:length(EST_names)) { # For each estimation
+      x <- append(get(x = EST_names[j]), mean(unlist(elt[j])))
+      assign(EST_names[j], x)
+    }
   }
@@
 ```{r}
-cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(EST_nb), "\n - for the volume of trees:", mean(EST_vol), "\n - for the ratio volume / number of trees:", mean(EST_ratio))
+cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(unlist(EST_nb)), "\n - for the volume of trees:", mean(unlist(EST_vol)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio)),
+        "\n\n - for the number of small trees:", mean(unlist(EST_nb_s)), "\n - for the volume of small trees:", mean(unlist(EST_vol_s)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_s)),
+    "\n\n - for the number of medium trees:", mean(unlist(EST_nb_m)), "\n - for the volume of medium trees:", mean(unlist(EST_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_m)),
+    "\n\n - for the number of big trees:", mean(unlist(EST_nb_b)), "\n - for the volume of big trees:", mean(unlist(EST_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_b)))
 
@@
 # to find the mean for each of these series
-VAR_nb <- c()
-VAR_vol <- c()
-VAR_ratio <- c()
+VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
+
+for (j in VAR_names) {
+  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
+}
+
 for (elt in res2$Variances) {
-  VAR_nb <- append(VAR_nb, elt$var_nb)
-  VAR_vol <- append(VAR_vol, elt$var_vol)
-  VAR_ratio <- append(VAR_ratio, elt$var_ratio)
+  for (j in 1:length(VAR_names)) { # For each estimation
+    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
+    assign(VAR_names[j], x)
+  }
 }
@@
 ```{r}
-cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", mean(VAR_nb), "\n - for the volume of trees:", mean(VAR_vol), "\n - for the ratio volume / number of trees:", mean(VAR_ratio))
+cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", mean(unlist(VAR_nb)), "\n - for the volume of trees:", mean(unlist(VAR_vol)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio)),
+        "\n\n - for the number of small trees:", mean(unlist(VAR_nb_s)), "\n - for the volume of small trees:", mean(unlist(VAR_vol_s)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_s)),
+    "\n\n - for the number of medium trees:", mean(unlist(VAR_nb_m)), "\n - for the volume of medium trees:", mean(unlist(VAR_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_m)),
+    "\n\n - for the number of big trees:", mean(unlist(VAR_nb_b)), "\n - for the volume of big trees:", mean(unlist(VAR_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_b)))
 
@@
 
-```{r eval=FALSE, include=FALSE}
-### DRAFT
-
-  # Coverage rate
-  TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb[1], CI_nb[2]) )
-  TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol[1], CI_vol[2]) )
-  TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio[1], CI_ratio[2]) )
-
-  # Lower tail
-  low_tail_nb <- (1/nrow(CI_nb))*sum( mapply(function(a){as.numeric(29272 < a)}, CI_nb[1]) )
-  low_tail_vol <- (1/nrow(CI_vol))*sum( mapply(function(a){as.numeric(5412.722 < a)}, CI_vol[1]) )
-  low_tail_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a){as.numeric(0.1849112 < a)}, CI_ratio[1]) )
-
-  # Upper tail
-  up_tail_nb <- (1/nrow(CI_nb))*sum( mapply(function(b){as.numeric(29272 > b)}, CI_nb[2]) )
-  up_tail_vol <- (1/nrow(CI_vol))*sum( mapply(function(b){as.numeric(5412.722 > b)}, CI_vol[2]) )
-  up_tail_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(b){as.numeric(0.1849112 > b)}, CI_ratio[2]) )
-
-  # Mean length of CIs
-  length_nb <- mean( mapply(function(a,b){b-a}, CI_nb[1], CI_nb[2]) )
-  length_vol <- mean( mapply(function(a,b){b-a}, CI_vol[1], CI_vol[2]) )
-  length_ratio <- mean( mapply(function(a,b){b-a}, CI_ratio[1], CI_ratio[2]) )
-
-  df_TC <- data.frame(TC = c(TC_nb, TC_vol, TC_ratio), Upper = c(low_tail_nb, low_tail_vol, low_tail_ratio), Lower = c(up_tail_nb, up_tail_vol, up_tail_ratio), Mean_length = c(length_nb, length_vol, length_ratio))
-```
-
 ```{r}
@@
 ```{r}
-diff_percent <- function(x,y){100*(max(res1$Variances[x],mean(y))-min(res1$Variances[x],mean(y)))/min(res1$Variances[x],mean(y))}
-cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1, VAR_nb), "%", "\n - for the volume of trees: ", diff_percent(2, VAR_vol), "%\n - for the ratio volume / number of trees: ", diff_percent(3, VAR_ratio), "%", sep = "")
+diff_percent <- function(x,y){100*(max(res1$Variances[x],mean(unlist(y)))-min(res1$Variances[x],mean(unlist(y))))/min(res1$Variances[x],mean(unlist(y)))}
+cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1, VAR_nb), "%", "\n - for the volume of trees: ", diff_percent(5, VAR_vol), "%\n - for the ratio volume / number of trees: ", diff_percent(9, VAR_ratio), "%",
+    "\n\n - for the number of small trees:", diff_percent(2, VAR_nb_s), "%", "\n - for the volume of small trees:", diff_percent(6, VAR_vol_s), "%", "\n - for the ratio volume / number of trees:", diff_percent(10, VAR_ratio_s), "%",
+    "\n\n - for the number of medium trees:", diff_percent(3, VAR_nb_m), "%", "\n - for the volume of medium trees:", diff_percent(7, VAR_vol_m), "%", "\n - for the ratio volume / number of trees:", diff_percent(11, VAR_ratio_m), "%",
+    "\n\n - for the number of big trees:", diff_percent(4, VAR_nb_b), "%", "\n - for the volume of big trees:", diff_percent(8, VAR_vol_b), "%", "\n - for the ratio volume / number of trees:", diff_percent(12, VAR_ratio_b), "%",
+    sep = "")
 

### 2024-08-13 Draft/Draft.Rmd
Ready to knit I hope

@@
 ```
+
+##### From All_param -----------
+
+```{r eval=FALSE, include=FALSE}
+### DRAFT
+
+  # Coverage rate
+  TC_nb <- (1/nrow(CI_nb))*sum( mapply(function(a,b){as.numeric((29272 > a) & (29272 < b))}, CI_nb[1], CI_nb[2]) )
+  TC_vol <- (1/nrow(CI_vol))*sum( mapply(function(a,b){as.numeric((5412.722 > a) & (5412.722 < b))}, CI_vol[1], CI_vol[2]) )
+  TC_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a,b){as.numeric((0.1849112 > a) & (0.1849112 < b))}, CI_ratio[1], CI_ratio[2]) )
+
+  # Lower tail
+  low_tail_nb <- (1/nrow(CI_nb))*sum( mapply(function(a){as.numeric(29272 < a)}, CI_nb[1]) )
+  low_tail_vol <- (1/nrow(CI_vol))*sum( mapply(function(a){as.numeric(5412.722 < a)}, CI_vol[1]) )
+  low_tail_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(a){as.numeric(0.1849112 < a)}, CI_ratio[1]) )
+
+  # Upper tail
+  up_tail_nb <- (1/nrow(CI_nb))*sum( mapply(function(b){as.numeric(29272 > b)}, CI_nb[2]) )
+  up_tail_vol <- (1/nrow(CI_vol))*sum( mapply(function(b){as.numeric(5412.722 > b)}, CI_vol[2]) )
+  up_tail_ratio <- (1/nrow(CI_ratio))*sum( mapply(function(b){as.numeric(0.1849112 > b)}, CI_ratio[2]) )
+
+  # Mean length of CIs
+  length_nb <- mean( mapply(function(a,b){b-a}, CI_nb[1], CI_nb[2]) )
+  length_vol <- mean( mapply(function(a,b){b-a}, CI_vol[1], CI_vol[2]) )
+  length_ratio <- mean( mapply(function(a,b){b-a}, CI_ratio[1], CI_ratio[2]) )
+
+  df_TC <- data.frame(TC = c(TC_nb, TC_vol, TC_ratio), Upper = c(low_tail_nb, low_tail_vol, low_tail_ratio), Lower = c(up_tail_nb, up_tail_vol, up_tail_ratio), Mean_length = c(length_nb, length_vol, length_ratio))
+```

### 2024-08-13 All_param.Rmd
Began to knit

@@
 
-# res1 <- MonteCarlo(n, 10000)
-res1 <- MonteCarlo(n, 10)
+res1 <- MonteCarlo(n, 10000)
 # Just one circle to begin with
@@
 
-# res2 <- MC_boot(n, B1 = 1000, B2 = 400)
-res2 <- MC_boot(n, B1 = 10, B2 = 4)
+res2 <- MC_boot(n, B1 = 1000, B2 = 400)
 # Just one circle to begin with

### 2024-08-13 All_param.Rmd
A few words

@@
 
-The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees, the ratio volume of trees / number of trees and \textbf{other ratios}) and variances of these estimators.
+The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees, the ratio volume of trees / number of trees as well as for \textbf{other totals and ratios}) and variances of these estimators.
 The same elements, along with confidence intervals, are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations.

### 2024-08-14 All_param.Rmd
Coverage rates rectified

@@
   return(big_est)
-  # Data frame with 3 estimations for each sample
+  # Data frame with estimations for each sample
 }
@@
   # Local Variables: local variables (number and volume) for each point in each sample
-  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
+  # Estimations: estimations (numbers, volumes, ratios volume / number) for each sample
   # Variances: mean of the bootstrap variance for each estimator
-  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
+  # Confidence Intervals: 4 different forms of 95% confidence intervals, for each total / ratio
 }
@@
 
-res2 <- MC_boot(n, B1 = 1000, B2 = 400)
+res2 <- MC_boot(n, B1 = 200, B2 = 100)
 # Just one circle to begin with
@@
 EST_names <- paste0("EST_", raw_names)[-(1:2)]
-# est_names <- paste0("est_", raw_names)[-(1:2)]
 
@@
   raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
+  nam_lim <- paste0("lim_", raw_names)[-(1:2)]
   CI_names <- paste0("CI_", raw_names)[-(1:2)]
@@
   for (elt in res2$`Confidence Intervals`) { # For each MC iteration
-    for (j in CI_names) { # For each estimation
-      x <- cbind(get(x = j), elt[k])
-      assign(j, x)
+    for (j in 1:length(CI_names)) { # For each estimation
+      x <- cbind(get(x = CI_names[j]), elt[k][[1]][colnames(elt[k][[1]]) == nam_lim[j]]) # elt[k]
+      assign(CI_names[j], x)
     }
@@
 cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1, VAR_nb), "%", "\n - for the volume of trees: ", diff_percent(5, VAR_vol), "%\n - for the ratio volume / number of trees: ", diff_percent(9, VAR_ratio), "%",
-    "\n\n - for the number of small trees:", diff_percent(2, VAR_nb_s), "%", "\n - for the volume of small trees:", diff_percent(6, VAR_vol_s), "%", "\n - for the ratio volume / number of trees:", diff_percent(10, VAR_ratio_s), "%",
-    "\n\n - for the number of medium trees:", diff_percent(3, VAR_nb_m), "%", "\n - for the volume of medium trees:", diff_percent(7, VAR_vol_m), "%", "\n - for the ratio volume / number of trees:", diff_percent(11, VAR_ratio_m), "%",
-    "\n\n - for the number of big trees:", diff_percent(4, VAR_nb_b), "%", "\n - for the volume of big trees:", diff_percent(8, VAR_vol_b), "%", "\n - for the ratio volume / number of trees:", diff_percent(12, VAR_ratio_b), "%",
+    "\n\n - for the number of small trees: ", diff_percent(2, VAR_nb_s), "%", "\n - for the volume of small trees: ", diff_percent(6, VAR_vol_s), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10, VAR_ratio_s), "%",
+    "\n\n - for the number of medium trees: ", diff_percent(3, VAR_nb_m), "%", "\n - for the volume of medium trees: ", diff_percent(7, VAR_vol_m), "%", "\n - for the ratio volume / number of trees: ", diff_percent(11, VAR_ratio_m), "%",
+    "\n\n - for the number of big trees: ", diff_percent(4, VAR_nb_b), "%", "\n - for the volume of big trees: ", diff_percent(8, VAR_vol_b), "%", "\n - for the ratio volume / number of trees: ", diff_percent(12, VAR_ratio_b), "%",
     sep = "")

### 2024-08-14 All_param.Rmd
tidier

@@
     rev_perc_CI <- data.frame(matrix(numeric(0), nrow = 2))
-    # norm_CI <- data.frame(useless = rep(0, 2))
-    # perc_CI <- data.frame(useless = rep(0, 2))
-    # rev_perc_CI <- data.frame(useless = rep(0, 2))
     for (l in 1:length(est_boot_val)) { # Loop: one estimator each time
@@
     }
-    # norm_CI$useless <- NULL
-    # perc_CI$useless <- NULL
-    # rev_perc_CI$useless <- NULL
     nam_lim <- paste0("lim_", raw_names)[-(1:2)]
@@
 
-res2 <- MC_boot(n, B1 = 200, B2 = 100)
+res2 <- MC_boot(n, B1 = 1000, B2 = 400)
 # Just one circle to begin with

### 2024-08-14 All_tables.Rmd
A long way to go to have pretty tables

--- 2024-08-14 All_param.Rmd
@@
 ---
-title: "Monte Carlo and bootstrap for ALL parameters"
+title: "Monte Carlo and bootstrap for ALL parameters with tables"
 output: pdf_document
@@
 library(tibble) # for add_column
+library(xtable) # To have LaTeX tables based on dataframes
 ```
@@
 
-res1 <- MonteCarlo(n, 10000)
+# res1 <- MonteCarlo(n, 500)
 # Just one circle to begin with
@@
 
-res2 <- MC_boot(n, B1 = 1000, B2 = 400)
+res2 <- MC_boot(n, B1 = 100, B2 = 50)
 # Just one circle to begin with
@@
 
+```{r}
+# Tables
+print(xtable(TC_normal, caption = "Test"))
+```
+
+```{r}
+# Tables
+addtorow <- list()
+# addtorow$pos <- list()
+addtorow$pos <- c(0, 2)
+# addtorow$pos[[2]] <- 4
+addtorow$command <- c('\vspace{2mm} \n', '\vspace{10mm} \n')
+print(xtable(TC_normal, caption = "Test", align = c("c", "|", "c", "c", "c", "c")), add.to.row = addtorow)
+```
+
 ## Comparison of the variances

### 2024-08-16 All_tables.Rmd
Better All_tables

@@
 library(xtable) # To have LaTeX tables based on dataframes
+```
+
+```{r}
+install.packages("kableExtra")
+library(kableExtra)
 ```
@@
 
-# res1 <- MonteCarlo(n, 500)
+res1 <- MonteCarlo(n, 50)
 # Just one circle to begin with
@@
 ```{r}
+B1 <- 100
+B2 <- 50
+```
+
+```{r}
 start.time <- Sys.time()
 
-res2 <- MC_boot(n, B1 = 100, B2 = 50)
+res2 <- MC_boot(n, B1, B2)
 # Just one circle to begin with
@@
 ```{r}
+# We want all the variances obtained for each parameter of interest, 
+# to find the mean for each of these series
+VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
+VAR_df <-
+
+for (j in VAR_names) {
+  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
+}
+
+for (elt in res2$Variances) {
+  for (j in 1:length(VAR_names)) { # For each estimation
+    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
+    assign(VAR_names[j], x)
+  }
+}
+```
+
+```{r}
 cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", mean(unlist(VAR_nb)), "\n - for the volume of trees:", mean(unlist(VAR_vol)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio)),
@@
   }
-  # CI_nb <- data.frame(matrix(numeric(0), nrow = 2))
-  # CI_vol <- data.frame(matrix(numeric(0), nrow = 2))
-  # CI_ratio <- data.frame(matrix(numeric(0), nrow = 2))
   for (elt in res2$`Confidence Intervals`) { # For each MC iteration
@@
     }
-    # elt2 <- as.data.frame(elt[k])
-    # CI_nb <- cbind(CI_nb, elt2[k])
-      # cbind(CI_nb2, c(elt2[k][1,], elt2[k][2,]))
-
-    # CI_nb <- cbind(CI_nb, c(unlist(elt[k])[1], unlist(elt[k])[2]))
-    # CI_vol <- cbind(CI_vol, c(unlist(elt[k])[3], unlist(elt[k])[4]))
-    # CI_ratio <- cbind(CI_ratio, c(unlist(elt[k])[5], unlist(elt[k])[6]))
   }
@@
   }
-  # CI_nb <- as.data.frame(t(CI_nb))
-  # CI_vol <- as.data.frame(t(CI_vol))
-  # CI_ratio <- as.data.frame(t(CI_ratio))
 
@@
 ```{r}
-# Tables
-addtorow <- list()
-# addtorow$pos <- list()
-addtorow$pos <- c(0, 2)
-# addtorow$pos[[2]] <- 4
-addtorow$command <- c('\vspace{2mm} \n', '\vspace{10mm} \n')
-print(xtable(TC_normal, caption = "Test", align = c("c", "|", "c", "c", "c", "c")), add.to.row = addtorow)
+truc <- TC_normal %>%
+  kable("latex", booktabs = TRUE)
+truc
+```
+
+```{r}
+TC_normal %>%
+  kable("latex", booktabs = TRUE) %>%
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>%
+  collapse_rows(columns = 1, latex_hline = "major")
+```
+
+```{r}
+df_total <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
+PARAM_names <- c("Number of trees", "Number of small trees", "Number of medium trees", "Number of big trees", "Volume of trees", "Volume of small trees", "Volume of medium trees", "Volume of big trees", "Ratio for all trees", "Ratio for small trees", "Ratio for medium trees", "Ratio for big trees")
+meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
+
+for (param in 1:12) {
+  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
+  k <- 1
+  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
+    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(TC_meth[param,1:3]*100, "%"), round(TC_meth[param,4], digits = 2) ))))
+    k <- k+1
+  }
+  df_total <- rbind(df_total, df_param)
+}
+
+colnames(df_total) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
+```
+
+```{r}
+truc <- df_total %>%
+  kable("latex", booktabs = TRUE, align = "llcccc", linesep = c("", "", "",
+  "\\addlinespace"), caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>% # \\hline
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
+  collapse_rows(columns = 1, latex_hline = "major")
+```
+
+```{r}
+print(truc)
+```
+
+```{r}
+cat(truc)
 ```

### 2024-08-16 All_tables.Rmd
Ready to knit I hope

@@
 ```{r}
+install.packages("kableExtra")
+```
+
+```{r}
 library(readxl) # to read the initial file
@@
 library(tibble) # for add_column
-library(xtable) # To have LaTeX tables based on dataframes
-```
-
-```{r}
-install.packages("kableExtra")
-library(kableExtra)
+library(kableExtra) # To have LaTeX tables based on dataframes
 ```
@@
 # True values
-cat("True integrals are the following:\n\nNumber of trees:", nrow(trees), "\nTotal volume:", sum(trees$v), 
-    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees),
-    "\n\nNumber of small trees:", nrow(trees[(pi*trees$d130 < 70.5),]), "\nVolume of small trees:", sum(trees[(pi*trees$d130 < 70.5),]$v), 
-    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]),
-    "\n\nNumber of medium trees:", nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), "\nVolume of medium trees:", sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), 
-    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]),
-    "\n\nNumber of big trees:", nrow(trees[(pi*trees$d130 > 117.5),]), "\nVolume of big trees:", sum(trees[(pi*trees$d130 > 117.5),]$v), 
-    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),])
+real_val <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
+  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
+  round(sum(trees$v)/nrow(trees), digits = 2), round(sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), digits = 2), round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), digits = 2), round(sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),]), digits = 2)
+  )
+
+cat("True integrals are the following:\n\nNumber of trees:", real_val[1], "\nTotal volume:", real_val[5], 
+    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", real_val[9],
+    "\n\nNumber of small trees:", real_val[2], "\nVolume of small trees:", real_val[6], 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[10],
+    "\n\nNumber of medium trees:", real_val[3], "\nVolume of medium trees:", real_val[7], 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[11],
+    "\n\nNumber of big trees:", real_val[4], "\nVolume of big trees:", real_val[8], 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[12]
     )
@@
 
-# Monte Carlo alone
+```{r}
+real_df <- data.frame(c("All trees", "Small trees", "Medium trees", "Big trees"), matrix(real_val, nrow = 4))
+colnames(real_df) <- c("", "Number", "Volume", "Ratio Volume/Number")
+```
+
+```{r}
+tab_real <- real_df %>%
+  kable("latex", booktabs = TRUE, align = "lccc", linesep = c("", "\\addlinespace", "", "", "", ""), 
+        caption = paste("True values proper to the database"), col.names = gsub("[.]", " ", names(real_df))) %>% # \\hline
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
+  collapse_rows(columns = 1, latex_hline = "major")
+```
+
+```{r}
+# The table itself
+print(tab_real)
+```
+
+```{r}
+# The code that produced the table
+cat(tab_real)
+```
+
+```{r}
+# For each sampled point of each sample, there will be the following information:
+# Coordinates, number of trees for each category, volume of trees for each category, ratios for each category
+# The four categories being the whole forest, small trees, medium trees, and big trees
+raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
+```
+
+# Functions
+
+## Monte Carlo alone
 
@@
 
-  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
   p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
@@
 
-# Bootstrap for each Monte Carlo iteration
+## Bootstrap for each Monte Carlo iteration
 
@@
 ```{r}
-## Nonparametric BCa
+## Nonparametric BCa: a method to create confidence intervals
 # Largely based on the code given in https://gitlab.com/scottkosty/bootstrap/-/blob/master/R/bcanon.R
@@
     z0 <- mapply( function(j){qnorm(sum(mapply(function(long){long<est_init[,j]},est_boot_val[,j]))/nboot)} , 1:12)
-    # Same as: mapply(function(one, long){qnorm(sum(long<one)/nboot)}, t(est_init),est_boot_val)
 
@@
   # df_sample: initial sample with nb_est variables and of size n; 
-  # B: number of bootstrap samples made thanks to df_sample
+  # B: number of bootstrap samples made thanks to df_sample;
+  # nb_var: number of variables of interest (for totals and not ratios)
 
@@
   return(df_boot)
-  # Return a data frame with B samples of 4 variables and of size (n-1)
+  # Return a data frame with B samples of (nb_var+2) variables and of size (n-1)
 }
@@
   # p: inclusion density function (constant in the uniform case)
+  # nb_var: number of variables of interest (for totals and not ratios)
 
-  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
   n <- nrow(df) + 1 # sample size of the initial sample
@@
 
-  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
   p <- sum(rep((1/1000)*(1/1000), n))
@@
     colnames(df_b) <- paste0(raw_names, ".MC", b)[-(11:14)]
-    from_local <- function(j){sum(df_b[2+j] /p)} # (nb_var+2)*(b-1)
+    from_local <- function(j){sum(df_b[2+j] /p)} # to produce HT estimators based on the sample
     est_b <- data.frame(from_local(1), from_local(2), from_local(3), from_local(4), from_local(5), from_local(6), from_local(7), from_local(8), 
@@
 ```{r}
+B0 <- 50
+```
+
+```{r}
 start.time <- Sys.time()
 
-res1 <- MonteCarlo(n, 50)
+res1 <- MonteCarlo(n, B0)
 # Just one circle to begin with
@@
 # to find the mean for each of these series
-raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
 EST_names <- paste0("EST_", raw_names)[-(1:2)]
@@
 VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
-VAR_df <-
+VAR_df <- c()
 
@@
 }
+
+VAR_df <- c(mapply(function(j){mean(unlist(get(x = VAR_names[j])))}, 1:12))
 ```
@@
 ```{r}
-cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", mean(unlist(VAR_nb)), "\n - for the volume of trees:", mean(unlist(VAR_vol)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio)),
-        "\n\n - for the number of small trees:", mean(unlist(VAR_nb_s)), "\n - for the volume of small trees:", mean(unlist(VAR_vol_s)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_s)),
-    "\n\n - for the number of medium trees:", mean(unlist(VAR_nb_m)), "\n - for the volume of medium trees:", mean(unlist(VAR_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_m)),
-    "\n\n - for the number of big trees:", mean(unlist(VAR_nb_b)), "\n - for the volume of big trees:", mean(unlist(VAR_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_b)))
+cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", VAR_df[1], "\n - for the volume of trees:", VAR_df[5], "\n - for the ratio volume / number of trees:", VAR_df[9],
+        "\n\n - for the number of small trees:", VAR_df[2], "\n - for the volume of small trees:", VAR_df[6], "\n - for the ratio volume / number of trees:", VAR_df[10],
+    "\n\n - for the number of medium trees:", VAR_df[3], "\n - for the volume of medium trees:", VAR_df[7], "\n - for the ratio volume / number of trees:", VAR_df[11],
+    "\n\n - for the number of big trees:", VAR_df[4], "\n - for the volume of big trees:", VAR_df[8], "\n - for the ratio volume / number of trees:", VAR_df[12])
 
@@
 
-  raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
   nam_lim <- paste0("lim_", raw_names)[-(1:2)]
@@
   length_names <- paste0("length_", raw_names)[-(1:2)]
-
-  real_val <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
-  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
-  sum(trees$v)/nrow(trees), sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),])
-  )
 
@@
 ```{r}
-# Tables
-print(xtable(TC_normal, caption = "Test"))
-```
+### Clean data frame to create a LaTeX table
 
-```{r}
-truc <- TC_normal %>%
-  kable("latex", booktabs = TRUE)
-truc
-```
-
-```{r}
-TC_normal %>%
-  kable("latex", booktabs = TRUE) %>%
-  kable_styling(latex_options = "hold_position") %>%
-  row_spec(0, bold = TRUE) %>%
-  collapse_rows(columns = 1, latex_hline = "major")
-```
-
-```{r}
 df_total <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
@@
 ```{r}
-truc <- df_total %>%
+tab_ci <- df_total %>%
   kable("latex", booktabs = TRUE, align = "llcccc", linesep = c("", "", "",
@@
 ```{r}
-print(truc)
+# The table itself
+print(tab_ci)
 ```
@@
 ```{r}
-cat(truc)
+# The code that produced the table
+cat(tab_ci)
 ```
@@
 ```{r}
-diff_percent <- function(x,y){100*(max(res1$Variances[x],mean(unlist(y)))-min(res1$Variances[x],mean(unlist(y))))/min(res1$Variances[x],mean(unlist(y)))}
-cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1, VAR_nb), "%", "\n - for the volume of trees: ", diff_percent(5, VAR_vol), "%\n - for the ratio volume / number of trees: ", diff_percent(9, VAR_ratio), "%",
-    "\n\n - for the number of small trees: ", diff_percent(2, VAR_nb_s), "%", "\n - for the volume of small trees: ", diff_percent(6, VAR_vol_s), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10, VAR_ratio_s), "%",
-    "\n\n - for the number of medium trees: ", diff_percent(3, VAR_nb_m), "%", "\n - for the volume of medium trees: ", diff_percent(7, VAR_vol_m), "%", "\n - for the ratio volume / number of trees: ", diff_percent(11, VAR_ratio_m), "%",
-    "\n\n - for the number of big trees: ", diff_percent(4, VAR_nb_b), "%", "\n - for the volume of big trees: ", diff_percent(8, VAR_vol_b), "%", "\n - for the ratio volume / number of trees: ", diff_percent(12, VAR_ratio_b), "%",
+diff_percent <- function(j){unlist(100*(max(res1$Variances[j],VAR_df[j])-min(res1$Variances[j],VAR_df[j]))/min(res1$Variances[j],VAR_df[j]))}
+cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1), "%", "\n - for the volume of trees: ", diff_percent(5), "%\n - for the ratio volume / number of trees: ", diff_percent(9), "%",
+    "\n\n - for the number of small trees: ", diff_percent(2), "%", "\n - for the volume of small trees: ", diff_percent(6), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10), "%",
+    "\n\n - for the number of medium trees: ", diff_percent(3), "%", "\n - for the volume of medium trees: ", diff_percent(7), "%", "\n - for the ratio volume / number of trees: ", diff_percent(11), "%",
+    "\n\n - for the number of big trees: ", diff_percent(4), "%", "\n - for the volume of big trees: ", diff_percent(8), "%", "\n - for the ratio volume / number of trees: ", diff_percent(12), "%",
     sep = "")
@@
 ```
+
+```{r}
+# Table for comparison
+diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Difference between variances` = paste0(round(mapply(function(x,y){100*(max(x,y)-min(x,y))/min(x,y)}, VAR_df, res1$Variances), digits = 3), "%") )
+```
+
+```{r}
+tab_var <- diff_var %>%
+  kable("latex", booktabs = TRUE, align = "lc", linesep = c("", "", "",
+  "\\addlinespace"), caption = paste("Comparison of the two methods when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
+  collapse_rows(columns = 1, latex_hline = "major")
+```
+
+```{r}
+# The table itself
+print(tab_var)
+```
+
+```{r}
+# The code that produced the table
+cat(tab_var)
+```

### 2024-08-16 Draft/Draft.Rmd
Ready to knit I hope

@@
 ```
+
+### LaTeX tables from R data frames ----------
+
+```{r}
+library(xtable)
+```
+
+```{r}
+# Tables
+print(xtable(TC_normal, caption = "Test"))
+```
+
+```{r}
+truc <- TC_normal %>%
+  kable("latex", booktabs = TRUE)
+truc
+```
+
+```{r}
+TC_normal %>%
+  kable("latex", booktabs = TRUE) %>%
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>%
+  collapse_rows(columns = 1, latex_hline = "major")
+```
+
+### Simplification of All_tables ------------
+
+```{r}
+test2 <- paste("True integrals are the following:\n\nNumber of trees:", nrow(trees), "\nTotal volume:", sum(trees$v), 
+    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees),
+    "\n\nNumber of small trees:", nrow(trees[(pi*trees$d130 < 70.5),]), "\nVolume of small trees:", sum(trees[(pi*trees$d130 < 70.5),]$v), 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]),
+    "\n\nNumber of medium trees:", nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), "\nVolume of medium trees:", sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]),
+    "\n\nNumber of big trees:", nrow(trees[(pi*trees$d130 > 117.5),]), "\nVolume of big trees:", sum(trees[(pi*trees$d130 > 117.5),]$v), 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),])
+    )
+```
+
+```{r}
+cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", VAR_df[1], "\n - for the volume of trees:", VAR_df[5], "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio)),
+        "\n\n - for the number of small trees:", VAR_df[2], "\n - for the volume of small trees:", VAR_df[6], "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_s)),
+    "\n\n - for the number of medium trees:", VAR_df[3], "\n - for the volume of medium trees:", mean(unlist(VAR_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_m)),
+    "\n\n - for the number of big trees:", VAR_df[4], "\n - for the volume of big trees:", mean(unlist(VAR_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(VAR_ratio_b)))
+
+# Example:
+```
+
+```{r}
+# For z0 in nonparametric BCa
+# Same as: mapply(function(one, long){qnorm(sum(long<one)/nboot)}, t(est_init),est_boot_val)
+```
+
+```{r}
+# Really useless
+from_local <- function(j){sum(df_b[2+j] /p)} # (nb_var+2)*(b-1)
+```

### 2024-08-16 All_tables.Rmd
Better tables and bigger test

@@
 output: pdf_document
-date: "2024-08-02"
+date: "2024-08-16"
 ---
@@
 # The table itself
-print(tab_real)
+tab_real
 ```
@@
 ```{r}
-B0 <- 50
+B0 <- 1000
 ```
@@
 ```{r}
-B1 <- 100
-B2 <- 50
+B1 <- 200
+B2 <- 100
 ```
@@
 tab_ci <- df_total %>%
-  kable("latex", booktabs = TRUE, align = "llcccc", linesep = c("", "", "",
-  "\\addlinespace"), caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>% # \\hline
+  kable("latex", booktabs = TRUE, align = "llcccc", linesep = c("", "", "", "\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "\\hline"), caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>% # \\hline
   kable_styling(latex_options = "hold_position") %>%
@@
 # The table itself
-print(tab_ci)
+tab_ci
 ```
@@
 # The table itself
-print(tab_var)
+tab_var
 ```

### 2024-08-16 All3_tables.Rmd
The same with 3 circles

--- 2024-08-16 All_tables.Rmd
@@
 
-In this document, \textbf{uniform sampling} is used to create a sample and \textbf{one single circle} with a radius of 5 is used to compute local variables.
+In this document, \textbf{uniform sampling} is used to create a sample and \textbf{three concentric circles} are used to compute local variables.
 
@@
     # Variables of interest derived from the sample
-    all_var <- as.data.frame(t(mapply(circle_ALL_, xy$a1, xy$a2)))
+    all_var <- as.data.frame(t(mapply(circle3_ALL_, xy$a1, xy$a2)))
     nb_var <- length(all_var) # number of variables of interest
@@
 ```{r}
-B1 <- 200
-B2 <- 100
+B1 <- 300
+B2 <- 200
 ```

### 2024-08-16 Useful_functions/Circle.R

@@ -141,9 +141,59 @@ circle_vol_size <- function(x1, x2, R=5, bounds = c(23.5, 70.5)){
 
 ### With three circles -----
 
+##### 3 circles, 8 local variables of interest -----------------
+
+circle3_ALL_ <- function(x1, x2, R1=15, R2=9, R3=6){
+  # 2 coordinates (x1, x2) and 3 radii (R1 > R2 > R3)
+  
+  list_trees <- which(((x1 - trees$x)^2 + (x2 - trees$y)^2 <= R1^2))
+  
+  list_trees1 <- list_trees[pi*trees[list_trees,]$d130 > 117.5] # List with the biggest trees
+  list_trees2 <- list_trees[(pi*trees[list_trees,]$d130 < 117.5) & (pi*trees[list_trees,]$d130 > 70.5) & ((x1 - trees[list_trees,]$x)^2 + (x2 - trees[list_trees,]$y)^2 <= R2^2)] # medium trees
+  list_trees3 <- list_trees[(pi*trees[list_trees,]$d130 < 70.5) & ((x1 - trees[list_trees,]$x)^2 + (x2 - trees[list_trees,]$y)^2 <= R3^2)] # smallest trees
+  
+  if (length(list_trees) != 0){
+    if (length(list_trees1) != 0){ # Big trees inside big circle
+      var_nb_big <- sum(1/mapply(inc_area, trees[list_trees1,]$x, trees[list_trees1,]$y, MoreArgs = list(0,0,1000,1000,R1)))
+      var_vol_big <- sum((trees[list_trees1,]$v)/mapply(inc_area, trees[list_trees1,]$x, trees[list_trees1,]$y, MoreArgs = list(0,0,1000,1000,R1)))
+    }
+    else{
+      var_nb_big <- 0
+      var_vol_big <- 0
+    }
+    
+    if (length(list_trees2) != 0){ # Medium trees inside medium circle
+      var_nb_medium <- sum(1/mapply(inc_area, trees[list_trees2,]$x, trees[list_trees2,]$y, MoreArgs = list(0,0,1000,1000,R2)))
+      var_vol_medium <- sum((trees[list_trees2,]$v)/mapply(inc_area, trees[list_trees2,]$x, trees[list_trees2,]$y, MoreArgs = list(0,0,1000,1000,R2)))
+    }
+    else{
+      var_nb_medium <- 0
+      var_vol_medium <- 0
+    }
+    
+    if (length(list_trees3) != 0){
[…]

### 2024-08-16 All3_tables_grid.Rmd
Same with 3 circles and a grid

--- 2024-08-16 All3_tables.Rmd
@@
 
-In this document, \textbf{uniform sampling} is used to create a sample and \textbf{three concentric circles} are used to compute local variables.
+In this document, \textbf{sampling through a grid} is used to create a sample and \textbf{three concentric circles} are used to compute local variables.
 
@@
 
+```{r}
+i <- sample(1:10, 1) # choice of the rank of the identifier we want
+i
+```
+
+```{r}
+# Dimension of a small square (length of one side of the square)
+# We assume that c_dim is a divisor of 1000
+c_dim <- 10
+```
+
+```{r}
+# Function to sample at random following the grid
+sampling_grid <- function(i,c_dim){
+random_points <- data.frame(x = numeric(), y = numeric())
+
+for (l in 0:((1000/c_dim)-1)) {
+  if (l==0){
+    x_init <- i*c_dim
+  }else if ((3*l+i)*c_dim < (10)*c_dim){
+    x_init <- (3*l+i)*c_dim
+  }else{
+    x_init <- (((3*l+i)*c_dim)%%(c_dim*10))
+  }
+  k <- 0
+  while (x_init + 10*c_dim*k < 1000) {
+    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + c_dim)
+    b <- runif(1, l*c_dim, (l+1)*c_dim)
+    random_points <- rbind(random_points, list(a,b))
+    k <- k+1
+  }
+}
+colnames(random_points) <- list("x", "y")
+return(random_points)
+}
+```
+
 # Functions
@@
   for (b in 1:B) { # All in one "for" loop
-    # Uniform sampling over the whole territory
-    xy <- data.frame(a1 = runif(n, 0, 1000), a2 = runif(n, 0, 1000))
+    # Sampling in the territory
+    df_grid <- sampling_grid(i,c_dim)
+    xy <- data.frame(a1 = df_grid$x, a2 = df_grid$y)
     # Variables of interest derived from the sample
@@
   for (b in 1:B1) { # One MC iteration at a time
-    # Uniform sampling over the whole territory
-    xy <- data.frame(a1 = runif(n, 0, 1000), a2 = runif(n, 0, 1000))
+    # Sampling in the territory
+    df_grid <- sampling_grid(i,c_dim)
+    xy <- data.frame(a1 = df_grid$x, a2 = df_grid$y)
     # Variables of interest derived from the sample

### 2024-08-18 All3_tables.Rmd
With more round

@@
     # Coverage rate
-    assign( TC_names[j], (1/nrow(x))*sum( mapply(function(a,b){as.numeric((real_val[j] > a) & (real_val[j] < b))}, x[1], x[2]) ))
+    assign( TC_names[j], round((1/nrow(x))*sum( mapply(function(a,b){as.numeric((real_val[j] > a) & (real_val[j] < b))}, x[1], x[2]) ), digits = 2) )
     TC <- append(TC, get(TC_names[j]))
     # Lower tail
-    assign( low_names[j], (1/nrow(x))*sum( mapply(function(a){as.numeric(real_val[j] < a)}, x[1]) ))
+    assign( low_names[j], round((1/nrow(x))*sum( mapply(function(a){as.numeric(real_val[j] < a)}, x[1]) ), digits = 2))
     Lower <- append(Lower, get(low_names[j]))
     # Upper tail
-    assign( up_names[j], (1/nrow(x))*sum( mapply(function(b){as.numeric(real_val[j] > b)}, x[2]) ))
+    assign( up_names[j], round((1/nrow(x))*sum( mapply(function(b){as.numeric(real_val[j] > b)}, x[2]) ), digits = 2))
     Upper <- append(Upper, get(up_names[j]))
     # Mean length of CIs
-    assign( length_names[j], (1/nrow(x))*sum( mapply(function(a,b){b-a}, x[1], x[2]) ))
+    assign( length_names[j], round((1/nrow(x))*sum( mapply(function(a,b){b-a}, x[1], x[2]) ), digits = 2))
     Mean_length <- append(Mean_length, get(length_names[j]))

### 2024-08-19 All3_tables_grid.Rmd
More rounds

@@
     # Coverage rate
-    assign( TC_names[j], (1/nrow(x))*sum( mapply(function(a,b){as.numeric((real_val[j] > a) & (real_val[j] < b))}, x[1], x[2]) ))
+    assign( TC_names[j], round((1/nrow(x))*sum( mapply(function(a,b){as.numeric((real_val[j] > a) & (real_val[j] < b))}, x[1], x[2]) ), digits = 2))
     TC <- append(TC, get(TC_names[j]))
     # Lower tail
-    assign( low_names[j], (1/nrow(x))*sum( mapply(function(a){as.numeric(real_val[j] < a)}, x[1]) ))
+    assign( low_names[j], round((1/nrow(x))*sum( mapply(function(a){as.numeric(real_val[j] < a)}, x[1]) ), digits = 2))
     Lower <- append(Lower, get(low_names[j]))
     # Upper tail
-    assign( up_names[j], (1/nrow(x))*sum( mapply(function(b){as.numeric(real_val[j] > b)}, x[2]) ))
+    assign( up_names[j], round((1/nrow(x))*sum( mapply(function(b){as.numeric(real_val[j] > b)}, x[2]) ), digits = 2))
     Upper <- append(Upper, get(up_names[j]))
     # Mean length of CIs
-    assign( length_names[j], (1/nrow(x))*sum( mapply(function(a,b){b-a}, x[1], x[2]) ))
+    assign( length_names[j], round((1/nrow(x))*sum( mapply(function(a,b){b-a}, x[1], x[2]) ), digits = 2))
     Mean_length <- append(Mean_length, get(length_names[j]))

### 2024-08-19 Test.Rmd
Adapted bootstrap is fine
Concentric circles not that clean

@@
 ```
+
+# Draft from adapt_boot
+
+```{r}
+plot(x = random_points[, 1], y = random_points$var, xlab = "x", main = "Points as a function of x", las = 1)
+```
+
+```{r}
+plot(x = random_points[, 2], y = random_points$var, xlab = "y", main = "Points as a function of y", las = 1)
+```
+
+# Plot concentric circles
+
+```{r}
+# Set up the plotting area
+plot(1, type="n", xlab="", ylab="", xlim=c(-16, 16), ylim=c(-16, 16), asp=1)
+
+# Draw three concentric circles with increasing radius
+symbols(rep(0, 3), rep(0, 3), circles=c(6, 9, 15), inches=FALSE, add=TRUE, fg = rep("navyblue", 2))
+
+# Medium trees
+symbols(c(10, -13), c(-5, 3), circles=c(2.5, 3.6), inches=FALSE, add=TRUE, fg = rep("forestgreen", 2))
+
+# Little trees (between 4 and 12 grosso modo)
+symbols(c(10, -13), c(-5, 3), circles=c(4, 6), inches=FALSE, add=TRUE, fg = rep("green", 2))
+
+# Centers of trees
+points(c(10, -13), c(-5, 3), pch=19, col="black", cex=0.2)
+
+# Add axis lines for reference (optional)
+abline(h=0, v=0, col="gray")
+
+```
+
+```{r}
+# Set up the plotting area
+plot(1, type="n", xlab="", ylab="", xlim=c(-16, 16), ylim=c(-10, 10), asp=1)
+
+# Draw three concentric circles with increasing radius
+symbols(rep(0, 2), rep(0, 2), circles=c(6, 9), inches=FALSE, add=TRUE, fg = rep("navyblue", 2))
+
+# Medium trees
+symbols(c(8, -4), c(2, 3), circles=c(2.5, 3.6), inches=FALSE, add=TRUE, fg = rep("forestgreen", 2))
+
+# Little trees (between 4 and 12 grosso modo)
+symbols(c(7, -3), c(-5, 3), circles=c(4, 6), inches=FALSE, add=TRUE, fg = rep("green", 2))
+
+# Centers of trees
+points(c(10, -13), c(-5, 3), pch=19, col="black", cex=0.2)
+
+# Add axis lines for reference (optional)
+abline(h=0, v=0, col="gray")
+
+```

### 2024-08-20 Map_FR.Rmd
Tentative map

---
title: "Map of France"
output: pdf_document
date: "2024-08-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
```

## Test

```{r}
map <- map_data("france")
ggplot(map)
```

# Another test

```{r}
install.packages("CARTElette")
library(CARTElette)
```

```{r}
shp_commune <- charger_carte(COG = 2019, nivsupra = "COM")
```

# No despair

```{r}
install.packages("sf")
install.packages("tmap")
```

```{r}
library(sf)
library(tmap)
```

```{r}
departements_l93 <- read_sf("~/work/Sim_article2024/DEPARTEMENT.shp")
```

# The cat

```{r}
# Installer les packages nécessaires si vous ne les avez pas déjà
install.packages(c("sf", "rnaturalearth", "ggplot2", "rnaturalearthdata"))

# Charger les packages
library(sf)
library(rnaturalearth)
library(ggplot2)
```

```{r}
# Télécharger les données du fond de carte
france_map <- ne_countries(scale = "medium", country = "France", returnclass = "sf")

# Afficher la carte de la France métropolitaine
ggplot(data = france_map) +
  geom_sf() +
  coord_sf(xlim = c(-6, 10), ylim = c(41, 52), expand = FALSE) +
  geom_tile(data = grid_data, aes(x = lon, y = lat, fill = color), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Carte de la France Métropolitaine")

```

```{r}

# Télécharger les données du fond de carte
france_map <- ne_countries(scale = "medium", country = "France", returnclass = "sf")

# Définir les limites de la France métropolitaine pour la grille
xlims <- c(-6, 10)
ylims <- c(40, 52)

cell_width <- 1.0  # largeur des cases
cell_height <- 1.0  # hauteur des cases

# Créer une grille régulière de coordonnées
grid_data <- expand.grid(
  lon = seq(xlims[1], xlims[2], by = 0.1),  # Espacement horizontal
  lat = seq(ylims[1], ylims[2], by = 0.1)   # Espacement vertical
)

# Créer une colonne fictive pour colorier certaines cases
grid_data$color <- ifelse(grid_data$lon > 2 & grid_data$lon < 4 & 
                            grid_data$lat > 46 & grid_data$lat < 48, 
                          "highlight", "normal")

# Afficher la carte avec la grille par-dessus
ggplot(data = france_map) +
  geom_sf(fill = "white", color = "black") +
  coord_sf(xlim = xlims, ylim = ylims, expand = FALSE) +
  geom_tile(data = grid_data, aes(x = lon, y = lat, fill = color), alpha = 0.5) +
  scale_fill_manual(values = c("highlight" = "red", "normal" = "transparent")) +
  theme_minimal() +
  labs(title = "Carte de la France Métropolitaine avec une Grille")

```

```{r}
# Définir les limites de la France métropolitaine pour la grille
xlims <- c(-5, 10)
ylims <- c(41, 52)

# Définir la taille des cases de la grille
cell_width <- 1.0  # largeur des cases
cell_height <- 1.0  # hauteur des cases

# Créer une grille régulière de coordonnées
grid_data <- expand.grid(
  lon = seq(xlims[1], xlims[2], by = cell_width),  # Espacement horizontal
  lat = seq(ylims[1], ylims[2], by = cell_height)  # Espacement vertical
)

# Créer une colonne fictive pour colorier certaines cases (à modifier selon vos besoins)
grid_data$color <- ifelse(grid_data$lon > 2 & grid_data$lon < 4 & 
                            grid_data$lat > 46 & grid_data$lat < 48, 
                          "highlight", "normal")

# Afficher la carte avec la grille par-dessus
ggplot() +
  geom_sf(data = france_map, fill = "white", color = "black") +
  coord_sf(xlim = xlims, ylim = ylims, expand = FALSE) +
  geom_tile(data = grid_data, aes(x = lon, y = lat, fill = color), 
            width = cell_width, height = cell_height, alpha = 0.5) +
  scale_fill_manual(values = c("highlight" = "red", "normal" = "transparent")) +
  theme_minimal() +
  labs(title = "Carte de la France Métropolitaine avec une Grille")

```

### 2024-08-21 Map_FR.Rmd
A finer map of France

@@
 ---
-title: "Map of France"
+title: "Map of France - only tests"
 output: pdf_document
@@
 ```
+
+```{r}
+install.packages("cowplot")
+library(cowplot)
+```
+
+```{r}
+plot_grid(france_map)
+```
+
+```{r}
+# Définir les limites de la France métropolitaine pour la grille
+xlims <- c(-5, 10)
+ylims <- c(41, 52)
+
+ggplot() +
+  geom_sf(data = france_map)+
+  coord_sf(xlim = xlims, ylim = ylims, expand = FALSE) +
+theme(
+panel.grid.major = element_line(
+    colour = "dodgerblue",
+    linewidth = 0.5, linetype = "dotdash"
+)
+)
+```
+
+```{r}
+library(maps)
+data(franceMapEnv)
+```
+
+```{r}
+map('france')
+```

### 2024-08-21 Test_map.Rmd
A finer map of France

---
title: "Test map France"
output: pdf_document
date: "2024-08-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("ggplot2")
install.packages("sf")
install.packages("ggspatial")
```

```{r}
library(ggplot2)
library(sf)
library(ggspatial)
```

```{r}
install.packages("rnaturalearth")
install.packages("rnaturalearthdata")
library(rnaturalearth)
library(rnaturalearthdata)

# Get the map data for metropolitan France
france <- ne_countries(scale = "medium", country = "France", returnclass = "sf")
# france <- ne_states(country = "France", returnclass = "sf") %>%
#   filter(!name %in% c("Guyane", "Martinique", "Guadeloupe", "Réunion", "Mayotte"))  # Exclude overseas regions
```

```{r}
# NB: map doesn't go along with ggplot

# library(maps)
# data(franceMapEnv)
```

```{r}
# Create a data frame with the coordinates and colors
# grid_data <- expand.grid(x = 1:30, y = 1:30)  # 10x10 grid
# grid_data$color <- "white"  # Default color for all squares

# (10--5)*2 = 30
# (51.5-41)*2 = 21

# Function to sample at random following the grid
sampling_grid <- function(i){
  cells_x <- c()
  cells_y <- c()

  for (l in 0:20) {
    if (l==0){
      x_init <- i
    }else if ((3*l+i) < 10){
      x_init <- (3*l+i)
    }else{
      x_init <- (((3*l+i))%%(10))
    }
    k <- 0
    while (x_init + 10*k < 30) {
      a <- x_init + 10*k
      b <- l
      cells_x <- append(cells_x, a)
      # print(a)
      cells_y <- append(cells_y, b)
      # print(b)
      k <- k+1
    }
  }
  return(data.frame(x = cells_x, y = cells_y))
}

test <- sampling_grid(3)
```

```{r}
# Define grid parameters
xmin <- -5   # Westernmost longitude
xmax <- 10   # Easternmost longitude
ymin <- 41   # Southernmost latitude
ymax <- 51.5   # Northernmost latitude
grid_size <- 0.5  # Grid size in degrees

# Create a grid
grid <- expand.grid(
  x = seq(xmin, xmax, by = grid_size),
  y = seq(ymin, ymax, by = grid_size)
)

# Convert the grid to an sf object
grid_sf <- st_as_sf(grid, coords = c("x", "y"), crs = 4326)

# Convert grid points to grid cells (polygons)
grid_sf <- st_make_grid(grid_sf, cellsize = c(grid_size, grid_size))

# Highlight specific cells
highlighted_cells <- grid_sf[test$x + (test$y)*30, ]  # Example: highlight specific cells
highlighted_cells <- st_sf(geometry = highlighted_cells, color = "red")  # Assign color

# Combine highlighted and non-highlighted cells
grid_sf <- st_sf(geometry = grid_sf, color = "white")
grid_sf$color[which(grid_sf$geometry %in% highlighted_cells$geometry)] <- highlighted_cells$color
```

```{r}
### First step: all chosen small squares in the grid

# Plot the map
ggplot() +
  geom_sf(data = france, fill = "lightblue") +
  geom_sf(data = grid_sf, aes(fill = color), color = "black", alpha = 0.4) +
  scale_fill_identity() +  # Use the colors defined in the grid_sf object
  coord_sf(xlim = c(xmin, xmax), ylim = c(ymin, ymax)) +
  theme_minimal() +
  ggtitle("Firs-stage sampling: sampling of cells within a grid") 
# +
  # annotation_scale(location = "bl") + # location = NULL
  # annotation_north_arrow(location = "bl")
```

```{r}
# Intersect grid with the map of France
intersected <- st_intersection(grid_sf, france)

# Create a new column to determine land or water (or other features)
# Here, we'll simply mark if a grid cell intersects with land (France)
grid_sf$color2 <- ifelse(st_intersects(grid_sf, france, sparse = FALSE), "green", "blue")
```

```{r}
grid_sf$color3 <- ifelse((grid_sf$color2 == "green") & (grid_sf$color == "red"), "orange", "white")
```

```{r}
### Second step: all chosen small squares that have at least a land part

# Plot the map with color-coded grid cells
ggplot() +
  geom_sf(data = france, fill = "lightblue") +
  geom_sf(data = grid_sf, aes(fill = color3), color = "black", alpha = 0.4) +
  scale_fill_identity() +  # Use the colors defined in the grid_sf object
  coord_sf(xlim = c(xmin, xmax), ylim = c(ymin, ymax)) +
  theme_minimal() 
# +
  # ggtitle("")
```

### 2024-08-21 Test.Rmd
Yet another circle

@@
 ```
+
+```{r}
+# Set up the plotting area
+plot(1, type="n", xlab="", ylab="", xlim=c(-20, 20), ylim=c(-20, 20), asp=1)
+
+# Draw three concentric circles with increasing radius
+symbols(0, 0, circles=10, inches=FALSE, add=TRUE, fg = "navyblue")
+
+# Bad trees
+symbols(c(15, -5), c(2, 10.5), circles=c(2.5, 3.7), inches=FALSE, add=TRUE, fg = rep("grey", 2))
+
+# good trees 
+symbols(c(7, 2,-4), c(-5, 3, -5), circles=c(4, 3, 2), inches=FALSE, add=TRUE, fg = rep("forestgreen", 2))
+
+# Centers of trees
+points(c(15, -5, 7, 2, -4), c(2, 10.5, -5, 3, -5), pch=as.character(1:5), col="black", cex=0.7) # pch=19
+
+# Add axis lines for reference (optional)
+# abline(h=0, v=0, col="gray")
+
+```
+
+```{r}
+# Set up the plotting area
+my_plot <- plot(1, type="n", xlab="", ylab="", xlim=c(-20, 20), ylim=c(-20, 20), asp=1, xaxt="n", yaxt="n")+
+
+  # axis.ticks.x = element_blank(),
+  # Draw three concentric circles with increasing radius
+  symbols(0, 0, circles=10, inches=FALSE, add=TRUE, fg = "navyblue")+
+
+  # Bad trees
+  symbols(c(15, -5, -11), c(2, 10.5, -11), circles=c(2.5, 3.7, 2), inches=FALSE, add=TRUE, fg = rep("grey", 2))+
+
+  # good trees 
+  symbols(c(7, 4,-4), c(-5, 3.5, -5), circles=c(4, 3.5, 2), inches=FALSE, add=TRUE, fg = rep("forestgreen", 2))+
+
+  # Centers of trees
+  points(c(15, -5, 7, 4, -4, -11), c(2, 10.5, -5, 3.5, -5, -11), pch=as.character(1:6), col="black", cex=0.7) # pch=19
+
+# Sampled point
+points(0, 0, pch=19, col="red", cex=0.7) # pch=19
+points(-0.2, -0.72, pch="S", col="red", cex=0.7)
+
+# theme(axis.text.x = element_blank(), axis.text.y = element_blank())
+#theme(axis.ticks.x = element_blank(), axis.ticks.y = element_blank())
+```
+
+```{r}
+# Set up the plotting area
+my_plot <- plot(1, type="n", xlab="", ylab="", xlim=c(-16, 16), ylim=c(-16, 16), asp=1, xaxt="n", yaxt="n")+
+
+  # axis.ticks.x = element_blank(),
+  # Draw three concentric circles with increasing radius
+  symbols(0, 0, circles=10, inches=FALSE, add=TRUE, fg = "navyblue")+
+
+  # Bad trees
+  symbols(c(15, -5, -11), c(2, 10.5, -11), circles=c(2.5, 3.7, 2), inches=FALSE, add=TRUE, fg = rep("grey", 2))+
+
+  # Good trees 
+  symbols(c(7, 4,-4), c(-5, 3.5, -5), circles=c(4, 3.5, 2), inches=FALSE, add=TRUE, fg = rep("forestgreen", 2))+
+
+  # Centers of trees
+  points(c(15, -5, 7, 4, -4, -11), c(2, 10.5, -5, 3.5, -5, -11), pch=as.character(1:6), col="black", cex=0.7) # pch=19
+
+# Sampled point
+points(0, 0, pch=19, col="red", cex=0.7) # pch=19
+points(-0.2, -0.72, pch="S", col="red", cex=0.7)
+```

### 2024-08-22 All3_tables.Rmd
Cleaner map and cleaner tables

@@
 tab_real <- real_df %>%
-  kable("latex", booktabs = TRUE, align = "lccc", linesep = c("", "\\addlinespace", "", "", "", ""), 
+  kable("latex", booktabs = FALSE, align = "lccc", linesep = c("", "\\addlinespace", "", "", "", ""), 
         caption = paste("True values proper to the database"), col.names = gsub("[.]", " ", names(real_df))) %>% # \\hline
@@
 tab_ci <- df_total %>%
-  kable("latex", booktabs = TRUE, align = "llcccc", linesep = c("", "", "", "\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "\\hline"), caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>% # \\hline
+  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>%
   kable_styling(latex_options = "hold_position") %>%
-  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
-  collapse_rows(columns = 1, latex_hline = "major")
+  row_spec(0, bold = TRUE) %>%
+  row_spec(c(0, 16,32), hline_after = T) %>% 
+  row_spec(c(16,32), hline_after = T) %>% 
+  collapse_rows(columns = 1, valign = "middle")
 ```

### 2024-08-22 All_tables.Rmd
Cleaner map and cleaner tables

@@
 ```{r}
-B0 <- 1000
+B0 <- 10
 ```
@@
 ```{r}
-B1 <- 200
-B2 <- 100
+B1 <- 10
+B2 <- 10
 ```
@@
 tab_ci <- df_total %>%
-  kable("latex", booktabs = TRUE, align = "llcccc", linesep = c("", "", "", "\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "\\hline"), caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>% # \\hline
+  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>% # \\hline
   kable_styling(latex_options = "hold_position") %>%
-  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
-  collapse_rows(columns = 1, latex_hline = "major")
+  row_spec(0, bold = TRUE) %>%
+  row_spec(c(0, 16,32), hline_after = T) %>% 
+  row_spec(c(16,32), hline_after = T) %>% 
+  collapse_rows(columns = 1, valign = "middle")
 ```
@@
 tab_var <- diff_var %>%
-  kable("latex", booktabs = TRUE, align = "lc", linesep = c("", "", "",
+  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
   "\\addlinespace"), caption = paste("Comparison of the two methods when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline

### 2024-08-22 Map_FR.Rmd
Cleaner map and cleaner tables

--- 2024-08-20 Map_FR.Rmd
@@
 ---
-title: "Map of France"
+title: "Map of France with a grid"
 output: pdf_document
-date: "2024-08-20"
+date: "2024-08-21"
 ---
+
+Goal: to produce a map of France with a grid and colored small squares
 
@@
 ```{r}
-library(ggplot2)
-```
-
-## Test
-
-```{r}
-map <- map_data("france")
-ggplot(map)
-```
-
-# Another test
-
-```{r}
-install.packages("CARTElette")
-library(CARTElette)
+install.packages("ggplot2")
+install.packages("sf")
+install.packages("ggspatial")
 ```
@@
 ```{r}
-shp_commune <- charger_carte(COG = 2019, nivsupra = "COM")
-```
-
-# No despair
-
-```{r}
-install.packages("sf")
-install.packages("tmap")
+library(ggplot2)
+library(sf)
+library(ggspatial)
 ```
@@
 ```{r}
-library(sf)
-library(tmap)
+install.packages("rnaturalearth")
+install.packages("rnaturalearthdata")
+library(rnaturalearth)
+library(rnaturalearthdata)
+
+# Get the map data for metropolitan France
+france <- ne_countries(scale = "medium", country = "France", returnclass = "sf")
 ```
@@
 ```{r}
-departements_l93 <- read_sf("~/work/Sim_article2024/DEPARTEMENT.shp")
-```
+# Create a data frame with the coordinates and colors
+# grid_data <- expand.grid(x = 1:30, y = 1:30)  # 10x10 grid
+# grid_data$color <- "white"  # Default color for all squares
 
-# The cat
+# (10--5)*2 = 30
+# (51.5-41)*2 = 21
 
-```{r}
-# Installer les packages nécessaires si vous ne les avez pas déjà
-install.packages(c("sf", "rnaturalearth", "ggplot2", "rnaturalearthdata"))
+# Function to sample at random following the grid
+sampling_grid <- function(i){
+  cells_x <- c()
+  cells_y <- c()
 
-# Charger les packages
-library(sf)
-library(rnaturalearth)
-library(ggplot2)
+  for (l in 0:20) {
+    if (l==0){
+      x_init <- i
+    }else if ((3*l+i) < 10){
+      x_init <- (3*l+i)
+    }else{
+      x_init <- (((3*l+i))%%(10))
+    }
+    k <- 0
+    while (x_init + 10*k < 30) {
+      a <- x_init + 10*k
+      b <- l
+      cells_x <- append(cells_x, a)
+      # print(a)
+      cells_y <- append(cells_y, b)
+      # print(b)
+      k <- k+1
+    }
+  }
+  return(data.frame(x = cells_x, y = cells_y))
+}
+
+test <- sampling_grid(3)
 ```
@@
 ```{r}
-# Télécharger les données du fond de carte
-france_map <- ne_countries(scale = "medium", country = "France", returnclass = "sf")
+# Define grid parameters
+xmin <- -5   # Westernmost longitude
+xmax <- 10   # Easternmost longitude
+ymin <- 41   # Southernmost latitude
+ymax <- 51.5   # Northernmost latitude
+grid_size <- 0.5  # Grid size in degrees
 
-# Afficher la carte de la France métropolitaine
-ggplot(data = france_map) +
-  geom_sf() +
-  coord_sf(xlim = c(-6, 10), ylim = c(41, 52), expand = FALSE) +
-  geom_tile(data = grid_data, aes(x = lon, y = lat, fill = color), alpha = 0.5) +
-  theme_minimal() +
-  labs(title = "Carte de la France Métropolitaine")
+# Create a grid
+grid <- expand.grid(
+  x = seq(xmin, xmax, by = grid_size),
+  y = seq(ymin, ymax, by = grid_size)
+)
 
+# Convert the grid to an sf object
+grid_sf <- st_as_sf(grid, coords = c("x", "y"), crs = 4326)
+
+# Convert grid points to grid cells (polygons)
+grid_sf <- st_make_grid(grid_sf, cellsize = c(grid_size, grid_size))
+
+# Highlight specific cells
+highlighted_cells <- grid_sf[test$x + (test$y)*30, ]  # Example: highlight specific cells
+highlighted_cells <- st_sf(geometry = highlighted_cells, color = "red")  # Assign color
+
+# Combine highlighted and non-highlighted cells
+grid_sf <- st_sf(geometry = grid_sf, color = "white")
+grid_sf$color[which(grid_sf$geometry %in% highlighted_cells$geometry)] <- highlighted_cells$color
 ```
@@
 ```{r}
+### First step: all chosen small squares in the grid
 
-# Télécharger les données du fond de carte
-france_map <- ne_countries(scale = "medium", country = "France", returnclass = "sf")
-
-# Définir les limites de la France métropolitaine pour la grille
-xlims <- c(-6, 10)
-ylims <- c(40, 52)
-
-cell_width <- 1.0  # largeur des cases
-cell_height <- 1.0  # hauteur des cases
-
-# Créer une grille régulière de coordonnées
-grid_data <- expand.grid(
-  lon = seq(xlims[1], xlims[2], by = 0.1),  # Espacement horizontal
-  lat = seq(ylims[1], ylims[2], by = 0.1)   # Espacement vertical
-)
-
-# Créer une colonne fictive pour colorier certaines cases
-grid_data$color <- ifelse(grid_data$lon > 2 & grid_data$lon < 4 & 
-                            grid_data$lat > 46 & grid_data$lat < 48, 
-                          "highlight", "normal")
-
-# Afficher la carte avec la grille par-dessus
-ggplot(data = france_map) +
-  geom_sf(fill = "white", color = "black") +
-  coord_sf(xlim = xlims, ylim = ylims, expand = FALSE) +
-  geom_tile(data = grid_data, aes(x = lon, y = lat, fill = color), alpha = 0.5) +
-  scale_fill_manual(values = c("highlight" = "red", "normal" = "transparent")) +
+# Plot the map
+ggplot() +
+  geom_sf(data = france, fill = "lightblue") +
+  geom_sf(data = grid_sf, aes(fill = color), color = "black", alpha = 0.4) +
+  scale_fill_identity() +  # Use the colors defined in the grid_sf object
+  coord_sf(xlim = c(xmin, xmax), ylim = c(ymin, ymax)) +
   theme_minimal() +
-  labs(title = "Carte de la France Métropolitaine avec une Grille")
-
+  ggtitle("Firs-stage sampling: sampling of cells within a grid") 
+# +
+  # annotation_scale(location = "bl") + # location = NULL
+  # annotation_north_arrow(location = "bl")
 ```
@@
 ```{r}
-# Définir les limites de la France métropolitaine pour la grille
-xlims <- c(-5, 10)
-ylims <- c(41, 52)
+# Intersect grid with the map of France
+intersected <- st_intersection(grid_sf, france)
 
-# Définir la taille des cases de la grille
-cell_width <- 1.0  # largeur des cases
-cell_height <- 1.0  # hauteur des cases
+# Create a new column to determine land or water (or other features)
+# Here, we'll simply mark if a grid cell intersects with land (France)
+grid_sf$color2 <- ifelse(st_intersects(grid_sf, france, sparse = FALSE), "green", "blue")
+```
 
-# Créer une grille régulière de coordonnées
-grid_data <- expand.grid(
-  lon = seq(xlims[1], xlims[2], by = cell_width),  # Espacement horizontal
-  lat = seq(ylims[1], ylims[2], by = cell_height)  # Espacement vertical
-)
+```{r}
+grid_sf$color3 <- ifelse((grid_sf$color2 == "green") & (grid_sf$color == "red"), "orange", "white")
+```
 
-# Créer une colonne fictive pour colorier certaines cases (à modifier selon vos besoins)
-grid_data$color <- ifelse(grid_data$lon > 2 & grid_data$lon < 4 & 
-                            grid_data$lat > 46 & grid_data$lat < 48, 
-                          "highlight", "normal")
+```{r}
+### Second step: all chosen small squares that have at least a land part
 
-# Afficher la carte avec la grille par-dessus
+# Plot the map with color-coded grid cells
 ggplot() +
-  geom_sf(data = france_map, fill = "white", color = "black") +
-  coord_sf(xlim = xlims, ylim = ylims, expand = FALSE) +
-  geom_tile(data = grid_data, aes(x = lon, y = lat, fill = color), 
-            width = cell_width, height = cell_height, alpha = 0.5) +
-  scale_fill_manual(values = c("highlight" = "red", "normal" = "transparent")) +
-  theme_minimal() +
-  labs(title = "Carte de la France Métropolitaine avec une Grille")
-
+  geom_sf(data = france, fill = "lightblue") +
+  geom_sf(data = grid_sf, aes(fill = color3), color = "black", alpha = 0.4) +
+  scale_fill_identity() +  # Use the colors defined in the grid_sf object
+  coord_sf(xlim = c(xmin, xmax), ylim = c(ymin, ymax)) +
+  theme_minimal() 
+# +
+  # ggtitle("")
 ```

### 2024-08-22 Plot_grids.R
One more grid V1 v2

@@ -6,7 +6,7 @@ library(ggplot2)
 ### Version 1 -----------
 
 # Create a data frame with the coordinates and colors
-grid_data <- expand.grid(x = 1:30, y = 1:30)  # 10x10 grid
+grid_data <- expand.grid(x = 1:30, y = 1:30)  # 30x30 grid
 grid_data$color <- "white"  # Default color for all squares
 
 # Specify the squares to be colored
@@ -33,10 +33,59 @@ ggplot(grid_data, aes(x = x, y = y, fill = color.y)) +
   ) +
   coord_fixed()  # Ensure squares are not stretched
 
+### 2nd version of Version 1 -----------
+
+# Create a data frame with the coordinates and colors
+grid_data <- expand.grid(x = 1:23, y = 1:30)  # 30x23 grid
+grid_data$color <- "white"  # Default color for all squares
+
+# Function to sample at random following the grid
+sampling_grid <- function(i){
+  cells_x <- c()
+  cells_y <- c()
+  raw <- c()
+  elt <- i
+  while (elt < (30*23)) {
+    raw <- append(raw, elt)
+    elt <- elt+10
+  }
+  for (j in raw) {
+    cells_x <- append(cells_x, j%%23)
+    cells_y <- append(cells_y, (j-(j%%23))/23)
+  }
+  return(data.frame(x = cells_x, y = cells_y))
+}
+
+test <- sampling_grid(3)
+
+colored_squares <- data.frame(
+  x = test$x,
+  y = test$y +1,
+  color = c(rep("orange", 30*23))
+)
+
+# Merge the colored squares into the grid data
+grid_data <- merge(grid_data, colored_squares, by = c("x", "y"), all.x = TRUE)
+grid_data$color.y[is.na(grid_data$color.y)] <- "white" # Set NA colors to white
+# c(rep("white", 100))
+
+ggplot(grid_data, aes(x = x, y = y, fill = color.y)) +
+  geom_tile(colour = "black") +  # Draw the squares with black borders # 
+  scale_fill_identity() +  # Use the colors specified in the data
+  theme_minimal() +  # Minimal theme for better visualization
+  theme(
+    axis.title = element_blank(),  # Remove axis titles
+    axis.text = element_blank(),   # Remove axis text
+    axis.ticks = element_blank(),  # Remove axis ticks
+    panel.grid = element_blank()   # Remove grid lines
+  ) +
+  coord_fixed()  # Ensure squares are not stretched
[…]

### 2024-08-22 Plot_grids.R
Corrected mistake

@@ -50,8 +50,8 @@ sampling_grid <- function(i){
     elt <- elt+10
   }
   for (j in raw) {
-    cells_x <- append(cells_x, j%%23)
-    cells_y <- append(cells_y, (j-(j%%23))/23)
+    cells_x <- append(cells_x, ifelse(j%%23 == 0, 23, j%%23))
+    cells_y <- append(cells_y, ifelse(j%%23 == 0, ((j-(j%%23))/23) - 1, (j-(j%%23))/23) )
   }
   return(data.frame(x = cells_x, y = cells_y))
 }

### 2024-08-23 Plot_circles.R
Correct plots for circles

@@ -1,0 +1,54 @@
+##### To plot circles and trees (for the report) ----------
+
+### Plot one circle -------------
+
+# Set up the plotting area
+my_plot <- plot(1, type="n", xlab="", ylab="", xlim=c(-16, 16), ylim=c(-16, 16), asp=1, xaxt="n", yaxt="n")+
+  
+  # Draw one circle
+  symbols(0, 0, circles=10, inches=FALSE, add=TRUE, fg = "navyblue")+
+  
+  # Bad trees
+  symbols(c(15, -5, -11), c(2, 10.5, -11), circles=c(2.5, 3.7, 2), inches=FALSE, add=TRUE, fg = rep("grey", 2))+
+  
+  # Good trees 
+  symbols(c(7, 4,-4), c(-5, 3.5, -5), circles=c(4, 3.5, 2), inches=FALSE, add=TRUE, fg = rep("forestgreen", 2))+
+  
+  # Centers of trees
+  points(c(15, -5, 7, 4, -4, -11), c(2, 10.5, -5, 3.5, -5, -11), pch=as.character(1:6), col="black", cex=0.7) # pch=19
+
+# Sampled point (center of the first circle)
+points(0, 0, pch=19, col="red", cex=0.7) # pch=19
+points(-0.2, -0.72, pch="S", col="red", cex=0.7)
+
+coord_fixed() 
+
+### Plot three circles -------------
+
+# Set up the plotting area
+my_plot3 <- plot(1, type="n", xlab="", ylab="", xlim=c(-10, 10), ylim=c(-10, 10), asp=1, xaxt="n", yaxt="n")
+
+# Draw three concentric circles with increasing radius
+symbols(rep(0, 2), rep(0, 2), circles=c(6, 9), inches=FALSE, add=TRUE, fg = rep("navyblue", 2))
+
+## Medium trees
+# 0.705/(2*pi) = 0.1122042; 1.175/(2*pi) = 0.1870071
+# Bad medium
+symbols(c(9.5), c(-6.5), circles=c(3), inches=FALSE, add=TRUE, fg = rep("grey", 1))
+# Good medium
+symbols(c(7, -4), c(2, 3), circles=c(2.5, 3.6), inches=FALSE, add=TRUE, fg = rep("forestgreen", 2))
+
+## Little trees
+# 0.235/(2*pi) = 0.03740141; 0.705/(2*pi) = 0.1122042
+# Bad little
[…]

### 2024-08-24 All3_tables_strat.Rmd
Minor changes and a file for stratified bootstrap

--- 2024-08-24 All3_tables_grid.Rmd
@@
 
-  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-1))
+  df_boot <- data.frame(useless = rep(0, nrow(df_sample)/2)) # Only one out of 2 values
   for (b in 1:B) {
-    nb <- sample(1:nrow(df_sample), (nrow(df_sample)-1), replace = TRUE)
-    # (n-1) points at random
+    nb <- c()
+    for (stratum in 1:(nrow(df_sample)/2)) {
+      strat_res <- sample(c(stratum*2-1, stratum*2), 1)
+      nb <- append(nb, strat_res)
+    }
+    # (n/2) points at random
     sample_b <- df_sample[nb,]
@@
   return(df_boot)
-  # Return a data frame with B samples of (nb_var+2) variables and of size (n-1)
+  # Return a data frame with B samples of (nb_var+2) variables and of size (n/2)
 }
@@
 
-  n <- nrow(df) + 1 # sample size of the initial sample
+  n <- nrow(df)*2 # sample size of the initial sample
   nboot <- length(df)/(nb_var+2) # number of bootstrap samples
@@
     big_est <- mapply(function(vec_, j){
-        vec_[c] <- (n/(n-1))*sum(df[, 2 + j + ((nb_var+2)*(c-1))]/p)
+        vec_[c] <- (2)*sum(df[, 2 + j + ((nb_var+2)*(c-1))]/p)
         return(as.data.frame(vec_))
         }, big_est, 1:nb_var)
-    # (n/(n-1)) is the correction needed since we choose only (n-1) points
+    # (2) is the correction needed since we choose only (n/2) points
   }
@@
 ```{r}
-B0 <- 1000
+B0 <- 10000
 ```
@@
 ```{r}
-B1 <- 300
-B2 <- 200
+B1 <- 1000
+B2 <- 400
 ```

### 2024-08-24 All_tables.Rmd
Minor changes and a file for stratified bootstrap

@@
   sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
-  round(sum(trees$v)/nrow(trees), digits = 2), round(sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), digits = 2), round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), digits = 2), round(sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),]), digits = 2)
+  round(sum(trees$v)/nrow(trees), digits = 3), round(sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),]), digits = 3)
   )
@@
 B1 <- 10
-B2 <- 10
+B2 <- 9
 ```

### 2024-08-26 All3_tables.Rmd
Changed rounds

@@
   sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
-  round(sum(trees$v)/nrow(trees), digits = 2), round(sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), digits = 2), round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), digits = 2), round(sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),]), digits = 2)
+  sum(trees$v)/nrow(trees), sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),])
   )
 
-cat("True integrals are the following:\n\nNumber of trees:", real_val[1], "\nTotal volume:", real_val[5], 
-    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", real_val[9],
-    "\n\nNumber of small trees:", real_val[2], "\nVolume of small trees:", real_val[6], 
-    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[10],
-    "\n\nNumber of medium trees:", real_val[3], "\nVolume of medium trees:", real_val[7], 
-    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[11],
-    "\n\nNumber of big trees:", real_val[4], "\nVolume of big trees:", real_val[8], 
-    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[12]
+real_val_read <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
+  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
+  round(sum(trees$v)/nrow(trees), digits = 3), round(sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),]), digits = 3)
+  )
+
+cat("True integrals are the following:\n\nNumber of trees:", real_val_read[1], "\nTotal volume:", real_val_read[5], 
+    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", real_val_read[9],
+    "\n\nNumber of small trees:", real_val_read[2], "\nVolume of small trees:", real_val_read[6], 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val_read[10],
+    "\n\nNumber of medium trees:", real_val_read[3], "\nVolume of medium trees:", real_val_read[7], 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val_read[11],
+    "\n\nNumber of big trees:", real_val_read[4], "\nVolume of big trees:", real_val_read[8], 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val_read[12]
     )
@@
 ```{r}
-real_df <- data.frame(c("All trees", "Small trees", "Medium trees", "Big trees"), matrix(real_val, nrow = 4))
+real_df <- data.frame(c("All trees", "Small trees", "Medium trees", "Big trees"), matrix(real_val_read, nrow = 4))
 colnames(real_df) <- c("", "Number", "Volume", "Ratio Volume/Number")

### 2024-08-26 All_tables.Rmd
Changed rounds

@@
   sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
+  sum(trees$v)/nrow(trees), sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),])
+  )
+
+real_val_read <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
+  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
   round(sum(trees$v)/nrow(trees), digits = 3), round(sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),]), digits = 3)
@@
 
-cat("True integrals are the following:\n\nNumber of trees:", real_val[1], "\nTotal volume:", real_val[5], 
-    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", real_val[9],
-    "\n\nNumber of small trees:", real_val[2], "\nVolume of small trees:", real_val[6], 
-    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[10],
-    "\n\nNumber of medium trees:", real_val[3], "\nVolume of medium trees:", real_val[7], 
-    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[11],
-    "\n\nNumber of big trees:", real_val[4], "\nVolume of big trees:", real_val[8], 
-    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val[12]
+cat("True integrals are the following:\n\nNumber of trees:", real_val_read[1], "\nTotal volume:", real_val_read[5], 
+    "\nWhich leads to the following ratio \"Total volume / Number of trees\":", real_val_read[9],
+    "\n\nNumber of small trees:", real_val_read[2], "\nVolume of small trees:", real_val_read[6], 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val_read[10],
+    "\n\nNumber of medium trees:", real_val_read[3], "\nVolume of medium trees:", real_val_read[7], 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val_read[11],
+    "\n\nNumber of big trees:", real_val_read[4], "\nVolume of big trees:", real_val_read[8], 
+    "\nWhich leads to the following ratio \"Volume / Number of trees\":", real_val_read[12]
     )

### 2024-08-27 First_steps/No_tree_no_grid.Rmd
No_tree with tables

--- 2024-07-08 No_tree_no_grid.Rmd
@@
 library(tibble) # for add_column and tibble
+library(kableExtra) # To have LaTeX tables based on dataframes
 ```
@@
 
+$V[\hat{\tau}_{y\pi}(S)] = \frac{n}{A} \times \frac{A}{2} - \frac{1}{n} \times (\frac{A}{2})^{2} $
+
 ```{r}
@@
 ```{r}
-# f_ind(x,y)^2 = f_ind(x,y)
 varTHEO_x <- val_x2/p - (1/n)*(val_x^2)
@@
 ```{r}
-res <- true_vs_MC(n = 1000, B = 1000, f = f_1)
-cat("True integral:", 1e+06, "\nMean of all the estimations:", res[1])
-cat("\n\nTheoretical variance:", varTHEO_area, "\nMonte-Carlo variance:", res[2])
+res1 <- true_vs_MC(n = 1000, B = 1000, f = f_1)
+cat("True integral:", 1e+06, "\nMean of all the estimations:", res1[1])
+cat("\n\nTheoretical variance:", varTHEO_area, "\nMonte-Carlo variance:", res1[2])
 # Totals: 1e+06 and 1e+06 (Equality as always)
@@
 ```{r}
-res <- true_vs_MC(n = 1000, B = 1000, f = f_ind)
-cat("True integral:", 500000, "\nMean of all the estimations:", res[1])
-cat("\n\nTheoretical variance:", varTHEO_ind, "\nMonte-Carlo variance:", res[2])
+res2 <- true_vs_MC(n = 1000, B = 1000, f = f_ind)
+cat("True integral:", 500000, "\nMean of all the estimations:", res2[1])
+cat("\n\nTheoretical variance:", varTHEO_ind, "\nMonte-Carlo variance:", res2[2])
 # Ex:
@@
 ```{r}
-res <- true_vs_MC(n = 1000, B = 1000, f = f_x)
-cat("True integral:", 5e+08, "\nMean of all the estimations:", res[1])
-cat("\n\nTheoretical variance:", varTHEO_x, "\nMonte-Carlo variance:", res[2])
+res3 <- true_vs_MC(n = 1000, B = 1000, f = f_x)
+cat("True integral:", 5e+08, "\nMean of all the estimations:", res3[1])
+cat("\n\nTheoretical variance:", varTHEO_x, "\nMonte-Carlo variance:", res3[2])
 # Ex:
@@
 ```
+# Nice table
+
+```{r}
+# Theoretical variances and values
+VAR_theo <- c(varTHEO_area, varTHEO_ind, varTHEO_x)
+VAL_theo <- c(area, half_area, val_x)
+THEO_df <- as.data.frame(cbind(VAL_theo, VAR_theo))
+```
+
+```{r}
+RES_df <- as.data.frame(rbind(res1,res2,res3))
+```
+
+```{r}
+# `Parameter of interest` = fct_names,
+
+# Table for comparison
+diff_var <- data.frame(`Difference between totals` = paste0(round(mapply(function(x,y){unlist(100*(max(x,y)-min(x,y))/min(x, y))}, unlist(THEO_df[1]), unlist(RES_df[1])), digits = 3), "%"), `Difference between variances` = paste0(round(mapply(function(x,y){100*(max(x,y)-min(x,y))/min(x,y)}, unlist(THEO_df[2]), unlist(RES_df[2])), digits = 3), "%") )
+# diff_var <- ifelse(diff_var == "NaN%", 0, diff_var)
+diff_var[diff_var == "NaN%"] <- "0%"
+```
+
+```{r}
+tab_var <- diff_var %>%
+  kable("latex", booktabs = FALSE, align = "cc", linesep = c("", "", "",
+  "\\addlinespace"), caption = paste("Assessment of the efficiency with samples with size 1000 and 1000 Monte Carlo iterations"), col.names = gsub("[.]", " ", names(diff_var))) %>%
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
+  collapse_rows(columns = 1, latex_hline = "major")
+```
+
+```{r}
+# The table itself
+tab_var
+```
+
+```{r}
+# The code that produced the table
+cat(tab_var)
+```

### 2024-08-29 Plot_grids.R
3rd strata scheme

@@ -3,6 +3,8 @@
 install.packages("ggplot2")
 library(ggplot2)
 
+library(tidyverse) # for arrange
+
 ### Version 1 -----------
 
 # Create a data frame with the coordinates and colors
@@ -81,7 +83,6 @@ ggplot(grid_data, aes(x = x, y = y, fill = color.y)) +
   ) +
   coord_fixed()  # Ensure squares are not stretched
 
-
 ### Version 2 -----------
 
 # Create a data frame with the coordinates and colors
@@ -105,9 +106,9 @@ sampling_grid <- function(i){
     while (x_init + 10*k < 30) {
       a <- x_init + 10*k
       b <- l
-      cells_x <- append(cells_x, a)
+      cells_x <- append(cells_x, ifelse(j%%23 == 0, 23, a))
       print(a)
-      cells_y <- append(cells_y, b)
+      cells_y <- append(cells_y, ifelse(j%%23 == 0, ((j-(j%%23))/23) - 1, b ))
       print(b)
       k <- k+1
     }
@@ -139,6 +140,7 @@ ggplot(grid_data, aes(x = x, y = y, fill = color.y)) +
     panel.grid = element_blank()   # Remove grid lines
   ) +
   coord_fixed()  # Ensure squares are not stretched
+
 
 ### Version 3 -----------
 
@@ -325,3 +327,67 @@ ggplot(grid_data, aes(x = x, y = y, fill = color)) +
     panel.grid = element_blank()   # Remove grid lines
   ) +
   coord_fixed()  # Ensure squares are not stretched
+
+### Strata 3: 2 by 2 ------------
+
+# Create a data frame with the coordinates and colors
+grid_data <- expand.grid(x = 1:30, y = 1:30)  # 30x30 grid
+grid_data$color <- "white"  # Default color for all squares
+
+# Function to sample at random following the grid
+sampling_grid <- function(i){
+  cells_x <- c()
+  cells_y <- c()
+  
+  for (l in 0:29) {
+    if (l==0){
+      x_init <- i
+    }else if ((3*l+i) < 10){
+      x_init <- (3*l+i)
+    }else{
+      x_init <- (((3*l+i))%%(10))
+    }
+    k <- 0
+    while (x_init + 10*k < 30) {
+      a <- x_init + 10*k
+      b <- l
+      cells_x <- append(cells_x, a)
+      print(a)
+      cells_y <- append(cells_y, b)
+      print(b)
+      k <- k+1
+    }
+  }
[…]

### 2024-08-30 First_steps/No_tree_no_grid.Rmd
RB instead of RPD

@@
 # Table for comparison
-diff_var <- data.frame(`Difference between totals` = paste0(round(mapply(function(x,y){unlist(100*(max(x,y)-min(x,y))/min(x, y))}, unlist(THEO_df[1]), unlist(RES_df[1])), digits = 3), "%"), `Difference between variances` = paste0(round(mapply(function(x,y){100*(max(x,y)-min(x,y))/min(x,y)}, unlist(THEO_df[2]), unlist(RES_df[2])), digits = 3), "%") )
+diff_var <- data.frame(`Difference between totals` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, unlist(THEO_df[1]), unlist(RES_df[1])), digits = 3), "%"), `Difference between variances` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, unlist(THEO_df[2]), unlist(RES_df[2])), digits = 3), "%") )
 # diff_var <- ifelse(diff_var == "NaN%", 0, diff_var)

### 2024-08-31 All3_tables_grid.Rmd
Right numbers
Relative stability

@@
 ```{r}
-B0 <- 1000
+B0 <- 10 #10000
 ```
@@
 ```{r}
-B1 <- 300
-B2 <- 200
+B1 <- 5 # 1000
+B2 <- 5 # 400
 ```
@@
 # Example:
+```
+
+```{r}
+# Relative stability
+RS <- function(list_var, target_var){
+  # 
+  in_sum <- c()
+  for (elt in list_var) {
+    in_sum <- append(in_sum, (elt - target_var)**2)
+  }
+  return(100*(((1/length(list_var))*sum(in_sum))**(1/2))/target_var)
+}
+```
+
+```{r}
+VAR_boot <- list()
+for (j in VAR_names) {
+  VAR_boot[[length(VAR_boot)+1]] <- get(x = j)
+}
+
+rs_df <- mapply(RS, VAR_boot, res1$Variances)
+```
+
+```{r}
+# Table for comparison
+DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(round(rs_df, digits = 3), "%") )
+```
+
+```{r}
+tab_rs <- DF_rs %>%
+  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
+  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
+  collapse_rows(columns = 1, latex_hline = "major")
+```
+
+```{r}
+# The table itself
+tab_rs
+```
+
+```{r}
+# The code that produced the table
+cat(tab_rs)
 ```

### 2024-08-31 All3_tables_strat.Rmd
Relative stability

@@
 ```{r}
+# Relative stability
+RS <- function(list_var, target_var){
+  # 
+  in_sum <- c()
+  for (elt in list_var) {
+    in_sum <- append(in_sum, (elt - target_var)**2)
+  }
+  return(100*(((1/length(list_var))*sum(in_sum))**(1/2))/target_var)
+}
+```
+
+```{r}
+VAR_boot <- list()
+for (j in VAR_names) {
+  VAR_boot[[length(VAR_boot)+1]] <- get(x = j)
+}
+
+rs_df <- mapply(RS, VAR_boot, res1$Variances)
+```
+
+```{r}
+# Table for comparison
+DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(round(rs_df, digits = 3), "%") )
+```
+
+```{r}
+tab_rs <- DF_rs %>%
+  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
+  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
+  collapse_rows(columns = 1, latex_hline = "major")
+```
+
+```{r}
+# The table itself
+tab_rs
+```
+
+```{r}
+# The code that produced the table
+cat(tab_rs)
+```
+
+```{r}
 coverage_rate <- function(k){

### 2024-09-02 All3_tables.Rmd
Right numbers
Relative Bias

@@
 raw_names <- c("x", "y", "nb", "nb_s","nb_m", "nb_b", "vol", "vol_s", "vol_m", "vol_b", "ratio", "ratio_s", "ratio_m", "ratio_b")
+```
+
+```{r}
+# All the names of the parameters of interest, explicitly
+PARAM_names <- c("Number of trees", "Number of small trees", "Number of medium trees", "Number of big trees", "Volume of trees", "Volume of small trees", "Volume of medium trees", "Volume of big trees", "Ratio for all trees", "Ratio for small trees", "Ratio for medium trees", "Ratio for big trees")
 ```
@@
 df_total <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-PARAM_names <- c("Number of trees", "Number of small trees", "Number of medium trees", "Number of big trees", "Volume of trees", "Volume of small trees", "Volume of medium trees", "Volume of big trees", "Ratio for all trees", "Ratio for small trees", "Ratio for medium trees", "Ratio for big trees")
 meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
@@
 ```{r}
-diff_percent <- function(j){unlist(100*(max(res1$Variances[j],VAR_df[j])-min(res1$Variances[j],VAR_df[j]))/min(res1$Variances[j],VAR_df[j]))}
-cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1), "%", "\n - for the volume of trees: ", diff_percent(5), "%\n - for the ratio volume / number of trees: ", diff_percent(9), "%",
+diff_percent <- function(j){unlist(100*(VAR_df[j]-res1$Variances[j])/res1$Variances[j])}
+# function(x,y){unlist(100*(y-x)/x)}
+cat("Relative Bias of the variance: \n - for the number of trees: ", diff_percent(1), "%", "\n - for the volume of trees: ", diff_percent(5), "%\n - for the ratio volume / number of trees: ", diff_percent(9), "%",
     "\n\n - for the number of small trees: ", diff_percent(2), "%", "\n - for the volume of small trees: ", diff_percent(6), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10), "%",
@@
 # Table for comparison
-diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Difference between variances` = paste0(round(mapply(function(x,y){100*(max(x,y)-min(x,y))/min(x,y)}, VAR_df, res1$Variances), digits = 3), "%") )
+diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Relative Bias` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, res1$Variances, VAR_df), digits = 3), "%") )
 ```

### 2024-09-02 All3_tables_grid.Rmd
Relative Bias

@@
 title: "Monte Carlo and bootstrap for ALL parameters with tables"
-output: pdf_document
+output:
+  html_document:
+    df_print: paged
 date: "2024-08-16"
@@
 ```{r}
-diff_percent <- function(j){unlist(100*(max(res1$Variances[j],VAR_df[j])-min(res1$Variances[j],VAR_df[j]))/min(res1$Variances[j],VAR_df[j]))}
-cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(1), "%", "\n - for the volume of trees: ", diff_percent(5), "%\n - for the ratio volume / number of trees: ", diff_percent(9), "%",
+diff_percent <- function(j){unlist(100*(VAR_df[j]-res1$Variances[j])/res1$Variances[j])}
+cat("Relative Bias of the variance: \n - for the number of trees: ", diff_percent(1), "%", "\n - for the volume of trees: ", diff_percent(5), "%\n - for the ratio volume / number of trees: ", diff_percent(9), "%",
     "\n\n - for the number of small trees: ", diff_percent(2), "%", "\n - for the volume of small trees: ", diff_percent(6), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10), "%",

### 2024-09-02 All3_tables.Rmd
Relative Stability

@@
 ```{r}
+# Relative stability
+RS <- function(list_var, target_var){
+  # 
+  in_sum <- c()
+  for (elt in list_var) {
+    in_sum <- append(in_sum, (elt - target_var)**2)
+  }
+  return(100*(((1/length(list_var))*sum(in_sum))**(1/2))/target_var)
+}
+```
+
+```{r}
+VAR_boot <- list()
+for (j in VAR_names) {
+  VAR_boot[[length(VAR_boot)+1]] <- get(x = j)
+}
+
+rs_df <- mapply(RS, VAR_boot, res1$Variances)
+```
+
+```{r}
+# Table for comparison
+DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(round(rs_df, digits = 3), "%") )
+```
+
+```{r}
+tab_rs <- DF_rs %>%
+  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
+  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
+  row_spec(c(0, 4, 8), hline_after = T) %>% 
+  collapse_rows(columns = 1, latex_hline = "major")
+```
+
+```{r}
+# The table itself
+tab_rs
+```
+
+```{r}
+# The code that produced the table
+cat(tab_rs)
+```
+
+```{r}
 coverage_rate <- function(k){
@@
   row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
+  row_spec(c(0, 4, 8), hline_after = T) %>% 
   collapse_rows(columns = 1, latex_hline = "major")

### 2024-09-02 All3_tables_grid.Rmd
Relative Stability

@@
     df_print: paged
+  pdf_document: default
 date: "2024-08-16"

### 2024-09-02 Plot_grids.R
Plot with strata 2 by 2

@@ -106,9 +106,9 @@ sampling_grid <- function(i){
     while (x_init + 10*k < 30) {
       a <- x_init + 10*k
       b <- l
-      cells_x <- append(cells_x, ifelse(j%%23 == 0, 23, a))
+      cells_x <- append(cells_x, ifelse(a%%30 == 0, 30, a))
       print(a)
-      cells_y <- append(cells_y, ifelse(j%%23 == 0, ((j-(j%%23))/23) - 1, b ))
+      cells_y <- append(cells_y, b) # ifelse(a%%23 == 0, b - 1, b )
       print(b)
       k <- k+1
     }
@@ -351,7 +351,7 @@ sampling_grid <- function(i){
     while (x_init + 10*k < 30) {
       a <- x_init + 10*k
       b <- l
-      cells_x <- append(cells_x, a)
+      cells_x <- append(cells_x, ifelse(a%%30 == 0, 30, a))
       print(a)
       cells_y <- append(cells_y, b)
       print(b)
@@ -380,7 +380,7 @@ grid_data[grid_data$color.y == "orange",]$number <- rep(1:45, each = 2)
 
 ggplot(grid_data, aes(x = x, y = y, fill = color.y)) +
   geom_tile(colour = "black") +  # Draw the squares with black borders
-  geom_text(aes(label = number), size = 5, na.rm = TRUE) +
+  geom_text(aes(label = number), size = 3, na.rm = TRUE) +
   scale_fill_identity() +  # Use the colors specified in the data
   theme_minimal() +  # Minimal theme for better visualization
   theme(

### 2024-09-02 Plot_grids.R
Correct Grid_V3

@@ -154,7 +154,7 @@ sampling_grid <- function(c_dim){
   
   for (l in 0:((30)-1)) { # For all lines
     for (bunch in 1:(30/10)) { # 10 is the size of each bunch
-      x_sampled <- sample(0:9, 1) + (bunch-1)*10
+      x_sampled <- sample(1:10, 1) + (bunch-1)*10
       a <- x_sampled
       b <- l
       random_points <- rbind(random_points, list(a,b))

### 2024-09-02 Plot_grids.R
Correct strata 1 and 2

@@ -215,7 +215,7 @@ sampling_grid <- function(i){
     while (x_init + 10*k < 30) {
       a <- x_init + 10*k
       b <- l
-      cells_x <- append(cells_x, a)
+      cells_x <- append(cells_x, ifelse(a%%30 == 0, 30, a))
       # print(a)
       cells_y <- append(cells_y, b)
       # print(b)
@@ -284,7 +284,7 @@ sampling_grid <- function(i){
       a <- x_init + 10*k
       b <- l
       h <- (length(cells_x)+1)%%10
-      cells_x <- append(cells_x, a)
+      cells_x <- append(cells_x, ifelse(a%%30 == 0, 30, a))
       # print(a)
       cells_y <- append(cells_y, b)
       # print(b)

### 2024-09-03 All3_tables_grid_copy.Rmd
A different way to build the grid

--- 2024-09-02 All3_tables_grid.Rmd
@@
 # Function to sample at random following the grid
-sampling_grid <- function(i,c_dim){
+# Algorithm 7 in the report (2024/10/02 version)
+sampling_grid1 <- function(i,c_dim){
 random_points <- data.frame(x = numeric(), y = numeric())
@@
 
+```{r}
+# A more random algorithm
+# Algorithm 8 in the report (2024/10/02 version)
+sampling_grid2 <- function(i, c_dim){
+  random_points <- data.frame(x = numeric(), y = numeric())
+
+  for (l in 0:((1000/c_dim)-1)) { # For all lines
+    for (bunch in 1:((1000/c_dim)/10)) { # 10 is the size of each bunch
+      x_sampled <- sample(0:9, 1) + (bunch-1)*10
+      # a <- x_sampled
+      a <- runif(1, x_sampled*c_dim, x_sampled*c_dim + c_dim) # + 10*c_dim*bunch
+      # b <- l
+      b <- runif(1, l*c_dim, (l+1)*c_dim)
+      random_points <- rbind(random_points, list(a,b))
+    }
+  }
+  colnames(random_points) <- list("x", "y")
+  return(random_points)
+}
+
+```
+
 # Functions
@@
 
-MonteCarlo <- function(n, B){
+MonteCarlo <- function(n, B, f_sampling){
   # n: sample size;
@@
     # Sampling in the territory
-    df_grid <- sampling_grid(i,c_dim)
+    df_grid <- f_sampling(i,c_dim)
     xy <- data.frame(a1 = df_grid$x, a2 = df_grid$y)
@@
 
-MC_boot <- function(n, B1, B2){
+MC_boot <- function(n, B1, B2, f_sampling){
   # n: sample size;
@@
 ```{r}
-B0 <- 10 #10000
+B0 <- 10000 # 10 # 
 ```
@@
 
-res1 <- MonteCarlo(n, B0)
+res1 <- MonteCarlo(n, B0, sampling_grid2)
 # Just one circle to begin with
@@
 ```{r}
-B1 <- 5 # 1000
-B2 <- 5 # 400
+B1 <- 1000 # 5
+B2 <- 400 # 5
 ```
@@
 
-res2 <- MC_boot(n, B1, B2)
+res2 <- MC_boot(n, B1, B2, sampling_grid2)
 # Just one circle to begin with
@@
 # Table for comparison
-DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(round(rs_df, digits = 3), "%") )
+DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(round(rs_df, digits = 2), "%") )
 ```
@@
     # Coverage rate
-    assign( TC_names[j], round((1/nrow(x))*sum( mapply(function(a,b){as.numeric((real_val[j] > a) & (real_val[j] < b))}, x[1], x[2]) ), digits = 2))
+    assign( TC_names[j], (1/nrow(x))*sum( mapply(function(a,b){as.numeric((real_val[j] > a) & (real_val[j] < b))}, x[1], x[2]) ))
     TC <- append(TC, get(TC_names[j]))
     # Lower tail
-    assign( low_names[j], round((1/nrow(x))*sum( mapply(function(a){as.numeric(real_val[j] < a)}, x[1]) ), digits = 2))
+    assign( low_names[j], (1/nrow(x))*sum( mapply(function(a){as.numeric(real_val[j] < a)}, x[1]) ))
     Lower <- append(Lower, get(low_names[j]))
     # Upper tail
-    assign( up_names[j], round((1/nrow(x))*sum( mapply(function(b){as.numeric(real_val[j] > b)}, x[2]) ), digits = 2))
+    assign( up_names[j], (1/nrow(x))*sum( mapply(function(b){as.numeric(real_val[j] > b)}, x[2]) ))
     Upper <- append(Upper, get(up_names[j]))
     # Mean length of CIs
-    assign( length_names[j], round((1/nrow(x))*sum( mapply(function(a,b){b-a}, x[1], x[2]) ), digits = 2))
+    assign( length_names[j], (1/nrow(x))*sum( mapply(function(a,b){b-a}, x[1], x[2]) ))
     Mean_length <- append(Mean_length, get(length_names[j]))
@@
 ### Clean data frame to create a LaTeX table
+# For totals
 
-df_total <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
+df_total1 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
 meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
 
-for (param in 1:12) {
+for (param in 1:8) {
   df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
@@
   for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
-    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(TC_meth[param,1:3]*100, "%"), round(TC_meth[param,4], digits = 2) ))))
+    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 2) ))))
     k <- k+1
   }
-  df_total <- rbind(df_total, df_param)
+  df_total1 <- rbind(df_total1, df_param)
 }
 
-colnames(df_total) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
+colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
 ```
@@
 ```{r}
-tab_ci <- df_total %>%
+tab_ci1 <- df_total1 %>%
   kable("latex", booktabs = FALSE, align = "llcccc", caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>%
@@
   row_spec(0, bold = TRUE) %>%
-  row_spec(c(0, 16,32), hline_after = T) %>% 
-  row_spec(c(16,32), hline_after = T) %>% 
+  row_spec(c(0, 16), hline_after = T) %>% 
+  row_spec(c(16), hline_after = T) %>% 
   collapse_rows(columns = 1, valign = "middle")
@@
 # The table itself
-tab_ci
+tab_ci1
 ```
@@
 # The code that produced the table
-cat(tab_ci)
+cat(tab_ci1)
+```
+
+```{r}
+### Clean data frame to create a LaTeX table
+# For totals
+
+df_total2 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
+meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
+
+for (param in 9:12) {
+  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
+  k <- 1
+  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
+    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 5) ))))
+    k <- k+1
+  }
+  df_total2 <- rbind(df_total2, df_param)
+}
+
+colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
+```
+
+```{r}
+tab_ci2 <- df_total2 %>%
+  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>%
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>%
+  row_spec(c(0), hline_after = T) %>% 
+  # row_spec(c(16,32), hline_after = T) %>% 
+  collapse_rows(columns = 1, valign = "middle")
+```
+
+```{r}
+# The table itself
+tab_ci2
+```
+
+```{r}
+# The code that produced the table
+cat(tab_ci2)
 ```
@@
 # Table for comparison
-diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Relative Bias` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, res1$Variances, VAR_df), digits = 3), "%") )
+diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Monte Carlo Relative Bias` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, res1$Variances, VAR_df), digits = 2), "%") )
 ```
@@
   kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\addlinespace"), caption = paste("Comparison of the two methods when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
+  "\\addlinespace"), caption = paste("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
   kable_styling(latex_options = "hold_position") %>%

### 2024-09-04 All3_tables_grid_copy.Rmd
Reorganised and more complete

@@
 
-```{r}
-# Sample size
-n <- 1000
-```
+## Target values
 
@@
 
+## Useful character vectors
+
 ```{r}
@@
 PARAM_names <- c("Number of trees", "Number of small trees", "Number of medium trees", "Number of big trees", "Volume of trees", "Volume of small trees", "Volume of medium trees", "Volume of big trees", "Ratio for all trees", "Ratio for small trees", "Ratio for medium trees", "Ratio for big trees")
+```
+
+## Values and functions necessary to sample
+
+```{r}
+# Sample size
+n <- 1000
 ```
@@
 ```{r}
+# Uniform sampling, no grid
+sampling_unif <- function(i,c_dim){
+  random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
+  return(random_points)
+}
+```
+
+```{r}
+# Function to sample at random following the grid
+# Algorithm 6 in the report (2024/10/02 version)
+sampling_grid1 <- function(i, c_dim){
+  cells_x <- c()
+  cells_y <- c()
+  raw <- c()
+  elt <- i
+  while (elt < (1000*1000)) {
+    raw <- append(raw, elt)
+    elt <- elt+10
+  }
+  for (j in raw) {
+    cells_x <- append(cells_x, ifelse(j%%23 == 0, 23, j%%23))
+    cells_y <- append(cells_y, ifelse(j%%23 == 0, ((j-(j%%23))/23) - 1, (j-(j%%23))/23) )
+  }
+  return(data.frame(x = cells_x, y = cells_y))
+}
+```
+
+```{r}
 # Function to sample at random following the grid
 # Algorithm 7 in the report (2024/10/02 version)
-sampling_grid1 <- function(i,c_dim){
+sampling_grid2 <- function(i,c_dim){
 random_points <- data.frame(x = numeric(), y = numeric())
@@
 # Algorithm 8 in the report (2024/10/02 version)
-sampling_grid2 <- function(i, c_dim){
+sampling_grid3 <- function(i, c_dim){
   random_points <- data.frame(x = numeric(), y = numeric())
@@
 
-# Example
+## Other useful functions
+
+```{r}
+# Relative stability
+RS <- function(list_var, target_var){
+  # 
+  in_sum <- c()
+  for (elt in list_var) {
+    in_sum <- append(in_sum, (elt - target_var)**2)
+  }
+  return(100*(((1/length(list_var))*sum(in_sum))**(1/2))/target_var)
+}
+```
+
+```{r}
+# Based on MC_boot results
+coverage_rate <- function(k, res2){
+  # k: integer to target one specific method to create confidence intervals
+  # res2: results from MC_boot
+
+  nam_lim <- paste0("lim_", raw_names)[-(1:2)]
+  CI_names <- paste0("CI_", raw_names)[-(1:2)]
+  TC_names <- paste0("TC_", raw_names)[-(1:2)]
+  low_names <- paste0("low_", raw_names)[-(1:2)]
+  up_names <- paste0("up_", raw_names)[-(1:2)]
+  length_names <- paste0("length_", raw_names)[-(1:2)]
+
+  for (j in CI_names) {
+    assign(j, data.frame(matrix(numeric(0), nrow = 2)))
+  }
+  for (elt in res2$`Confidence Intervals`) { # For each MC iteration
+    for (j in 1:length(CI_names)) { # For each estimation
+      x <- cbind(get(x = CI_names[j]), elt[k][[1]][colnames(elt[k][[1]]) == nam_lim[j]]) # elt[k]
+      assign(CI_names[j], x)
+    }
+  }
+
+  TC <- c()
+  Lower <- c()
+  Upper <- c()
+  Mean_length <- c()
+  for (j in 1:(length(CI_names))) {
+    x <- as.data.frame(t(get(x = CI_names[j])))
+    # Coverage rate
+    assign( TC_names[j], (1/nrow(x))*sum( mapply(function(a,b){as.numeric((real_val[j] > a) & (real_val[j] < b))}, x[1], x[2]) ))
+    TC <- append(TC, get(TC_names[j]))
+    # Lower tail
+    assign( low_names[j], (1/nrow(x))*sum( mapply(function(a){as.numeric(real_val[j] < a)}, x[1]) ))
+    Lower <- append(Lower, get(low_names[j]))
+    # Upper tail
+    assign( up_names[j], (1/nrow(x))*sum( mapply(function(b){as.numeric(real_val[j] > b)}, x[2]) ))
+    Upper <- append(Upper, get(up_names[j]))
+    # Mean length of CIs
+    assign( length_names[j], (1/nrow(x))*sum( mapply(function(a,b){b-a}, x[1], x[2]) ))
+    Mean_length <- append(Mean_length, get(length_names[j]))
+  }
+
+  df_TC <- data.frame(TC, Lower, Upper, Mean_length)
+
+  return(df_TC)
+}
+```
+
+# Examples
+
+```{r}
+# Monte carlo alone
+# Number of MC iterations
+B0 <- 10000 # 10 # 
+```
+
+```{r}
+# Monte Carlo and bootstrap
+# Number of MC iterations
+B1 <- 1000 # 5 # 
+# Number of bootstrap replications
+B2 <- 400 # 5 # 
+```
+
+# Example: Algorithm 8
 
@@
 ```{r}
-B0 <- 10000 # 10 # 
+fun_samp <- sampling_grid3
 ```
@@
 
-res1 <- MonteCarlo(n, B0, sampling_grid2)
+res1 <- MonteCarlo(n, B0, fun_samp)
 # Just one circle to begin with
@@
 ```{r}
-B1 <- 1000 # 5
-B2 <- 400 # 5
-```
-
-```{r}
 start.time <- Sys.time()
 
-res2 <- MC_boot(n, B1, B2, sampling_grid2)
+res2 <- MC_boot(n, B1, B2, fun_samp)
 # Just one circle to begin with
@@
 ```{r}
-# Relative stability
-RS <- function(list_var, target_var){
-  # 
-  in_sum <- c()
-  for (elt in list_var) {
-    in_sum <- append(in_sum, (elt - target_var)**2)
-  }
-  return(100*(((1/length(list_var))*sum(in_sum))**(1/2))/target_var)
-}
-```
-
-```{r}
 VAR_boot <- list()
@@
 ```{r}
-coverage_rate <- function(k){
-  # k: integer to target one specific method to create confidence intervals
-
-  nam_lim <- paste0("lim_", raw_names)[-(1:2)]
-  CI_names <- paste0("CI_", raw_names)[-(1:2)]
-  TC_names <- paste0("TC_", raw_names)[-(1:2)]
-  low_names <- paste0("low_", raw_names)[-(1:2)]
-  up_names <- paste0("up_", raw_names)[-(1:2)]
-  length_names <- paste0("length_", raw_names)[-(1:2)]
-
-  for (j in CI_names) {
-    assign(j, data.frame(matrix(numeric(0), nrow = 2)))
-  }
-  for (elt in res2$`Confidence Intervals`) { # For each MC iteration
-    for (j in 1:length(CI_names)) { # For each estimation
-      x <- cbind(get(x = CI_names[j]), elt[k][[1]][colnames(elt[k][[1]]) == nam_lim[j]]) # elt[k]
-      assign(CI_names[j], x)
-    }
-  }
-
-  TC <- c()
-  Lower <- c()
-  Upper <- c()
-  Mean_length <- c()
-  for (j in 1:(length(CI_names))) {
-    x <- as.data.frame(t(get(x = CI_names[j])))
-    # Coverage rate
-    assign( TC_names[j], (1/nrow(x))*sum( mapply(function(a,b){as.numeric((real_val[j] > a) & (real_val[j] < b))}, x[1], x[2]) ))
-    TC <- append(TC, get(TC_names[j]))
-    # Lower tail
-    assign( low_names[j], (1/nrow(x))*sum( mapply(function(a){as.numeric(real_val[j] < a)}, x[1]) ))
-    Lower <- append(Lower, get(low_names[j]))
-    # Upper tail
-    assign( up_names[j], (1/nrow(x))*sum( mapply(function(b){as.numeric(real_val[j] > b)}, x[2]) ))
-    Upper <- append(Upper, get(up_names[j]))
-    # Mean length of CIs
-    assign( length_names[j], (1/nrow(x))*sum( mapply(function(a,b){b-a}, x[1], x[2]) ))
-    Mean_length <- append(Mean_length, get(length_names[j]))
-  }
-
-  df_TC <- data.frame(TC, Lower, Upper, Mean_length)
-
-  return(df_TC)
-}
-```
-
-```{r}
-TC_normal <- coverage_rate(1)
+TC_normal <- coverage_rate(1, res2)
 cat("Concerning the normal approach, the coverage rates are the following: \n - for the number of trees: ", 
@@
 ```{r}
-TC_perc <- coverage_rate(2)
+TC_perc <- coverage_rate(2, res2)
 cat("Concerning the percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
@@
 ```{r}
-TC_rev_perc <- coverage_rate(3)
+TC_rev_perc <- coverage_rate(3, res2)
 cat("Concerning the reverse percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
@@
 ```{r}
-TC_bca <- coverage_rate(4)
+TC_bca <- coverage_rate(4, res2)
 cat("Concerning the BCa approach, the coverage rates are the following: \n - for the number of trees: ", 

### 2024-09-04 All3_tables_grid_copy.Rmd
Add labels and alterbate colors in tables

@@
 
-```{r}
+```{r RS_algo8}
 tab_rs <- DF_rs %>%
@@
   "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
-  kable_styling(latex_options = "hold_position") %>%
+  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
   row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
@@
 
-```{r}
+```{r CI_tot_algo8}
 tab_ci1 <- df_total1 %>%
-  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>%
+  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (totals)")) %>%
   kable_styling(latex_options = "hold_position") %>%
@@
 
-```{r}
+```{r CI_ratio_algo8}
 tab_ci2 <- df_total2 %>%
-  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>%
+  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (ratios)")) %>%
   kable_styling(latex_options = "hold_position") %>%
@@
 
-```{r}
+```{r RB_algo8}
 tab_var <- diff_var %>%
   kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\addlinespace"), caption = paste("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
-  kable_styling(latex_options = "hold_position") %>%
+  "\\addlinespace"), caption = paste0("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
+  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
   row_spec(0, bold = TRUE) %>% # , hline_after = TRUE

### 2024-09-04 All3_tables_grid_copy.Rmd
With or without stratified boot

@@
 ```{r}
+## Making of bootstrap samples based on an initial sample
+f_boot_strat <- function(df_sample, B, nb_var){
+  # df_sample: initial sample with nb_est variables and of size n; 
+  # B: number of bootstrap samples made thanks to df_sample;
+  # nb_var: number of variables of interest (for totals and not ratios)
+
+  df_boot <- data.frame(useless = rep(0, nrow(df_sample)/2)) # Only one out of 2 values
+  for (b in 1:B) {
+    nb <- c()
+    for (stratum in 1:(nrow(df_sample)/2)) {
+      strat_res <- sample(c(stratum*2-1, stratum*2), 1)
+      nb <- append(nb, strat_res)
+    }
+    # (n/2) points at random
+    sample_b <- df_sample[nb,]
+    df_boot <- cbind(df_boot, sample_b)
+    colnames(df_boot)[((b-1)*(nb_var+2)+1 + 1):(b*(nb_var+2)+1)] <- as.vector(mapply(function(j){paste("ech", b, colnames(df_sample)[j], sep = "")}, 1:(nb_var+2)))
+  }
+  df_boot$useless <- NULL
+  return(df_boot)
+  # Return a data frame with B samples of (nb_var+2) variables and of size (n/2)
+}
+```
+
+```{r}
 ## Making of estimations for each sample made by the bootstrap method
@@
 ```{r}
+## Making of estimations for each sample made by the bootstrap method
+est_boot_strat <- function(df, p, nb_var){
+  # df: data frame with (nb_var+2)*B columns and (n-1) rows
+  # p: inclusion density function (constant in the uniform case)
+  # nb_var: number of variables of interest (for totals and not ratios)
+
+  n <- nrow(df)*2 # sample size of the initial sample
+  nboot <- length(df)/(nb_var+2) # number of bootstrap samples
+  big_est <- as.data.frame(matrix(NA, ncol = nb_var, nrow = nboot))
+
+  # Estimations of totals
+  for (c in 1:nboot) {
+    big_est <- mapply(function(vec_, j){
+        vec_[c] <- (2)*sum(df[, 2 + j + ((nb_var+2)*(c-1))]/p)
+        return(as.data.frame(vec_))
+        }, big_est, 1:nb_var)
+    # (2) is the correction needed since we choose only (n/2) points
+  }
+  # Estimations of ratios
+  l_big_est <- length(big_est)
+  big_est <- as.data.frame(big_est)
+  for (k in 1:4) {
+    big_est <- add_column(big_est, rep(NA, nrow(big_est)))
+  }
+  for (c in 1:nboot) {
+    ratio_c <- mapply(function(j){big_est[c,j+4]/big_est[c,j]
+    }, 1:4) # 4 ratios
+    big_est[c, (l_big_est+1):(l_big_est+4) ] <- ratio_c
+  }
+  colnames(big_est) <- paste0("est_", raw_names)[-(1:2)]
+  return(big_est)
+  # Data frame with estimations for each sample
+}
+```
+
+```{r}
 ### Function to automate Monte Carlo + bootstrap method
 
-MC_boot <- function(n, B1, B2, f_sampling){
+MC_boot <- function(n, B1, B2, f_sampling, strat=FALSE){ # strat=c('TRUE','FALSE')
   # n: sample size;
@@
   # B2: number of iterations for bootstrap
-
+  # strat: which type of bootstrap
+
+  if (strat == FALSE){
+    fun_f_boot <- f_boot
+    fun_est_boot <- est_boot
+  }else{
+    fun_f_boot <- f_boot_strat
+    fun_est_boot <- est_boot_strat
+  }
   p <- sum(rep((1/1000)*(1/1000), n))
@@
     # Bootstrap iterations
-    df_boot <- f_boot(df_b, B2, nb_var)
-    est_boot_val <- est_boot(df_boot, p, nb_var)
+    df_boot <- fun_f_boot(df_b, B2, nb_var)
+    est_boot_val <- fun_est_boot(df_boot, p, nb_var)
 
@@
 
-# Example: Algorithm 8
+# Example: Algorithm 8 with basic bootstrap
+
+```{r}
+fun_samp <- sampling_grid3
+```
 
 ## Monte Carlo alone
-
-```{r}
-fun_samp <- sampling_grid3
-```
 
@@
 ```
+
+# Example: Algorithm 8 with stratified bootstrap
+
+```{r}
+fun_samp <- sampling_grid3
+```
+
+## Monte Carlo alone
+
+```{r}
+start.time <- Sys.time()
+
+res1 <- MonteCarlo(n, B0, fun_samp)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```
+
+```{r}
+cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(unlist(res1$Estimations[1])), "\n - for the volume of trees:", mean(unlist(res1$Estimations[5])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[9])),
+    "\n\n - for the number of small trees:", mean(unlist(res1$Estimations[2])), "\n - for the volume of small trees:", mean(unlist(res1$Estimations[6])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[10])),
+    "\n\n - for the number of medium trees:", mean(unlist(res1$Estimations[3])), "\n - for the volume of medium trees:", mean(unlist(res1$Estimations[7])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[11])),
+    "\n\n - for the number of big trees:", mean(unlist(res1$Estimations[4])), "\n - for the volume of big trees:", mean(unlist(res1$Estimations[8])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[12]))
+    )
+
+# Example:
+```
+
+```{r}
+cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[5], "\n - for the ratio volume / number of trees:", res1$Variances[9],
+    "\n\n - for the number of small trees:", res1$Variances[2], "\n - for the volume of small trees:", res1$Variances[6], "\n - for the ratio volume / number of trees:", res1$Variances[10],
+    "\n\n - for the number of medium trees:", res1$Variances[3], "\n - for the volume of medium trees:", res1$Variances[7], "\n - for the ratio volume / number of trees:", res1$Variances[11],
+    "\n\n - for the number of big trees:", res1$Variances[4], "\n - for the volume of big trees:", res1$Variances[8], "\n - for the ratio volume / number of trees:", res1$Variances[12])
+
+# Example:
+```
+
+## Monte Carlo and bootstrap
+
+```{r}
+start.time <- Sys.time()
+
+res2 <- MC_boot(n, B1, B2, fun_samp, strat = TRUE)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```
+
+```{r}
+# We want all the variances obtained for each parameter of interest, 
+# to find the mean for each of these series
+EST_names <- paste0("EST_", raw_names)[-(1:2)]
+
+for (j in EST_names) {
+  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
+}
+
+for (elt in res2$Estimations) {
+  if ( nrow(elt) != 1 ){ # we target bootstrap samples made from each MC iteration
+    for (j in 1:length(EST_names)) { # For each estimation
+      x <- append(get(x = EST_names[j]), mean(unlist(elt[j])))
+      assign(EST_names[j], x)
+    }
+  }
+}
+```
+
+```{r}
+cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(unlist(EST_nb)), "\n - for the volume of trees:", mean(unlist(EST_vol)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio)),
+        "\n\n - for the number of small trees:", mean(unlist(EST_nb_s)), "\n - for the volume of small trees:", mean(unlist(EST_vol_s)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_s)),
+    "\n\n - for the number of medium trees:", mean(unlist(EST_nb_m)), "\n - for the volume of medium trees:", mean(unlist(EST_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_m)),
+    "\n\n - for the number of big trees:", mean(unlist(EST_nb_b)), "\n - for the volume of big trees:", mean(unlist(EST_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_b)))
+
+# Example:
+```
+
+```{r}
+# We want all the variances obtained for each parameter of interest, 
+# to find the mean for each of these series
+VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
+
+for (j in VAR_names) {
+  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
+}
+
+for (elt in res2$Variances) {
+  for (j in 1:length(VAR_names)) { # For each estimation
+    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
+    assign(VAR_names[j], x)
+  }
+}
+```
+
+```{r}
+# We want all the variances obtained for each parameter of interest, 
+# to find the mean for each of these series
+VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
+VAR_df <- c()
+
+for (j in VAR_names) {
+  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
+}
+
+for (elt in res2$Variances) {
+  for (j in 1:length(VAR_names)) { # For each estimation
+    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
+    assign(VAR_names[j], x)
+  }
+}
+
+VAR_df <- c(mapply(function(j){mean(unlist(get(x = VAR_names[j])))}, 1:12))
+```
+
+```{r}
+cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", VAR_df[1], "\n - for the volume of trees:", VAR_df[5], "\n - for the ratio volume / number of trees:", VAR_df[9],
+        "\n\n - for the number of small trees:", VAR_df[2], "\n - for the volume of small trees:", VAR_df[6], "\n - for the ratio volume / number of trees:", VAR_df[10],
+    "\n\n - for the number of medium trees:", VAR_df[3], "\n - for the volume of medium trees:", VAR_df[7], "\n - for the ratio volume / number of trees:", VAR_df[11],
+    "\n\n - for the number of big trees:", VAR_df[4], "\n - for the volume of big trees:", VAR_df[8], "\n - for the ratio volume / number of trees:", VAR_df[12])
+
+# Example:
+```
+
+```{r}
+VAR_boot <- list()
+for (j in VAR_names) {
+  VAR_boot[[length(VAR_boot)+1]] <- get(x = j)
+}
+
+rs_df <- mapply(RS, VAR_boot, res1$Variances)
+```
+
+```{r}
+# Table for comparison
+DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(round(rs_df, digits = 2), "%") )
+```
+
+```{r RS_algo8_strat}
+tab_rs <- DF_rs %>%
+  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
+  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
+  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
+  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
+  row_spec(c(0, 4, 8), hline_after = T) %>% 
+  collapse_rows(columns = 1, latex_hline = "major")
+```
+
+```{r}
+# The table itself
+tab_rs
+```
+
+```{r}
+# The code that produced the table
+cat(tab_rs)
+```
+
+```{r}
+TC_normal <- coverage_rate(1, res2)
+cat("Concerning the normal approach, the coverage rates are the following: \n - for the number of trees: ", 
+    TC_normal[1,1], "\n - for the volume of trees: ", TC_normal[2,1], "\n - for the ratio volume / number of trees: ", TC_normal[3,1],
+    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_normal[1,2], "\n - for the volume of trees: ", TC_normal[2,2], "\n - for the ratio volume / number of trees: ", TC_normal[3,2],
+    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_normal[1,3], "\n - for the volume of trees: ", TC_normal[2,3], "\n - for the ratio volume / number of trees: ", TC_normal[3,3],
+    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
+    TC_normal[1,4], "\n - for the volume of trees: ", TC_normal[2,4], "\n - for the ratio volume / number of trees: ", TC_normal[3,4])
+```
+
+```{r}
+TC_perc <- coverage_rate(2, res2)
+cat("Concerning the percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
+    TC_perc[1,1], "\n - for the volume of trees: ", TC_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_perc[3,1],
+    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_perc[1,2], "\n - for the volume of trees: ", TC_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_perc[3,2],
+    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_perc[1,3], "\n - for the volume of trees: ", TC_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_perc[3,3],
+    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
+    TC_perc[1,4], "\n - for the volume of trees: ", TC_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_perc[3,4])
+```
+
+```{r}
+TC_rev_perc <- coverage_rate(3, res2)
+cat("Concerning the reverse percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
+    TC_rev_perc[1,1], "\n - for the volume of trees: ", TC_rev_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,1],
+    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_rev_perc[1,2], "\n - for the volume of trees: ", TC_rev_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,2],
+    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_rev_perc[1,3], "\n - for the volume of trees: ", TC_rev_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,3],
+    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
+    TC_rev_perc[1,4], "\n - for the volume of trees: ", TC_rev_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,4])
+```
+
+```{r}
+TC_bca <- coverage_rate(4, res2)
+cat("Concerning the BCa approach, the coverage rates are the following: \n - for the number of trees: ", 
+    TC_bca[1,1], "\n - for the volume of trees: ", TC_bca[2,1], "\n - for the ratio volume / number of trees: ", TC_bca[3,1],
+    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_bca[1,2], "\n - for the volume of trees: ", TC_bca[2,2], "\n - for the ratio volume / number of trees: ", TC_bca[3,2],
+    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_bca[1,3], "\n - for the volume of trees: ", TC_bca[2,3], "\n - for the ratio volume / number of trees: ", TC_bca[3,3],
+    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
+    TC_bca[1,4], "\n - for the volume of trees: ", TC_bca[2,4], "\n - for the ratio volume / number of trees: ", TC_bca[3,4])
+```
+
+```{r}
+### Clean data frame to create a LaTeX table
+# For totals
+
+df_total1 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
+meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
+
+for (param in 1:8) {
+  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
+  k <- 1
+  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
+    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 2) ))))
+    k <- k+1
+  }
+  df_total1 <- rbind(df_total1, df_param)
+}
+
+colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
+```
+
+```{r CI_tot_algo8_strat}
+tab_ci1 <- df_total1 %>%
+  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (totals)")) %>%
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>%
+  row_spec(c(0, 16), hline_after = T) %>% 
+  row_spec(c(16), hline_after = T) %>% 
+  collapse_rows(columns = 1, valign = "middle")
+```
+
+```{r}
+# The table itself
+tab_ci1
+```
+
+```{r}
+# The code that produced the table
+cat(tab_ci1)
+```
+
+```{r}
+### Clean data frame to create a LaTeX table
+# For totals
+
+df_total2 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
+meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
+
+for (param in 9:12) {
+  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
+  k <- 1
+  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
+    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 5) ))))
+    k <- k+1
+  }
+  df_total2 <- rbind(df_total2, df_param)
+}
+
+colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
+```
+
+```{r CI_ratio_algo8_strat}
+tab_ci2 <- df_total2 %>%
+  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (ratios)")) %>%
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>%
+  row_spec(c(0), hline_after = T) %>% 
+  # row_spec(c(16,32), hline_after = T) %>% 
+  collapse_rows(columns = 1, valign = "middle")
+```
+
+```{r}
+# The table itself
+tab_ci2
+```
+
+```{r}
+# The code that produced the table
+cat(tab_ci2)
+```
+
+## Comparison of the variances
+
+```{r}
+diff_percent <- function(j){unlist(100*(VAR_df[j]-res1$Variances[j])/res1$Variances[j])}
+cat("Relative Bias of the variance: \n - for the number of trees: ", diff_percent(1), "%", "\n - for the volume of trees: ", diff_percent(5), "%\n - for the ratio volume / number of trees: ", diff_percent(9), "%",
+    "\n\n - for the number of small trees: ", diff_percent(2), "%", "\n - for the volume of small trees: ", diff_percent(6), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10), "%",
+    "\n\n - for the number of medium trees: ", diff_percent(3), "%", "\n - for the volume of medium trees: ", diff_percent(7), "%", "\n - for the ratio volume / number of trees: ", diff_percent(11), "%",
+    "\n\n - for the number of big trees: ", diff_percent(4), "%", "\n - for the volume of big trees: ", diff_percent(8), "%", "\n - for the ratio volume / number of trees: ", diff_percent(12), "%",
+    sep = "")
+
+# Example:
+```
+
+```{r}
+# Table for comparison
+diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Monte Carlo Relative Bias` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, res1$Variances, VAR_df), digits = 2), "%") )
+```
+
+```{r RB_algo8_strat}
+tab_var <- diff_var %>%
+  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
+  "\\addlinespace"), caption = paste0("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
+  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
+  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
+  row_spec(c(0, 4, 8), hline_after = T) %>% 
+  collapse_rows(columns = 1, latex_hline = "major")
+```
+
+```{r}
+# The table itself
+tab_var
+```
+
+```{r}
+# The code that produced the table
+cat(tab_var)
+```

### 2024-09-05 First_steps/No_tree_no_grid.Rmd
Cleaner table

@@
 title: "Uniform sampling across the whole territory without any cells"
-output: pdf_document
+output:
+  html_document:
+    df_print: paged
 date: "2024-06-25"
@@
   est_MC <- c()
+  var_est <- c()
   for (c in 1:B) {
     est_MC <- append(est_MC, sum((rho_MC[c])/p))
+    in_sum <- unlist(mapply(function(x){((x*area) - sum((rho_MC[c])/p))^2}, rho_MC[c]))
+    var_est <- append(var_est, (1/(n*(n-1)))*sum(in_sum))
   }
 
-  return(c(mean(est_MC), var(est_MC)))
+  # var_est <- (1/(n(n-1)))*sum(in_sum)
+
+  return(c(mean(est_MC), mean(var_est))) # , var(est_MC)
   # Estimated value and Monte-Carlo variance
@@
 # Table for comparison
-diff_var <- data.frame(`Difference between totals` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, unlist(THEO_df[1]), unlist(RES_df[1])), digits = 3), "%"), `Difference between variances` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, unlist(THEO_df[2]), unlist(RES_df[2])), digits = 3), "%") )
-# diff_var <- ifelse(diff_var == "NaN%", 0, diff_var)
-diff_var[diff_var == "NaN%"] <- "0%"
+diff_var <- data.frame(Functions = c("$(x_1,x_2) \\mapsto 1$", "$(x_1,x_2) \\mapsto \\mathds{1} \\{x_1>x_2\\}$", "$(x_1,x_2) \\mapsto x_1$"), `Difference between totals` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, unlist(THEO_df[1]), unlist(RES_df[1])), digits = 2), "\\%"), `Difference between variances` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, unlist(THEO_df[2]), unlist(RES_df[2])), digits = 2), "\\%") )
+diff_var[diff_var == "NaN\\%"] <- "0\\%" # In case unlist(THEO_df[X]) == 0
 ```
 
-```{r}
+```{r MC_simple}
 tab_var <- diff_var %>%
-  kable("latex", booktabs = FALSE, align = "cc", linesep = c("", "", "",
+  kable("latex", escape = FALSE, booktabs = FALSE, align = "cc", linesep = c("", "", "",
   "\\addlinespace"), caption = paste("Assessment of the efficiency with samples with size 1000 and 1000 Monte Carlo iterations"), col.names = gsub("[.]", " ", names(diff_var))) %>%

### 2024-09-06 All3_tables_grid_algo7.Rmd
One file for each algo

--- 2024-09-04 All3_tables_grid_copy.Rmd
@@
 
-# Example: Algorithm 8 with basic bootstrap
-
-```{r}
-fun_samp <- sampling_grid3
+# Example: Algorithm 7 with basic bootstrap
+
+```{r}
+fun_samp <- sampling_grid2
 ```
@@
 
-```{r RS_algo8}
+```{r RS_algo7}
 tab_rs <- DF_rs %>%
@@
 
-```{r CI_tot_algo8}
+```{r CI_tot_algo7}
 tab_ci1 <- df_total1 %>%
@@
 
-```{r CI_ratio_algo8}
+```{r CI_ratio_algo7}
 tab_ci2 <- df_total2 %>%
@@
 
-```{r RB_algo8}
+```{r RB_algo7}
 tab_var <- diff_var %>%
@@
 
-# Example: Algorithm 8 with stratified bootstrap
-
-```{r}
-fun_samp <- sampling_grid3
+# Example: Algorithm 7 with stratified bootstrap
+
+```{r}
+fun_samp <- sampling_grid1
 ```
@@
 
-```{r RS_algo8_strat}
+```{r RS_algo7_strat}
 tab_rs <- DF_rs %>%
@@
 
-colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
-```
-
-```{r CI_tot_algo8_strat}
+colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
+```
+
+```{r CI_tot_algo7_strat}
 tab_ci1 <- df_total1 %>%
@@
 
-colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
-```
-
-```{r CI_ratio_algo8_strat}
+colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
+```
+
+```{r CI_ratio_algo7_strat}
 tab_ci2 <- df_total2 %>%
@@
 
-```{r RB_algo8_strat}
+```{r RB_algo7_strat}
 tab_var <- diff_var %>%

### 2024-09-07 Last_tables/All3_tab_algo6.Rmd
Split codes

--- 2024-09-04 All3_tables_grid_copy.Rmd
@@
 # Number of MC iterations
-B0 <- 10000 # 10 # 
+B0 <- 10 # 10000 # 
 ```
@@
 # Number of MC iterations
-B1 <- 1000 # 5 # 
+B1 <- 5 # 1000 # 
 # Number of bootstrap replications
-B2 <- 400 # 5 # 
-```
-
-# Example: Algorithm 8 with basic bootstrap
-
-```{r}
-fun_samp <- sampling_grid3
+B2 <- 5 # 400 # 
+```
+
+# Example: Algorithm 6 with basic bootstrap
+
+```{r}
+fun_samp <- sampling_grid1
 ```
@@
 
-```{r RS_algo8}
+```{r RS_algo6}
 tab_rs <- DF_rs %>%
@@
 
-```{r CI_tot_algo8}
+```{r CI_tot_algo6}
 tab_ci1 <- df_total1 %>%
@@
 
-```{r CI_ratio_algo8}
+```{r CI_ratio_algo6}
 tab_ci2 <- df_total2 %>%
@@
 
-```{r RB_algo8}
+```{r RB_algo6}
 tab_var <- diff_var %>%
@@
 ```
-
-# Example: Algorithm 8 with stratified bootstrap
-
-```{r}
-fun_samp <- sampling_grid3
-```
-
-## Monte Carlo alone
-
-```{r}
-start.time <- Sys.time()
-
-res1 <- MonteCarlo(n, B0, fun_samp)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(unlist(res1$Estimations[1])), "\n - for the volume of trees:", mean(unlist(res1$Estimations[5])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[9])),
-    "\n\n - for the number of small trees:", mean(unlist(res1$Estimations[2])), "\n - for the volume of small trees:", mean(unlist(res1$Estimations[6])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[10])),
-    "\n\n - for the number of medium trees:", mean(unlist(res1$Estimations[3])), "\n - for the volume of medium trees:", mean(unlist(res1$Estimations[7])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[11])),
-    "\n\n - for the number of big trees:", mean(unlist(res1$Estimations[4])), "\n - for the volume of big trees:", mean(unlist(res1$Estimations[8])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[12]))
-    )
-
-# Example:
-```
-
-```{r}
-cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[5], "\n - for the ratio volume / number of trees:", res1$Variances[9],
-    "\n\n - for the number of small trees:", res1$Variances[2], "\n - for the volume of small trees:", res1$Variances[6], "\n - for the ratio volume / number of trees:", res1$Variances[10],
-    "\n\n - for the number of medium trees:", res1$Variances[3], "\n - for the volume of medium trees:", res1$Variances[7], "\n - for the ratio volume / number of trees:", res1$Variances[11],
-    "\n\n - for the number of big trees:", res1$Variances[4], "\n - for the volume of big trees:", res1$Variances[8], "\n - for the ratio volume / number of trees:", res1$Variances[12])
-
-# Example:
-```
-
-## Monte Carlo and bootstrap
-
-```{r}
-start.time <- Sys.time()
-
-res2 <- MC_boot(n, B1, B2, fun_samp, strat = TRUE)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-EST_names <- paste0("EST_", raw_names)[-(1:2)]
-
-for (j in EST_names) {
-  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
-}
-
-for (elt in res2$Estimations) {
-  if ( nrow(elt) != 1 ){ # we target bootstrap samples made from each MC iteration
-    for (j in 1:length(EST_names)) { # For each estimation
-      x <- append(get(x = EST_names[j]), mean(unlist(elt[j])))
-      assign(EST_names[j], x)
-    }
-  }
-}
-```
-
-```{r}
-cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(unlist(EST_nb)), "\n - for the volume of trees:", mean(unlist(EST_vol)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio)),
-        "\n\n - for the number of small trees:", mean(unlist(EST_nb_s)), "\n - for the volume of small trees:", mean(unlist(EST_vol_s)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_s)),
-    "\n\n - for the number of medium trees:", mean(unlist(EST_nb_m)), "\n - for the volume of medium trees:", mean(unlist(EST_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_m)),
-    "\n\n - for the number of big trees:", mean(unlist(EST_nb_b)), "\n - for the volume of big trees:", mean(unlist(EST_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_b)))
-
-# Example:
-```
-
-```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
-
-for (j in VAR_names) {
-  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
-}
-
-for (elt in res2$Variances) {
-  for (j in 1:length(VAR_names)) { # For each estimation
-    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
-    assign(VAR_names[j], x)
-  }
-}
-```
-
-```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
-VAR_df <- c()
-
-for (j in VAR_names) {
-  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
-}
-
-for (elt in res2$Variances) {
-  for (j in 1:length(VAR_names)) { # For each estimation
-    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
-    assign(VAR_names[j], x)
-  }
-}
-
-VAR_df <- c(mapply(function(j){mean(unlist(get(x = VAR_names[j])))}, 1:12))
-```
-
-```{r}
-cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", VAR_df[1], "\n - for the volume of trees:", VAR_df[5], "\n - for the ratio volume / number of trees:", VAR_df[9],
-        "\n\n - for the number of small trees:", VAR_df[2], "\n - for the volume of small trees:", VAR_df[6], "\n - for the ratio volume / number of trees:", VAR_df[10],
-    "\n\n - for the number of medium trees:", VAR_df[3], "\n - for the volume of medium trees:", VAR_df[7], "\n - for the ratio volume / number of trees:", VAR_df[11],
-    "\n\n - for the number of big trees:", VAR_df[4], "\n - for the volume of big trees:", VAR_df[8], "\n - for the ratio volume / number of trees:", VAR_df[12])
-
-# Example:
-```
-
-```{r}
-VAR_boot <- list()
-for (j in VAR_names) {
-  VAR_boot[[length(VAR_boot)+1]] <- get(x = j)
-}
-
-rs_df <- mapply(RS, VAR_boot, res1$Variances)
-```
-
-```{r}
-# Table for comparison
-DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(round(rs_df, digits = 2), "%") )
-```
-
-```{r RS_algo8_strat}
-tab_rs <- DF_rs %>%
-  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
-  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
-  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
-  row_spec(c(0, 4, 8), hline_after = T) %>% 
-  collapse_rows(columns = 1, latex_hline = "major")
-```
-
-```{r}
-# The table itself
-tab_rs
-```
-
-```{r}
-# The code that produced the table
-cat(tab_rs)
-```
-
-```{r}
-TC_normal <- coverage_rate(1, res2)
-cat("Concerning the normal approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_normal[1,1], "\n - for the volume of trees: ", TC_normal[2,1], "\n - for the ratio volume / number of trees: ", TC_normal[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_normal[1,2], "\n - for the volume of trees: ", TC_normal[2,2], "\n - for the ratio volume / number of trees: ", TC_normal[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_normal[1,3], "\n - for the volume of trees: ", TC_normal[2,3], "\n - for the ratio volume / number of trees: ", TC_normal[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_normal[1,4], "\n - for the volume of trees: ", TC_normal[2,4], "\n - for the ratio volume / number of trees: ", TC_normal[3,4])
-```
-
-```{r}
-TC_perc <- coverage_rate(2, res2)
-cat("Concerning the percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_perc[1,1], "\n - for the volume of trees: ", TC_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_perc[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_perc[1,2], "\n - for the volume of trees: ", TC_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_perc[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_perc[1,3], "\n - for the volume of trees: ", TC_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_perc[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_perc[1,4], "\n - for the volume of trees: ", TC_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_perc[3,4])
-```
-
-```{r}
-TC_rev_perc <- coverage_rate(3, res2)
-cat("Concerning the reverse percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_rev_perc[1,1], "\n - for the volume of trees: ", TC_rev_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_rev_perc[1,2], "\n - for the volume of trees: ", TC_rev_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_rev_perc[1,3], "\n - for the volume of trees: ", TC_rev_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_rev_perc[1,4], "\n - for the volume of trees: ", TC_rev_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,4])
-```
-
-```{r}
-TC_bca <- coverage_rate(4, res2)
-cat("Concerning the BCa approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_bca[1,1], "\n - for the volume of trees: ", TC_bca[2,1], "\n - for the ratio volume / number of trees: ", TC_bca[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_bca[1,2], "\n - for the volume of trees: ", TC_bca[2,2], "\n - for the ratio volume / number of trees: ", TC_bca[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_bca[1,3], "\n - for the volume of trees: ", TC_bca[2,3], "\n - for the ratio volume / number of trees: ", TC_bca[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_bca[1,4], "\n - for the volume of trees: ", TC_bca[2,4], "\n - for the ratio volume / number of trees: ", TC_bca[3,4])
-```
-
-```{r}
-### Clean data frame to create a LaTeX table
-# For totals
-
-df_total1 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
-
-for (param in 1:8) {
-  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-  k <- 1
-  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
-    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 2) ))))
-    k <- k+1
-  }
-  df_total1 <- rbind(df_total1, df_param)
-}
-
-colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
-```
-
-```{r CI_tot_algo8_strat}
-tab_ci1 <- df_total1 %>%
-  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (totals)")) %>%
-  kable_styling(latex_options = "hold_position") %>%
-  row_spec(0, bold = TRUE) %>%
-  row_spec(c(0, 16), hline_after = T) %>% 
-  row_spec(c(16), hline_after = T) %>% 
-  collapse_rows(columns = 1, valign = "middle")
-```
-
-```{r}
-# The table itself
-tab_ci1
-```
-
-```{r}
-# The code that produced the table
-cat(tab_ci1)
-```
-
-```{r}
-### Clean data frame to create a LaTeX table
-# For totals
-
-df_total2 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
-
-for (param in 9:12) {
-  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-  k <- 1
-  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
-    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 5) ))))
-    k <- k+1
-  }
-  df_total2 <- rbind(df_total2, df_param)
-}
-
-colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
-```
-
-```{r CI_ratio_algo8_strat}
-tab_ci2 <- df_total2 %>%
-  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (ratios)")) %>%
-  kable_styling(latex_options = "hold_position") %>%
-  row_spec(0, bold = TRUE) %>%
-  row_spec(c(0), hline_after = T) %>% 
-  # row_spec(c(16,32), hline_after = T) %>% 
-  collapse_rows(columns = 1, valign = "middle")
-```
-
-```{r}
-# The table itself
-tab_ci2
-```
-
-```{r}
-# The code that produced the table
-cat(tab_ci2)
-```
-
-## Comparison of the variances
-
-```{r}
-diff_percent <- function(j){unlist(100*(VAR_df[j]-res1$Variances[j])/res1$Variances[j])}
-cat("Relative Bias of the variance: \n - for the number of trees: ", diff_percent(1), "%", "\n - for the volume of trees: ", diff_percent(5), "%\n - for the ratio volume / number of trees: ", diff_percent(9), "%",
-    "\n\n - for the number of small trees: ", diff_percent(2), "%", "\n - for the volume of small trees: ", diff_percent(6), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10), "%",
-    "\n\n - for the number of medium trees: ", diff_percent(3), "%", "\n - for the volume of medium trees: ", diff_percent(7), "%", "\n - for the ratio volume / number of trees: ", diff_percent(11), "%",
-    "\n\n - for the number of big trees: ", diff_percent(4), "%", "\n - for the volume of big trees: ", diff_percent(8), "%", "\n - for the ratio volume / number of trees: ", diff_percent(12), "%",
-    sep = "")
-
-# Example:
-```
-
-```{r}
-# Table for comparison
-diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Monte Carlo Relative Bias` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, res1$Variances, VAR_df), digits = 2), "%") )
-```
-
-```{r RB_algo8_strat}
-tab_var <- diff_var %>%
-  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\addlinespace"), caption = paste0("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
-  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
-  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
-  row_spec(c(0, 4, 8), hline_after = T) %>% 
-  collapse_rows(columns = 1, latex_hline = "major")
-```
-
-```{r}
-# The table itself
-tab_var
-```
-
-```{r}
-# The code that produced the table
-cat(tab_var)
-```

### 2024-09-07 Last_tables/All3_tab_algo6_strat.Rmd
Split codes

--- 2024-09-06 All3_tables_grid_algo7.Rmd
@@
 
-In this document, \textbf{sampling through a grid} is used to create a sample and \textbf{three concentric circles} are used to compute local variables.
+In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{algorithm 6}, and \textbf{three concentric circles} are used to compute local variables.
+
+\textbf{Stratified bootstrap} is used.
 
@@
 
-# Example: Algorithm 7 with basic bootstrap
-
-```{r}
-fun_samp <- sampling_grid2
+# Example: Algorithm 6 with stratified bootstrap
+
+```{r}
+fun_samp <- sampling_grid1
 ```
@@
 
-res2 <- MC_boot(n, B1, B2, fun_samp)
+res2 <- MC_boot(n, B1, B2, fun_samp, strat = TRUE)
 # Just one circle to begin with
@@
 
-```{r RS_algo7}
+```{r RS_algo6_strat}
 tab_rs <- DF_rs %>%
@@
 
-colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
-```
-
-```{r CI_tot_algo7}
+colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
+```
+
+```{r CI_tot_algo6_strat}
 tab_ci1 <- df_total1 %>%
@@
 
-colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
-```
-
-```{r CI_ratio_algo7}
+colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
+```
+
+```{r CI_ratio_algo6_strat}
 tab_ci2 <- df_total2 %>%
@@
 
-```{r RB_algo7}
+```{r RB_algo6_strat}
 tab_var <- diff_var %>%
@@
 ```
-
-# Example: Algorithm 7 with stratified bootstrap
-
-```{r}
-fun_samp <- sampling_grid1
-```
-
-## Monte Carlo alone
-
-```{r}
-start.time <- Sys.time()
-
-res1 <- MonteCarlo(n, B0, fun_samp)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(unlist(res1$Estimations[1])), "\n - for the volume of trees:", mean(unlist(res1$Estimations[5])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[9])),
-    "\n\n - for the number of small trees:", mean(unlist(res1$Estimations[2])), "\n - for the volume of small trees:", mean(unlist(res1$Estimations[6])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[10])),
-    "\n\n - for the number of medium trees:", mean(unlist(res1$Estimations[3])), "\n - for the volume of medium trees:", mean(unlist(res1$Estimations[7])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[11])),
-    "\n\n - for the number of big trees:", mean(unlist(res1$Estimations[4])), "\n - for the volume of big trees:", mean(unlist(res1$Estimations[8])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[12]))
-    )
-
-# Example:
-```
-
-```{r}
-cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[5], "\n - for the ratio volume / number of trees:", res1$Variances[9],
-    "\n\n - for the number of small trees:", res1$Variances[2], "\n - for the volume of small trees:", res1$Variances[6], "\n - for the ratio volume / number of trees:", res1$Variances[10],
-    "\n\n - for the number of medium trees:", res1$Variances[3], "\n - for the volume of medium trees:", res1$Variances[7], "\n - for the ratio volume / number of trees:", res1$Variances[11],
-    "\n\n - for the number of big trees:", res1$Variances[4], "\n - for the volume of big trees:", res1$Variances[8], "\n - for the ratio volume / number of trees:", res1$Variances[12])
-
-# Example:
-```
-
-## Monte Carlo and bootstrap
-
-```{r}
-start.time <- Sys.time()
-
-res2 <- MC_boot(n, B1, B2, fun_samp, strat = TRUE)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-EST_names <- paste0("EST_", raw_names)[-(1:2)]
-
-for (j in EST_names) {
-  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
-}
-
-for (elt in res2$Estimations) {
-  if ( nrow(elt) != 1 ){ # we target bootstrap samples made from each MC iteration
-    for (j in 1:length(EST_names)) { # For each estimation
-      x <- append(get(x = EST_names[j]), mean(unlist(elt[j])))
-      assign(EST_names[j], x)
-    }
-  }
-}
-```
-
-```{r}
-cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(unlist(EST_nb)), "\n - for the volume of trees:", mean(unlist(EST_vol)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio)),
-        "\n\n - for the number of small trees:", mean(unlist(EST_nb_s)), "\n - for the volume of small trees:", mean(unlist(EST_vol_s)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_s)),
-    "\n\n - for the number of medium trees:", mean(unlist(EST_nb_m)), "\n - for the volume of medium trees:", mean(unlist(EST_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_m)),
-    "\n\n - for the number of big trees:", mean(unlist(EST_nb_b)), "\n - for the volume of big trees:", mean(unlist(EST_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_b)))
-
-# Example:
-```
-
-```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
-
-for (j in VAR_names) {
-  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
-}
-
-for (elt in res2$Variances) {
-  for (j in 1:length(VAR_names)) { # For each estimation
-    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
-    assign(VAR_names[j], x)
-  }
-}
-```
-
-```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
-VAR_df <- c()
-
-for (j in VAR_names) {
-  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
-}
-
-for (elt in res2$Variances) {
-  for (j in 1:length(VAR_names)) { # For each estimation
-    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
-    assign(VAR_names[j], x)
-  }
-}
-
-VAR_df <- c(mapply(function(j){mean(unlist(get(x = VAR_names[j])))}, 1:12))
-```
-
-```{r}
-cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", VAR_df[1], "\n - for the volume of trees:", VAR_df[5], "\n - for the ratio volume / number of trees:", VAR_df[9],
-        "\n\n - for the number of small trees:", VAR_df[2], "\n - for the volume of small trees:", VAR_df[6], "\n - for the ratio volume / number of trees:", VAR_df[10],
-    "\n\n - for the number of medium trees:", VAR_df[3], "\n - for the volume of medium trees:", VAR_df[7], "\n - for the ratio volume / number of trees:", VAR_df[11],
-    "\n\n - for the number of big trees:", VAR_df[4], "\n - for the volume of big trees:", VAR_df[8], "\n - for the ratio volume / number of trees:", VAR_df[12])
-
-# Example:
-```
-
-```{r}
-VAR_boot <- list()
-for (j in VAR_names) {
-  VAR_boot[[length(VAR_boot)+1]] <- get(x = j)
-}
-
-rs_df <- mapply(RS, VAR_boot, res1$Variances)
-```
-
-```{r}
-# Table for comparison
-DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(round(rs_df, digits = 2), "%") )
-```
-
-```{r RS_algo7_strat}
-tab_rs <- DF_rs %>%
-  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
-  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
-  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
-  row_spec(c(0, 4, 8), hline_after = T) %>% 
-  collapse_rows(columns = 1, latex_hline = "major")
-```
-
-```{r}
-# The table itself
-tab_rs
-```
-
-```{r}
-# The code that produced the table
-cat(tab_rs)
-```
-
-```{r}
-TC_normal <- coverage_rate(1, res2)
-cat("Concerning the normal approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_normal[1,1], "\n - for the volume of trees: ", TC_normal[2,1], "\n - for the ratio volume / number of trees: ", TC_normal[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_normal[1,2], "\n - for the volume of trees: ", TC_normal[2,2], "\n - for the ratio volume / number of trees: ", TC_normal[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_normal[1,3], "\n - for the volume of trees: ", TC_normal[2,3], "\n - for the ratio volume / number of trees: ", TC_normal[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_normal[1,4], "\n - for the volume of trees: ", TC_normal[2,4], "\n - for the ratio volume / number of trees: ", TC_normal[3,4])
-```
-
-```{r}
-TC_perc <- coverage_rate(2, res2)
-cat("Concerning the percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_perc[1,1], "\n - for the volume of trees: ", TC_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_perc[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_perc[1,2], "\n - for the volume of trees: ", TC_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_perc[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_perc[1,3], "\n - for the volume of trees: ", TC_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_perc[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_perc[1,4], "\n - for the volume of trees: ", TC_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_perc[3,4])
-```
-
-```{r}
-TC_rev_perc <- coverage_rate(3, res2)
-cat("Concerning the reverse percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_rev_perc[1,1], "\n - for the volume of trees: ", TC_rev_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_rev_perc[1,2], "\n - for the volume of trees: ", TC_rev_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_rev_perc[1,3], "\n - for the volume of trees: ", TC_rev_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_rev_perc[1,4], "\n - for the volume of trees: ", TC_rev_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,4])
-```
-
-```{r}
-TC_bca <- coverage_rate(4, res2)
-cat("Concerning the BCa approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_bca[1,1], "\n - for the volume of trees: ", TC_bca[2,1], "\n - for the ratio volume / number of trees: ", TC_bca[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_bca[1,2], "\n - for the volume of trees: ", TC_bca[2,2], "\n - for the ratio volume / number of trees: ", TC_bca[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_bca[1,3], "\n - for the volume of trees: ", TC_bca[2,3], "\n - for the ratio volume / number of trees: ", TC_bca[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_bca[1,4], "\n - for the volume of trees: ", TC_bca[2,4], "\n - for the ratio volume / number of trees: ", TC_bca[3,4])
-```
-
-```{r}
-### Clean data frame to create a LaTeX table
-# For totals
-
-df_total1 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
-
-for (param in 1:8) {
-  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-  k <- 1
-  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
-    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 2) ))))
-    k <- k+1
-  }
-  df_total1 <- rbind(df_total1, df_param)
-}
-
-colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
-```
-
-```{r CI_tot_algo7_strat}
-tab_ci1 <- df_total1 %>%
-  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (totals)")) %>%
-  kable_styling(latex_options = "hold_position") %>%
-  row_spec(0, bold = TRUE) %>%
-  row_spec(c(0, 16), hline_after = T) %>% 
-  row_spec(c(16), hline_after = T) %>% 
-  collapse_rows(columns = 1, valign = "middle")
-```
-
-```{r}
-# The table itself
-tab_ci1
-```
-
-```{r}
-# The code that produced the table
-cat(tab_ci1)
-```
-
-```{r}
-### Clean data frame to create a LaTeX table
-# For totals
-
-df_total2 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
-
-for (param in 9:12) {
-  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-  k <- 1
-  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
-    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 5) ))))
-    k <- k+1
-  }
-  df_total2 <- rbind(df_total2, df_param)
-}
-
-colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
-```
-
-```{r CI_ratio_algo7_strat}
-tab_ci2 <- df_total2 %>%
-  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (ratios)")) %>%
-  kable_styling(latex_options = "hold_position") %>%
-  row_spec(0, bold = TRUE) %>%
-  row_spec(c(0), hline_after = T) %>% 
-  # row_spec(c(16,32), hline_after = T) %>% 
-  collapse_rows(columns = 1, valign = "middle")
-```
-
-```{r}
-# The table itself
-tab_ci2
-```
-
-```{r}
-# The code that produced the table
-cat(tab_ci2)
-```
-
-## Comparison of the variances
-
-```{r}
-diff_percent <- function(j){unlist(100*(VAR_df[j]-res1$Variances[j])/res1$Variances[j])}
-cat("Relative Bias of the variance: \n - for the number of trees: ", diff_percent(1), "%", "\n - for the volume of trees: ", diff_percent(5), "%\n - for the ratio volume / number of trees: ", diff_percent(9), "%",
-    "\n\n - for the number of small trees: ", diff_percent(2), "%", "\n - for the volume of small trees: ", diff_percent(6), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10), "%",
-    "\n\n - for the number of medium trees: ", diff_percent(3), "%", "\n - for the volume of medium trees: ", diff_percent(7), "%", "\n - for the ratio volume / number of trees: ", diff_percent(11), "%",
-    "\n\n - for the number of big trees: ", diff_percent(4), "%", "\n - for the volume of big trees: ", diff_percent(8), "%", "\n - for the ratio volume / number of trees: ", diff_percent(12), "%",
-    sep = "")
-
-# Example:
-```
-
-```{r}
-# Table for comparison
-diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Monte Carlo Relative Bias` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, res1$Variances, VAR_df), digits = 2), "%") )
-```
-
-```{r RB_algo7_strat}
-tab_var <- diff_var %>%
-  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\addlinespace"), caption = paste0("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
-  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
-  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
-  row_spec(c(0, 4, 8), hline_after = T) %>% 
-  collapse_rows(columns = 1, latex_hline = "major")
-```
-
-```{r}
-# The table itself
-tab_var
-```
-
-```{r}
-# The code that produced the table
-cat(tab_var)
-```

### 2024-09-07 Last_tables/All3_tab_algo7.Rmd
Split codes

--- 2024-09-06 All3_tables_grid_algo7.Rmd
@@
 
-In this document, \textbf{sampling through a grid} is used to create a sample and \textbf{three concentric circles} are used to compute local variables.
+In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{algorithm 7}, and \textbf{three concentric circles} are used to compute local variables.
+
+\textbf{Basic bootstrap} is used.
 

### 2024-09-07 Last_tables/All3_tab_algo7_strat.Rmd
Split codes

--- 2024-09-06 All3_tables_grid_algo7.Rmd
@@
 
-In this document, \textbf{sampling through a grid} is used to create a sample and \textbf{three concentric circles} are used to compute local variables.
+In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{algorithm 7}, and \textbf{three concentric circles} are used to compute local variables.
+
+\textbf{Stratified bootstrap} is used.
 
@@
 
-# Example: Algorithm 7 with basic bootstrap
+# Example: Algorithm 7 with stratified bootstrap
 
@@
 
-```{r RS_algo7}
+```{r RS_algo7_strat}
 tab_rs <- DF_rs %>%
@@
 
-colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
-```
-
-```{r CI_tot_algo7}
-tab_ci1 <- df_total1 %>%
-  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (totals)")) %>%
-  kable_styling(latex_options = "hold_position") %>%
-  row_spec(0, bold = TRUE) %>%
-  row_spec(c(0, 16), hline_after = T) %>% 
-  row_spec(c(16), hline_after = T) %>% 
-  collapse_rows(columns = 1, valign = "middle")
-```
-
-```{r}
-# The table itself
-tab_ci1
-```
-
-```{r}
-# The code that produced the table
-cat(tab_ci1)
-```
-
-```{r}
-### Clean data frame to create a LaTeX table
-# For totals
-
-df_total2 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
-
-for (param in 9:12) {
-  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-  k <- 1
-  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
-    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 5) ))))
-    k <- k+1
-  }
-  df_total2 <- rbind(df_total2, df_param)
-}
-
-colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
-```
-
-```{r CI_ratio_algo7}
-tab_ci2 <- df_total2 %>%
-  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (ratios)")) %>%
-  kable_styling(latex_options = "hold_position") %>%
-  row_spec(0, bold = TRUE) %>%
-  row_spec(c(0), hline_after = T) %>% 
-  # row_spec(c(16,32), hline_after = T) %>% 
-  collapse_rows(columns = 1, valign = "middle")
-```
-
-```{r}
-# The table itself
-tab_ci2
-```
-
-```{r}
-# The code that produced the table
-cat(tab_ci2)
-```
-
-## Comparison of the variances
-
-```{r}
-diff_percent <- function(j){unlist(100*(VAR_df[j]-res1$Variances[j])/res1$Variances[j])}
-cat("Relative Bias of the variance: \n - for the number of trees: ", diff_percent(1), "%", "\n - for the volume of trees: ", diff_percent(5), "%\n - for the ratio volume / number of trees: ", diff_percent(9), "%",
-    "\n\n - for the number of small trees: ", diff_percent(2), "%", "\n - for the volume of small trees: ", diff_percent(6), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10), "%",
-    "\n\n - for the number of medium trees: ", diff_percent(3), "%", "\n - for the volume of medium trees: ", diff_percent(7), "%", "\n - for the ratio volume / number of trees: ", diff_percent(11), "%",
-    "\n\n - for the number of big trees: ", diff_percent(4), "%", "\n - for the volume of big trees: ", diff_percent(8), "%", "\n - for the ratio volume / number of trees: ", diff_percent(12), "%",
-    sep = "")
-
-# Example:
-```
-
-```{r}
-# Table for comparison
-diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Monte Carlo Relative Bias` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, res1$Variances, VAR_df), digits = 2), "%") )
-```
-
-```{r RB_algo7}
-tab_var <- diff_var %>%
-  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\addlinespace"), caption = paste0("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
-  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
-  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
-  row_spec(c(0, 4, 8), hline_after = T) %>% 
-  collapse_rows(columns = 1, latex_hline = "major")
-```
-
-```{r}
-# The table itself
-tab_var
-```
-
-```{r}
-# The code that produced the table
-cat(tab_var)
-```
-
-# Example: Algorithm 7 with stratified bootstrap
-
-```{r}
-fun_samp <- sampling_grid1
-```
-
-## Monte Carlo alone
-
-```{r}
-start.time <- Sys.time()
-
-res1 <- MonteCarlo(n, B0, fun_samp)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(unlist(res1$Estimations[1])), "\n - for the volume of trees:", mean(unlist(res1$Estimations[5])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[9])),
-    "\n\n - for the number of small trees:", mean(unlist(res1$Estimations[2])), "\n - for the volume of small trees:", mean(unlist(res1$Estimations[6])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[10])),
-    "\n\n - for the number of medium trees:", mean(unlist(res1$Estimations[3])), "\n - for the volume of medium trees:", mean(unlist(res1$Estimations[7])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[11])),
-    "\n\n - for the number of big trees:", mean(unlist(res1$Estimations[4])), "\n - for the volume of big trees:", mean(unlist(res1$Estimations[8])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[12]))
-    )
-
-# Example:
-```
-
-```{r}
-cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[5], "\n - for the ratio volume / number of trees:", res1$Variances[9],
-    "\n\n - for the number of small trees:", res1$Variances[2], "\n - for the volume of small trees:", res1$Variances[6], "\n - for the ratio volume / number of trees:", res1$Variances[10],
-    "\n\n - for the number of medium trees:", res1$Variances[3], "\n - for the volume of medium trees:", res1$Variances[7], "\n - for the ratio volume / number of trees:", res1$Variances[11],
-    "\n\n - for the number of big trees:", res1$Variances[4], "\n - for the volume of big trees:", res1$Variances[8], "\n - for the ratio volume / number of trees:", res1$Variances[12])
-
-# Example:
-```
-
-## Monte Carlo and bootstrap
-
-```{r}
-start.time <- Sys.time()
-
-res2 <- MC_boot(n, B1, B2, fun_samp, strat = TRUE)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-EST_names <- paste0("EST_", raw_names)[-(1:2)]
-
-for (j in EST_names) {
-  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
-}
-
-for (elt in res2$Estimations) {
-  if ( nrow(elt) != 1 ){ # we target bootstrap samples made from each MC iteration
-    for (j in 1:length(EST_names)) { # For each estimation
-      x <- append(get(x = EST_names[j]), mean(unlist(elt[j])))
-      assign(EST_names[j], x)
-    }
-  }
-}
-```
-
-```{r}
-cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(unlist(EST_nb)), "\n - for the volume of trees:", mean(unlist(EST_vol)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio)),
-        "\n\n - for the number of small trees:", mean(unlist(EST_nb_s)), "\n - for the volume of small trees:", mean(unlist(EST_vol_s)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_s)),
-    "\n\n - for the number of medium trees:", mean(unlist(EST_nb_m)), "\n - for the volume of medium trees:", mean(unlist(EST_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_m)),
-    "\n\n - for the number of big trees:", mean(unlist(EST_nb_b)), "\n - for the volume of big trees:", mean(unlist(EST_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_b)))
-
-# Example:
-```
-
-```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
-
-for (j in VAR_names) {
-  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
-}
-
-for (elt in res2$Variances) {
-  for (j in 1:length(VAR_names)) { # For each estimation
-    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
-    assign(VAR_names[j], x)
-  }
-}
-```
-
-```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
-VAR_df <- c()
-
-for (j in VAR_names) {
-  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
-}
-
-for (elt in res2$Variances) {
-  for (j in 1:length(VAR_names)) { # For each estimation
-    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
-    assign(VAR_names[j], x)
-  }
-}
-
-VAR_df <- c(mapply(function(j){mean(unlist(get(x = VAR_names[j])))}, 1:12))
-```
-
-```{r}
-cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", VAR_df[1], "\n - for the volume of trees:", VAR_df[5], "\n - for the ratio volume / number of trees:", VAR_df[9],
-        "\n\n - for the number of small trees:", VAR_df[2], "\n - for the volume of small trees:", VAR_df[6], "\n - for the ratio volume / number of trees:", VAR_df[10],
-    "\n\n - for the number of medium trees:", VAR_df[3], "\n - for the volume of medium trees:", VAR_df[7], "\n - for the ratio volume / number of trees:", VAR_df[11],
-    "\n\n - for the number of big trees:", VAR_df[4], "\n - for the volume of big trees:", VAR_df[8], "\n - for the ratio volume / number of trees:", VAR_df[12])
-
-# Example:
-```
-
-```{r}
-VAR_boot <- list()
-for (j in VAR_names) {
-  VAR_boot[[length(VAR_boot)+1]] <- get(x = j)
-}
-
-rs_df <- mapply(RS, VAR_boot, res1$Variances)
-```
-
-```{r}
-# Table for comparison
-DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(round(rs_df, digits = 2), "%") )
-```
-
-```{r RS_algo7_strat}
-tab_rs <- DF_rs %>%
-  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
-  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
-  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
-  row_spec(c(0, 4, 8), hline_after = T) %>% 
-  collapse_rows(columns = 1, latex_hline = "major")
-```
-
-```{r}
-# The table itself
-tab_rs
-```
-
-```{r}
-# The code that produced the table
-cat(tab_rs)
-```
-
-```{r}
-TC_normal <- coverage_rate(1, res2)
-cat("Concerning the normal approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_normal[1,1], "\n - for the volume of trees: ", TC_normal[2,1], "\n - for the ratio volume / number of trees: ", TC_normal[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_normal[1,2], "\n - for the volume of trees: ", TC_normal[2,2], "\n - for the ratio volume / number of trees: ", TC_normal[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_normal[1,3], "\n - for the volume of trees: ", TC_normal[2,3], "\n - for the ratio volume / number of trees: ", TC_normal[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_normal[1,4], "\n - for the volume of trees: ", TC_normal[2,4], "\n - for the ratio volume / number of trees: ", TC_normal[3,4])
-```
-
-```{r}
-TC_perc <- coverage_rate(2, res2)
-cat("Concerning the percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_perc[1,1], "\n - for the volume of trees: ", TC_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_perc[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_perc[1,2], "\n - for the volume of trees: ", TC_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_perc[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_perc[1,3], "\n - for the volume of trees: ", TC_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_perc[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_perc[1,4], "\n - for the volume of trees: ", TC_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_perc[3,4])
-```
-
-```{r}
-TC_rev_perc <- coverage_rate(3, res2)
-cat("Concerning the reverse percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_rev_perc[1,1], "\n - for the volume of trees: ", TC_rev_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_rev_perc[1,2], "\n - for the volume of trees: ", TC_rev_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_rev_perc[1,3], "\n - for the volume of trees: ", TC_rev_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_rev_perc[1,4], "\n - for the volume of trees: ", TC_rev_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,4])
-```
-
-```{r}
-TC_bca <- coverage_rate(4, res2)
-cat("Concerning the BCa approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_bca[1,1], "\n - for the volume of trees: ", TC_bca[2,1], "\n - for the ratio volume / number of trees: ", TC_bca[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_bca[1,2], "\n - for the volume of trees: ", TC_bca[2,2], "\n - for the ratio volume / number of trees: ", TC_bca[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_bca[1,3], "\n - for the volume of trees: ", TC_bca[2,3], "\n - for the ratio volume / number of trees: ", TC_bca[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_bca[1,4], "\n - for the volume of trees: ", TC_bca[2,4], "\n - for the ratio volume / number of trees: ", TC_bca[3,4])
-```
-
-```{r}
-### Clean data frame to create a LaTeX table
-# For totals
-
-df_total1 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
-
-for (param in 1:8) {
-  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-  k <- 1
-  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
-    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 2) ))))
-    k <- k+1
-  }
-  df_total1 <- rbind(df_total1, df_param)
-}
-
 colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")

### 2024-09-07 Last_tables/All3_tab_algo8.Rmd
Split codes

--- 2024-09-04 All3_tables_grid_copy.Rmd
@@
 
-In this document, \textbf{sampling through a grid} is used to create a sample and \textbf{three concentric circles} are used to compute local variables.
+In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{algorithm 8}, and \textbf{three concentric circles} are used to compute local variables.
+
+\textbf{Basic bootstrap} is used.
 

### 2024-09-07 Last_tables/All3_tab_algo8_strat.Rmd
Split codes

--- 2024-09-04 All3_tables_grid_copy.Rmd
@@
 
-In this document, \textbf{sampling through a grid} is used to create a sample and \textbf{three concentric circles} are used to compute local variables.
+In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{algorithm 8}, and \textbf{three concentric circles} are used to compute local variables.
+
+\textbf{Stratified bootstrap} is used.
 
@@
 
-# Example: Algorithm 8 with basic bootstrap
+# Example: Algorithm 8 with stratified bootstrap
 
@@
 
-```{r RS_algo8}
+```{r RS_algo8_strat}
 tab_rs <- DF_rs %>%
@@
 
-colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
-```
-
-```{r CI_tot_algo8}
-tab_ci1 <- df_total1 %>%
-  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (totals)")) %>%
-  kable_styling(latex_options = "hold_position") %>%
-  row_spec(0, bold = TRUE) %>%
-  row_spec(c(0, 16), hline_after = T) %>% 
-  row_spec(c(16), hline_after = T) %>% 
-  collapse_rows(columns = 1, valign = "middle")
-```
-
-```{r}
-# The table itself
-tab_ci1
-```
-
-```{r}
-# The code that produced the table
-cat(tab_ci1)
-```
-
-```{r}
-### Clean data frame to create a LaTeX table
-# For totals
-
-df_total2 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
-
-for (param in 9:12) {
-  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-  k <- 1
-  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
-    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 5) ))))
-    k <- k+1
-  }
-  df_total2 <- rbind(df_total2, df_param)
-}
-
-colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
-```
-
-```{r CI_ratio_algo8}
-tab_ci2 <- df_total2 %>%
-  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (ratios)")) %>%
-  kable_styling(latex_options = "hold_position") %>%
-  row_spec(0, bold = TRUE) %>%
-  row_spec(c(0), hline_after = T) %>% 
-  # row_spec(c(16,32), hline_after = T) %>% 
-  collapse_rows(columns = 1, valign = "middle")
-```
-
-```{r}
-# The table itself
-tab_ci2
-```
-
-```{r}
-# The code that produced the table
-cat(tab_ci2)
-```
-
-## Comparison of the variances
-
-```{r}
-diff_percent <- function(j){unlist(100*(VAR_df[j]-res1$Variances[j])/res1$Variances[j])}
-cat("Relative Bias of the variance: \n - for the number of trees: ", diff_percent(1), "%", "\n - for the volume of trees: ", diff_percent(5), "%\n - for the ratio volume / number of trees: ", diff_percent(9), "%",
-    "\n\n - for the number of small trees: ", diff_percent(2), "%", "\n - for the volume of small trees: ", diff_percent(6), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10), "%",
-    "\n\n - for the number of medium trees: ", diff_percent(3), "%", "\n - for the volume of medium trees: ", diff_percent(7), "%", "\n - for the ratio volume / number of trees: ", diff_percent(11), "%",
-    "\n\n - for the number of big trees: ", diff_percent(4), "%", "\n - for the volume of big trees: ", diff_percent(8), "%", "\n - for the ratio volume / number of trees: ", diff_percent(12), "%",
-    sep = "")
-
-# Example:
-```
-
-```{r}
-# Table for comparison
-diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Monte Carlo Relative Bias` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, res1$Variances, VAR_df), digits = 2), "%") )
-```
-
-```{r RB_algo8}
-tab_var <- diff_var %>%
-  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\addlinespace"), caption = paste0("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
-  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
-  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
-  row_spec(c(0, 4, 8), hline_after = T) %>% 
-  collapse_rows(columns = 1, latex_hline = "major")
-```
-
-```{r}
-# The table itself
-tab_var
-```
-
-```{r}
-# The code that produced the table
-cat(tab_var)
-```
-
-# Example: Algorithm 8 with stratified bootstrap
-
-```{r}
-fun_samp <- sampling_grid3
-```
-
-## Monte Carlo alone
-
-```{r}
-start.time <- Sys.time()
-
-res1 <- MonteCarlo(n, B0, fun_samp)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(unlist(res1$Estimations[1])), "\n - for the volume of trees:", mean(unlist(res1$Estimations[5])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[9])),
-    "\n\n - for the number of small trees:", mean(unlist(res1$Estimations[2])), "\n - for the volume of small trees:", mean(unlist(res1$Estimations[6])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[10])),
-    "\n\n - for the number of medium trees:", mean(unlist(res1$Estimations[3])), "\n - for the volume of medium trees:", mean(unlist(res1$Estimations[7])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[11])),
-    "\n\n - for the number of big trees:", mean(unlist(res1$Estimations[4])), "\n - for the volume of big trees:", mean(unlist(res1$Estimations[8])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[12]))
-    )
-
-# Example:
-```
-
-```{r}
-cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[5], "\n - for the ratio volume / number of trees:", res1$Variances[9],
-    "\n\n - for the number of small trees:", res1$Variances[2], "\n - for the volume of small trees:", res1$Variances[6], "\n - for the ratio volume / number of trees:", res1$Variances[10],
-    "\n\n - for the number of medium trees:", res1$Variances[3], "\n - for the volume of medium trees:", res1$Variances[7], "\n - for the ratio volume / number of trees:", res1$Variances[11],
-    "\n\n - for the number of big trees:", res1$Variances[4], "\n - for the volume of big trees:", res1$Variances[8], "\n - for the ratio volume / number of trees:", res1$Variances[12])
-
-# Example:
-```
-
-## Monte Carlo and bootstrap
-
-```{r}
-start.time <- Sys.time()
-
-res2 <- MC_boot(n, B1, B2, fun_samp, strat = TRUE)
-# Just one circle to begin with
-
-end.time <- Sys.time()
-time.taken <- end.time - start.time
-
-time.taken
-```
-
-```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-EST_names <- paste0("EST_", raw_names)[-(1:2)]
-
-for (j in EST_names) {
-  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
-}
-
-for (elt in res2$Estimations) {
-  if ( nrow(elt) != 1 ){ # we target bootstrap samples made from each MC iteration
-    for (j in 1:length(EST_names)) { # For each estimation
-      x <- append(get(x = EST_names[j]), mean(unlist(elt[j])))
-      assign(EST_names[j], x)
-    }
-  }
-}
-```
-
-```{r}
-cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(unlist(EST_nb)), "\n - for the volume of trees:", mean(unlist(EST_vol)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio)),
-        "\n\n - for the number of small trees:", mean(unlist(EST_nb_s)), "\n - for the volume of small trees:", mean(unlist(EST_vol_s)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_s)),
-    "\n\n - for the number of medium trees:", mean(unlist(EST_nb_m)), "\n - for the volume of medium trees:", mean(unlist(EST_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_m)),
-    "\n\n - for the number of big trees:", mean(unlist(EST_nb_b)), "\n - for the volume of big trees:", mean(unlist(EST_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_b)))
-
-# Example:
-```
-
-```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
-
-for (j in VAR_names) {
-  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
-}
-
-for (elt in res2$Variances) {
-  for (j in 1:length(VAR_names)) { # For each estimation
-    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
-    assign(VAR_names[j], x)
-  }
-}
-```
-
-```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
-VAR_df <- c()
-
-for (j in VAR_names) {
-  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
-}
-
-for (elt in res2$Variances) {
-  for (j in 1:length(VAR_names)) { # For each estimation
-    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
-    assign(VAR_names[j], x)
-  }
-}
-
-VAR_df <- c(mapply(function(j){mean(unlist(get(x = VAR_names[j])))}, 1:12))
-```
-
-```{r}
-cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", VAR_df[1], "\n - for the volume of trees:", VAR_df[5], "\n - for the ratio volume / number of trees:", VAR_df[9],
-        "\n\n - for the number of small trees:", VAR_df[2], "\n - for the volume of small trees:", VAR_df[6], "\n - for the ratio volume / number of trees:", VAR_df[10],
-    "\n\n - for the number of medium trees:", VAR_df[3], "\n - for the volume of medium trees:", VAR_df[7], "\n - for the ratio volume / number of trees:", VAR_df[11],
-    "\n\n - for the number of big trees:", VAR_df[4], "\n - for the volume of big trees:", VAR_df[8], "\n - for the ratio volume / number of trees:", VAR_df[12])
-
-# Example:
-```
-
-```{r}
-VAR_boot <- list()
-for (j in VAR_names) {
-  VAR_boot[[length(VAR_boot)+1]] <- get(x = j)
-}
-
-rs_df <- mapply(RS, VAR_boot, res1$Variances)
-```
-
-```{r}
-# Table for comparison
-DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(round(rs_df, digits = 2), "%") )
-```
-
-```{r RS_algo8_strat}
-tab_rs <- DF_rs %>%
-  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
-  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
-  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
-  row_spec(c(0, 4, 8), hline_after = T) %>% 
-  collapse_rows(columns = 1, latex_hline = "major")
-```
-
-```{r}
-# The table itself
-tab_rs
-```
-
-```{r}
-# The code that produced the table
-cat(tab_rs)
-```
-
-```{r}
-TC_normal <- coverage_rate(1, res2)
-cat("Concerning the normal approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_normal[1,1], "\n - for the volume of trees: ", TC_normal[2,1], "\n - for the ratio volume / number of trees: ", TC_normal[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_normal[1,2], "\n - for the volume of trees: ", TC_normal[2,2], "\n - for the ratio volume / number of trees: ", TC_normal[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_normal[1,3], "\n - for the volume of trees: ", TC_normal[2,3], "\n - for the ratio volume / number of trees: ", TC_normal[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_normal[1,4], "\n - for the volume of trees: ", TC_normal[2,4], "\n - for the ratio volume / number of trees: ", TC_normal[3,4])
-```
-
-```{r}
-TC_perc <- coverage_rate(2, res2)
-cat("Concerning the percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_perc[1,1], "\n - for the volume of trees: ", TC_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_perc[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_perc[1,2], "\n - for the volume of trees: ", TC_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_perc[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_perc[1,3], "\n - for the volume of trees: ", TC_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_perc[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_perc[1,4], "\n - for the volume of trees: ", TC_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_perc[3,4])
-```
-
-```{r}
-TC_rev_perc <- coverage_rate(3, res2)
-cat("Concerning the reverse percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_rev_perc[1,1], "\n - for the volume of trees: ", TC_rev_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_rev_perc[1,2], "\n - for the volume of trees: ", TC_rev_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_rev_perc[1,3], "\n - for the volume of trees: ", TC_rev_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_rev_perc[1,4], "\n - for the volume of trees: ", TC_rev_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,4])
-```
-
-```{r}
-TC_bca <- coverage_rate(4, res2)
-cat("Concerning the BCa approach, the coverage rates are the following: \n - for the number of trees: ", 
-    TC_bca[1,1], "\n - for the volume of trees: ", TC_bca[2,1], "\n - for the ratio volume / number of trees: ", TC_bca[3,1],
-    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_bca[1,2], "\n - for the volume of trees: ", TC_bca[2,2], "\n - for the ratio volume / number of trees: ", TC_bca[3,2],
-    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
-    TC_bca[1,3], "\n - for the volume of trees: ", TC_bca[2,3], "\n - for the ratio volume / number of trees: ", TC_bca[3,3],
-    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
-    TC_bca[1,4], "\n - for the volume of trees: ", TC_bca[2,4], "\n - for the ratio volume / number of trees: ", TC_bca[3,4])
-```
-
-```{r}
-### Clean data frame to create a LaTeX table
-# For totals
-
-df_total1 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
-
-for (param in 1:8) {
-  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
-  k <- 1
-  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
-    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 2) ))))
-    k <- k+1
-  }
-  df_total1 <- rbind(df_total1, df_param)
-}
-
-colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
+colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
 ```
@@
 
-colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
+colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
 ```

### 2024-09-07 Last_tables/All3_tab_algo6.Rmd
It seems to work

@@
 sampling_grid1 <- function(i, c_dim){
+  # i = 1,...,10
   cells_x <- c()
@@
   raw <- c()
-  elt <- i
-  while (elt < (1000*1000)) {
+  elt <- (i-1)*10
+  while (elt < (100*1000)) {
     raw <- append(raw, elt)
-    elt <- elt+10
+    elt <- elt+100
   }
   for (j in raw) {
-    cells_x <- append(cells_x, ifelse(j%%23 == 0, 23, j%%23))
-    cells_y <- append(cells_y, ifelse(j%%23 == 0, ((j-(j%%23))/23) - 1, (j-(j%%23))/23) )
+    cells_x <- append(cells_x, ifelse(j%%1000 == 0, 1000, j%%1000))
+    cells_y <- append(cells_y, ifelse(j%%1000 == 0, ((j-(j%%1000))/1000) - 1, (j-(j%%1000))/1000) )
   }
-  return(data.frame(x = cells_x, y = cells_y))
+  cells_y <- cells_y*10
+  a <- mapply(function(x){runif(1, x, x+10)}, cells_x)
+  b <- mapply(function(x){runif(1, x, x+10)}, cells_y)
+  return(data.frame(x = a, y = b))
 }
@@
 sampling_grid2 <- function(i,c_dim){
+  # i = 1,...,10
+  i <- i-1
 random_points <- data.frame(x = numeric(), y = numeric())

### 2024-09-07 Last_tables/All3_tab_algo7.Rmd
It seems to work

@@
 # Number of MC iterations
-B1 <- 1000 # 5 # 
+B1 <- 5 # 1000 # 
 # Number of bootstrap replications
-B2 <- 400 # 5 # 
+B2 <- 5 # 400 # 
 ```

### 2024-09-08 Last_tables/All3_tab_algo6.Rmd
Right numbers

@@
 # Number of MC iterations
-B0 <- 10 # 10000 # 
+B0 <- 10000 # 10 # 
 ```
@@
 # Number of MC iterations
-B1 <- 5 # 1000 # 
+B1 <- 1000 # 5 # 
 # Number of bootstrap replications
-B2 <- 5 # 400 # 
+B2 <- 400 # 5 # 
 ```

### 2024-09-08 Last_tables/All3_tab_algo7.Rmd
L U and uniform sampling

@@
 
-colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "Lower part", "Upper part", "Mean length")
+colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
 ```

### 2024-09-08 Last_tables/All3_tab_unif.Rmd
L U and uniform sampling

--- 2024-09-08 Last_tables/All3_tab_algo8.Rmd
@@
 
-In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{algorithm 8}, and \textbf{three concentric circles} are used to compute local variables.
+In this document, \textbf{uniform sampling} is used to create a sample and \textbf{three concentric circles} are used to compute local variables.
 
@@
 
-# Example: Algorithm 8 with basic bootstrap
+# Example: Algorithm 6 with basic bootstrap
 
 ```{r}
-fun_samp <- sampling_grid3
+fun_samp <- sampling_unif
 ```
@@
 
-```{r RS_algo8}
+```{r RS_unif}
 tab_rs <- DF_rs %>%
@@
 
-```{r CI_tot_algo8}
+```{r CI_tot_unif}
 tab_ci1 <- df_total1 %>%
@@
 
-```{r CI_ratio_algo8}
+```{r CI_ratio_unif}
 tab_ci2 <- df_total2 %>%
@@
 
-```{r RB_algo8}
+```{r RB_unif}
 tab_var <- diff_var %>%

### 2024-09-10 Tests.R
Not yet clean enough

@@ -1,26 +1,0 @@
-### Premier essai avec ChatGPT -----
-
-# Générer la séquence
-sequence <- seq(200, 300, by = .01)
-
-# Tester l'appartenance
-is_in_sequence <- 297.21 %in% sequence
-
-# Afficher le résultat
-print(is_in_sequence)
-
-### Second essai avec ChatGPT -----
-
-# Générer la séquence
-sequence <- seq(234, 300, by = .01)
-
-# Tester l'appartenance
-is_in_sequence <- 297.21 %in% sequence
-
-# Afficher le résultat
-print(is_in_sequence) # TRUE with 234, FALSE with 233
-
-# Afficher une partie de la séquence autour de 297.21 pour vérifier la présence
-nearby_values <- sequence[which(abs(sequence - 297.21) < .001)]
-print(nearby_values) # Dans tous les cas, affiche 297.21
-

### 2024-09-12 Draft/Test.Rmd
Better organized

--- 2024-08-21 Test.Rmd
@@
 ```
-
-```{r}
-# Set up the plotting area
-my_plot <- plot(1, type="n", xlab="", ylab="", xlim=c(-16, 16), ylim=c(-16, 16), asp=1, xaxt="n", yaxt="n")+
-
-  # axis.ticks.x = element_blank(),
-  # Draw three concentric circles with increasing radius
-  symbols(0, 0, circles=10, inches=FALSE, add=TRUE, fg = "navyblue")+
-
-  # Bad trees
-  symbols(c(15, -5, -11), c(2, 10.5, -11), circles=c(2.5, 3.7, 2), inches=FALSE, add=TRUE, fg = rep("grey", 2))+
-
-  # Good trees 
-  symbols(c(7, 4,-4), c(-5, 3.5, -5), circles=c(4, 3.5, 2), inches=FALSE, add=TRUE, fg = rep("forestgreen", 2))+
-
-  # Centers of trees
-  points(c(15, -5, 7, 4, -4, -11), c(2, 10.5, -5, 3.5, -5, -11), pch=as.character(1:6), col="black", cex=0.7) # pch=19
-
-# Sampled point
-points(0, 0, pch=19, col="red", cex=0.7) # pch=19
-points(-0.2, -0.72, pch="S", col="red", cex=0.7)
-```

### 2024-09-12 Intermediary_steps/All3_tables_grid_algo6.Rmd
Better organized

--- 2024-09-07 Last_tables/All3_tab_algo6.Rmd
@@
 ```
+
+# Example: Algorithm 6 with stratified bootstrap
+
+```{r}
+fun_samp <- sampling_grid1
+```
+
+## Monte Carlo alone
+
+```{r}
+start.time <- Sys.time()
+
+res1 <- MonteCarlo(n, B0, fun_samp)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```
+
+```{r}
+cat("Monte Carlo means of estimations: \n - for the number of trees:", mean(unlist(res1$Estimations[1])), "\n - for the volume of trees:", mean(unlist(res1$Estimations[5])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[9])),
+    "\n\n - for the number of small trees:", mean(unlist(res1$Estimations[2])), "\n - for the volume of small trees:", mean(unlist(res1$Estimations[6])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[10])),
+    "\n\n - for the number of medium trees:", mean(unlist(res1$Estimations[3])), "\n - for the volume of medium trees:", mean(unlist(res1$Estimations[7])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[11])),
+    "\n\n - for the number of big trees:", mean(unlist(res1$Estimations[4])), "\n - for the volume of big trees:", mean(unlist(res1$Estimations[8])), "\n - for the ratio volume / number of trees:", mean(unlist(res1$Estimations[12]))
+    )
+
+# Example:
+```
+
+```{r}
+cat("Monte Carlo variances: \n - for the number of trees:", res1$Variances[1], "\n - for the volume of trees:", res1$Variances[5], "\n - for the ratio volume / number of trees:", res1$Variances[9],
+    "\n\n - for the number of small trees:", res1$Variances[2], "\n - for the volume of small trees:", res1$Variances[6], "\n - for the ratio volume / number of trees:", res1$Variances[10],
+    "\n\n - for the number of medium trees:", res1$Variances[3], "\n - for the volume of medium trees:", res1$Variances[7], "\n - for the ratio volume / number of trees:", res1$Variances[11],
+    "\n\n - for the number of big trees:", res1$Variances[4], "\n - for the volume of big trees:", res1$Variances[8], "\n - for the ratio volume / number of trees:", res1$Variances[12])
+
+# Example:
+```
+
+## Monte Carlo and bootstrap
+
+```{r}
+start.time <- Sys.time()
+
+res2 <- MC_boot(n, B1, B2, fun_samp, strat = TRUE)
+# Just one circle to begin with
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
+```
+
+```{r}
+# We want all the variances obtained for each parameter of interest, 
+# to find the mean for each of these series
+EST_names <- paste0("EST_", raw_names)[-(1:2)]
+
+for (j in EST_names) {
+  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
+}
+
+for (elt in res2$Estimations) {
+  if ( nrow(elt) != 1 ){ # we target bootstrap samples made from each MC iteration
+    for (j in 1:length(EST_names)) { # For each estimation
+      x <- append(get(x = EST_names[j]), mean(unlist(elt[j])))
+      assign(EST_names[j], x)
+    }
+  }
+}
+```
+
+```{r}
+cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(unlist(EST_nb)), "\n - for the volume of trees:", mean(unlist(EST_vol)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio)),
+        "\n\n - for the number of small trees:", mean(unlist(EST_nb_s)), "\n - for the volume of small trees:", mean(unlist(EST_vol_s)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_s)),
+    "\n\n - for the number of medium trees:", mean(unlist(EST_nb_m)), "\n - for the volume of medium trees:", mean(unlist(EST_vol_m)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_m)),
+    "\n\n - for the number of big trees:", mean(unlist(EST_nb_b)), "\n - for the volume of big trees:", mean(unlist(EST_vol_b)), "\n - for the ratio volume / number of trees:", mean(unlist(EST_ratio_b)))
+
+# Example:
+```
+
+```{r}
+# We want all the variances obtained for each parameter of interest, 
+# to find the mean for each of these series
+VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
+
+for (j in VAR_names) {
+  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
+}
+
+for (elt in res2$Variances) {
+  for (j in 1:length(VAR_names)) { # For each estimation
+    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
+    assign(VAR_names[j], x)
+  }
+}
+```
+
+```{r}
+# We want all the variances obtained for each parameter of interest, 
+# to find the mean for each of these series
+VAR_names <- paste0("VAR_", raw_names)[-(1:2)]
+VAR_df <- c()
+
+for (j in VAR_names) {
+  assign(j, data.frame(matrix( numeric(0), nrow = (length(res2$Estimations)/2) )))
+}
+
+for (elt in res2$Variances) {
+  for (j in 1:length(VAR_names)) { # For each estimation
+    x <- append(get(x = VAR_names[j]), mean(unlist(elt[j])))
+    assign(VAR_names[j], x)
+  }
+}
+
+VAR_df <- c(mapply(function(j){mean(unlist(get(x = VAR_names[j])))}, 1:12))
+```
+
+```{r}
+cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", VAR_df[1], "\n - for the volume of trees:", VAR_df[5], "\n - for the ratio volume / number of trees:", VAR_df[9],
+        "\n\n - for the number of small trees:", VAR_df[2], "\n - for the volume of small trees:", VAR_df[6], "\n - for the ratio volume / number of trees:", VAR_df[10],
+    "\n\n - for the number of medium trees:", VAR_df[3], "\n - for the volume of medium trees:", VAR_df[7], "\n - for the ratio volume / number of trees:", VAR_df[11],
+    "\n\n - for the number of big trees:", VAR_df[4], "\n - for the volume of big trees:", VAR_df[8], "\n - for the ratio volume / number of trees:", VAR_df[12])
+
+# Example:
+```
+
+```{r}
+VAR_boot <- list()
+for (j in VAR_names) {
+  VAR_boot[[length(VAR_boot)+1]] <- get(x = j)
+}
+
+rs_df <- mapply(RS, VAR_boot, res1$Variances)
+```
+
+```{r}
+# Table for comparison
+DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(round(rs_df, digits = 2), "%") )
+```
+
+```{r RS_algo6_strat}
+tab_rs <- DF_rs %>%
+  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
+  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
+  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
+  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
+  row_spec(c(0, 4, 8), hline_after = T) %>% 
+  collapse_rows(columns = 1, latex_hline = "major")
+```
+
+```{r}
+# The table itself
+tab_rs
+```
+
+```{r}
+# The code that produced the table
+cat(tab_rs)
+```
+
+```{r}
+TC_normal <- coverage_rate(1, res2)
+cat("Concerning the normal approach, the coverage rates are the following: \n - for the number of trees: ", 
+    TC_normal[1,1], "\n - for the volume of trees: ", TC_normal[2,1], "\n - for the ratio volume / number of trees: ", TC_normal[3,1],
+    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_normal[1,2], "\n - for the volume of trees: ", TC_normal[2,2], "\n - for the ratio volume / number of trees: ", TC_normal[3,2],
+    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_normal[1,3], "\n - for the volume of trees: ", TC_normal[2,3], "\n - for the ratio volume / number of trees: ", TC_normal[3,3],
+    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
+    TC_normal[1,4], "\n - for the volume of trees: ", TC_normal[2,4], "\n - for the ratio volume / number of trees: ", TC_normal[3,4])
+```
+
+```{r}
+TC_perc <- coverage_rate(2, res2)
+cat("Concerning the percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
+    TC_perc[1,1], "\n - for the volume of trees: ", TC_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_perc[3,1],
+    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_perc[1,2], "\n - for the volume of trees: ", TC_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_perc[3,2],
+    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_perc[1,3], "\n - for the volume of trees: ", TC_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_perc[3,3],
+    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
+    TC_perc[1,4], "\n - for the volume of trees: ", TC_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_perc[3,4])
+```
+
+```{r}
+TC_rev_perc <- coverage_rate(3, res2)
+cat("Concerning the reverse percentile approach, the coverage rates are the following: \n - for the number of trees: ", 
+    TC_rev_perc[1,1], "\n - for the volume of trees: ", TC_rev_perc[2,1], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,1],
+    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_rev_perc[1,2], "\n - for the volume of trees: ", TC_rev_perc[2,2], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,2],
+    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_rev_perc[1,3], "\n - for the volume of trees: ", TC_rev_perc[2,3], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,3],
+    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
+    TC_rev_perc[1,4], "\n - for the volume of trees: ", TC_rev_perc[2,4], "\n - for the ratio volume / number of trees: ", TC_rev_perc[3,4])
+```
+
+```{r}
+TC_bca <- coverage_rate(4, res2)
+cat("Concerning the BCa approach, the coverage rates are the following: \n - for the number of trees: ", 
+    TC_bca[1,1], "\n - for the volume of trees: ", TC_bca[2,1], "\n - for the ratio volume / number of trees: ", TC_bca[3,1],
+    " \n\nThe parts of the estimators under the lower limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_bca[1,2], "\n - for the volume of trees: ", TC_bca[2,2], "\n - for the ratio volume / number of trees: ", TC_bca[3,2],
+    " \n\nThe parts of the estimators over the upper limit of the coverage rate are the following: \n - for the number of trees: ",
+    TC_bca[1,3], "\n - for the volume of trees: ", TC_bca[2,3], "\n - for the ratio volume / number of trees: ", TC_bca[3,3],
+    " \n\nThe mean lengths of coverage rates are the following: \n - for the number of trees: ",
+    TC_bca[1,4], "\n - for the volume of trees: ", TC_bca[2,4], "\n - for the ratio volume / number of trees: ", TC_bca[3,4])
+```
+
+```{r}
+### Clean data frame to create a LaTeX table
+# For totals
+
+df_total1 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
+meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
+
+for (param in 1:8) {
+  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
+  k <- 1
+  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
+    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 2) ))))
+    k <- k+1
+  }
+  df_total1 <- rbind(df_total1, df_param)
+}
+
+colnames(df_total1) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
+```
+
+```{r CI_tot_algo6_strat}
+tab_ci1 <- df_total1 %>%
+  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (totals)")) %>%
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>%
+  row_spec(c(0, 16), hline_after = T) %>% 
+  row_spec(c(16), hline_after = T) %>% 
+  collapse_rows(columns = 1, valign = "middle")
+```
+
+```{r}
+# The table itself
+tab_ci1
+```
+
+```{r}
+# The code that produced the table
+cat(tab_ci1)
+```
+
+```{r}
+### Clean data frame to create a LaTeX table
+# For totals
+
+df_total2 <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
+meth_nam <- c("Normal", "Percentile", "Reverse Percentile", "BCa")
+
+for (param in 9:12) {
+  df_param <- data.frame(Parameter.of.interest = character(0), Method = character(0), TC = numeric(0), Lower = numeric(0), Upper = numeric(0), Mean_length = numeric(0))
+  k <- 1
+  for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
+    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 5) ))))
+    k <- k+1
+  }
+  df_total2 <- rbind(df_total2, df_param)
+}
+
+colnames(df_total2) <- c("Parameter of interest", "Method", "Coverage rate", "L", "U", "Mean length")
+```
+
+```{r CI_ratio_algo6_strat}
+tab_ci2 <- df_total2 %>%
+  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (ratios)")) %>%
+  kable_styling(latex_options = "hold_position") %>%
+  row_spec(0, bold = TRUE) %>%
+  row_spec(c(0), hline_after = T) %>% 
+  # row_spec(c(16,32), hline_after = T) %>% 
+  collapse_rows(columns = 1, valign = "middle")
+```
+
+```{r}
+# The table itself
+tab_ci2
+```
+
+```{r}
+# The code that produced the table
+cat(tab_ci2)
+```
+
+## Comparison of the variances
+
+```{r}
+diff_percent <- function(j){unlist(100*(VAR_df[j]-res1$Variances[j])/res1$Variances[j])}
+cat("Relative Bias of the variance: \n - for the number of trees: ", diff_percent(1), "%", "\n - for the volume of trees: ", diff_percent(5), "%\n - for the ratio volume / number of trees: ", diff_percent(9), "%",
+    "\n\n - for the number of small trees: ", diff_percent(2), "%", "\n - for the volume of small trees: ", diff_percent(6), "%", "\n - for the ratio volume / number of trees: ", diff_percent(10), "%",
+    "\n\n - for the number of medium trees: ", diff_percent(3), "%", "\n - for the volume of medium trees: ", diff_percent(7), "%", "\n - for the ratio volume / number of trees: ", diff_percent(11), "%",
+    "\n\n - for the number of big trees: ", diff_percent(4), "%", "\n - for the volume of big trees: ", diff_percent(8), "%", "\n - for the ratio volume / number of trees: ", diff_percent(12), "%",
+    sep = "")
+
+# Example:
+```
+
+```{r}
+# Table for comparison
+diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Monte Carlo Relative Bias` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, res1$Variances, VAR_df), digits = 2), "%") )
+```
+
+```{r RB_algo6_strat}
+tab_var <- diff_var %>%
+  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
+  "\\addlinespace"), caption = paste0("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
+  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
+  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
+  row_spec(c(0, 4, 8), hline_after = T) %>% 
+  collapse_rows(columns = 1, latex_hline = "major")
+```
+
+```{r}
+# The table itself
+tab_var
+```
+
+```{r}
+# The code that produced the table
+cat(tab_var)
+```

### 2024-09-12 Intermediary_steps/Boot_grid_bis.Rmd
Better organized

--- 2024-08-01 Boot_grid_ter.Rmd
@@
 output: pdf_document
-date: "2024-08-01"
+date: "2024-07-26"
 ---
@@
 
-Motivation: specific sampling from a grid, random small square inside a first bunch of 10 small squares, for a beginning. Then, systematic sampling without any shifts when changing line.
+Motivation: specific sampling from a grid, random small square inside a bunch of 10 small squares, for each bunch of 10 small squares
 
@@
 ```{r}
-i <- sample(1:10, 1) # choice of the rank of the identifier we want
-i
+# i <- sample(1:10, 1) # choice of the rank of the identifier we want
+# i
 ```
@@
 # Function to sample at random following the grid
-sampling_grid <- function(i,c_dim){
+sampling_grid <- function(c_dim){
 random_points <- data.frame(x = numeric(), y = numeric())
 
-for (l in 0:((1000/c_dim)-1)) {
-  x_init <- i*c_dim
-  k <- 0
-  while (x_init + 10*c_dim*k < 1000) {
-    a <- runif(1, x_init + 10*c_dim*k, x_init + 10*c_dim*k + c_dim)
+for (l in 0:((1000/c_dim)-1)) { # For all lines
+  for (bunch in 1:(1000/(c_dim*10))) { # 10 is the size of each bunch
+    x_sampled <- sample(0:9, 1)*c_dim + (bunch-1)*10*c_dim
+    a <- runif(1, x_sampled, x_sampled + c_dim)
     b <- runif(1, l*c_dim, (l+1)*c_dim)
     random_points <- rbind(random_points, list(a,b))
-    k <- k+1
   }
@@
 # Small example
-ex_grid <- sampling_grid(i, c_dim)
+ex_grid <- sampling_grid(c_dim)
 ```
@@
     # Uniform sampling over the whole territory
-    df_grid <- sampling_grid(i, c_dim)
+    df_grid <- sampling_grid(c_dim)
     a1 <- df_grid$x

### 2024-09-12 Intermediary_steps/Comparison_test.Rmd
Better organized

--- 2024-09-12 Intermediary_steps/Boot_grid_bis.Rmd
@@
 ---
-title: "Monte Carlo and bootstrap for all parameters with a grid"
+title: "Comparison_test"
 output: pdf_document
-date: "2024-07-26"
+date: "2024-08-08"
 ---
@@
 ```
-
-Motivation: specific sampling from a grid, random small square inside a bunch of 10 small squares, for each bunch of 10 small squares
-
-The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees and the ratio volume of trees / number of trees) and variances of these estimators.
-The same elements, along with confidence intervals, are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations.
-By comparing the two results, we may verify the invalidity of the bootstrap strategy to find the estimation of the variances.
-We reuse the results from another file for the function that exploits Monte Carlo alone.
-
-In this document, one single circle with a radius of 5 is used to compute local variables. Besides, and more importantly, a grid is used for sampling.
 
@@
 n <- 1000
+a1 <- runif(n, 0, 1000)
+a2 <- runif(n, 0, 1000)
 ```
 
-```{r}
-# i <- sample(1:10, 1) # choice of the rank of the identifier we want
-# i
-```
-
-```{r}
-# Dimension of a small square (length of one side of the square)
-# We assume that c_dim is a divisor of 1000
-c_dim <- 10
-```
-
-```{r}
-# Function to sample at random following the grid
-sampling_grid <- function(c_dim){
-random_points <- data.frame(x = numeric(), y = numeric())
-
-for (l in 0:((1000/c_dim)-1)) { # For all lines
-  for (bunch in 1:(1000/(c_dim*10))) { # 10 is the size of each bunch
-    x_sampled <- sample(0:9, 1)*c_dim + (bunch-1)*10*c_dim
-    a <- runif(1, x_sampled, x_sampled + c_dim)
-    b <- runif(1, l*c_dim, (l+1)*c_dim)
-    random_points <- rbind(random_points, list(a,b))
-  }
-}
-colnames(random_points) <- list("x", "y")
-return(random_points)
-}
-```
-
-```{r}
-# Small example
-ex_grid <- sampling_grid(c_dim)
-```
-
-```{r}
-plot(ex_grid, xlab="", ylab="", main = "Random points within the grid", las = 1)
-```
-
-```{r}
-plot(ex_grid, xlab="", ylab="", main = "Only one point", xlim = c(0, 100), ylim = c(0, 10), las = 1)
-```
-
-```{r}
-# True values
-cat("Number of trees:", length(trees$x), "\nTotal volume:", sum(trees$v), "\nWhich leads to the following ratio \"Total volume / Number of trees\":", sum(trees$v)/nrow(trees))
-```
-
-# Bootstrap for each Monte Carlo iteration
-
-1 000 Monte Carlo iterations and 400 bootstrap iterations for each one are appropriated.
-
-```{r}
-f_boot <- function(df_sample, B){
-  # df_sample: original sample; 
-  # B: number of bootstrap samples made thanks to df_sample
-
-  df_boot <- data.frame(useless = rep(0, nrow(df_sample)-1))
-  for (b in 1:B) {
-    nb <- sample(1:nrow(df_sample), (nrow(df_sample)-1), replace = TRUE)
-    # (n-1) points at random
-    sample_b <- df_sample[nb,]
-    df_boot <- cbind(df_boot, sample_b)
-    colnames(df_boot)[((b-1)*4+1 + 1):(b*4+1)] <- c(paste("ech", b, colnames(df_sample)[1], sep = ""), paste("ech", b, colnames(df_sample)[2], sep = ""), paste("ech", b, colnames(df_sample)[3], sep = ""), paste("ech", b, colnames(df_sample)[4], sep = ""))
-  }
-  df_boot$useless <- NULL
-  return(df_boot)
-  # Return a data frame with B samples of as many variables as we want (in this application, 4) and of size (n-1)
-}
-```
-
-```{r}
-# Making of estimations for each sample made by the bootstrap method
-est_boot <- function(df, p){
-  # df: dataframe with 4*B columns and n rows
-
-  n <- nrow(df) + 1 # sample size of the initial sample
-  nboot <- length(df)/4 # number of bootstrap samples
-  vec_est1 <- c()
-  vec_est2 <- c()
-  vec_est3 <- c()
-  for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + (4*(c-1))]/p))
-    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,4*c]/p))
-    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,4*c]/p))/((n/(n-1))*sum(df[,3 + (4*(c-1))]/p)))
-    # (n/(n-1)) is the correction needed since we choose only (n-1) points
-  }
-  vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
-  return(vec_est)
-  # Data frame with 3 estimations for each sample
-}
-```
-
-```{r}
-### Function to automate Monte Carlo + bootstrap method
-
-MC_boot <- function(n, B1, B2){
-  # B1: number of iterations for MC;
-  # B2: number of iterations for bootstrap
-
-  p <- sum(rep((1/1000)*(1/1000), n))
-  BOOT_df <- list() # All local variables
-  BOOT_est <- list() # All estimations
-  BOOT_var <- list() # Variances
-  BOOT_CI <- list() # Confidence Intervals
-  for (b in 1:B1) { # One MC iteration at a time
-    # Uniform sampling over the whole territory
-    df_grid <- sampling_grid(c_dim)
-    a1 <- df_grid$x
-    a2 <- df_grid$y
-    # n <- nrow(df_grid) # sample size
-    # p <- sum(rep((1/1000)*(1/1000), n)) # inclusion density
-    var <- mapply(circle_all, a1, a2)
-    df_b <- data.frame(x = a1, y = a2, z = t(var)[,1], t = t(var)[,2])
-    colnames(df_b) <- c(paste("x.MC", b, sep = ""), paste("y.MC", b, sep = ""), paste("nb.MC", b, sep = ""), paste("vol.MC", b, sep = ""))
-    est_b <- t(data.frame(x = sum(df_b[3] /p), y = sum(df_b[4] /p), z = (sum(df_b[4] /p))/(sum(df_b[3]/p))))
-
-    # Bootstrap iterations
-    df_boot <- f_boot(df_b, B2)
-    est_boot_val <- est_boot(df_boot, p)
-
-    BOOT_var[[b]] <- list(var_nb = var(est_boot_val$est_nb), var_vol = var(est_boot_val$est_vol), var_ratio = var(est_boot_val$est_ratio))
-    names(BOOT_var)[b] <- paste("Variance", b, sep = "")
-    BOOT_df <- c(BOOT_df, list(data_init = df_b, data_boot = df_boot))
-    names(BOOT_df)[(2*b-1):(2*b)] <- c(paste("df_MC", b, sep = ""), paste("df_boot", b, sep = ""))
-    BOOT_est <- c(BOOT_est, list(est_init_b = est_b, est_boot_b = est_boot_val))
-    names(BOOT_est)[(2*b-1):(2*b)] <- c(paste("est_MC", b, sep = ""), paste("est_boot", b, sep = ""))
-
-    # Confidence intervals
-    norm_CI <- data.frame(useless = rep(0, 2))
-    perc_CI <- data.frame(useless = rep(0, 2))
-    rev_perc_CI <- data.frame(useless = rep(0, 2))
-    for (l in 1:3) { # Loop: one estimator each time
-      sorted_est <- sort(est_boot_val[,l])
-      lim_inf <- sorted_est[floor(B2*2.5/100)]
-      lim_sup <- sorted_est[B2 - floor(B2*2.5/100)]
-      perc_CI <- cbind(perc_CI, data.frame(c(lim_inf, lim_sup)))
-      rev_perc_CI <- cbind(rev_perc_CI, data.frame(c(est_b[l,]*2 - lim_sup, est_b[l,]*2 - lim_inf)))
-      norm_CI <- cbind(norm_CI, data.frame(c(est_b[l,]-qnorm(0.975)*sqrt(var(est_boot_val[,l])), est_b[l,]+qnorm(0.975)*sqrt(var(est_boot_val[,l])))))
-    }
-    norm_CI$useless <- NULL
-    perc_CI$useless <- NULL
-    rev_perc_CI$useless <- NULL
-    colnames(norm_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-    colnames(perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-    colnames(rev_perc_CI) <- c("lim_nb", "lim_vol", "lim_ratio")
-    all_CI <- list(Normal = norm_CI, Percentile = perc_CI, `Reverse percentile` = rev_perc_CI)
-    # BOOT_CI <- c(BOOT_CI, CI_b = all_CI)
-    BOOT_CI[[b]] <- all_CI
-    names(BOOT_CI)[b] <- paste("CI", b, sep = "")
-  }
-  return(list(`Local Variables` = BOOT_df, Estimations = BOOT_est, Variances = BOOT_var, `Confidence Intervals` = BOOT_CI))
-  # Local Variables: local variables (number and volume) for each point in each sample
-  # Estimations: 3 estimations (number, volume, ratio volume / number) for each sample
-  # Variances: mean of the bootstrap variance for each estimator
-  # Confidence Intervals: 3 different forms of 95% confidence intervals, for each total / ratio
-}
-```
-
-# Example
-
-## Monte Carlo and bootstrap
+# Comparison
 
@@
 
-res2 <- MC_boot(n, B1 = 1000, B2 = 400)
-# Just one circle to begin with
+var1 <- mapply(circle_all, a1, a2)
 
@@
 ```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-EST_nb <- c()
-EST_vol <- c()
-EST_ratio <- c()
-for (elt in res2$Estimations) {
-  if ("data.frame" %in% class(elt)){ # we target bootstrap samples made from each MC iteration
-    EST_nb <- append(EST_nb, mean(elt$est_nb))
-    EST_vol <- append(EST_vol, mean(elt$est_vol))
-    EST_ratio <- append(EST_ratio, mean(elt$est_ratio))
-  }
-}
+start.time <- Sys.time()
+
+var3 <- mapply(circle_ALL_bis, a1, a2)
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
 ```
@@
 ```{r}
-cat("Mean of the means of estimations obtained through each bootstrap process:\n - for the number of trees:", mean(EST_nb), "\n - for the volume of trees:", mean(EST_vol), "\n - for the ratio volume / number of trees:", mean(EST_ratio))
+start.time <- Sys.time()
+
+var5 <- mapply(circle_ALL_quater, a1, a2)
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
 ```
@@
 ```{r}
-# We want all the variances obtained for each parameter of interest, 
-# to find the mean for each of these series
-VAR_nb <- c()
-VAR_vol <- c()
-VAR_ratio <- c()
-for (elt in res2$Variances) {
-  VAR_nb <- append(VAR_nb, elt$var_nb)
-  VAR_vol <- append(VAR_vol, elt$var_vol)
-  VAR_ratio <- append(VAR_ratio, elt$var_ratio)
-}
+start.time <- Sys.time()
+
+var2 <- mapply(circle_ALL, a1, a2)
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
 ```
-
-```{r}
-cat("Mean of the variance of bootstrap samples:\n - for the number of trees:", mean(VAR_nb), "\n - for the volume of trees:", mean(VAR_vol), "\n - for the ratio volume / number of trees:", mean(VAR_ratio))
-```
-
-## Comparison of the variances
-
-```{r}
-diff_percent <- function(x,y)100*(max(x,y)-min(x,y))/min(x,y)
-cat("Difference between the two estimations of variance: \n - for the number of trees: ", diff_percent(240516.7, mean(VAR_nb)), "%", "\n - for the volume of trees: ", diff_percent(14084.96, mean(VAR_vol)), "%\n - for the ratio volume / number of trees: ", diff_percent(6.397115e-06, mean(VAR_ratio)), "%", sep = "")
-```

### 2024-09-12 Intermediary_steps/MC3_all_old.Rmd
Better organized

--- 2024-08-02 MC_all_old.Rmd
@@
 ---
-title: "Monte Carlo and bootstrap for all parameters"
+title: "Monte Carlo and bootstrap for all parameters with 3 circles"
 output: pdf_document
@@
 
-In this document, one single circle with a radius of 5 is used to compute local variables.
+In this document, three circles are used to compute local variables, like the French NFI process.
 
@@
 res1 <- MonteCarlo(n, 10000)
-# Just one circle to begin with
+# With 3 circles
 
@@
 # Example:
-## Monte Carlo means of estimations:
-##  - for the number of trees: 29251.69
-##  - for the volume of trees: 5407.967
-##  - for the ratio volume / number of trees: 0.184873
+
 ```
@@
 # Example:
-## Monte Carlo variances:
-##  - for the number of trees: 2604340
-##  - for the volume of trees: 99936.6
-##  - for the ratio volume / number of trees: 1.122037e-05
+
 ```
@@
 # Example:
-## 95% confidence intervals using the normal method:
-##  - for the number of trees: [ 23345.86 ; 29671.83 ]
-##  - for the volume of trees: [ 4320.113 ; 5559.31 ]
-##  - for the ratio volume / number of trees: [ 0.1797767 ; 0.1929072 ]
+
 ```
@@
 # Example:
-## 95% confidence intervals using the percentile method:
-##  - for the number of trees: [ 26139.61 ; 32467.61 ]
-##  - for the volume of trees: [ 4798.827 ; 6037.256 ]
-##  - for the ratio volume / number of trees: [ 0.1783755 ; 0.1915082 ]
+
 ```
@@
 # Example:
-## 95% confidence intervals using the reverse percentile method:
-##  - for the number of trees: [ 20550.09 ; 26878.09 ]
-##  - for the volume of trees: [ 3842.166 ; 5080.595 ]
-##  - for the ratio volume / number of trees: [ 0.1811758 ; 0.1943085 ]
+
 ```
@@
 res2 <- MC_boot(n, B1 = 1000, B2 = 400)
-# Just one circle to begin with
+# With 3 circles
 
@@
 # Example:
-## Mean of the means of estimations obtained through each bootstrap process:
-##  - for the number of trees: 29280.52
-##  - for the volume of trees: 5411.916
-##  - for the ratio volume / number of trees: 0.1848212
+
 ```
@@
 # Example:
-## Mean of the variance of bootstrap samples:
-##  - for the number of trees: 2562574
-##  - for the volume of trees: 98333.62
-##  - for the ratio volume / number of trees: 1.121868e-05
+
 ```
@@
 # Example:
-## Difference between the two estimations of variance:
-##  - for the number of trees: 1.629866%
-##  - for the volume of trees: 1.630143%
-##  - for the ratio volume / number of trees: 0.01505727%
+
 ```

### 2024-09-12 Intermediary_steps/MC_adagrid_2.Rmd
Better organized

--- 2024-07-31 Untitled_.Rmd
@@
 ---
-title: "Testing bootstrap processes"
+title: "Another stratification"
 output: pdf_document
-date: "2024-07-30"
+date: "2024-07-29"
 ---
@@
   for (b in 1:B) {
-    # nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
+    nb <- sample(unique(df_sample[,3]), (length(unique(df_sample[,3]))-1), replace = TRUE)
     # (H-1) strata at random
     sample_b <- data.frame(x = numeric(), y = numeric(), z = numeric(), t = numeric(), w = numeric())
-    for (number in unique(df_sample[,3])){
-      truc <- sample(df_sample[df_sample[,3] == number,], nrow(df_sample[df_sample[,3] == number,]) -1, replace = TRUE)
-      sample_b <- rbind(sample_b, truc)
-      # sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
+    for (number in nb){
+      sample_b <- rbind(sample_b, df_sample[df_sample[,3] == number,])
     }
@@
   for (c in 1:nboot) {
-    vec_est1 <- append(vec_est1, (900/899)*sum(df[,4 + (5*(c-1))]/p))
-    vec_est2 <- append(vec_est2, (900/899)*sum(df[,5*c]/p))
-    vec_est3 <- append(vec_est3, ((900/899)*sum(df[,5*c]/p))/((900/899)*sum(df[,4 + (5*(c-1))]/p)))
+    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,4 + (5*(c-1))]/p))
+    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,5*c]/p))
+    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,5*c]/p))/((n/(n-1))*sum(df[,4 + (5*(c-1))]/p)))
     # (n/(n-1)) is the correction needed since we choose only (n-1) points

### 2024-09-12 Intermediary_steps/MC_boot.Rmd
Better organized

--- 2024-07-09 MC_boot.Rmd
@@
 
+# Tests
+
 ```{r}
-MC_boot(n = 100, B1 = 1000, B2 = 200, f = circle3_nb)
+start.time <- Sys.time()
+
+res <- MC_boot(n = 100, B1 = 1000, B2 = 200, f = circle3_nb)
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
 ```
@@
 ```{r}
+cat("Mean of Monte-Carlo samples:", res[1], "\nMonte-Carlo variance:", res[2], "\nMean of the variance of bootstrap samples:", res[3])
+```
 
+# A second possibility
+
+Stop calculating the local variable for each bootstrap sample: it is already done with the initial sample!!!
+
+```{r}
+# Making of one estimation for each sample made by the bootstrap method
+est_boot1 <- function(df, p){
+  # df: dataframe with 3*B columns and n rows
+
+  nboot <- length(df)/3
+  vec_est <- c()
+  for (c in 1:nboot) {
+    vec_est <- append(vec_est, sum(df[,3*c]/p))
+  }
+  vec_est <- sort(vec_est)
+  return(vec_est)
+  # Vector with one estimation for each sample
+}
 ```
+
+```{r}
+### Function to automate Monte Carlo method
+
+MC_boot <- function(n, B1, B2, f){
+  # n: sample size; B1: number of iterations for MC;
+  # B2: number of iterations for bootstrap;
+  # f: function to consider (2 arguments)
+  # Argument grid? (change n then)
+  p <- sum(rep((1/1000)*(1/1000), n))
+
+  est_MC <- c()
+  mean_est_boot <- c()
+  var_est_boot <- c()
+
+  for (b in 2:B1) {
+    # One MC iteration at a time
+    random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
+    random_points$var <- mapply(f, random_points[, 1], random_points[, 2])
+    a <- sum(random_points$var/p)
+    est_MC <- append(est_MC, a)
+
+    # Bootstrap iterations
+    df_boot <- f_boot(random_points, B2)
+    est_boot_val <- est_boot1(df_boot, p)
+    mean_est_boot <- append(mean_est_boot, mean(est_boot_val))
+    var_est_boot <- append(var_est_boot, var(est_boot_val))
+  }
+  return(c(mean(est_MC), var(est_MC), mean(var_est_boot)))
+  # Estimated value of the total, Monte-Carlo variance, mean of the bootstrap variance
+}
+```

### 2024-09-12 Intermediary_steps/MC_grid.Rmd
Better organized

--- 2024-09-12 Intermediary_steps/MC_all.Rmd
@@
 ---
-title: "Monte Carlo and bootstrap for all parameters"
+title: "Monte Carlo and bootstrap for all parameters with a grid"
 output: pdf_document
@@
 
-In this document, \textbf{uniform sampling} is used to create a sample and \textbf{one single circle} with a radius of 5 is used to compute local variables.
+In this document, \textbf{sampling with a grid} is used to create a sample and \textbf{one single circle} with a radius of 5 is used to compute local variables.
 
@@
     # Uniform sampling over the whole territory
-    a1 <- runif(n, 0, 1000)
-    a2 <- runif(n, 0, 1000)
+    df_grid <- sampling_grid(i,c_dim)
+    a1 <- df_grid$x
+    a2 <- df_grid$y
     # Variables of interest derived from the sample
@@
     # Uniform sampling over the whole territory
-    a1 <- runif(n, 0, 1000)
-    a2 <- runif(n, 0, 1000)
+    df_grid <- sampling_grid(i,c_dim)
+    a1 <- df_grid$x
+    a2 <- df_grid$y
     var <- mapply(circle_all, a1, a2)
@@
 ## Monte Carlo means of estimations:
-##  - for the number of trees: 29251.69
-##  - for the volume of trees: 5407.967
-##  - for the ratio volume / number of trees: 0.184873
+##  - for the number of trees: 29529.27
+##  - for the volume of trees: 5428.676
+##  - for the ratio volume / number of trees: 0.1838376
 ```
@@
 ## Monte Carlo variances:
-##  - for the number of trees: 2604340
-##  - for the volume of trees: 99936.6
-##  - for the ratio volume / number of trees: 1.122037e-05
+##  - for the number of trees: 263478.6
+##  - for the volume of trees: 15475.27
+##  - for the ratio volume / number of trees: 6.470082e-06
 ```
@@
 ## Mean of the means of estimations obtained through each bootstrap process:
-##  - for the number of trees: 29280.52
-##  - for the volume of trees: 5411.916
-##  - for the ratio volume / number of trees: 0.1848212
+##  - for the number of trees: 29546.03
+##  - for the volume of trees: 5431.112
+##  - for the ratio volume / number of trees: 0.1838134
 ```
@@
 ## Mean of the variance of bootstrap samples:
-##  - for the number of trees: 2562574
-##  - for the volume of trees: 98333.62
-##  - for the ratio volume / number of trees: 1.121868e-05
+##  - for the number of trees: 2630037
+##  - for the volume of trees: 99634.96
+##  - for the ratio volume / number of trees: 1.033748e-05
 ```
@@
 ## Difference between the two estimations of variance:
-##  - for the number of trees: 1.629866%
-##  - for the volume of trees: 1.630143%
-##  - for the ratio volume / number of trees: 0.01505727%
+##  - for the number of trees: 898.1975%
+##  - for the volume of trees: 543.8335%
+##  - for the ratio volume / number of trees: 59.77348%
 ```

### 2024-09-12 Intermediary_steps/Ratio_boot.Rmd
Better organized

---
title: "Bootstrap method with estimated ratios"
output: pdf_document
date: "2024-07-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
```

# Preliminaries

```{r}
# Importing the database with the artificial forest
trees <- read_excel("~/work/Sim_article2024/Data/artificial_forest_round.xls")
```

```{r}
# Functions to produce a local variable
source("~/work/Sim_article2024/Useful_functions/Circle.R")
```

```{r}
# Sample size
n <- 1000

# Inclusion density
p <- sum(rep((1/1000)*(1/1000), n))
```

# Ratio volume/number of trees

```{r}
# True ratio
cat("True ratio \"total volume over number of trees\":", sum(trees$v)/nrow(trees))
```

```{r}
random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
```

```{r}
# An estimation of the ratio
a1 <- mapply(circle_nb, random_points[, 1], random_points[, 2])
a1 <- sum(a1/p)
a2 <- mapply(circle_vol, random_points[, 1], random_points[, 2])
a2 <- sum(a2/p)
est_ratio <- a2/a1
# 0.1761545 e.g.
```

```{r}
# A second estimation of the ratio with 3 categories
b1 <- mapply(circle_nb_3cats, random_points[, 1], random_points[, 2])
b11 <- sum(b1[1,]/p)
b12 <- sum(b1[2,]/p)
b13 <- sum(b1[3,]/p)
b2 <- mapply(circle_vol_3cats, random_points[, 1], random_points[, 2])
b21 <- sum(b2[1,]/p)
b22 <- sum(b2[2,]/p)
b23 <- sum(b2[3,]/p)

est_vol <- b11*b21/a1 + b12*b22/a1 + b13*b23/a1
```

```{r}
# Underlying model?
reg <- lm(v ~ d130, data = trees)
cat("R^2:", summary(reg)$r.squared)
```

### 2024-09-12 Intermediary_steps/adapt_boot2.Rmd
Better organized

--- 2024-07-11 adapt_boot2.Rmd
@@
 # Number of trees
+# Local variable for each sampled point
 random_points$var <- mapply(circle3_nb, random_points[, 1], random_points[, 2], MoreArgs = list(15, 9, 6))
@@
 ```{r}
-# We only keep x and y in the dataframe
+# We only keep x, y and var in the dataframe
 random_points_1 <- random_points
@@
 
-# Comparison between both methods
+# Comparison between the two methods
 
@@
   # df_init: initial data frame with 4 variables, just as random_points
-  # B: number of bootstrap replications each time
+  # B: maximum number of bootstrap replications for the last series
   # small_step: step to decide how many bootstrap series will be computed
@@
   var_vec2 <- c()
-  b1 <- 100
+  b1 <- 100 # minimum number of bootstrap samples for one single series
   while (b1  < B) {
     ## First method
-    # We only keep x and y in the dataframe
+    # We only keep x, y and var in the dataframe
     df_init_1 <- df_init
@@
 
-    # tot_mean <- append(tot_mean, as.numeric(abs(mean(est_boot_2)-30942) <  abs(mean(est_boot_1)-30942))*2-1)
-    # 1: the second method is better
-    # tot_var <- append(tot_var, as.numeric(var(est_boot_2) <  var(est_boot_1))*2-1)
-    # 1: the second method is better
     b1 <- b1+small_step
@@
 df_test <- random_points
+
+start.time <- Sys.time()
+
 res2 <- comparison2(df_test, B_test, 1)
+
+end.time <- Sys.time()
+time.taken <- end.time - start.time
+
+time.taken
 ```
@@
 
-p <- ggplot(data, aes(data[,1], data[,2] - data[,3]))
+p <- ggplot(data, aes(data[,1]+100, data[,2] - data[,3]))
 p + geom_point() +ggtitle("Comparison of the mean of estimators") + xlab("Number of bootstrap replications") + ylab("First method minus Second method")
 ```
+Figure 2.
+**Comparison of estimators obtained through the two methods depending on the number of bootstrap replications**.
+What is plotted is the gap between the result following the first method and the true value *minus* the gap between the result following the second method and the true value, as a function of the number of bootstrap replications.
+If it is positive, the second method gives estimators that are closer to the true value.
 
 ```{r}
+# We look at the variance of the estimators
 data_var = as.data.frame(cbind(1:length(res2[[1]]), res2[[3]], res2[[4]]))
 
-p <- ggplot(data_var, aes(data_var[,1], data_var[,2] - data_var[,3]))
+p <- ggplot(data_var, aes(data_var[,1]+100, data_var[,2] - data_var[,3]))
 p + geom_point() + ggtitle("Comparison of the variance of estimators") + xlab("Number of bootstrap replications") + ylab("First method minus Second method")
@@
 ```
+Figure 3.
+**Comparison of the variance of the estimators obtained through the two methods depending on the number of bootstrap replications**.
+What is plotted is the variance obtained by following the first method *minus* the variance obtained by following the second method, as a function of the number of bootstrap replications.
+If it is positive, the second method gives estimators that have smaller variances.
 
@@
 # To what extent does the second method improve variance?
-cat("If it is positive, it indicates that the second method improve reducing the variance.")
+cat("If it is positive, it indicates that the second method helps reducing the variance.")
 cat("\nWith all bootstrap samples:", mean(data_var[,2] - data_var[,3]))

### 2024-09-12 Intermediary_steps/test_boot_short_2.Rmd
Better organized

--- 2024-08-02 test_boot_short_3.Rmd
@@
 ---
-title: "Testing some bootstrap process"
+title: "Testing bootstrap processes"
 output: pdf_document
-date: "2024-08-02"
+date: "2024-08-05"
 ---
@@
 
-Idea for the bootstrap: for each line l, containing $n_l$ sampled points, $n_l - 1$ points are sampled with replacement.
-As a result, $100(n_l-1)$ points are sampled from the initial sample.
+Idea for the bootstrap: for each stratum $h$, containing $n_h$ sampled points, $n_h - 1$ points are sampled with replacement.
+As a result, $100(n_h-1)$ points are sampled from the initial sample.
 In this case, 900 points are sampled.
@@
     b <- runif(1, l*c_dim, (l+1)*c_dim)
-    h <- l # 100 lines = 100 strata
+    h <- nrow(random_points)%%100 # 100 strata
     random_points <- rbind(random_points, list(a,b, h))

### 2024-09-12 Plots/Map_FR.Rmd
Better organized

--- 2024-08-22 Map_FR.Rmd
@@
 ```{r}
-# Create a data frame with the coordinates and colors
-# grid_data <- expand.grid(x = 1:30, y = 1:30)  # 10x10 grid
-# grid_data$color <- "white"  # Default color for all squares
+### Create a data frame with the coordinates and colors
 
-# (10--5)*2 = 30
-# (51.5-41)*2 = 21
+# (10--5)*2 = 30 columns
+# (51.5-41)*2 = 21 lines
 
@@
       cells_x <- append(cells_x, a)
-      # print(a)
       cells_y <- append(cells_y, b)
-      # print(b)
       k <- k+1
@@
 # Highlight specific cells
-highlighted_cells <- grid_sf[test$x + (test$y)*30, ]  # Example: highlight specific cells
+highlighted_cells <- grid_sf[test$x + (test$y)*30, ]  # highlight specific cells
 highlighted_cells <- st_sf(geometry = highlighted_cells, color = "red")  # Assign color
@@
 # Combine highlighted and non-highlighted cells
-grid_sf <- st_sf(geometry = grid_sf, color = "white")
+grid_sf <- st_sf(geometry = grid_sf, color = "white") # Default color for all squares
 grid_sf$color[which(grid_sf$geometry %in% highlighted_cells$geometry)] <- highlighted_cells$color
@@
   ggtitle("Firs-stage sampling: sampling of cells within a grid")
-# +
-  # annotation_scale(location = "bl") + # location = NULL
-  # annotation_north_arrow(location = "bl")
 ```
@@
 
-# Create a new column to determine land or water (or other features)
+# Create a new column to determine land or water
 # Here, we'll simply mark if a grid cell intersects with land (France)
@@
   theme_minimal()
-# +
-  # ggtitle("")
 ```

### 2024-09-12 Results/All3_tab_algo6.Rmd
Better organized

--- 2024-09-08 Last_tables/All3_tab_algo6.Rmd
@@
 
-In this document, \textbf{sampling through a grid} is used to create a sample and \textbf{three concentric circles} are used to compute local variables.
+In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{algorithm 6}, and \textbf{three concentric circles} are used to compute local variables.
+
+\textbf{Basic bootstrap} is used.
 

### 2024-09-12 Results/All3_tab_unif.Rmd
Corrections

--- 2024-09-08 Last_tables/All3_tab_unif.Rmd
@@
 output:
+  pdf_document: default
   html_document:
     df_print: paged
-  pdf_document: default
 date: "2024-08-16"
@@
 real_val_read <- c(nrow(trees), nrow(trees[(pi*trees$d130 < 70.5),]), nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), nrow(trees[(pi*trees$d130 > 117.5),]), 
-  sum(trees$v), sum(trees[(pi*trees$d130 < 70.5),]$v), sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), sum(trees[(pi*trees$d130 > 117.5),]$v), 
-  round(sum(trees$v)/nrow(trees), digits = 3), round(sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), digits = 3), round(sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),]), digits = 3)
+  format(round(sum(trees$v), digits = 3), nsmall = 3), format(round(sum(trees[(pi*trees$d130 < 70.5),]$v), digits = 3), nsmall = 3), format(round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v), digits = 3), nsmall = 3), format(round(sum(trees[(pi*trees$d130 > 117.5),]$v), digits = 3), nsmall = 3),
+  format(round(sum(trees$v)/nrow(trees), digits = 3), nsmall = 3), format(round(sum(trees[(pi*trees$d130 < 70.5),]$v)/nrow(trees[(pi*trees$d130 < 70.5),]), digits = 3), nsmall = 3), format(round(sum(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]$v)/nrow(trees[(pi*trees$d130 < 117.5) & (pi*trees$d130 > 70.5),]), digits = 3), nsmall = 3), format(round(sum(trees[(pi*trees$d130 > 117.5),]$v)/nrow(trees[(pi*trees$d130 > 117.5),]), digits = 3), nsmall = 3)
   )
@@
 PARAM_names <- c("Number of trees", "Number of small trees", "Number of medium trees", "Number of big trees", "Volume of trees", "Volume of small trees", "Volume of medium trees", "Volume of big trees", "Ratio for all trees", "Ratio for small trees", "Ratio for medium trees", "Ratio for big trees")
+```
+
+```{r}
+# Names of sampling techniques
+samp_tech <- c("uniform sampling", "Algorithm \\ref{grid1}", "Algorithm \\ref{grid2}", "Algorithm \\ref{grid3}")
 ```
@@
 }
+```
+
+```{r}
+# List of sampling functions
+fun_tech <- c(sampling_unif, sampling_grid1, sampling_grid2, sampling_grid3)
 ```
@@
 # Number of MC iterations
-B1 <- 1000 # 5 # 
+B1 <- 5 # 1000 # 
 # Number of bootstrap replications
-B2 <- 400 # 5 # 
+B2 <- 5 # 400 # 
 ```
 
-# Example: Algorithm 6 with basic bootstrap
+# Example: Uniform sampling with basic bootstrap
 
 ```{r}
-fun_samp <- sampling_unif
+# The adequate function and its name
+k <- 1 # Uniform sampling
+fun_samp <- fun_tech[k][[1]]
+name_samp <- samp_tech[k]
 ```
@@
 # Table for comparison
-DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(round(rs_df, digits = 2), "%") )
+DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(format(round(rs_df, digits = 2), nsmall = 2), "%") )
 ```
@@
   kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
+  "\\hline"), caption = paste0("Approximation of Relative Stability of bootstrap variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
   kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
@@
   for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
-    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 2) ))))
+    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(format(round(TC_meth[param,1:3]*100, digits = 1), nsmall = 1), "%"), format(round(TC_meth[param,4], digits = 2), nsmall = 2) ))))
     k <- k+1
@@
 tab_ci1 <- df_total1 %>%
-  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (totals)")) %>%
+  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp, " (totals)")) %>%
   kable_styling(latex_options = "hold_position") %>%
@@
   for (TC_meth in list(TC_normal, TC_perc, TC_rev_perc, TC_bca)) {
-    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(round(TC_meth[param,1:3]*100, digits = 2), "%"), round(TC_meth[param,4], digits = 5) ))))
+    df_param <- rbind(df_param, as.data.frame(t(c(`Parameter of interest` = PARAM_names[param], Method = meth_nam[k], paste0(format(round(TC_meth[param,1:3]*100, digits = 1), nsmall = 1), "%"), format(round(TC_meth[param,4], digits = 5), nsmall = 5) ))))
     k <- k+1
@@
 # Table for comparison
-diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Monte Carlo Relative Bias` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, res1$Variances, VAR_df), digits = 2), "%") )
+diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Monte Carlo Relative Bias` = paste0(format(round(mapply(function(x,y){unlist(100*(y-x)/x)}, res1$Variances, VAR_df), digits = 2), nsmall = 2), "%") )
 ```
@@
   kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\addlinespace"), caption = paste0("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
+  "\\addlinespace"), caption = paste0("Approximation of Relative Bias of bootstrap variance when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
   kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 

### 2024-09-13 Results/All3_tab_unif.Rmd
Table label and names

@@
 output:
-  pdf_document: default
   html_document:
     df_print: paged
+  pdf_document: default
 date: "2024-08-16"
@@
 
-```{r}
+```{r Real_val}
 tab_real <- real_df %>%
@@
   kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\hline"), caption = paste0("Approximation of Relative Stability of bootstrap variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
+  "\\hline"), caption = paste0("Approximation of Relative Stability of bootstrap variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
   kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
@@
 tab_ci2 <- df_total2 %>%
-  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (ratios)")) %>%
+  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp, " (ratios)")) %>%
   kable_styling(latex_options = "hold_position") %>%
@@
   kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\addlinespace"), caption = paste0("Approximation of Relative Bias of bootstrap variance when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
+  "\\addlinespace"), caption = paste0("Approximation of Relative Bias of bootstrap variance when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case with ", name_samp), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
   kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 

### 2024-09-13 Results/All3_tab_algo6.Rmd
More complete files

@@
 ---
-title: "Monte Carlo and bootstrap for ALL parameters with tables"
+title: "Monte Carlo and bootstrap for all parameters with tables"
 output:
@@
 By comparing the two results, we may ensure the validity of the bootstrap strategy to find the estimation of the variances.
-We may also compare the coverage rates of each type of confidence interval.
+We may also compare the characteristics of each type of confidence interval.
 
-In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{algorithm 6}, and \textbf{three concentric circles} are used to compute local variables.
+In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{Algorithm 6}, and \textbf{three concentric circles} are used to compute local variables.
 
@@
 ```{r}
-fun_samp <- sampling_grid1
+# The adequate function and its name
+k <- 2 # Algorithm 6
+fun_samp <- fun_tech[k][[1]]
+name_samp <- samp_tech[k]
 ```
@@
 res1 <- MonteCarlo(n, B0, fun_samp)
-# Just one circle to begin with
 
@@
 res2 <- MC_boot(n, B1, B2, fun_samp)
-# Just one circle to begin with
 
@@
   kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
+  "\\hline"), caption = paste0("Approximation of Relative Stability of bootstrap variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
   kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
@@
   kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
-  "\\addlinespace"), caption = paste0("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
+  "\\addlinespace"), caption = paste0("Approximation of Relative Bias of bootstrap variance when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case with ", name_samp), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
   kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 

### 2024-09-13 Results/All3_tab_algo7.Rmd
More complete files

--- 2024-09-13 Results/All3_tab_algo6.Rmd
@@
 
-In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{Algorithm 6}, and \textbf{three concentric circles} are used to compute local variables.
+In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{Algorithm 7}, and \textbf{three concentric circles} are used to compute local variables.
 
@@
 
-# Example: Algorithm 6 with basic bootstrap
+# Example: Algorithm 7 with basic bootstrap
 
@@
 # The adequate function and its name
-k <- 2 # Algorithm 6
+k <- 3 # Algorithm 7
 fun_samp <- fun_tech[k][[1]]
@@
 
-```{r RS_algo6}
+```{r RS_algo7}
 tab_rs <- DF_rs %>%
@@
 
-```{r CI_tot_algo6}
+```{r CI_tot_algo7}
 tab_ci1 <- df_total1 %>%
@@
 
-```{r CI_ratio_algo6}
+```{r CI_ratio_algo7}
 tab_ci2 <- df_total2 %>%
@@
 
-```{r RB_algo6}
+```{r RB_algo7}
 tab_var <- diff_var %>%

### 2024-09-13 Results/All3_tab_algo8.Rmd
More complete files

--- 2024-09-13 Results/All3_tab_algo7.Rmd
@@
 
-In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{Algorithm 7}, and \textbf{three concentric circles} are used to compute local variables.
+In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{Algorithm 8}, and \textbf{three concentric circles} are used to compute local variables.
 
@@
 
-# Example: Algorithm 7 with basic bootstrap
+# Example: Algorithm 8 with basic bootstrap
 
@@
 # The adequate function and its name
-k <- 3 # Algorithm 7
+k <- 4 # Algorithm 8
 fun_samp <- fun_tech[k][[1]]
@@
 
-```{r RS_algo7}
+```{r RS_algo8}
 tab_rs <- DF_rs %>%
@@
 
-```{r CI_tot_algo7}
+```{r CI_tot_algo8}
 tab_ci1 <- df_total1 %>%
@@
 
-```{r CI_ratio_algo7}
+```{r CI_ratio_algo8}
 tab_ci2 <- df_total2 %>%
@@
 
-```{r RB_algo7}
+```{r RB_algo8}
 tab_var <- diff_var %>%

### 2024-09-13 Results/All3_tab_unif.Rmd
More complete files

@@
 By comparing the two results, we may ensure the validity of the bootstrap strategy to find the estimation of the variances.
-We may also compare the coverage rates of each type of confidence interval.
+We may also compare the characteristics of each type of confidence interval.
 

### 2024-09-13 Results/All3_tab_algo6_strat.Rmd
Cleaner strat files

--- 2024-09-13 Results/All3_tab_algo6.Rmd
@@
 
-\textbf{Basic bootstrap} is used.
+\textbf{Stratified bootstrap} is used.
 
@@
 
-# Example: Algorithm 6 with basic bootstrap
+# Example: Algorithm 6 with stratified bootstrap
 
@@
 
-res2 <- MC_boot(n, B1, B2, fun_samp)
+res2 <- MC_boot(n, B1, B2, fun_samp, strat = TRUE)
 
@@
 
-```{r RS_algo6}
+```{r RS_algo6_strat}
 tab_rs <- DF_rs %>%
@@
 
-```{r CI_tot_algo6}
+```{r CI_tot_algo6_strat}
 tab_ci1 <- df_total1 %>%
@@
 
-```{r CI_ratio_algo6}
+```{r CI_ratio_algo6_strat}
 tab_ci2 <- df_total2 %>%
@@
 
-```{r RB_algo6}
+```{r RB_algo6_strat}
 tab_var <- diff_var %>%

### 2024-09-13 Results/All3_tab_algo7_strat.Rmd
Cleaner strat files

--- 2024-09-13 Results/All3_tab_algo7.Rmd
@@
 
-```{r CI_tot_algo7}
+```{r CI_tot_algo7_strat}
 tab_ci1 <- df_total1 %>%
@@
 
-```{r CI_ratio_algo7}
+```{r CI_ratio_algo7_strat}
 tab_ci2 <- df_total2 %>%
@@
 
-```{r RB_algo7}
+```{r RB_algo7_strat}
 tab_var <- diff_var %>%

### 2024-09-13 Results/All3_tab_algo8_strat.Rmd
Cleaner strat files

@@
 By comparing the two results, we may ensure the validity of the bootstrap strategy to find the estimation of the variances.
-We may also compare the coverage rates of each type of confidence interval.
+We may also compare the characteristics of each type of confidence interval.
 
-In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{algorithm 8}, and \textbf{three concentric circles} are used to compute local variables.
+In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{Algorithm 8}, and \textbf{three concentric circles} are used to compute local variables.
 
@@
 ```{r}
-fun_samp <- sampling_grid3
+# The adequate function and its name
+k <- 4 # Algorithm 8
+fun_samp <- fun_tech[k][[1]]
+name_samp <- samp_tech[k]
 ```
@@
 res2 <- MC_boot(n, B1, B2, fun_samp, strat = TRUE)
-# Just one circle to begin with
 
